### 2012-09-17 paper.tex
initial commit

% mn2esample.tex
%
% v2.1 released 22nd May 2002 (G. Hutton)
%
% The mnsample.tex file has been amended to highlight
% the proper use of LaTeX2e code with the class file
% and using natbib cross-referencing. These changes
% do not reflect the original paper by A. V. Raveendran.
%
% Previous versions of this sample document were
% compatible with the LaTeX 2.09 style file mn.sty
% v1.2 released 5th September 1994 (M. Reed)
% v1.1 released 18th July 1994
% v1.0 released 28th January 1994

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{graphicx}

% If your system does not have the AMS fonts version 2.0 installed, then
% remove the useAMS option.
%
% useAMS allows you to obtain upright Greek characters.
% e.g. \umu, \upi etc.  See the section on "Upright Greek characters" in
% this guide for further information.
%
% If you are using AMS 2.0 fonts, bold math letters/symbols are available
% at a larger range of sizes for NFSS release 1 and 2 (using \boldmath or
% preferably \bmath).
%
% The usenatbib command allows the use of Patrick Daly's natbib.sty for
% cross-referencing.
%
% If you wish to typeset the paper in Times font (if you do not have the
% PostScript Type 1 Computer Modern fonts you will need to do this to get
% smoother fonts in a PDF file) then uncomment the next line
% \usepackage{Times}

%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title[Disc stuff]{Disc stuff}
\author[Tom  Douglas, Paola Caselli]{Tom Douglas$^{1}$\thanks{E-mail:
pytd@leeds.ac.uk}, Paola Caselli$^{1}$\\
$^{1}$School of Physics and Astronomy, University of Leeds, Leeds LS2 9JT, UK}
\begin{document}

\date{Accepted 1988 December 15. Received 1988 December 14; in original form 1988 October 11}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2002}

\maketitle

\label{firstpage}

\begin{abstract}
Abstract here
\end{abstract}

\begin{keywords}
circumstellar matter -- infrared: stars.
\end{keywords}

\section{Introduction}

1. description of what has been done so far on the modeling and radiative transfer of disks (this includes also more evolved disks -- Visser et al., Walsh et al., Aikawa et al. ..)
2. focus on the young disks (work done by Machida et al., Dapp, Basu \& Kunz 2012, .. for their formation; work by Boley et al. on the physical evolution ; Ilee et al. for chemistry) 
3. previous attempts to observe these young disks: (a) simulations (Cossins et al. 2010); (b) observations: Fuente et al. 2010 (AB Aur); Jorgensen \& van Dishoeck (H$_2^{18}$O and the HDO/H2O ratio); Pineda et al. (2012); other papers talking about "hot corinos" (Bottinelli et al. ....)

\section{Description of the Model}

-describe the envelope structure (pre-stellar core)
Keto \& Caselli model (2010), disc is embedded in an infalling pre-stellar core, with densities temperatures and velocities given by the model of the collapse of a 10 solar mass Bonnor-Ebert sphere and providing similar line profiles to the pre-stellar core L1544 as described by Keto \& Caselli (2010), truncated at 80$\,$au and extending out to 10,000$\,$au. The model is 1D spherically symetric model with inward motions (see figure).
For the models using a smoothed disc the same physical and chemical model is used but with the temperature, density and abundance averaged in $\phi$.

\begin{figure}
 \includegraphics[width=84mm]{Figures/model/L1544model_used.png}

 \caption{enevlope model}
\end{figure}

\begin{figure*}
 \includegraphics[width=168mm]{Figures/model/rhoT.png}

 \caption{this is a density \& temp plot}
\end{figure*}

\begin{figure*}
 \includegraphics[width=168mm]{Figures/model/velocity_rzSlice_thetaColourScale2.png}

 \caption{this is a velocity slice in the rz plane}
\end{figure*}

-describe the physical structure of the disk (density and temperature) -- one figure showing the physical structure and the kinematics (2-panels figure)
The physical strucure of the disc is the same as the one used in Ilee et al. (2011), based on the work of Boley(2007), Boley \& Durisen(2008) and Boley(2009). This model describes a 0.39$\,rm{M}_\odot$ self-gravitating disc featuring prominent spiral arms. Densities in the disc range from 10$^{10}$-10$^{21}\,\rm{m}^{-3}$, and temperatures range from 30-400 K. The model is sampled over a regular grid of size 256$\times$256$\times$64 with spatial resolution of 0.5$\,$au in x, y and z. The majority of the mass lies in the midplane of the disc.\newline

-describe the chemistry  - refer to Ilee et al. which have been taken as input to the rad transf (RT) code
Chemical abundances in the disc were taken from Ilee et. al (2011) which followed the changes of chemical abundances of trace particles moving through the disc as it evolved. The abundances of 125 speices related by 1334 reactions where followed through the time evoltion of the disc. These abundances ware interpolated onto a 51$^3$ grid covering the disc with cells of size 2.2$\times$2.2$\times$0.22$\,$au. Abundances in the envelope model were as follows:\newline

tableify ?
HCO$^+$: as the H2O profile from ??? scaled so that the maximum abundance is 10$^{-8}$
HNO: constant abundance of 5$\times$10${-11}$
HCS$^+$: 10$^{-11}$
OCS: constant abundance of 10$^{-9}$
H$_2$CO: 1.5$\times$10$^{-9}$ decreased by a factor of 40 at radii less than 8250au (Young et al 2004)
CS:  3$\times$10$^{-9}$ decreased by a factor of 10,000 at radii less than 6700au (Tafalla, santiago-garcia and myers 2006)
CO: as the H2O profile from ??? scaled so that the maximum abundance is CO maximum\newline

-describe the RT used (LIME) 
LIME, the radiative transfer program used, calculates line intensities based on a weighted sample of randomly chosen points in a continous 3d model. The method of selecting these points is given in the gridding section. At each of these points the density of the main collision partner (in this case H$_2$), gas and dust temperatures, velocity, molecular abundances and turbulent velocity and taken from the model. These points are then smoothed by Lloyds algorithm (Lloyd 1982) in order to minimise the vairiation in distance between points whilst keeping the same underlying distribution. These points are then connected by Delaunay triangulation and it is down these paths that photons are restricted to propagating. The levels of molecules in question are then  calculated at each of these points from collional and radiative (de)excitation and the local radiation field is calculated. This is repeated 20 times with the populations of each level converging towards a single value.
 Dust opacities used\newline

-how did you build the grid  (if this is too long it can go in an appendix)  - figure with the grid

\begin{figure}
 \includegraphics[width=84mm]{Figures/model/Lime_grid3.png}

 \caption{plot of the gridding overlaided on a smoothed density model}
\end{figure}
Grid points are selected at random in cylindrical co-ordinates, linearly spaced in z and $\phi$ and logarithmicly spaced in r. For each point to be selected a random number [0-1), $\alpha$ is generated as a threshold. After selection of random co-ordinates the Hydrogen density and molecular density at the point (n and m) are compaired against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$). If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use, if not then another r,$\phi$,z co-ordinte is selected. The weighting function and gridding functions were selected empiricly to sample both the all scales while ensuring the majority of the points went into the inner disc which is the region of interest.

fraction of points linear in xyz and unweighted (forces points into outmost regions)
fraction of points forced into the outer half in logarithmic spacing

\section{Model Results}

Figures showing the RT results in a few molecules/transitions (CO, HCO$^+$, HCN, OCS, H2CO, NH3 --- maybe H2O,H2$^{18}$O [to try first])  
Figure showing different inclinations  
Figure showing different transitions of the same molecule (e.g. CO(1-0), ...(7-6) , OCS,  H2CO ) for same inclination but in different disks (Boley et al. and the smooth disk)

\section{ALMA Predictions}

- current status (Cycle 1) - Figure
OCS + C18O + H2CO + HNO/CS/
- final status - Figure

\section{Conclusions}

stuff here
note that all speices show up in absorption and some show a little bit of emission around the edges of the disc
OCS is good for showing up spiral structure
enevelope only contaminates the central plusminus 500 m/s or so

\section*{Acknowledgments}

I thank Professor N. Kameswara Rao for some helpful suggestions,
Dr H. C. Bhatt for a critical reading of the original version of the
paper and an anonymous referee for very useful comments that improved
the presentation of the paper.

%\appendix
%
%\section[]{Large gaps in L\lowercase{y}${\balpha}$ forests\\* due to fluctuations in line %distribution}
%
%(This appendix was not part of the original paper by
%A.V.~Raveendran and is included here just for illustrative
%purposes. The references are not relevant to the text of the
%appendix, they are references from the bibliography used to
%illustrate text before and after citations.)
%
%Spectroscopic observations of bright quasars show that the mean
%number density of Ly$\alpha$ forest lines, which satisfy certain
%criteria, evolves like $\rmn{d}N/\rmn{d}z=A(1+z)^\gamma$, where
%$A$ and~$\gamma$ are two constants.  Given the above intrinsic
%line distribution we examine the probability of finding large gaps
%in the Ly$\alpha$ forests.  We concentrate here only on the
%statistics and neglect all observational complications such as the
%line blending effect \citep[see][for example]{b11}.
%
%Suppose we have observed a Ly$\alpha$ forest between redshifts $z_1$
%and~$z_2$ and found $N-1$ lines.  For high-redshift quasars $z_2$~is
%usually the emission redshift $z_{\rmn{em}}$ and $z_1$ is set to
%$(\lambda_{\rmn{Ly}\beta}/\lambda_{\rmn{Ly}\alpha})(1+z_{\rmn{em}})=0.844
%(1+z_{\rmn{em}})$ to avoid contamination by Ly$\beta$ lines.  We
%want to know whether the largest gaps observed in the forest are
%significantly inconsistent with the above line distribution.  To do
%this we introduce a new variable~$x$:
%%
%\begin{equation}
%x={(1+z)^{\gamma+1}-(1+z_1)^{\gamma+1} \over
%     (1+z_2)^{\gamma+1}-(1+z_1)^{\gamma+1}}.
%\end{equation}
%%
%$x$ varies from 0 to 1.  We then have $\rmn{d}N/\rmn{d}x=\lambda$, where $\lambda$
%is the mean number of lines between $z_1$ and $z_2$ and is given by
%%
%\begin{equation}
%\lambda\equiv{A[(1+z_2)^{\gamma+1}-(1+z_1)^{\gamma+1}]\over\gamma+1}.
%\end{equation}
%%
%This means that the Ly$\alpha$ forest lines are uniformly
%distributed in~$x$. The probability of finding $N-1$ lines between $z_1$
%and~$z_2$, $P_{N-1}$, is assumed to be the Poisson distribution.
%%
%\newpage
%%
%\begin{figure}
%\vspace{11pc}
%\caption{$P(>x_{\rmn{gap}})$ as a function of $x_{\rmn{gap}}$ for,
% from left to right, $N=160$, 150, 140, 110, 100, 90, 50, 45 and~40.
% Compare this with \protect\citet{b15}.}
%\label{appenfig}
%\end{figure}
%
%\subsection{Subsection title}
%
%We plot in Fig.~\ref{appenfig} $P(>x_{\rmn{gap}})$ for several $N$
%values. We see that, for $N=100$ and $x_{\rmn{gap}}=0.06$,
%$P(>0.06)\approx20$ per cent.  This means that the probability of
%finding a gap with a size larger than six times the mean
%separation is not significantly small. When the mean number of
%lines is large, $\lambda\sim N>>1$, our $P(>x_{\rmn{gap}})$
%approaches the result obtained by \citet[fig. 4]{b22} for small
%(but still very large if measured in units of the mean separation)
%$x_{\rmn{gap}}$, i.e., $P(>x_{\rmn{gap}})\sim N(1-
%x_{\rmn{gap}})^{N-1}\sim N {\rmn{exp}}(-\lambda x_{\rmn{gap}})$.
%
\bsp
%
\label{lastpage}
%
\end{document}

### 2012-09-21 paper.tex
added uniform run figs

@@
 \end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/model/lime_points_rz.png}
+
+ \caption{plot of the points selected in the model}
+\end{figure}
+
 Grid points are selected at random in cylindrical co-ordinates, linearly spaced in z and $\phi$ and logarithmicly spaced in r.
@@
 The weighting function and gridding functions were selected empiricly to sample both the all scales while ensuring the majority of the points went into the inner disc which is the region of interest.
-
-fraction of points linear in xyz and unweighted (forces points into outmost regions)
-fraction of points forced into the outer half in logarithmic spacing
+20\% of these points are forced to be at radii greater than $\sqrt{R_{min}R_{max}}$ (where $R_{min}$ and $R_{max}$ are the inner and outer radius of the model) in order to stop too many of the selecected points clustering in the high density disc and leaving the envelope undersampled.
+In addiation to this method of selection 5\% of the points are randomly distributed about the model with no bias with regards to density or abundance.
+This provides a minimum level of sampling for the large low density regions in the outer regions of the simulated volume.
 
@@
 
-stuff here
 note that all speices show up in absorption and some show a little bit of emission around the edges of the disc

### 2012-09-21 paper.tex
added some figs to paper

@@
 
- \caption{enevlope model}
+ \caption{enevlope model with temp and dust temp (red, green) in kelvin, log number density (blue) in cm$^{-1}$ and inward velocity$\times$100 (cyan) in m$\,$s$^{-1}$}
 \end{figure}
@@
 Densities in the disc range from 10$^{10}$-10$^{21}\,\rm{m}^{-3}$, and temperatures range from 30-400 K.
+The dust and gas temperatures in the disc are assumed to be equal.
+The gas/dust mass ratio was assumed to be 1/100 throughout the model and the opacities were given by the model of dust grains with thick icy mantles and 10$^6\,$yr coagulation from Ossenkopf and Henning (1994).
 The model is sampled over a regular grid of size 256$\times$256$\times$64 with spatial resolution of 0.5$\,$au in x, y and z.
@@
 This is repeated 20 times with the populations of each level converging towards a single value.
- Dust opacities used\newline
-
--how did you build the grid  (if this is too long it can go in an appendix)  - figure with the grid
+\newline
 
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/model/lime_points_rz.png}
+ \includegraphics[width=84mm]{Figures/model/lime_points_rz2.png}
 
@@
 
+In order to construct the grid, points are randomly selected from the volume being simulated then compaired against a reference point.
 Grid points are selected at random in cylindrical co-ordinates, linearly spaced in z and $\phi$ and logarithmicly spaced in r.
-For each point to be selected a random number [0-1), $\alpha$ is generated as a threshold.
+For each point to be selected a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) as a threshold.
 After selection of random co-ordinates the Hydrogen density and molecular density at the point (n and m) are compaired against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$).
@@
 20\% of these points are forced to be at radii greater than $\sqrt{R_{min}R_{max}}$ (where $R_{min}$ and $R_{max}$ are the inner and outer radius of the model) in order to stop too many of the selecected points clustering in the high density disc and leaving the envelope undersampled.
-In addiation to this method of selection 5\% of the points are randomly distributed about the model with no bias with regards to density or abundance.
-This provides a minimum level of sampling for the large low density regions in the outer regions of the simulated volume.
+In addiation to this method of selection 5\% of the points are lineraly distributed in x, y and z with no bias with regards to density or abundance.
+This provides a minimum level of sampling for the large low density regions in the outer parts of the simulated volume.
+See figure 5 for example of the points distribution in r, z.
 
@@
 
-Figures showing the RT results in a few molecules/transitions (CO, HCO$^+$, HCN, OCS, H2CO, NH3 --- maybe H2O,H2$^{18}$O [to try first])  
+Figures showing the RT results in a few molecules/transitions (CO, HCO$^+$, HCN, OCS, H2CO, NH3 --- maybe H2O,H2$^{18}$O [to try first]) (Note the moment 1 and 0 map were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in the some PV diagrams as the strong absorption feature at all positions around zero velocity, mom1maps are shown with a cutoff of 1/1000 of the peak emission/apsorption value)
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_contSub.png}
+
+ \caption{CO 3-2 Continuum subtracted mom0}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_mom1.png}
+
+ \caption{CO 3-2 mom1map}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_PV_centre.png}
+
+ \caption{CO 3-2 PV through centre}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageOCS_28-27_30deg_contSub.png}
+
+ \caption{OCS 28-27 Continuum subtracted mom0}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageOCS_28-27_30deg_mom1.png}
+
+ \caption{OCS 28-27 mom1map}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageOCS_28-27_30deg_PV_centre.png}
+
+ \caption{OCS 28-27 PV through centre}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageH2CO_4-0-4->3-0-3_30deg_contSub.png}
+
+ \caption{H$_2$CO 4$\,$0$\,$4 - 3$\,$0$\,$3 Continuum subtracted mom0}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageH2CO_4-0-4->3-0-3_30deg_mom1.png}
+
+ \caption{H$_2$CO 4$\,$0$\,$4 - 3$\,$0$\,$3 mom1map}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageH2CO_4-0-4->3-0-3_30deg_PV_centre.png}
+
+ \caption{H$_2$CO 4$\,$0$\,$4 - 3$\,$0$\,$3 PV through centre}
+\end{figure}
+
 Figure showing different inclinations  
@@
 note that all speices show up in absorption and some show a little bit of emission around the edges of the disc
-OCS is good for showing up spiral structure
+OCS is good for showing up spiral structure without being able to resolve it.
 enevelope only contaminates the central plusminus 500 m/s or so

### 2012-09-27 paper.tex
Figures

@@
 
- \caption{enevlope model with temp and dust temp (red, green) in kelvin, log number density (blue) in cm$^{-1}$ and inward velocity$\times$100 (cyan) in m$\,$s$^{-1}$}
+ \caption{enevlope model with temp and dust temp (red, green) in kelvin, log number density (blue) in cm$^{-3}$ and inward velocity$\times$100 (cyan) in m$\,$s$^{-1}$}
 \end{figure}
@@
 al (2011) which followed the changes of chemical abundances of trace particles moving through the disc as it evolved.
-The abundances of 125 speices related by 1334 reactions where followed through the time evoltion of the disc.
-These abundances ware interpolated onto a 51$^3$ grid covering the disc with cells of size 2.2$\times$2.2$\times$0.22$\,$au.
+The abundances of 125 speices related by 1334 reactions were followed through the time evoltion of the disc.
+These abundances were interpolated onto a 51$^3$ grid covering the disc with cells of size 2.2$\times$2.2$\times$0.22$\,$au.
 Abundances in the envelope model were as follows:\newline
 
-tableify ?
-HCO$^+$: as the H2O profile from ??? scaled so that the maximum abundance is 10$^{-8}$
-HNO: constant abundance of 5$\times$10${-11}$
-HCS$^+$: 10$^{-11}$
-OCS: constant abundance of 10$^{-9}$
-H$_2$CO: 1.5$\times$10$^{-9}$ decreased by a factor of 40 at radii less than 8250au (Young et al 2004)
-CS:  3$\times$10$^{-9}$ decreased by a factor of 10,000 at radii less than 6700au (Tafalla, santiago-garcia and myers 2006)
-CO: as the H2O profile from ??? scaled so that the maximum abundance is CO maximum\newline
+(tableify this?)\newline
+HCO$^+$: as the H2O profile from (find out where L1544 H2O profile is from) scaled so that the maximum abundance is 10$^{-8}$\newline
+HNO: constant abundance of 5$\times$10${-11}$\newline
+HCS$^+$: 10$^{-11}$\newline
+OCS: constant abundance of 10$^{-9}$\newline
+H$_2$CO: 1.5$\times$10$^{-9}$ decreased by a factor of 40 at radii less than 8250au (Young et al 2004)\newline
+CS:  3$\times$10$^{-9}$ decreased by a factor of 10,000 at radii less than 6700au (Tafalla, santiago-garcia and myers 2006)\newline
+CO: as the H2O profile from ??? scaled so that the maximum abundance is CO maximum\newline\
 
 -describe the RT used (LIME) 
-LIME, the radiative transfer program used, calculates line intensities based on a weighted sample of randomly chosen points in a continous 3d model.
+LIME (Brinch 2011), the radiative transfer program used, calculates line intensities based on a weighted sample of randomly chosen points in a continous 3d model.
 The method of selecting these points is given in the gridding section.
@@
 20\% of these points are forced to be at radii greater than $\sqrt{R_{min}R_{max}}$ (where $R_{min}$ and $R_{max}$ are the inner and outer radius of the model) in order to stop too many of the selecected points clustering in the high density disc and leaving the envelope undersampled.
-In addiation to this method of selection 5\% of the points are lineraly distributed in x, y and z with no bias with regards to density or abundance.
+In addiation to this method of selection 5\% of the points are linearly distributed in x, y and z with no bias with regards to density or abundance.
 This provides a minimum level of sampling for the large low density regions in the outer parts of the simulated volume.
@@
 Figures showing the RT results in a few molecules/transitions (CO, HCO$^+$, HCN, OCS, H2CO, NH3 --- maybe H2O,H2$^{18}$O [to try first]) (Note the moment 1 and 0 map were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in the some PV diagrams as the strong absorption feature at all positions around zero velocity, mom1maps are shown with a cutoff of 1/1000 of the peak emission/apsorption value)
+
 \begin{figure}
@@
 
+These syntetic images of the CO 3-2 line at 345.8$\,$GHz.
+As the upper level for this line is at 33$\,$K above the ground state this transition should be excited through out disc.
+CO line will be thick so this is only mapping the outer regions of the disc.
+Spiral structure can be seen
+
 \begin{figure}
@@
  \caption{OCS 28-27 PV through centre}
+\end{figure}
+
+The OCS lines in alma band 7 (22-21 through 30-29) with upper energy levels between 161 and 271 K above the ground state provide a way to trace hot shocked gas in spiral arms without resolving structure.
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imagesmoothedOCS_28-27_30deg_contSub.png}
+
+ \caption{SmoothedOCS 28-27 Continuum subtracted mom0}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imagesmoothedOCS_28-27_30deg_mom1.png}
+
+ \caption{SmoothedOCS 28-27 mom1map}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imagesmoothedOCS_28-27_30deg_PV_centre.png}
+
+In comparison to the model with spiral arms the absorbtion and emission from this smoothed model is far weaker.
+
+gdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfd gfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdf gfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsg fsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfds
+
+ \caption{SmoothedOCS 28-27 PV through centre}
 \end{figure}
@@
 
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageHCOp_1-0_30deg_contSub.png}
+
+ \caption{HCO$^+$ 1-0 Continuum subtracted mom0}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageHCOp_1-0_30deg_mom1.png}
+
+ \caption{HCO$^+$ 1-0 mom1map}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageHCOp_1-0_30deg_PV_centre.png}
+
+ \caption{HCO$^+$ 1-0 PV through centre}
+\end{figure}
+
+gdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsg fsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfd gdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgf sgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfd gdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfdsgdfsgfdsgfds
+
 Figure showing different inclinations
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_contSub.png}
+
+ \caption{C18O 3-2 15 deg Continuum subtracted mom0}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_mom1.png}
+
+ \caption{C18O 3-2 15 deg mom1map}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_PV_centre.png}
+
+ \caption{C18O 3-2 PV 15 deg through centre}
+\end{figure}
+
+15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg 15 deg
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_contSub.png}
+
+ \caption{C18O 3-2  30 deg Continuum subtracted mom0}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_mom1.png}
+
+ \caption{C18O 3-2 30 deg mom1map}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_PV_centre.png}
+
+ \caption{C18O 3-2 30 deg PV through centre}
+\end{figure}
+
+30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg 30 deg
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_contSub.png}
+
+ \caption{C18O 3-2 45 deg Continuum subtracted mom0}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_mom1.png}
+
+ \caption{C18O 3-2 45 deg mom1map}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_PV_centre.png}
+
+ \caption{C18O 3-2 45 deg PV through centre}
+\end{figure}
+
+45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg 45 deg
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_contSub.png}
+
+ \caption{C18O 3-2 60 deg Continuum subtracted mom0}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_mom1.png}
+
+ \caption{C18O 3-2 60 deg mom1map}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_PV_centre.png}
+
+ \caption{C18O 3-2 60 deg PV through centre}
+\end{figure}
+
+60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg 60 deg
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_contSub.png}
+
+ \caption{C18O 3-2 75 deg Continuum subtracted mom0}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_mom1.png}
+
+ \caption{C18O 3-2 75 deg mom1map}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_PV_centre.png}
+
+ \caption{C18O 3-2 75 deg PV through centre}
+\end{figure}
+
+75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg 75 deg
+
 Figure showing different transitions of the same molecule (e.g. CO(1-0), ...(7-6) , OCS,  H2CO ) for same inclination but in different disks (Boley et al. and the smooth disk)

### 2012-10-10 paper.tex
stuff

--- 2012-09-21 paper.tex
@@
 \title[Disc stuff]{Disc stuff}
-\author[Tom  Douglas, Paola Caselli]{Tom Douglas$^{1}$\thanks{E-mail:
+\author[Tom  Douglas, Paola Caselli, Et al.]{Tom Douglas$^{1}$\thanks{E-mail:
 pytd@leeds.ac.uk}, Paola Caselli$^{1}$\\
@@
 
-\date{Accepted 1988 December 15. Received 1988 December 14; in original form 1988 October 11}
+\date{In original form 2012}
 
@@
 
-1. description of what has been done so far on the modeling and radiative transfer of disks (this includes also more evolved disks -- Visser et al., Walsh et al., Aikawa et al. ..)
+1. description of what has been done so far on the modelling and radiative transfer of disks (this includes also more evolved disks -- Visser et al., Walsh et al., Aikawa et al. ..)
 2. focus on the young disks (work done by Machida et al., Dapp, Basu \& Kunz 2012, .. for their formation; work by Boley et al. on the physical evolution ; Ilee et al. for chemistry) 
@@
 
--describe the envelope structure (pre-stellar core)
-Keto \& Caselli model (2010), disc is embedded in an infalling pre-stellar core, with densities temperatures and velocities given by the model of the collapse of a 10 solar mass Bonnor-Ebert sphere and providing similar line profiles to the pre-stellar core L1544 as described by Keto \& Caselli (2010), truncated at 80$\,$au and extending out to 10,000$\,$au.
-The model is 1D spherically symetric model with inward motions (see figure).
-For the models using a smoothed disc the same physical and chemical model is used but with the temperature, density and abundance averaged in $\phi$.
+The model used to simulate the emission from a young protoplantary disc is a hybrid model created from hydrodynamical models of an infalling prestellar core and a gravitationally unstable protoplanetary disc.
+The prestellar core model is based upon the model of Keto \& Caselli (2010).
+This describes an infalling pre-stellar core, with densities temperatures and velocities given by the model of the collapse of a 10 solar mass Bonnor-Ebert sphere and provides a match to line profiles seen in the pre-stellar core L1544.
+Some slight modification due to the addition of Oxygen lines (Keto et al 2012 in prep) have been been added to this model resulting in a slight decrease in the peak infall velocity.
+This prestellar core model extends from 80$\,$au out to 10,000$\,$AU.
+The model is a 1D spherically symmetric model with inward motions (see figure \ref{l1544model}).
 
@@
  \includegraphics[width=84mm]{Figures/model/L1544model_used.png}
-
- \caption{enevlope model with temp and dust temp (red, green) in kelvin, log number density (blue) in cm$^{-1}$ and inward velocity$\times$100 (cyan) in m$\,$s$^{-1}$}
+ \label{l1544model}
+ \caption{envelope model showing temp and dust temp (red, green) in kelvin, log number density (blue) in cm$^{-3}$ and inward velocity$\times$10 (cyan) in m$\,$s$^{-1}$, adapted from Keto \& Caselli (2010)}
 \end{figure}
@@
  \includegraphics[width=168mm]{Figures/model/rhoT.png}
-
- \caption{this is a density \& temp plot}
+ \label{discModel}
+ \caption{The density and temperatures of the 0.4$\,\rm{M}_\odot$ gravitationally unstable disc model used in inside 80$\,$AU.
+The dense and hot regions are confinded to a few AU about the rotation plane.}
 \end{figure*}
@@
  \includegraphics[width=168mm]{Figures/model/velocity_rzSlice_thetaColourScale2.png}
-
- \caption{this is a velocity slice in the rz plane}
+ \label{discVel}
+ \caption{The line of sight (colour scale) and plane of sky (arrows) velocities in the y=0 slice through the disc model.}
 \end{figure*}
 
--describe the physical structure of the disk (density and temperature) -- one figure showing the physical structure and the kinematics (2-panels figure)
-The physical strucure of the disc is the same as the one used in Ilee et al.
-(2011), based on the work of Boley(2007), Boley \& Durisen(2008) and Boley(2009).
-This model describes a 0.39$\,rm{M}_\odot$ self-gravitating disc featuring prominent spiral arms.
-Densities in the disc range from 10$^{10}$-10$^{21}\,\rm{m}^{-3}$, and temperatures range from 30-400 K.
-The dust and gas temperatures in the disc are assumed to be equal.
-The gas/dust mass ratio was assumed to be 1/100 throughout the model and the opacities were given by the model of dust grains with thick icy mantles and 10$^6\,$yr coagulation from Ossenkopf and Henning (1994).
+At radii less than 80$\,$au the physical structure is the given by the hydrodynamic model described in Ilee et al.
+(2011), based on the work of Boley(2007), and Boley(2009).
+This model describes a 0.39$\,\rm{M}_\odot$ self-gravitating disc featuring prominent spiral arms.
+H$_2$ number densities in the disc range from 10$^{10}$-10$^{19}\,\rm{m}^{-3}$, and temperatures range from 30-400 K.
+The dust and gas temperatures in the disc are assumed to be in equilibrium.
 The model is sampled over a regular grid of size 256$\times$256$\times$64 with spatial resolution of 0.5$\,$au in x, y and z.
-The majority of the mass lies in the midplane of the disc.\newline
+The majority of the mass lies in the mid-plane of the disc.
+For the models using a smoothed disc the same physical and chemical model is used but with the temperature, density and abundance averaged in $\phi$.
+The gas/dust mass ratio was assumed to be 1/100 throughout both sections model and the opacities were given by the model of dust grains with thick icy mantles and 10$^6\,$yr coagulation from Ossenkopf and Henning (1994)\newline
 
--describe the chemistry  - refer to Ilee et al. which have been taken as input to the rad transf (RT) code
 Chemical abundances in the disc were taken from Ilee et.
 al (2011) which followed the changes of chemical abundances of trace particles moving through the disc as it evolved.
-The abundances of 125 speices related by 1334 reactions where followed through the time evoltion of the disc.
-These abundances ware interpolated onto a 51$^3$ grid covering the disc with cells of size 2.2$\times$2.2$\times$0.22$\,$au.
+The abundances of 125 species related by 1334 reactions were followed through the time evolution of the disc.
+These abundances were interpolated onto a 51$^3$ grid covering the disc with cells of size 2.2$\times$2.2$\times$0.22$\,$au.
 Abundances in the envelope model were as follows:\newline
 
-tableify ?
-HCO$^+$: as the H2O profile from ??? scaled so that the maximum abundance is 10$^{-8}$
-HNO: constant abundance of 5$\times$10${-11}$
-HCS$^+$: 10$^{-11}$
-OCS: constant abundance of 10$^{-9}$
-H$_2$CO: 1.5$\times$10$^{-9}$ decreased by a factor of 40 at radii less than 8250au (Young et al 2004)
-CS:  3$\times$10$^{-9}$ decreased by a factor of 10,000 at radii less than 6700au (Tafalla, santiago-garcia and myers 2006)
-CO: as the H2O profile from ??? scaled so that the maximum abundance is CO maximum\newline
+(tableify this?)\newline
+HCO$^+$: as the H2O profile from (find out where L1544 H2O profile is from) scaled so that the maximum abundance is 10$^{-8}$\newline
+HNO: constant abundance of 5$\times$10${-11}$\newline
+HCS$^+$: 10$^{-11}$\newline
+OCS: constant abundance of 10$^{-9}$\newline
+H$_2$CO: 1.5$\times$10$^{-9}$ decreased by a factor of 40 at radii less than 8250au (Young et al 2004)\newline
+CS:  3$\times$10$^{-9}$ decreased by a factor of 10,000 at radii less than 6700au (Tafalla, santiago-garcia and myers 2006)\newline
+CO: as the H2O profile from before scaled so that the maximum abundance is CO maximum\newline
 
--describe the RT used (LIME) 
-LIME, the radiative transfer program used, calculates line intensities based on a weighted sample of randomly chosen points in a continous 3d model.
-The method of selecting these points is given in the gridding section.
+\section{description of radiative transfer program}
+LIME (Brinch 2011), the radiative transfer program used, calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3d model.
+The method of selecting these points is given in the griding section.
 At each of these points the density of the main collision partner (in this case H$_2$), gas and dust temperatures, velocity, molecular abundances and turbulent velocity and taken from the model.
-These points are then smoothed by Lloyds algorithm (Lloyd 1982) in order to minimise the vairiation in distance between points whilst keeping the same underlying distribution.
-These points are then connected by Delaunay triangulation and it is down these paths that photons are restricted to propagating.
-The levels of molecules in question are then  calculated at each of these points from collional and radiative (de)excitation and the local radiation field is calculated.
-This is repeated 20 times with the populations of each level converging towards a single value.
-\newline
+These points are then smoothed by Lloyds algorithm (Lloyd 1982) in order to minimise the variation in distance between points whilst keeping the same underlying distribution.
+These points are then connected by Delaunay triangulation and it is down these paths that photons are restricted to propagating (figures \ref{grid}).
+The levels of molecules in question are then  calculated at each of these points from collisional and radiative (de)excitation and the local radiation field is calculated.
+This is repeated 20 times with the populations of each level converging towards a single value.\newline
 
@@
  \includegraphics[width=84mm]{Figures/model/Lime_grid3.png}
-
- \caption{plot of the gridding overlaided on a smoothed density model}
+ \label{grid}
+ \caption{An example of the points distribution chosen by lime for a model of a smooth protoplanetary disc.
+The nodes of the grid are the points at which the underlying physical model is sampled and the edges are teh paths down which photons can travel during the excitation-radiation emission stage of the computation.}
 \end{figure}
@@
  \includegraphics[width=84mm]{Figures/model/lime_points_rz2.png}
-
- \caption{plot of the points selected in the model}
+ \label{points}
+ \caption{the rz distribution of points selected to sample the model.
+The points in the dense region at 10$^9<\rm{z}<10^12$ and 7*10$^{11}<\rm{r}<10^{13}$ are sampling the disc model and the points at larger values are those foreced into the outer regions to sample the envelople.}
 \end{figure}
 
-In order to construct the grid, points are randomly selected from the volume being simulated then compaired against a reference point.
-Grid points are selected at random in cylindrical co-ordinates, linearly spaced in z and $\phi$ and logarithmicly spaced in r.
+In order to construct the grid, points are randomly selected from the volume being simulated then compared against a reference point.
+Grid points are selected at random in cylindrical co-ordinates, linearly spaced in z and $\phi$ and logarithmically spaced in r.
 For each point to be selected a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) as a threshold.
-After selection of random co-ordinates the Hydrogen density and molecular density at the point (n and m) are compaired against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$).
-If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use, if not then another r,$\phi$,z co-ordinte is selected.
-The weighting function and gridding functions were selected empiricly to sample both the all scales while ensuring the majority of the points went into the inner disc which is the region of interest.
+After selection of random co-ordinates the Hydrogen density and molecular density at the point (n and m) are compared against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$).
+If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use, if not then another r, $\phi$, z co-ordinate is selected.
+The weighting function and griding functions were selected empirically to sample both the all scales while ensuring the majority of the points went into the inner disc which is the region of interest.
 20\% of these points are forced to be at radii greater than $\sqrt{R_{min}R_{max}}$ (where $R_{min}$ and $R_{max}$ are the inner and outer radius of the model) in order to stop too many of the selecected points clustering in the high density disc and leaving the envelope undersampled.
-In addiation to this method of selection 5\% of the points are lineraly distributed in x, y and z with no bias with regards to density or abundance.
+In addiation to this method of selection 5\% of the points are linearly distributed in x, y and z with no bias with regards to density or abundance.
 This provides a minimum level of sampling for the large low density regions in the outer parts of the simulated volume.
-See figure 5 for example of the points distribution in r, z.
+See figure \ref{points} for example of the points distribution in r, z.
+\newline
 
@@
 
-Figures showing the RT results in a few molecules/transitions (CO, HCO$^+$, HCN, OCS, H2CO, NH3 --- maybe H2O,H2$^{18}$O [to try first]) (Note the moment 1 and 0 map were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in the some PV diagrams as the strong absorption feature at all positions around zero velocity, mom1maps are shown with a cutoff of 1/1000 of the peak emission/apsorption value)
+Continuum emission from the model.
+Able to do this as the majority of the computing time on the model is taken up with calculating molecule population levels.
+This image has been created by averaging the output images of 100 unique runs.
+This averaging mitigates the granularity of output images from lime due to the nature of the gridding.
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/continuum.png}
+
+ \caption{A composite image of 100 runs of continuum emission at 350$\,$GHz}
+\end{figure}
+
+Figures showing the RT results in a few molecules/transitions (CO, HCO$^+$, HCN, OCS, H2CO, NH3 --- maybe H2O,H2$^{18}$O [to try first]) (Note the moment 1 and 0 map were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in the some PV diagrams as the strong absorption feature at all positions around zero velocity, mom1maps are shown with a cutoff of 1/1000 of the peak emission/absorption value)\newline
+
 \begin{figure}
@@
 
+These synthetic images of the CO 3-2 line at 345.8$\,$GHz.
+As the upper level for this line is at 33$\,$K above the ground state this transition should be excited through out disc.
+CO line will be thick so this is only mapping the outer regions of the disc.
+Spiral structure can be seen.\newline
+
 \begin{figure}
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageOCS_28-27_30deg_mom1.png}
-
- \caption{OCS 28-27 mom1map}
-\end{figure}
-
-\begin{figure}
  \includegraphics[width=84mm]{Figures/sim/imageOCS_28-27_30deg_PV_centre.png}
@@
 \end{figure}
+
+The OCS lines in alma band 7 (22-21 through 30-29) with upper energy levels between 161 and 271 K above the ground state provide a way to trace hot shocked gas in spiral arms without resolving structure.\newline
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imagesmoothedOCS_28-27_30deg_contSub.png}
+
+ \caption{SmoothedOCS 28-27 Continuum subtracted mom0}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imagesmoothedOCS_28-27_30deg_PV_centre.png}
+
+ \caption{SmoothedOCS 28-27 PV through centre}
+\end{figure}
+
+In comparison to the model with spiral arms the absorbtion and emission from this smoothed model is far weaker.\newline
 
@@
 
- \caption{H$_2$CO 4$\,$0$\,$4 - 3$\,$0$\,$3 mom1map}
+ \caption{H$_2$CO 4$\,$0$\,$4 - 3$\,$0$\,$3 PV through centre}
 \end{figure}
@@
 
-Figure showing different inclinations  
-Figure showing different transitions of the same molecule (e.g. CO(1-0), ...(7-6) , OCS,  H2CO ) for same inclination but in different disks (Boley et al. and the smooth disk)
+line ratios of many lined spieces can help us calculate temperatures of the emitting regions.
+
+(figure of temperature as a function of line ratio for 2 sets of formaldehyde lines and map of derived temperature, talk to P about this)\newline
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageHCOp_1-0_30deg_contSub.png}
+
+ \caption{HCO$^+$ 1-0 Continuum subtracted mom0}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageHCOp_1-0_30deg_mom1.png}
+
+ \caption{HCO$^+$ 1-0 mom1map}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageHCOp_1-0_30deg_PV_centre.png}
+
+ \caption{HCO$^+$ 1-0 PV through centre}
+\end{figure}
+
+some molecules such as HCO$^+$ trace only the inner disc (ref ilee 2011) and so can be used to look at the extended velocity and physical structure.\newline
+
+Figures showing different inclinations  
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_contSub.png}
+
+ \caption{C18O 3-2 15 deg Continuum subtracted mom0}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_mom1.png}
+
+ \caption{C18O 3-2 15 deg mom1map}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_PV_centre.png}
+
+ \caption{C18O 3-2 PV 15 deg through centre}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_contSub.png}
+
+ \caption{C18O 3-2  30 deg Continuum subtracted mom0}
+\end{figure}
+
+fdagfdabfdsbfdbds fdbfd  fdfbfvdfd g rbfd fdbfdbc \newline fdagfdabfdsbfdbds fdbfd  fdfbfvdfd g rbfd fdbfdbc \newline fdagfdabfdsbfdbds fdbfd  fdfbfvdfd g rbfd fdbfdbc \newline fdagfdabfdsbfdbds fdbfd  fdfbfvdfd g rbfd fdbfdbc \newline fdagfdabfdsbfdbds fdbfd  fdfbfvdfd g rbfd fdbfdbc \newline fdagfdabfdsbfdbds fdbfd  fdfbfvdfd g rbfd fdbfdbc \newline
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_mom1.png}
+
+ \caption{C18O 3-2 30 deg mom1map}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_PV_centre.png}
+
+ \caption{C18O 3-2 30 deg PV through centre}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_contSub.png}
+
+ \caption{C18O 3-2 45 deg Continuum subtracted mom0}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_mom1.png}
+
+ \caption{C18O 3-2 45 deg mom1map}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_PV_centre.png}
+
+ \caption{C18O 3-2 45 deg PV through centre}
+\end{figure}
+
+nfsdankjdsankj vdjsk nvjdks nvkds jkkd jkvd jkvf djk fj\newline nfsdankjdsankj vdjsk nvjdks nvkds jkkd jkvd jkvf djk fj\newline nfsdankjdsankj vdjsk nvjdks nvkds jkkd jkvd jkvf djk fj\newline nfsdankjdsankj vdjsk nvjdks nvkds jkkd jkvd jkvf djk fj\newline nfsdankjdsankj vdjsk nvjdks nvkds jkkd jkvd jkvf djk fj\newline nfsdankjdsankj vdjsk nvjdks nvkds jkkd jkvd jkvf djk fj\newline nfsdankjdsankj vdjsk nvjdks nvkds jkkd jkvd jkvf djk fj\newline
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_contSub.png}
+
+ \caption{C18O 3-2 60 deg Continuum subtracted mom0}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_mom1.png}
+
+ \caption{C18O 3-2 60 deg mom1map}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_PV_centre.png}
+
+ \caption{C18O 3-2 60 deg PV through centre}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_contSub.png}
+
+ \caption{C18O 3-2 75 deg Continuum subtracted mom0}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_mom1.png}
+
+ \caption{C18O 3-2 75 deg mom1map}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_PV_centre.png}
+
+ \caption{C18O 3-2 75 deg PV through centre}
+\end{figure}
+
+Figure showing different transitions of the same molecule (e.g. CO(1-0), ...(7-6) , OCS,  H2CO ) for same inclination but in different disks (Boley et al. and the smooth disk)\newline
 
@@
 
-note that all speices show up in absorption and some show a little bit of emission around the edges of the disc
+note that all species show up in absorption and some show a little bit of emission around the edges of the disc
 OCS is good for showing up spiral structure without being able to resolve it.
-enevelope only contaminates the central plusminus 500 m/s or so
+envelope only contaminates the central plus-minus 500 m/s or so
 
-\section*{Acknowledgments}
+\section*{Acknowledgements}
 

### 2012-10-23 paper.tex
Revert "stuff"
This reverts commit 1670e6e4081bbc62f0d8bab3b33c2d541a565556.

@@
 
-The model used to simulate the emission from a young protoplantary disc is a hybrid model created from hydrodynamical models of an infalling prestellar core and a gravitationally unstable protoplanetary disc.
-The prestellar core model is based upon the model of Keto \& Caselli (2010).
-This describes an infalling pre-stellar core, with densities temperatures and velocities given by the model of the collapse of a 10 solar mass Bonnor-Ebert sphere and provides a match to line profiles seen in the pre-stellar core L1544.
-Some slight modification due to the addition of Oxygen lines (Keto et al 2012 in prep) have been been added to this model resulting in a slight decrease in the peak infall velocity.
-This prestellar core model extends from 80$\,$au out to 10,000$\,$AU.
-The model is a 1D spherically symmetric model with inward motions (see figure \ref{l1544model}).
+-describe the envelope structure (pre-stellar core)
+Keto \& Caselli model (2010), disc is embedded in an infalling pre-stellar core, with densities temperatures and velocities given by the model of the collapse of a 10 solar mass Bonnor-Ebert sphere and providing similar line profiles to the pre-stellar core L1544 as described by Keto \& Caselli (2010), with some slight modification due to the addition of Oxygen lines (keto et al 2012 in prep).
+This prestellar core model extends from 80$\,$au out to 10,000$\,$au.
+The model is 1D spherically symmetric model with inward motions (see figure).
 
@@
  \includegraphics[width=84mm]{Figures/model/L1544model_used.png}
- \label{l1544model}
- \caption{envelope model showing temp and dust temp (red, green) in kelvin, log number density (blue) in cm$^{-3}$ and inward velocity$\times$10 (cyan) in m$\,$s$^{-1}$, adapted from Keto \& Caselli (2010)}
+
+ \caption{envelope model with temp and dust temp (red, green) in kelvin, log number density (blue) in cm$^{-3}$ and inward velocity$\times$100 (cyan) in m$\,$s$^{-1}$}
 \end{figure}
@@
  \includegraphics[width=168mm]{Figures/model/rhoT.png}
- \label{discModel}
- \caption{The density and temperatures of the 0.4$\,\rm{M}_\odot$ gravitationally unstable disc model used in inside 80$\,$AU.
-The dense and hot regions are confinded to a few AU about the rotation plane.}
+
+ \caption{this is a density \& temp plot}
 \end{figure*}
@@
  \includegraphics[width=168mm]{Figures/model/velocity_rzSlice_thetaColourScale2.png}
- \label{discVel}
- \caption{The line of sight (colour scale) and plane of sky (arrows) velocities in the y=0 slice through the disc model.}
+
+ \caption{this is a velocity slice in the rz plane}
 \end{figure*}
 
-At radii less than 80$\,$au the physical structure is the given by the hydrodynamic model described in Ilee et al.
-(2011), based on the work of Boley(2007), and Boley(2009).
+-describe the physical structure of the disk (density and temperature) -- one figure showing the physical structure and the kinematics (2-panels figure)
+The physical structure of the disc is the same as the one used in Ilee et al.
+(2011), based on the work of Boley(2007), Boley \& Durisen(2008) and Boley(2009).
 This model describes a 0.39$\,\rm{M}_\odot$ self-gravitating disc featuring prominent spiral arms.
-H$_2$ number densities in the disc range from 10$^{10}$-10$^{19}\,\rm{m}^{-3}$, and temperatures range from 30-400 K.
-The dust and gas temperatures in the disc are assumed to be in equilibrium.
+Densities in the disc range from 10$^{10}$-10$^{21}\,\rm{m}^{-3}$, and temperatures range from 30-400 K.
+The dust and gas temperatures in the disc are assumed to be equal.
+The gas/dust mass ratio was assumed to be 1/100 throughout the model and the opacities were given by the model of dust grains with thick icy mantles and 10$^6\,$yr coagulation from Ossenkopf and Henning (1994).
 The model is sampled over a regular grid of size 256$\times$256$\times$64 with spatial resolution of 0.5$\,$au in x, y and z.
 The majority of the mass lies in the mid-plane of the disc.
-For the models using a smoothed disc the same physical and chemical model is used but with the temperature, density and abundance averaged in $\phi$.
-The gas/dust mass ratio was assumed to be 1/100 throughout both sections model and the opacities were given by the model of dust grains with thick icy mantles and 10$^6\,$yr coagulation from Ossenkopf and Henning (1994)\newline
+For the models using a smoothed disc the same physical and chemical model is used but with the temperature, density and abundance averaged in $\phi$.\newline
 
+-describe the chemistry  - refer to Ilee et al. which have been taken as input to the rad transfer (RT) code
 Chemical abundances in the disc were taken from Ilee et.
@@
 CS:  3$\times$10$^{-9}$ decreased by a factor of 10,000 at radii less than 6700au (Tafalla, santiago-garcia and myers 2006)\newline
-CO: as the H2O profile from before scaled so that the maximum abundance is CO maximum\newline
+CO: as the H2O profile from ??? scaled so that the maximum abundance is CO maximum\newline\
 
-\section{description of radiative transfer program}
+-describe the RT used (LIME) 
 LIME (Brinch 2011), the radiative transfer program used, calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3d model.
@@
 These points are then smoothed by Lloyds algorithm (Lloyd 1982) in order to minimise the variation in distance between points whilst keeping the same underlying distribution.
-These points are then connected by Delaunay triangulation and it is down these paths that photons are restricted to propagating (figures \ref{grid}).
+These points are then connected by Delaunay triangulation and it is down these paths that photons are restricted to propagating.
 The levels of molecules in question are then  calculated at each of these points from collisional and radiative (de)excitation and the local radiation field is calculated.
-This is repeated 20 times with the populations of each level converging towards a single value.\newline
+This is repeated 20 times with the populations of each level converging towards a single value.
+\newline
 
@@
  \includegraphics[width=84mm]{Figures/model/Lime_grid3.png}
- \label{grid}
- \caption{An example of the points distribution chosen by lime for a model of a smooth protoplanetary disc.
-The nodes of the grid are the points at which the underlying physical model is sampled and the edges are teh paths down which photons can travel during the excitation-radiation emission stage of the computation.}
+
+ \caption{plot of the griding overlaid on a smoothed density model}
 \end{figure}
@@
  \includegraphics[width=84mm]{Figures/model/lime_points_rz2.png}
- \label{points}
- \caption{the rz distribution of points selected to sample the model.
-The points in the dense region at 10$^9<\rm{z}<10^12$ and 7*10$^{11}<\rm{r}<10^{13}$ are sampling the disc model and the points at larger values are those foreced into the outer regions to sample the envelople.}
+
+ \caption{plot of the points selected in the model}
 \end{figure}
@@
 After selection of random co-ordinates the Hydrogen density and molecular density at the point (n and m) are compared against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$).
-If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use, if not then another r, $\phi$, z co-ordinate is selected.
+If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use, if not then another r,$\phi$,z co-ordinate is selected.
 The weighting function and griding functions were selected empirically to sample both the all scales while ensuring the majority of the points went into the inner disc which is the region of interest.
@@
 This provides a minimum level of sampling for the large low density regions in the outer parts of the simulated volume.
-See figure \ref{points} for example of the points distribution in r, z.
-\newline
+See figure 5 for example of the points distribution in r, z.
 
 \section{Model Results}
-
-Continuum emission from the model.
-Able to do this as the majority of the computing time on the model is taken up with calculating molecule population levels.
-This image has been created by averaging the output images of 100 unique runs.
-This averaging mitigates the granularity of output images from lime due to the nature of the gridding.
-
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/continuum.png}
-
- \caption{A composite image of 100 runs of continuum emission at 350$\,$GHz}
-\end{figure}
 

### 2012-10-31 paper.tex
some new figs model description section written up

--- 2012-10-10 paper.tex
@@
 \usepackage{graphicx}
+\usepackage{float}
 
@@
 
+%-describe the envelope structure (pre-stellar core)
 The model used to simulate the emission from a young protoplantary disc is a hybrid model created from hydrodynamical models of an infalling prestellar core and a gravitationally unstable protoplanetary disc.
@@
 This prestellar core model extends from 80$\,$au out to 10,000$\,$AU.
-The model is a 1D spherically symmetric model with inward motions (see figure \ref{l1544model}).
+The model is a 1D spherically symmetric model with inward motions (see figure \ref{l1544model}).\newline
 
@@
  \includegraphics[width=84mm]{Figures/model/L1544model_used.png}
- \label{l1544model}
- \caption{envelope model showing temp and dust temp (red, green) in kelvin, log number density (blue) in cm$^{-3}$ and inward velocity$\times$10 (cyan) in m$\,$s$^{-1}$, adapted from Keto \& Caselli (2010)}
+ \label{L1544}
+ \caption{Model of the prestellar core L1544 used as the envelope in the hybrid model.
+Showing temperature and dust temperature (red, green) in kelvin, log number density (blue) in cm$^{-3}$ and inward velocity$\times$100 (cyan) in m$\,$s$^{-1}$.
+Adapted from Keto \& Caselli (2010)}
 \end{figure}
@@
 \begin{figure*}
- \includegraphics[width=168mm]{Figures/model/rhoT.png}
- \label{discModel}
- \caption{The density and temperatures of the 0.4$\,\rm{M}_\odot$ gravitationally unstable disc model used in inside 80$\,$AU.
-The dense and hot regions are confinded to a few AU about the rotation plane.}
+ \includegraphics[width=168mm]{Figures/model/rhoT2.png}
+ \label{rhoT} 
+ \caption{Left: A 3D plot of log density (m$^3$) showing the spiral structure in the xy plane and scale height of the disc.
+Right: The 3D temperature strucure of the disc; regions less than 40 degrees are not shown in 3D, demonstrating the narrow central region containing hot material.}
 \end{figure*}
 
-\begin{figure*}
- \includegraphics[width=168mm]{Figures/model/velocity_rzSlice_thetaColourScale2.png}
- \label{discVel}
- \caption{The line of sight (colour scale) and plane of sky (arrows) velocities in the y=0 slice through the disc model.}
-\end{figure*}
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/model/rotational_velocities.png}
+ \label{velocity}
+ \caption{Azimuthaly avereaged rotational velocity in the disc midplane with best fit curve}
+\end{figure}
 
-At radii less than 80$\,$au the physical structure is the given by the hydrodynamic model described in Ilee et al.
+%-describe the physical structure of the disk (density and temperature) -- one figure showing the physical structure and the kinematics (2-panels figure)
+At radii less than 80$\,$au the physical structure is given by the hydrodynamic model described in Ilee et al.
 (2011), based on the work of Boley(2007), and Boley(2009).
 This model describes a 0.39$\,\rm{M}_\odot$ self-gravitating disc featuring prominent spiral arms.
-H$_2$ number densities in the disc range from 10$^{10}$-10$^{19}\,\rm{m}^{-3}$, and temperatures range from 30-400 K.
+H$_2$ number densities in the disc range from 10$^{10}$-10$^{19}\,\rm{m}^{-3}$, and temperatures range from 30-400 K (figure \ref{rhoT}).
 The dust and gas temperatures in the disc are assumed to be in equilibrium.
@@
 
+%-describe the chemistry  - refer to Ilee et al. which have been taken as input to the rad transfer (RT) code
 Chemical abundances in the disc were taken from Ilee et.
@@
 (tableify this?)\newline
-HCO$^+$: as the H2O profile from (find out where L1544 H2O profile is from) scaled so that the maximum abundance is 10$^{-8}$\newline
+HCO$^+$: as the H2O profile from Caselli (2012, submitted) scaled so that the maximum abundance is 10$^{-8}$\newline
 HNO: constant abundance of 5$\times$10${-11}$\newline
@@
 CS:  3$\times$10$^{-9}$ decreased by a factor of 10,000 at radii less than 6700au (Tafalla, santiago-garcia and myers 2006)\newline
-CO: as the H2O profile from before scaled so that the maximum abundance is CO maximum\newline
+CO: as the H2O profile from Caselli (2012, submitted) scaled so that the maximum abundance is CO maximum\newline
 
-\section{description of radiative transfer program}
+%-describe the RT used (LIME) 
 LIME (Brinch 2011), the radiative transfer program used, calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3d model.
@@
  \label{grid}
- \caption{An example of the points distribution chosen by lime for a model of a smooth protoplanetary disc.
-The nodes of the grid are the points at which the underlying physical model is sampled and the edges are teh paths down which photons can travel during the excitation-radiation emission stage of the computation.}
+ \caption{A plot of the points selected by the gridding process and the paths down which photons can propagate overlaid on a smoothed density model.
+The points are more concentrated at small radii and in the densest regions.}
 \end{figure}
@@
  \label{points}
- \caption{the rz distribution of points selected to sample the model.
-The points in the dense region at 10$^9<\rm{z}<10^12$ and 7*10$^{11}<\rm{r}<10^{13}$ are sampling the disc model and the points at larger values are those foreced into the outer regions to sample the envelople.}
+ \caption{A plot of the positions of the points selected to sample the model}
 \end{figure}
@@
 
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/average_comparison.png}
+ \label{averages}
+ \caption{A plot showing the difference between a single LIME continuum image at 300$\,$GHz and the average of ten such images from different runs of the same model in LIME}
+\end{figure}
+
 \section{Model Results}
 
-Continuum emission from the model.
-Able to do this as the majority of the computing time on the model is taken up with calculating molecule population levels.
-This image has been created by averaging the output images of 100 unique runs.
-This averaging mitigates the granularity of output images from lime due to the nature of the gridding.
+%Figures showing the RT results in a few molecules/transitions (CO, HCO$^+$, HCN, OCS, H2CO, NH3 --- maybe H2O,H2$^{18}$O [to try first])
+The results of these simulations for the molecules OCS, HCO$^+$, H$_2$CO and isotopologues of CO are shown here, other molecules simulated but not shown include HCN, HNC, HNO, HCS$^+$ and  CS.
+For the purpose of simulating observations the model was placed at roughly the distance of nearby low-mass star forming regions (100$\,$pc) and is inclined 30$^\circ$ to edge on.
+From these observations integrated intensity, intensity weighted velocity and position velocity diagrams through the centre of the model were created.
+The simulations done are focused upon frequencies within ALMA band 7, selected to give the best trade off between resolution and sensitivity for early ALMA science.
+(Note the moment 1 and 0 maps were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in some PV diagrams as the strong absorption feature at all positions around zero velocity, moment 1 maps are shown with a cutoff of 1/1000 of the peak emission/absorption value)\newline
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/continuum.png}
+\begin{figure}[H]
+ \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_contSub.png}
 
- \caption{A composite image of 100 runs of continuum emission at 350$\,$GHz}
+ \caption{CO J=3-2 Continuum subtracted mom0}
 \end{figure}
 
-Figures showing the RT results in a few molecules/transitions (CO, HCO$^+$, HCN, OCS, H2CO, NH3 --- maybe H2O,H2$^{18}$O [to try first]) (Note the moment 1 and 0 map were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in the some PV diagrams as the strong absorption feature at all positions around zero velocity, mom1maps are shown with a cutoff of 1/1000 of the peak emission/absorption value)\newline
+\begin{figure}[H]
+ \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_mom1.png}
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_contSub.png}
-
- \caption{CO 3-2 Continuum subtracted mom0}
+ \caption{CO J=3-2 moment 1 map}
 \end{figure}
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_mom1.png}
+\begin{figure}[H]
+ \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_PV_centre.png}
 
- \caption{CO 3-2 mom1map}
+ \caption{CO J=3-2 PV through y=0''}
 \end{figure}
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_PV_centre.png}
+Figures 6,7 and 8 show synthetic images of the CO J=3-2 line at 345.8$\,$GHz.
+As the upper level for this line is at 33$\,$K above the ground state this transition should be excited through out disc.
+given the large and uniform nature of the abundance of CO in the disc this line will be optically thick and this is only mapping the outer regions of the disc.
+In common with most transitions simulated, the line is seen almost exclusively in absorption of the disc continuum.
+The region of emission in the centre is where there is no continuum background to be absorbed.
+Some indications of spiral structure can be seen but are indistinct.
+***not sure how usefull these are, might be worth cutting them?***\newline
 
- \caption{CO 3-2 PV through centre}
-\end{figure}
-
-These synthetic images of the CO 3-2 line at 345.8$\,$GHz.
-As the upper level for this line is at 33$\,$K above the ground state this transition should be excited through out disc.
-CO line will be thick so this is only mapping the outer regions of the disc.
-Spiral structure can be seen.\newline
-
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageOCS_28-27_30deg_contSub.png}
-
+\begin{figure}[H]
+ \includegraphics[width=84mm]{Figures/sim/imageOCS_28-27_30deg_composite_contSub.png}
+ \label{OCS_mom0}
  \caption{OCS 28-27 Continuum subtracted mom0}
@@
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageOCS_28-27_30deg_PV_centre.png}
+\begin{figure}[H]
+ \includegraphics[width=84mm]{Figures/sim/imageOCS_28-27_30deg_composite_PV_centre.png}
 
@@
 
-The OCS lines in alma band 7 (22-21 through 30-29) with upper energy levels between 161 and 271 K above the ground state provide a way to trace hot shocked gas in spiral arms without resolving structure.\newline
+The OCS lines in alma band 7 (22-21 through 30-29) with upper energy levels between 161 and 271 K above the ground state provide a way to trace hot shocked gas in spiral arms without resolving structure.
+Figures \ref{OCS_mom0} \& \ref{smoothOCS_mom0} show the integrated intensity of the OCS J=28-27 line in the model described previously and one where the disc section of the model is an axis-symmetric model created by taking the azimuthal average of density, temperature and molecular abundance.
+The order of magnitude difference in the line intensity provides a method to detect hot dense gas without being able to reolve the spiral structure spatially.\newline
 
@@
  \includegraphics[width=84mm]{Figures/sim/imagesmoothedOCS_28-27_30deg_contSub.png}
-
+ \label{smoothOCS_mom0}
  \caption{SmoothedOCS 28-27 Continuum subtracted mom0}
@@
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imagesmoothedOCS_28-27_30deg_PV_centre.png}
-
- \caption{SmoothedOCS 28-27 PV through centre}
-\end{figure}
-
-In comparison to the model with spiral arms the absorbtion and emission from this smoothed model is far weaker.\newline
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/imagesmoothedOCS_28-27_30deg_PV_centre.png}
+%
+% \caption{SmoothedOCS 28-27 PV through centre}
+%\end{figure}
 
@@
 
-line ratios of many lined spieces can help us calculate temperatures of the emitting regions.
+More complex molecules such as H$_2$CO with many closely spaced spectral lines can be used to gain an estimate on the temperature of a region.
 
-(figure of temperature as a function of line ratio for 2 sets of formaldehyde lines and map of derived temperature, talk to P about this)\newline
+(figure of temperature as a function of line ratio for 2 sets of formaldehyde lines and map of derived temperature, talk to P about this.
+This doesnt seem doable with the lines around 1mm for alma)\newline
 
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageHCOp_1-0_30deg_contSub.png}
+ \includegraphics[width=84mm]{Figures/sim/imageHCOp_3-2_30deg_contSub.png}
 
- \caption{HCO$^+$ 1-0 Continuum subtracted mom0}
+ \caption{HCO$^+$ 3-2 Continuum subtracted mom0}
 \end{figure}
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageHCOp_1-0_30deg_mom1.png}
+ \includegraphics[width=84mm]{Figures/sim/imageHCOp_3-2_30deg_mom1.png}
 
- \caption{HCO$^+$ 1-0 mom1map}
+ \caption{HCO$^+$ 3-2 mom1map}
 \end{figure}
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageHCOp_1-0_30deg_PV_centre.png}
+ \includegraphics[width=84mm]{Figures/sim/imageHCOp_3-2_30deg_PV_centre_2.png}
 
- \caption{HCO$^+$ 1-0 PV through centre}
+ \caption{HCO$^+$ 3-2 PV through centre with rotation curve from figure \ref{velocity}}
 \end{figure}
 
-some molecules such as HCO$^+$ trace only the inner disc (ref ilee 2011) and so can be used to look at the extended velocity and physical structure.\newline
+Some molecules such as HCO$^+$ trace only the outer regions of the disc (ref ilee 2011) and so can be used to look at the extended velocity and physical structure.
+In these colder less dense regions we see the molecular lines in emission rather than absorption \newline
+\newline \newline
 
@@
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_mom1.png}
-
- \caption{C18O 3-2 15 deg mom1map}
-\end{figure}
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_mom1.png}
+%
+% \caption{C18O 3-2 15 deg mom1map}
+%\end{figure}
 
@@
 
-fdagfdabfdsbfdbds fdbfd  fdfbfvdfd g rbfd fdbfdbc \newline fdagfdabfdsbfdbds fdbfd  fdfbfvdfd g rbfd fdbfdbc \newline fdagfdabfdsbfdbds fdbfd  fdfbfvdfd g rbfd fdbfdbc \newline fdagfdabfdsbfdbds fdbfd  fdfbfvdfd g rbfd fdbfdbc \newline fdagfdabfdsbfdbds fdbfd  fdfbfvdfd g rbfd fdbfdbc \newline fdagfdabfdsbfdbds fdbfd  fdfbfvdfd g rbfd fdbfdbc \newline
-
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_mom1.png}
-
- \caption{C18O 3-2 30 deg mom1map}
-\end{figure}
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_mom1.png}
+%
+% \caption{C18O 3-2 30 deg mom1map}
+%\end{figure}
 
@@
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_mom1.png}
-
- \caption{C18O 3-2 45 deg mom1map}
-\end{figure}
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_mom1.png}
+%
+% \caption{C18O 3-2 45 deg mom1map}
+%\end{figure}
 
@@
 
-nfsdankjdsankj vdjsk nvjdks nvkds jkkd jkvd jkvf djk fj\newline nfsdankjdsankj vdjsk nvjdks nvkds jkkd jkvd jkvf djk fj\newline nfsdankjdsankj vdjsk nvjdks nvkds jkkd jkvd jkvf djk fj\newline nfsdankjdsankj vdjsk nvjdks nvkds jkkd jkvd jkvf djk fj\newline nfsdankjdsankj vdjsk nvjdks nvkds jkkd jkvd jkvf djk fj\newline nfsdankjdsankj vdjsk nvjdks nvkds jkkd jkvd jkvf djk fj\newline nfsdankjdsankj vdjsk nvjdks nvkds jkkd jkvd jkvf djk fj\newline
-
 \begin{figure}
@@
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_mom1.png}
-
- \caption{C18O 3-2 60 deg mom1map}
-\end{figure}
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_mom1.png}
+%
+% \caption{C18O 3-2 60 deg mom1map}
+%\end{figure}
 
@@
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_mom1.png}
-
- \caption{C18O 3-2 75 deg mom1map}
-\end{figure}
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_mom1.png}
+%
+% \caption{C18O 3-2 75 deg mom1map}
+%\end{figure}
 
@@
 
-Figure showing different transitions of the same molecule (e.g. CO(1-0), ...(7-6) , OCS,  H2CO ) for same inclination but in different disks (Boley et al. and the smooth disk)\newline
+In all the simulations except HCO$^+$ we see molecular lines in absorption throughout the majority of the disc and in some cases a small amount of emission towards the centre, where the inclination of the disc allows us the view the low density but moderate temparture region inside the inner edge of the spiral structures.\newline
 
@@
 
-- current status (Cycle 1) - Figure
-OCS + C18O + H2CO + HNO/CS/
-- final status - Figure
+%- current status (Cycle 1) - Figure
+%OCS + C18O + H2CO + HNO/CS/
+%- final status - Figure
 
-\section{Conclusions}
+casa continuum, OCS and HCO+ figs here
 
-note that all species show up in absorption and some show a little bit of emission around the edges of the disc
-OCS is good for showing up spiral structure without being able to resolve it.
-envelope only contaminates the central plus-minus 500 m/s or so
+\section{Discussion}
+
+In this paper we have performed radiative transfer simulations of a hybrid model comprising a 0.4$\, M_\odot$ self gravitating disc with radius 64$\,AU$ showing spiral density waves, surrounded by an envelope simulated as a collapsing 10$\,M_\odot$ BE-sphere.
+CASA simulations show that at a distance of 100$\,pc$ both spatial resolution of the spirals in such a disc and extraction of kinematic and temperature from molecular lines are possible in ALMA band 7.
+Our simulations show that many  molecular spieces are prodominantly seen in absorbtion towards the centre of  self-gravitating protoplanetary discs.\newline
+The quiesient nature of the envelope around such discs only obscures them within $\pm\,0.5 km\,s^{-1}$.\newline
+Hot, shocked gas can be detected in such a disc without resolving it by observing OCS transitions between 26-27 to 30-29.\newline
+Mention that dust and gas are assumed to be in temperature equilibrium if they arent and dust is significantly cooler then transitions may not show up in absorption.
+atm spirals shock heat the mid-plane layer and the colder more difusse gas absorbs the continuum from it (need to ask aaron whether this is the case, the narrow midplane is much hotter than the rest but should check that this is due to shock heating, though with there being no accreation or iradiation i dont see what else it could be)\newline
+note that the disc mass is on the high end for early discs\newline
+rotation curves can be gatherered from these observations even with spiral structure\newline
 
@@
 
-I thank Professor N. Kameswara Rao for some helpful suggestions,
-Dr H. C. Bhatt for a critical reading of the original version of the
-paper and an anonymous referee for very useful comments that improved
-the presentation of the paper.
+stuff here
 

### 2012-10-31 paper.tex
spell check

@@
 %-describe the envelope structure (pre-stellar core)
-The model used to simulate the emission from a young protoplantary disc is a hybrid model created from hydrodynamical models of an infalling prestellar core and a gravitationally unstable protoplanetary disc.
+The model used to simulate the emission from a young protoplanetary disc is a hybrid model created from hydrodynamical models of an infalling prestellar core and a gravitationally unstable protoplanetary disc.
 The prestellar core model is based upon the model of Keto \& Caselli (2010).
@@
  \caption{Left: A 3D plot of log density (m$^3$) showing the spiral structure in the xy plane and scale height of the disc.
-Right: The 3D temperature strucure of the disc; regions less than 40 degrees are not shown in 3D, demonstrating the narrow central region containing hot material.}
+Right: The 3D temperature structure of the disc; regions less than 40 degrees are not shown in 3D, demonstrating the narrow central region containing hot material.}
 \end{figure*}
@@
  \label{velocity}
- \caption{Azimuthaly avereaged rotational velocity in the disc midplane with best fit curve}
+ \caption{Azimuthaly averaged rotational velocity in the disc mid-plane with best fit curve}
 \end{figure}
@@
  \label{grid}
- \caption{A plot of the points selected by the gridding process and the paths down which photons can propagate overlaid on a smoothed density model.
+ \caption{A plot of the points selected by the griding process and the paths down which photons can propagate overlaid on a smoothed density model.
 The points are more concentrated at small radii and in the densest regions.}
@@
 Some indications of spiral structure can be seen but are indistinct.
-***not sure how usefull these are, might be worth cutting them?***\newline
+***not sure how useful these are, might be worth cutting them?***\newline
 
@@
 Figures \ref{OCS_mom0} \& \ref{smoothOCS_mom0} show the integrated intensity of the OCS J=28-27 line in the model described previously and one where the disc section of the model is an axis-symmetric model created by taking the azimuthal average of density, temperature and molecular abundance.
-The order of magnitude difference in the line intensity provides a method to detect hot dense gas without being able to reolve the spiral structure spatially.\newline
+The order of magnitude difference in the line intensity provides a method to detect hot dense gas without being able to resolve the spiral structure spatially.\newline
 
@@
 (figure of temperature as a function of line ratio for 2 sets of formaldehyde lines and map of derived temperature, talk to P about this.
-This doesnt seem doable with the lines around 1mm for alma)\newline
+This doesn't seem doable with the lines around 1mm for alma)\newline
 
@@
 
- \caption{HCO$^+$ 3-2 PV through centre with rotation curve from figure \ref{velocity}}
+ \caption{HCO$^+$ 3-2 PV through centre with rotation curve from figure \ref{velocity} *** should the velocities in this be reduced by cos(30) as we're not in the plane of rotation? ***}
 \end{figure}
@@
 
-In all the simulations except HCO$^+$ we see molecular lines in absorption throughout the majority of the disc and in some cases a small amount of emission towards the centre, where the inclination of the disc allows us the view the low density but moderate temparture region inside the inner edge of the spiral structures.\newline
+In all the simulations except HCO$^+$ we see molecular lines in absorption throughout the majority of the disc and in some cases a small amount of emission towards the centre, where the inclination of the disc allows us the view the low density but moderate temperature region inside the inner edge of the spiral structures.\newline
 
@@
 CASA simulations show that at a distance of 100$\,pc$ both spatial resolution of the spirals in such a disc and extraction of kinematic and temperature from molecular lines are possible in ALMA band 7.
-Our simulations show that many  molecular spieces are prodominantly seen in absorbtion towards the centre of  self-gravitating protoplanetary discs.\newline
-The quiesient nature of the envelope around such discs only obscures them within $\pm\,0.5 km\,s^{-1}$.\newline
+Our simulations show that many  molecular species are predominantly seen in absorption towards the centre of  self-gravitating protoplanetary discs.\newline
+The quiescent nature of the envelope around such discs only obscures them within $\pm\,0.5 km\,s^{-1}$.\newline
 Hot, shocked gas can be detected in such a disc without resolving it by observing OCS transitions between 26-27 to 30-29.\newline
-Mention that dust and gas are assumed to be in temperature equilibrium if they arent and dust is significantly cooler then transitions may not show up in absorption.
-atm spirals shock heat the mid-plane layer and the colder more difusse gas absorbs the continuum from it (need to ask aaron whether this is the case, the narrow midplane is much hotter than the rest but should check that this is due to shock heating, though with there being no accreation or iradiation i dont see what else it could be)\newline
+Mention that dust and gas are assumed to be in temperature equilibrium if they aren't and dust is significantly cooler then transitions may not show up in absorption.
+atm spirals shock heat the mid-plane layer and the colder more diffuse gas absorbs the continuum from it (need to ask Aaron whether this is the case, the narrow mid-plane is much hotter than the rest but should check that this is due to shock heating, though with there being no accretion or irradiation i don't see what else it could be)\newline
 note that the disc mass is on the high end for early discs\newline
-rotation curves can be gatherered from these observations even with spiral structure\newline
+rotation curves can be gathered from these observations even with spiral structure\newline
 

### 2012-11-15 paper.tex
More figures, some small tweaks to text

@@
 %-describe the envelope structure (pre-stellar core)
-The model used to simulate the emission from a young protoplanetary disc is a hybrid model created from hydrodynamical models of an infalling prestellar core and a gravitationally unstable protoplanetary disc.
+The physical and chemical models used to simulate the emission from a young protoplanetary disc is a hybrid model created from hydrodynamical models of an infalling prestellar core and a gravitationally unstable protoplanetary disc.
 The prestellar core model is based upon the model of Keto \& Caselli (2010).
@@
  \label{rhoT} 
- \caption{Left: A 3D plot of log density (m$^3$) showing the spiral structure in the xy plane and scale height of the disc.
-Right: The 3D temperature structure of the disc; regions less than 40 degrees are not shown in 3D, demonstrating the narrow central region containing hot material.}
+ \caption{Left: A 3D plot of log number density (m$^{-3}$) showing the spiral structure in the xy plane and scale height of the disc.
+Right: The 3D temperature structure of the disc; regions cooler than 40 degrees are not shown in 3D, demonstrating the narrow central region containing hot material.}
+\end{figure*}
+
+\begin{figure*}
+ \includegraphics[width=168mm]{Figures/model/columnDensities2.png}
+ \label{Chemistry} 
+ \caption{Column densities of H$_2$CO, OCS and HCO$^+$ used in the disc model. Figure adapted from Ilee at al. (2011)}
 \end{figure*}
@@
 
-(tableify this?)\newline
-HCO$^+$: as the H2O profile from Caselli (2012, submitted) scaled so that the maximum abundance is 10$^{-8}$\newline
-HNO: constant abundance of 5$\times$10${-11}$\newline
-HCS$^+$: 10$^{-11}$\newline
-OCS: constant abundance of 10$^{-9}$\newline
+%(tableify this?)
+HCO$^+$: As the H$_2$O profile from Caselli et al. (2012, submitted) scaled so that the maximum abundance is 10$^{-8}$\newline
+HNO: Constant abundance of 5$\times$10$^{-11}$\newline
+HCS$^+$: Constant abundance of 10$^{-11}$\newline
+OCS: Constant abundance of 10$^{-9}$\newline
 H$_2$CO: 1.5$\times$10$^{-9}$ decreased by a factor of 40 at radii less than 8250au (Young et al 2004)\newline
 CS:  3$\times$10$^{-9}$ decreased by a factor of 10,000 at radii less than 6700au (Tafalla, santiago-garcia and myers 2006)\newline
-CO: as the H2O profile from Caselli (2012, submitted) scaled so that the maximum abundance is CO maximum\newline
+CO: As the H2O profile from Caselli (2012, submitted) scaled so that the maximum abundance is CO maximum ***which is....***\newline
 
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/model/lime_points_rz2.png}
+ \includegraphics[width=84mm]{Figures/model/lime_points_rz_histo.png}
  \label{points}
- \caption{A plot of the positions of the points selected to sample the model}
+ \caption{A histogram of the point distribution throughout the model.}
 \end{figure}
@@
  \label{averages}
- \caption{A plot showing the difference between a single LIME continuum image at 300$\,$GHz and the average of ten such images from different runs of the same model in LIME}
+ \caption{A plot showing the difference between a single LIME continuum image at 300$\,$GHz (right) and the average of ten such images from different runs of the same model in LIME (left).}
 \end{figure}
@@
 given the large and uniform nature of the abundance of CO in the disc this line will be optically thick and this is only mapping the outer regions of the disc.
-In common with most transitions simulated, the line is seen almost exclusively in absorption of the disc continuum.
+In common with most transitions simulated, the line is seen almost exclusively in absorption against the disc continuum.
 The region of emission in the centre is where there is no continuum background to be absorbed.
@@
 
-The OCS lines in alma band 7 (22-21 through 30-29) with upper energy levels between 161 and 271 K above the ground state provide a way to trace hot shocked gas in spiral arms without resolving structure.
+After looking at a variety of lines which could be observed of ALMA band 6 or 7 (211-275$\,$GHz and 275-373$\,$GHz) we found that the OCS lines in alma band 7 (22-21 through 30-29) with upper energy levels between 161 and 271 K above the ground state provide a way to trace hot shocked gas in spiral arms without resolving structure.
 Figures \ref{OCS_mom0} \& \ref{smoothOCS_mom0} show the integrated intensity of the OCS J=28-27 line in the model described previously and one where the disc section of the model is an axis-symmetric model created by taking the azimuthal average of density, temperature and molecular abundance.
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageHCOp_3-2_30deg_contSub.png}
+ \includegraphics[width=84mm]{Figures/sim/imageHCOp_1-0_30deg_contSub.png}
 
- \caption{HCO$^+$ 3-2 Continuum subtracted mom0}
+ \caption{HCO$^+$ 1-0 Continuum subtracted mom0}
 \end{figure}
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageHCOp_3-2_30deg_mom1.png}
+ \includegraphics[width=84mm]{Figures/sim/imageHCOp_1-0_30deg_mom1.png}
 
- \caption{HCO$^+$ 3-2 mom1map}
+ \caption{HCO$^+$ 1-0 mom1map}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/imageHCOp_1-0_30deg_PV_centre.png}
+
+ \caption{HCO$^+$ 1-0 pv through centre}
 \end{figure}
@@
  \includegraphics[width=84mm]{Figures/sim/imageHCOp_3-2_30deg_PV_centre_2.png}
-
+ \label{hcop_pv}
  \caption{HCO$^+$ 3-2 PV through centre with rotation curve from figure \ref{velocity} *** should the velocities in this be reduced by cos(30) as we're not in the plane of rotation? ***}
@@
 
-Some molecules such as HCO$^+$ trace only the outer regions of the disc (ref ilee 2011) and so can be used to look at the extended velocity and physical structure.
-In these colder less dense regions we see the molecular lines in emission rather than absorption \newline
+Some molecules such as HCO$^+$ trace only the outer regions of the disc (Ilee 2011) and so can be used to look at the extended velocity and physical structure.
+In these colder less dense regions we see the molecular lines in emission rather than absorption.
+Figure \ref{hcop_pv} shows the rotation curve of the model as shown in figure \ref{velocity} against the HCO$^+$ J=3-2 line emission.
+It is clear that from observations such as these the rotation curve of a disc could be reconstructed.\newline
 \newline \newline
+
+In all the simulations except HCO$^+$ we see molecular lines in absorption throughout the majority of the disc and in some cases a small amount of emission towards the centre, where the inclination of the disc allows us the view the low density but moderate temperature region inside the inner edge of the spiral structures without any high temperature and density material behind it.\newline
+
+\section{ALMA Predictions}
+
+%- current status (Cycle 1) - Figure
+%OCS + C18O + H2CO + HNO/CS/
+%- final status - Figure
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/casa_cont_337GHz.png}
+
+ \caption{continuum emission at 337GHz simulated for ALMA most extended configuration}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=54mm]{Figures/sim/casa_OCS_28-27_pv.png}
+
+ \caption{OCS 28-29 pv diagram simulated for ALMA most extended configuration}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/casa_OCS_28-27_mom0.png}
+
+ \caption{OCS 28-29 integrated intesity simulated for ALMA most extended configuration}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=54mm]{Figures/sim/casa_C17O_3-2_pv.png}
+
+ \caption{C17O 3-2 30 deg PV through centre simulated for ALMA most extended configuration}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/casa_C17O_3-2_mom0.png}
+
+ \caption{C17O 3-2 30 deg integrated intensity simulated for ALMA most extended configuration}
+\end{figure}
+
+\section{Discussion}
+
+In this paper we have performed radiative transfer simulations of a hybrid model comprising a 0.4$\, M_\odot$ self gravitating disc with radius 64$\,AU$ showing spiral density waves, surrounded by an envelope simulated as a collapsing 10$\,M_\odot$ BE-sphere.
+CASA simulations show that at a distance of 100$\,$pc both spatial resolution of the spirals in such a disc and extraction of kinematic and temperature from molecular lines are possible in ALMA band 7.
+Our simulations show that many  molecular species are predominantly seen in absorption towards the centre of  self-gravitating protoplanetary discs.\newline
+The quiescent nature of the envelope around such discs only obscures them within $\pm\,0.5 km\,s^{-1}$.\newline
+Hot, shocked gas can be detected in such a disc without resolving it by observing OCS transitions between 26-27 to 30-29.\newline
+One assumption made in this model is that the gas and dust are in thermal equilibrium.
+If they are not and the dust is significantly cooler than the gas then transitions may not show up in absorption.
+In the model spirals shock heat the mid-plane layer and the colder more diffuse gas absorbs the continuum from it (need to ask Aaron whether this is the case, the narrow mid-plane is much hotter than the rest but should check that this is due to shock heating, though with there being no accretion or irradiation i don't see what else it could be)\newline
+note that the disc mass is on the high end for early discs\newline
+rotation curves can be gathered from these observations even with spiral structure\newline
+
+\section*{Acknowledgements}
+
+stuff here
+\newpage
+
+\appendix
+
+\section[]{Other Inclinations}
 
@@
 
-In all the simulations except HCO$^+$ we see molecular lines in absorption throughout the majority of the disc and in some cases a small amount of emission towards the centre, where the inclination of the disc allows us the view the low density but moderate temperature region inside the inner edge of the spiral structures.\newline
-
-\section{ALMA Predictions}
-
-%- current status (Cycle 1) - Figure
-%OCS + C18O + H2CO + HNO/CS/
-%- final status - Figure
-
-casa continuum, OCS and HCO+ figs here
-
-\section{Discussion}
-
-In this paper we have performed radiative transfer simulations of a hybrid model comprising a 0.4$\, M_\odot$ self gravitating disc with radius 64$\,AU$ showing spiral density waves, surrounded by an envelope simulated as a collapsing 10$\,M_\odot$ BE-sphere.
-CASA simulations show that at a distance of 100$\,pc$ both spatial resolution of the spirals in such a disc and extraction of kinematic and temperature from molecular lines are possible in ALMA band 7.
-Our simulations show that many  molecular species are predominantly seen in absorption towards the centre of  self-gravitating protoplanetary discs.\newline
-The quiescent nature of the envelope around such discs only obscures them within $\pm\,0.5 km\,s^{-1}$.\newline
-Hot, shocked gas can be detected in such a disc without resolving it by observing OCS transitions between 26-27 to 30-29.\newline
-Mention that dust and gas are assumed to be in temperature equilibrium if they aren't and dust is significantly cooler then transitions may not show up in absorption.
-atm spirals shock heat the mid-plane layer and the colder more diffuse gas absorbs the continuum from it (need to ask Aaron whether this is the case, the narrow mid-plane is much hotter than the rest but should check that this is due to shock heating, though with there being no accretion or irradiation i don't see what else it could be)\newline
-note that the disc mass is on the high end for early discs\newline
-rotation curves can be gathered from these observations even with spiral structure\newline
-
-\section*{Acknowledgements}
-
-stuff here
-
-%\appendix
-%
-%\section[]{Large gaps in L\lowercase{y}${\balpha}$ forests\\* due to fluctuations in line %distribution}
 %

### 2012-11-16 paper.tex
small tweak

@@
 2010); (b) observations: Fuente et al.
-2010 (AB Aur); Jorgensen \& van Dishoeck (H$_2^{18}$O and the HDO/H2O ratio); Pineda et al.
+2010 (AB Aur); Jorgensen \& van Dishoeck (H$_2^{18}$O and the HDO/H$_2$O ratio); Pineda et al.
 (2012); other papers talking about "hot corinos" (Bottinelli et al.
@@
 %-describe the RT used (LIME) 
-LIME (Brinch 2011), the radiative transfer program used, calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3d model.
+The radiative transfer program used, LIME (Brinch 2011), calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3d model.
 The method of selecting these points is given in the griding section.
@@
 
-\begin{figure}[H]
+\begin{figure}
  \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_contSub.png}
@@
 
-\begin{figure}[H]
+\begin{figure}
  \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_mom1.png}
@@
 
-\begin{figure}[H]
+\begin{figure}
  \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_PV_centre.png}
@@
 
-\begin{figure}[H]
+\begin{figure}
  \includegraphics[width=84mm]{Figures/sim/imageOCS_28-27_30deg_composite_contSub.png}
@@
 
-\begin{figure}[H]
+\begin{figure}
  \includegraphics[width=84mm]{Figures/sim/imageOCS_28-27_30deg_composite_PV_centre.png}
@@
 It is clear that from observations such as these the rotation curve of a disc could be reconstructed.\newline
-\newline \newline
+\newline
 
@@
 CASA simulations show that at a distance of 100$\,$pc both spatial resolution of the spirals in such a disc and extraction of kinematic and temperature from molecular lines are possible in ALMA band 7.
-Our simulations show that many  molecular species are predominantly seen in absorption towards the centre of  self-gravitating protoplanetary discs.\newline
+Our simulations show that many  molecular species are predominantly seen in absorption towards the centre of  self-gravitating protoplanetary discs.
 The quiescent nature of the envelope around such discs only obscures them within $\pm\,0.5 km\,s^{-1}$.\newline
 Hot, shocked gas can be detected in such a disc without resolving it by observing OCS transitions between 26-27 to 30-29.\newline
-One assumption made in this model is that the gas and dust are in thermal equilibrium.
-If they are not and the dust is significantly cooler than the gas then transitions may not show up in absorption.
-In the model spirals shock heat the mid-plane layer and the colder more diffuse gas absorbs the continuum from it (need to ask Aaron whether this is the case, the narrow mid-plane is much hotter than the rest but should check that this is due to shock heating, though with there being no accretion or irradiation i don't see what else it could be)\newline
-note that the disc mass is on the high end for early discs\newline
-rotation curves can be gathered from these observations even with spiral structure\newline
+One assumption made in this model is that the gas and dust are in thermal equilibrium.If they are not and the dust is significantly cooler than the gas then transitions may not show up in absorption.\newline
+The mass of the disc used (0.4$\,\rm{M}_\odot$) is on the high end for early discs (citations for estimate of early class 1 disc masses).\newline 
+In the model spirals shock heat the mid-plane layer and the colder more diffuse gas absorbs the continuum from it, this results in molecular lines being seen in absorbtion whenever lines of sight pass through the cold diffuse gas at larger heights on to the hot dense midplane of the disc.
+Rotation curves can be gathered from these observations even with spiral structure\newline
 

### 2012-11-27 paper_pc.tex
added comments file from paola

--- 2012-11-16 paper.tex
@@
 
-\title[Disc stuff]{Disc stuff}
+\title[Simulated observations of young protoplanetary disks]{Young protoplanetary disks}
 \author[Tom  Douglas, Paola Caselli, Et al.]{Tom Douglas$^{1}$\thanks{E-mail:
@@
 
-1. description of what has been done so far on the modelling and radiative transfer of disks (this includes also more evolved disks -- Visser et al., Walsh et al., Aikawa et al. ..)
-2. focus on the young disks (work done by Machida et al., Dapp, Basu \& Kunz 2012, .. for their formation; work by Boley et al. on the physical evolution ; Ilee et al. for chemistry) 
-3.
+The formation and early evolution of protoplanetary disks around solar-type and low-mass protostars has little observational support, despite of the fast growing list of theoretical models on the dynamical evolution of star forming dense cores (e.g.
+Krasnopolsky et al.
+2011; Machida et al.
+2011; Braiding \& Wardle 2012).
+The reason for this is that young protostars are surrounded by thick envelopes and power energetic outflows, thus observations of the young disks, predicted to have sizes of about 100\,AU and masses as large as 10\% the original core mass (e.g.
+Joos et al.
+2012), are challenging.
+The use of sensitive interferometers is needed to achieve high angular resolution and spatially/spectrally disentangle the various (disk + envelope + outflow) components as well to filter out the extended emission tracing envelope material.
+
+After the pioneer work of, e.g., Chandler et al.
+(1995), Brown et al.
+(2000), Looney et al.
+(2000), recent interferometric observations have discovered compact embedded disks in a sample of Class 0 (Andr\'e et al.
+2000) sources, finding masses between 0.4 and  $>$1 M$_{\odot}$ (Jorgensen et al.
+2007, 2009; Enoch et al.
+2011).
+A 130\,AU disk was discovered toward a Class 0 source in Perseus, using Jansky Very Large Array (JVLA) observations of NH$_3$ (Choi et al.
+2007).
+Pineda et al.
+(2012) observed methyl formate with the Atacama Millimeter and sub-millimeter Array (ALMA) and found evidence of rotation toward one of the proto-binary Class 0 sources embedded in IRAS 16293-2422.
+These observations are consistent with an almost edge-on disk.
+When ALMA will be completed, it will be finally possible to spatially resolve these young disks and, for the first time, put stringent constraints on theoretical models.
+As full-operational ALMA is fast approaching, it is important to provide observational predictions based on dynamical models of young protoplanetary disks.
+
+In this paper, we focus our attention to the young self-gravitating disks of Boley \& Durisen (2008), where episodic heating induced by spiral shocks is present, as this may be a good representation of the earliest phases of protoplanetary disks and an alternative to the young "static" disks studied by, e.g.
+Visser et al.
+(2009, 2011).
+As shown by Ilee et al.
+(2011), the spiral shocks cause desorption of volatiles from dust icy mantles and trigger gas-phase chemical reactions with activation energies, which are inactive at lower temperatures.
+These processes produce clear chemical signatures of the disk dynamics.
+With the use of 3D radiative transfer modeling, we perform simulated ALMA observations of the disk studied by Ilee et al.
+(2011) and identify the best tracers of the physical structure of self-gravitating disks.
+The physical, chemical and radiative transfer models are described in Sect\,\ref{sec:description_model}.
+Radiative transfer results are in Sect.\,\ref{sec:model_results}, while ALMA simulated observations are in Sec.\,\ref{sec:alma_predictions}.
+Discussions and conclusions can be found in Sect.\,\ref{sec:discussion}.
+
+%1. description of what has been done so far on the modelling and radiative transfer of disks (this includes also more evolved disks -- Visser et al., Walsh et al., Aikawa et al. ..)
+%2. focus on the young disks (work done by Machida et al., Dapp, Basu \& Kunz 2012, .. for their formation; work by Boley et al. on the physical evolution ; Ilee et al. for chemistry) 
+%3.
 previous attempts to observe these young disks: (a) simulations (Cossins et al.
@@
 
-\section{Description of the Model}
+\section{Description of the Model} \label{sec:description_model}
+
+\subsection{Physical and chemical structure} \label{subsec:physical_structure}
 
 %-describe the envelope structure (pre-stellar core)
-The physical and chemical models used to simulate the emission from a young protoplanetary disc is a hybrid model created from hydrodynamical models of an infalling prestellar core and a gravitationally unstable protoplanetary disc.
-The prestellar core model is based upon the model of Keto \& Caselli (2010).
-This describes an infalling pre-stellar core, with densities temperatures and velocities given by the model of the collapse of a 10 solar mass Bonnor-Ebert sphere and provides a match to line profiles seen in the pre-stellar core L1544.
-Some slight modification due to the addition of Oxygen lines (Keto et al 2012 in prep) have been been added to this model resulting in a slight decrease in the peak infall velocity.
-This prestellar core model extends from 80$\,$au out to 10,000$\,$AU.
-The model is a 1D spherically symmetric model with inward motions (see figure \ref{l1544model}).\newline
+
+The physical model used to simulate the emission from a young protoplanetary disc is a hybrid model obtained from embedding a gravitationally unstable protoplanetary disk  within an envelope with characteristics similar to the well-studied pre-stellar core L1544, as derived by Keto \& Caselli (2010; hereafter KC2010).
+The KC2010 model follows the dynamical, chemical and thermal evolution of a contracting Bonnor-Ebert (Bonnor 1956; Ebert 1957) sphere with total mass of 10\,M$_{\odot}$, until it reaches the density, temperature and velocity profiles which best match observations.
+The pre-stellar core model adopted here contains slight modifications due to the inclusion of oxygen cooling in the outer regions of the cloud, where CO is mostly photodissociated (Keto et al., in preparation), and it is shown in Fig.\,\ref{fig:l1544_model}.
+\newline
 
@@
  \includegraphics[width=84mm]{Figures/model/L1544model_used.png}
- \label{L1544}
- \caption{Model of the prestellar core L1544 used as the envelope in the hybrid model.
-Showing temperature and dust temperature (red, green) in kelvin, log number density (blue) in cm$^{-3}$ and inward velocity$\times$100 (cyan) in m$\,$s$^{-1}$.
-Adapted from Keto \& Caselli (2010)}
+ \label{fig:l1544_model}
+ \caption{Model of the pre-stellar core L1544 used as the envelope of the young protoplanetary disk in the hybrid model.
+Showing temperature (red) and dust (green) temperature in kelvin, log number density (blue) in cm$^{-3}$ and inward velocity$\times$100 (cyan) in m$\,$s$^{-1}$.
+Adapted from Keto \& Caselli (2010) and Keto et al.
+(2012, in preparation).}
 \end{figure}
@@
 %-describe the physical structure of the disk (density and temperature) -- one figure showing the physical structure and the kinematics (2-panels figure)
-At radii less than 80$\,$au the physical structure is given by the hydrodynamic model described in Ilee et al.
-(2011), based on the work of Boley(2007), and Boley(2009).
-This model describes a 0.39$\,\rm{M}_\odot$ self-gravitating disc featuring prominent spiral arms.
+The pre-stellar core structure is maintained down to a radius of 80\,AU, within which the young protoplanetary disk has been plugged in.
+The disk structure is derived by the hydrodynamic model of Boley(2007) and Boley (2009).
+The particular model considered here (as well as in Ilee et al.
+2011) is a 0.39$\,\rm{M}_\odot$ self-gravitating disc featuring prominent spiral arms.
 H$_2$ number densities in the disc range from 10$^{10}$-10$^{19}\,\rm{m}^{-3}$, and temperatures range from 30-400 K (figure \ref{rhoT}).
@@
 The model is sampled over a regular grid of size 256$\times$256$\times$64 with spatial resolution of 0.5$\,$au in x, y and z.
-The majority of the mass lies in the mid-plane of the disc.
+The gas/dust mass ratio was assumed to be 1/100 throughout both sections model and the opacities were given by the model of dust grains with thick icy mantles and 10$^6\,$yr coagulation from Ossenkopf and Henning (1994).
+THe gas number density and temperature structure are displayed in Fig.
+XX.
+\newline
+
+%The majority of the mass lies in the mid-plane of the disc.
 For the models using a smoothed disc the same physical and chemical model is used but with the temperature, density and abundance averaged in $\phi$.
@@
 These abundances were interpolated onto a 51$^3$ grid covering the disc with cells of size 2.2$\times$2.2$\times$0.22$\,$au.
-Abundances in the envelope model were as follows:\newline
+Fig.
+XX shows a sample of column density maps from Ilee et al.
+(2011), pointing out the different regions traced by H$_2$CO and OCS, which mostly probe the central warm regions, and HCO$^+$, which preferentially trace the outer spiral pattern as in the central region is destroyed by water molecules (see Ilee et al.
+2011 for details).
+The simple chemistry in the KC2010 model, adopted here as the envelope of the protoplanetary disk, does not provide detailed abundances of molecular species (besides CO and H$_2$O, see also Caselli et al.
+2012).
+As discussed in the result section (Sec.\,\ref{sec:model_results}), rough guesses have been made based on values measured toward similar object.
+
+%NOTE: WE SHOULD TALK ABOUT THESE SPECIES AFTER WE SHOW WHICH SPECIES WE SELECT FOR THE RADIATIVE TRANSFER. 
+%Abundances in the envelope model were as follows:\newline
 
 %(tableify this?)
-HCO$^+$: As the H$_2$O profile from Caselli et al. (2012, submitted) scaled so that the maximum abundance is 10$^{-8}$\newline
-HNO: Constant abundance of 5$\times$10$^{-11}$\newline
-HCS$^+$: Constant abundance of 10$^{-11}$\newline
-OCS: Constant abundance of 10$^{-9}$\newline
-H$_2$CO: 1.5$\times$10$^{-9}$ decreased by a factor of 40 at radii less than 8250au (Young et al 2004)\newline
-CS:  3$\times$10$^{-9}$ decreased by a factor of 10,000 at radii less than 6700au (Tafalla, santiago-garcia and myers 2006)\newline
-CO: As the H2O profile from Caselli (2012, submitted) scaled so that the maximum abundance is CO maximum ***which is....***\newline
+%HCO$^+$: As the H$_2$O profile from Caselli et al. (2012, submitted) scaled so that the maximum abundance is 10$^{-8}$\newline
+%HNO: Constant abundance of 5$\times$10$^{-11}$\newline
+%HCS$^+$: Constant abundance of 10$^{-11}$\newline
+%OCS: Constant abundance of 10$^{-9}$\newline
+%H$_2$CO: 1.5$\times$10$^{-9}$ decreased by a factor of 40 at radii less than 8250au (Young et al 2004)\newline
+%CS:  3$\times$10$^{-9}$ decreased by a factor of 10,000 at radii less than 6700au (Tafalla, santiago-garcia and myers 2006)\newline
+%CO: As the H2O profile from Caselli (2012, submitted) scaled so that the maximum abundance is CO maximum ***which is....***\newline
 
+\subsection{The radiative transfer code} \label{subsec:radiative_transfer_code}
 %-describe the RT used (LIME) 
-The radiative transfer program used, LIME (Brinch 2011), calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3d model.
-The method of selecting these points is given in the griding section.
-At each of these points the density of the main collision partner (in this case H$_2$), gas and dust temperatures, velocity, molecular abundances and turbulent velocity and taken from the model.
+The radiative transfer program used, LIME (Brinch \&Hogerheijde 2010), calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3D model.
+The method of selecting these points is given in the griding section (NOTE: WHERE IS THE GRIDING SECTION?).
+At each of these points, the density of the main collision partner (H$_2$), gas and dust temperatures, velocity, molecular abundances and turbulent velocity are taken from the model.
 These points are then smoothed by Lloyds algorithm (Lloyd 1982) in order to minimise the variation in distance between points whilst keeping the same underlying distribution.
-These points are then connected by Delaunay triangulation and it is down these paths that photons are restricted to propagating (figures \ref{grid}).
-The levels of molecules in question are then  calculated at each of these points from collisional and radiative (de)excitation and the local radiation field is calculated.
+These points are then connected by Delaunay triangulation (NOTE: YOU NEED TO EXPLAIN THIS - MAYBE IN A FOOTNOTE) and it is down these paths that photon propagation is restricted (figures \ref{grid}).
+The level populations of the selected molecules are calculated at each of these points from collisional and radiative (de)excitation and the local radiation field is calculated.
 This is repeated 20 times with the populations of each level converging towards a single value.\newline
@@
 
-In order to construct the grid, points are randomly selected from the volume being simulated then compared against a reference point.
+In order to construct the grid, points are randomly selected from the volume, then compared against a reference point (NOTE: WHAT IS THE COMPARISON FOR?).
 Grid points are selected at random in cylindrical co-ordinates, linearly spaced in z and $\phi$ and logarithmically spaced in r.
-For each point to be selected a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) as a threshold.
-After selection of random co-ordinates the Hydrogen density and molecular density at the point (n and m) are compared against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$).
+For each point to be selected, a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) as a threshold.
+After selection of random co-ordinates, the hydrogen density and molecular density at the point (n and m, respectively) are compared against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$).
 If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use, if not then another r, $\phi$, z co-ordinate is selected.
-The weighting function and griding functions were selected empirically to sample both the all scales while ensuring the majority of the points went into the inner disc which is the region of interest.
+The weighting function and griding functions (NOTE: CAN YOU PLEASE EXPLAIN WHAT A GRIDING FUNCTION IS?) were selected empirically to sample all the scales while ensuring that the majority of points are located into the inner disc (where the density is higher --IS THIS LAST STATEMENT, WHICH I JUST ADDED, CORRECT?).
 20\% of these points are forced to be at radii greater than $\sqrt{R_{min}R_{max}}$ (where $R_{min}$ and $R_{max}$ are the inner and outer radius of the model) in order to stop too many of the selecected points clustering in the high density disc and leaving the envelope undersampled.
-In addiation to this method of selection 5\% of the points are linearly distributed in x, y and z with no bias with regards to density or abundance.
+In addiation to this method of selection, 5\% of the points are linearly distributed in x, y and z with no bias with regards to density or abundance.
 This provides a minimum level of sampling for the large low density regions in the outer parts of the simulated volume.
@@
 
-\section{Model Results}
+\section{Model Results} \label{sec:model_results}
 
+NOTE: YOU NEED TO ADD A LITTLE HISTORY ON WHY YOU SELECTED THESE SPECIES TO DO THE RADIATIVE TRANSFER. CAN YOU PLEASE RESTRUCTURE THIS SECTION ?
 %Figures showing the RT results in a few molecules/transitions (CO, HCO$^+$, HCN, OCS, H2CO, NH3 --- maybe H2O,H2$^{18}$O [to try first])
@@
 
-\section{ALMA Predictions}
+\section{ALMA Predictions} \label{sec:alma_predictions}
 
@@
 
-\section{Discussion}
+\section{Discussion and conclusions} \label{sec:discussion}
 

### 2012-11-29 paper.tex

@@
 
-1. description of what has been done so far on the modelling and radiative transfer of disks (this includes also more evolved disks -- Visser et al., Walsh et al., Aikawa et al. ..)
-2. focus on the young disks (work done by Machida et al., Dapp, Basu \& Kunz 2012, .. for their formation; work by Boley et al. on the physical evolution ; Ilee et al. for chemistry) 
-3.
-previous attempts to observe these young disks: (a) simulations (Cossins et al.
-2010); (b) observations: Fuente et al.
-2010 (AB Aur); Jorgensen \& van Dishoeck (H$_2^{18}$O and the HDO/H$_2$O ratio); Pineda et al.
-(2012); other papers talking about "hot corinos" (Bottinelli et al.
-....)
+The formation and early evolution of protoplanetary disks around solar-type and low-mass protostars has little observational support, despite of the fast growing list of theoretical models on the dynamical evolution of star forming dense cores (e.g.
+Krasnopolsky et al.
+2011; Machida et al.
+2011; Braiding \& Wardle 2012).
+The reason for this is that young protostars are surrounded by thick envelopes and power energetic outflows, thus observations of the young disks, predicted to have sizes of about 100\,AU and masses as large as 10\% the original core mass (e.g.
+Joos et al.
+2012), are challenging.
+The use of sensitive interferometers is needed to achieve high angular resolution and spatially/spectrally disentangle the various (disk + envelope + outflow) components as well to filter out the extended emission tracing envelope material.
 
-\section{Description of the Model}
+After the pioneer work of, e.g., Chandler et al.
+(1995), Brown et al.
+(2000), Looney et al.
+(2000), recent interferometric observations have discovered compact embedded disks in a sample of Class 0 (Andr\'e et al.
+2000) sources, finding masses between 0.4 and  $>$1 M$_{\odot}$ (Jorgensen et al.
+2007, 2009; Enoch et al.
+2011).
+A 130\,AU disk was discovered toward a Class 0 source in Perseus, using Jansky Very Large Array (JVLA) observations of NH$_3$ (Choi et al.
+2007).
+Pineda et al.
+(2012) observed methyl formate with the Atacama Millimeter and sub-millimeter Array (ALMA) and found evidence of rotation toward one of the proto-binary Class 0 sources embedded in IRAS 16293-2422.
+These observations are consistent with an almost edge-on disk.
+When ALMA will be completed, it will be finally possible to spatially resolve these young disks and, for the first time, put stringent constraints on theoretical models.
+As full-operational ALMA is fast approaching, it is important to provide observational predictions based on dynamical models of young protoplanetary disks.
 
-%-describe the envelope structure (pre-stellar core)
-The physical and chemical models used to simulate the emission from a young protoplanetary disc is a hybrid model created from hydrodynamical models of an infalling prestellar core and a gravitationally unstable protoplanetary disc.
-The prestellar core model is based upon the model of Keto \& Caselli (2010).
-This describes an infalling pre-stellar core, with densities temperatures and velocities given by the model of the collapse of a 10 solar mass Bonnor-Ebert sphere and provides a match to line profiles seen in the pre-stellar core L1544.
-Some slight modification due to the addition of Oxygen lines (Keto et al 2012 in prep) have been been added to this model resulting in a slight decrease in the peak infall velocity.
-This prestellar core model extends from 80$\,$au out to 10,000$\,$AU.
-The model is a 1D spherically symmetric model with inward motions (see figure \ref{l1544model}).\newline
+In this paper, we focus our attention to the young self-gravitating disks of Boley \& Durisen (2008), where episodic heating induced by spiral shocks is present, as this may be a good representation of the earliest phases of protoplanetary disks and an alternative to the young "static" disks studied by, e.g.
+Visser et al.
+(2009, 2011).
+As shown by Ilee et al.
+(2011), the spiral shocks cause desorption of volatiles from dust icy mantles and trigger gas-phase chemical reactions with activation energies, which are inactive at lower temperatures.
+These processes produce clear chemical signatures of the disk dynamics.
+With the use of 3D radiative transfer modeling, we perform simulated ALMA observations of the disk studied by Ilee et al.
+(2011) and identify the best tracers of the physical structure of self-gravitating disks.
+The physical, chemical and radiative transfer models are described in Sect\,\ref{sec:description_model}.
+Radiative transfer results are in Sect.\,\ref{sec:model_results}, while ALMA simulated observations are in Sec.\,\ref{sec:alma_predictions}.
+Discussions and conclusions can be found in Sect.\,\ref{sec:discussion}.
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/model/L1544model_used.png}
- \label{L1544}
- \caption{Model of the prestellar core L1544 used as the envelope in the hybrid model.
-Showing temperature and dust temperature (red, green) in kelvin, log number density (blue) in cm$^{-3}$ and inward velocity$\times$100 (cyan) in m$\,$s$^{-1}$.
-Adapted from Keto \& Caselli (2010)}
-\end{figure}
+\section{Description of the Model} \label{sec:description_model}
+
+\subsection{Physical and chemical structure} \label{subsec:physical_structure}
+
+The physical model used to simulate the emission from a young protoplanetary disc is a hybrid model obtained from embedding a gravitationally unstable protoplanetary disk  within an envelope with characteristics similar to the well-studied pre-stellar core L1544, as derived by Keto \& Caselli (2010; hereafter KC2010).
+The KC2010 model follows the dynamical, chemical and thermal evolution of a contracting Bonnor-Ebert (Bonnor 1956; Ebert 1957) sphere with total mass of 10\,M$_{\odot}$, until it reaches the density, temperature and velocity profiles which best match observations.
+The pre-stellar core model adopted here contains slight modifications due to the inclusion of oxygen cooling in the outer regions of the cloud, where CO is mostly photodissociated (Keto et al., in preparation), and it is shown in Fig.\,\ref{fig:l1544_model}.
+\newline
 
@@
 \begin{figure}
+ \includegraphics[width=84mm]{Figures/model/L1544model_used.png}
+ \label{fig:l1544_model}
+ \caption{Model of the pre-stellar core L1544 used as the envelope of the young protoplanetary disk in the hybrid model.
+Showing temperature (red) and dust (green) temperature in kelvin, log number density (blue) in cm$^{-3}$ and inward velocity$\times$100 (cyan) in m$\,$s$^{-1}$.
+Adapted from Keto \& Caselli (2010) and Keto et al.
+(2012, in preparation).}
+\end{figure}
+
+\begin{figure}
  \includegraphics[width=84mm]{Figures/model/rotational_velocities.png}
@@
 These abundances were interpolated onto a 51$^3$ grid covering the disc with cells of size 2.2$\times$2.2$\times$0.22$\,$au.
-Abundances in the envelope model were as follows:\newline
+Fig.
+XX shows a sample of column density maps from Ilee et al.
+(2011), pointing out the different regions traced by H$_2$CO and OCS, which mostly probe the central warm regions, and HCO$^+$, which preferentially trace the outer spiral pattern as in the central region is destroyed by water molecules (see Ilee et al.
+2011 for details).
+The simple chemistry in the KC2010 model, adopted here as the envelope of the protoplanetary disk, does not provide detailed abundances of molecular species (besides CO and H$_2$O, see also Caselli et al.
+2012).
+As discussed in the result section (Sec.\,\ref{sec:model_results}), rough guesses have been made based on values measured toward similar object.
+
+%NOTE: WE SHOULD TALK ABOUT THESE SPECIES AFTER WE SHOW WHICH SPECIES WE SELECT FOR THE RADIATIVE TRANSFER. 
+%Abundances in the envelope model were as follows:\newline
 
 %(tableify this?)
-HCO$^+$: As the H$_2$O profile from Caselli et al. (2012, submitted) scaled so that the maximum abundance is 10$^{-8}$\newline
-HNO: Constant abundance of 5$\times$10$^{-11}$\newline
-HCS$^+$: Constant abundance of 10$^{-11}$\newline
-OCS: Constant abundance of 10$^{-9}$\newline
-H$_2$CO: 1.5$\times$10$^{-9}$ decreased by a factor of 40 at radii less than 8250au (Young et al 2004)\newline
-CS:  3$\times$10$^{-9}$ decreased by a factor of 10,000 at radii less than 6700au (Tafalla, santiago-garcia and myers 2006)\newline
-CO: As the H2O profile from Caselli (2012, submitted) scaled so that the maximum abundance is CO maximum ***which is....***\newline
+%HCO$^+$: As the H$_2$O profile from Caselli et al. (2012, submitted) scaled so that the maximum abundance is 10$^{-8}$\newline
+%HNO: Constant abundance of 5$\times$10$^{-11}$\newline
+%HCS$^+$: Constant abundance of 10$^{-11}$\newline
+%OCS: Constant abundance of 10$^{-9}$\newline
+%H$_2$CO: 1.5$\times$10$^{-9}$ decreased by a factor of 40 at radii less than 8250au (Young et al 2004)\newline
+%CS:  3$\times$10$^{-9}$ decreased by a factor of 10,000 at radii less than 6700au (Tafalla, santiago-garcia and myers 2006)\newline
+%CO: As the H2O profile from Caselli (2012, submitted) scaled so that the maximum abundance is CO maximum ***which is....***\newline
 
+\subsection{The radiative transfer code} \label{subsec:radiative_transfer_code}
 %-describe the RT used (LIME) 
-The radiative transfer program used, LIME (Brinch 2011), calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3d model.
+The radiative transfer program used, LIME (Brinch \&Hogerheijde 2010), calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3D model.
 The method of selecting these points is given in the griding section.
-At each of these points the density of the main collision partner (in this case H$_2$), gas and dust temperatures, velocity, molecular abundances and turbulent velocity and taken from the model.
+At each of these points, the density of the main collision partner (H$_2$), gas and dust temperatures, velocity, molecular abundances and turbulent velocity are taken from the model.
 These points are then smoothed by Lloyds algorithm (Lloyd 1982) in order to minimise the variation in distance between points whilst keeping the same underlying distribution.
-These points are then connected by Delaunay triangulation and it is down these paths that photons are restricted to propagating (figures \ref{grid}).
-The levels of molecules in question are then  calculated at each of these points from collisional and radiative (de)excitation and the local radiation field is calculated.
-This is repeated 20 times with the populations of each level converging towards a single value.\newline
+These points are then connected by Delaunay triangulation \footnote{In three dimensions this means that if four points are conneted into a tetrahedron, the sphere circumscribing these four points contains no other points.
+It can be shown that this connection is unique for a given set of points.} and it is down these paths that photon propagation is restricted (figures \ref{grid}).
+The level populations of the selected molecules are calculated at each of these points from collisional and radiative (de)excitation and the local radiation field is calculated.
+This is repeated 20 times with the populations of each level converging towards a single value.
+This number of iterations is sufficient for the signal to noise ratio of the level populations (as defined in Brinch \&Hogerheijde 2010) to exceed 1000 in 99\% of the points \newline
 
@@
  \label{points}
- \caption{A histogram of the point distribution throughout the model.}
+ \caption{A histogram of the point distribution throughout the model. The disc and envelope can be seen as two separate entities which have to be sampled using different point distributions}
 \end{figure}
 
-In order to construct the grid, points are randomly selected from the volume being simulated then compared against a reference point.
+\subsection{Grid Construction} \label{subsec:gridding}
+In order to construct the grid, points are randomly selected from the volume, then compared against a reference point.
 Grid points are selected at random in cylindrical co-ordinates, linearly spaced in z and $\phi$ and logarithmically spaced in r.
-For each point to be selected a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) as a threshold.
-After selection of random co-ordinates the Hydrogen density and molecular density at the point (n and m) are compared against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$).
+For each point to be selected, a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) as a threshold.
+After selection of random co-ordinates, the hydrogen density and molecular density at the point (n and m, respectively) are compared against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$).
 If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use, if not then another r, $\phi$, z co-ordinate is selected.
-The weighting function and griding functions were selected empirically to sample both the all scales while ensuring the majority of the points went into the inner disc which is the region of interest.
+The weighting function and point distribution were selected empirically to sample all the scales while ensuring that the majority of points are located in the inner disc where the density is higher.
 20\% of these points are forced to be at radii greater than $\sqrt{R_{min}R_{max}}$ (where $R_{min}$ and $R_{max}$ are the inner and outer radius of the model) in order to stop too many of the selecected points clustering in the high density disc and leaving the envelope undersampled.
-In addiation to this method of selection 5\% of the points are linearly distributed in x, y and z with no bias with regards to density or abundance.
+In addiation to this method of selection, 5\% of the points are linearly distributed in x, y and z with no bias with regards to density or abundance.
 This provides a minimum level of sampling for the large low density regions in the outer parts of the simulated volume.
-See figure \ref{points} for example of the points distribution in r, z.
+See figure \ref{points} for an example of the points distribution in r, z.
 \newline
@@
 
- \caption{HCO$^+$ 1-0 pv through centre}
+ \caption{HCO$^+$ 1-0 pv through centre, with the rotation curve from figure \ref{velocity} for comparison}
 \end{figure}
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageHCOp_3-2_30deg_PV_centre_2.png}
- \label{hcop_pv}
- \caption{HCO$^+$ 3-2 PV through centre with rotation curve from figure \ref{velocity} *** should the velocities in this be reduced by cos(30) as we're not in the plane of rotation? ***}
-\end{figure}
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/imageHCOp_3-2_30deg_PV_centre_2.png}
+% \label{hcop_pv}
+% \caption{HCO$^+$ 3-2 PV through centre with rotation curve from figure \ref{velocity} *** should the velocities in this be reduced by cos(30) as we're not in the plane of rotation? ***}
+%\end{figure}
 

### 2012-12-03 paper.tex
3/12/12

@@
 \author[Tom  Douglas, Paola Caselli, Et al.]{Tom Douglas$^{1}$\thanks{E-mail:
-pytd@leeds.ac.uk}, Paola Caselli$^{1}$\\
+pytd@leeds.ac.uk}, Paola Caselli$^{1}$, Et al.\\
 $^{1}$School of Physics and Astronomy, University of Leeds, Leeds LS2 9JT, UK}
@@
 \subsection{Grid Construction} \label{subsec:gridding}
-In order to construct the grid, points are randomly selected from the volume, then compared against a reference point.
+In order to construct the grid, points are randomly selected from the volume then have the density and molecular density at the point compared against a reference point in order to decide if the point is to be accepted or not.
 Grid points are selected at random in cylindrical co-ordinates, linearly spaced in z and $\phi$ and logarithmically spaced in r.
@@
 
-NOTE: YOU NEED TO ADD A LITTLE HISTORY ON WHY YOU SELECTED THESE SPECIES TO DO THE RADIATIVE TRANSFER. CAN YOU PLEASE RESTRUCTURE THIS SECTION ?
+Simulated molecules were confined to speices where the chemical abundance in the disc and envelope are known, or have simulated abundances.
+In addition radative transfer simulations are limited to are limited to molecules where the collisional and Einstein co-efficients are known.
+Lines for these molecules were simulated with LIME for freqencies 50$\sim$500$\,$GHz, with focus on lines which could be observed in ALMA band 7.
+The results presented in this section represent those lines which show dectectable emission/absorption which can be used to trace either spiral structure or rotation.\newline
+
 %Figures showing the RT results in a few molecules/transitions (CO, HCO$^+$, HCN, OCS, H2CO, NH3 --- maybe H2O,H2$^{18}$O [to try first])
 The results of these simulations for the molecules OCS, HCO$^+$, H$_2$CO and isotopologues of CO are shown here, other molecules simulated but not shown include HCN, HNC, HNO, HCS$^+$ and  CS.
-For the purpose of simulating observations the model was placed at roughly the distance of nearby low-mass star forming regions (100$\,$pc) and is inclined 30$^\circ$ to edge on.
+For the purpose of simulating observations the model was placed at roughly the distance of nearby low-mass star forming regions (100$\,$pc) and is inclined at 30$^\circ$ to edge on.
 From these observations integrated intensity, intensity weighted velocity and position velocity diagrams through the centre of the model were created.
-The simulations done are focused upon frequencies within ALMA band 7, selected to give the best trade off between resolution and sensitivity for early ALMA science.
+The simulations done are focused upon frequencies within ALMA band 7, selected to give the best trade off between resolution and sensitivity for early ALMA science {\bf IS BAND 7 STILL THE BEST FOR US TO LOOK AT SEEING AS WE ARE NOW LOOKING AT ALMA FULL CAPABILITY RATHER THAN CYCLE1?}.
 (Note the moment 1 and 0 maps were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in some PV diagrams as the strong absorption feature at all positions around zero velocity, moment 1 maps are shown with a cutoff of 1/1000 of the peak emission/absorption value)\newline
@@
 Some indications of spiral structure can be seen but are indistinct.
-***not sure how useful these are, might be worth cutting them?***\newline
+{\bf not sure how useful these are, might be worth cutting them?}\newline
 
@@
 The order of magnitude difference in the line intensity provides a method to detect hot dense gas without being able to resolve the spiral structure spatially.\newline
-
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imagesmoothedOCS_28-27_30deg_contSub.png}
- \label{smoothOCS_mom0}
- \caption{SmoothedOCS 28-27 Continuum subtracted mom0}
-\end{figure}
+%
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/imagesmoothedOCS_28-27_30deg_contSub.png}
+% \label{smoothOCS_mom0}
+% \caption{SmoothedOCS 28-27 Continuum subtracted mom0}
+%\end{figure}
 
@@
 
-More complex molecules such as H$_2$CO with many closely spaced spectral lines can be used to gain an estimate on the temperature of a region.
-
-(figure of temperature as a function of line ratio for 2 sets of formaldehyde lines and map of derived temperature, talk to P about this.
-This doesn't seem doable with the lines around 1mm for alma)\newline
+More complex molecules such as H$_2$CO with many closely spaced spectral lines can be used to gain an estimate on the temperature of a region.\newline
 
@@
 In these colder less dense regions we see the molecular lines in emission rather than absorption.
-Figure \ref{hcop_pv} shows the rotation curve of the model as shown in figure \ref{velocity} against the HCO$^+$ J=3-2 line emission.
+Figure \ref{hcop_pv} shows the rotation curve of the model as shown in figure \ref{velocity} against the HCO$^+$ J=1-0 line emission.
 It is clear that from observations such as these the rotation curve of a disc could be reconstructed.\newline
-\newline
 
-In all the simulations except HCO$^+$ we see molecular lines in absorption throughout the majority of the disc and in some cases a small amount of emission towards the centre, where the inclination of the disc allows us the view the low density but moderate temperature region inside the inner edge of the spiral structures without any high temperature and density material behind it.\newline
+In all the simulations except HCO$^+$ we see molecular lines in absorption throughout the majority of the disc and in some cases a small amount of emission towards the centre.
+Molecular lines throughout the plane of the disc show up in absorption against the continuum emission of the shock heated, dense midplane.
 
@@
 The quiescent nature of the envelope around such discs only obscures them within $\pm\,0.5 km\,s^{-1}$.\newline
-Hot, shocked gas can be detected in such a disc without resolving it by observing OCS transitions between 26-27 to 30-29.\newline
 One assumption made in this model is that the gas and dust are in thermal equilibrium.If they are not and the dust is significantly cooler than the gas then transitions may not show up in absorption.\newline
-The mass of the disc used (0.4$\,\rm{M}_\odot$) is on the high end for early discs (citations for estimate of early class 1 disc masses).\newline 
+%The mass of the disc used (0.4$\,\rm{M}_\odot$) is on the high end for early discs (citations for estimate of early class 1 disc masses).\newline
 In the model spirals shock heat the mid-plane layer and the colder more diffuse gas absorbs the continuum from it, this results in molecular lines being seen in absorbtion whenever lines of sight pass through the cold diffuse gas at larger heights on to the hot dense midplane of the disc.
 Rotation curves can be gathered from these observations even with spiral structure\newline
+Outflows could contaminate measurements of rotation curves meaning that speices  which commonly trace outflows, such as C$^{16}$O and HC$^{16}$O$^+$ are not going to be good tracers of disc rotation.
+However speices such as OCS and C$^{18}$O which are not seen in outflows can be used to trace disc rotation.
 
@@
 
-%
-%(This appendix was not part of the original paper by
-%A.V.~Raveendran and is included here just for illustrative
-%purposes. The references are not relevant to the text of the
-%appendix, they are references from the bibliography used to
-%illustrate text before and after citations.)
-%
-%Spectroscopic observations of bright quasars show that the mean
-%number density of Ly$\alpha$ forest lines, which satisfy certain
-%criteria, evolves like $\rmn{d}N/\rmn{d}z=A(1+z)^\gamma$, where
-%$A$ and~$\gamma$ are two constants.  Given the above intrinsic
-%line distribution we examine the probability of finding large gaps
-%in the Ly$\alpha$ forests.  We concentrate here only on the
-%statistics and neglect all observational complications such as the
-%line blending effect \citep[see][for example]{b11}.
-%
-%Suppose we have observed a Ly$\alpha$ forest between redshifts $z_1$
-%and~$z_2$ and found $N-1$ lines.  For high-redshift quasars $z_2$~is
-%usually the emission redshift $z_{\rmn{em}}$ and $z_1$ is set to
-%$(\lambda_{\rmn{Ly}\beta}/\lambda_{\rmn{Ly}\alpha})(1+z_{\rmn{em}})=0.844
-%(1+z_{\rmn{em}})$ to avoid contamination by Ly$\beta$ lines.  We
-%want to know whether the largest gaps observed in the forest are
-%significantly inconsistent with the above line distribution.  To do
-%this we introduce a new variable~$x$:
-%%
-%\begin{equation}
-%x={(1+z)^{\gamma+1}-(1+z_1)^{\gamma+1} \over
-%     (1+z_2)^{\gamma+1}-(1+z_1)^{\gamma+1}}.
-%\end{equation}
-%%
-%$x$ varies from 0 to 1.  We then have $\rmn{d}N/\rmn{d}x=\lambda$, where $\lambda$
-%is the mean number of lines between $z_1$ and $z_2$ and is given by
-%%
-%\begin{equation}
-%\lambda\equiv{A[(1+z_2)^{\gamma+1}-(1+z_1)^{\gamma+1}]\over\gamma+1}.
-%\end{equation}
-%%
-%This means that the Ly$\alpha$ forest lines are uniformly
-%distributed in~$x$. The probability of finding $N-1$ lines between $z_1$
-%and~$z_2$, $P_{N-1}$, is assumed to be the Poisson distribution.
-%%
-%\newpage
-%%
-%\begin{figure}
-%\vspace{11pc}
-%\caption{$P(>x_{\rmn{gap}})$ as a function of $x_{\rmn{gap}}$ for,
-% from left to right, $N=160$, 150, 140, 110, 100, 90, 50, 45 and~40.
-% Compare this with \protect\citet{b15}.}
-%\label{appenfig}
-%\end{figure}
-%
-%\subsection{Subsection title}
-%
-%We plot in Fig.~\ref{appenfig} $P(>x_{\rmn{gap}})$ for several $N$
-%values. We see that, for $N=100$ and $x_{\rmn{gap}}=0.06$,
-%$P(>0.06)\approx20$ per cent.  This means that the probability of
-%finding a gap with a size larger than six times the mean
-%separation is not significantly small. When the mean number of
-%lines is large, $\lambda\sim N>>1$, our $P(>x_{\rmn{gap}})$
-%approaches the result obtained by \citet[fig. 4]{b22} for small
-%(but still very large if measured in units of the mean separation)
-%$x_{\rmn{gap}}$, i.e., $P(>x_{\rmn{gap}})\sim N(1-
-%x_{\rmn{gap}})^{N-1}\sim N {\rmn{exp}}(-\lambda x_{\rmn{gap}})$.
-%
 \bsp

### 2012-12-04 paper.tex
changes to tex file

@@
 
-\title[Simulated observations of young protoplanetary disks]{Young protoplanetary disks}
+\title[Simulated observations of young protoplanetary discs]{Young protoplanetary discs}
 \author[Tom  Douglas, Paola Caselli, Et al.]{Tom Douglas$^{1}$\thanks{E-mail:
@@
 
-The formation and early evolution of protoplanetary disks around solar-type and low-mass protostars has little observational support, despite of the fast growing list of theoretical models on the dynamical evolution of star forming dense cores (e.g.
+The formation and early evolution of protoplanetary discs around solar-type and low-mass protostars has little observational support, despite of the fast growing list of theoretical models on the dynamical evolution of star forming dense cores (e.g.
 Krasnopolsky et al.
@@
 2011; Braiding \& Wardle 2012).
-The reason for this is that young protostars are surrounded by thick envelopes and power energetic outflows, thus observations of the young disks, predicted to have sizes of about 100\,AU and masses as large as 10\% the original core mass (e.g.
+The reason for this is that young protostars are surrounded by thick envelopes and power energetic outflows, thus observations of the young discs, predicted to have sizes of about 100\,AU and masses as large as 10\% the original core mass (e.g.
 Joos et al.
 2012), are challenging.
-The use of sensitive interferometers is needed to achieve high angular resolution and spatially/spectrally disentangle the various (disk + envelope + outflow) components as well to filter out the extended emission tracing envelope material.
+The use of sensitive interferometers is needed to achieve high angular resolution and spatially/spectrally disentangle the various (disc + envelope + outflow) components as well to filter out the extended emission tracing envelope material.
 
@@
 (2000), Looney et al.
-(2000), recent interferometric observations have discovered compact embedded disks in a sample of Class 0 (Andr\'e et al.
+(2000), recent interferometric observations have discovered compact embedded discs in a sample of Class 0 (Andr\'e et al.
 2000) sources, finding masses between 0.4 and  $>$1 M$_{\odot}$ (Jorgensen et al.
@@
 2011).
-A 130\,AU disk was discovered toward a Class 0 source in Perseus, using Jansky Very Large Array (JVLA) observations of NH$_3$ (Choi et al.
+A 130\,AU disc was discovered toward a Class 0 source in Perseus, using Jansky Very Large Array (JVLA) observations of NH$_3$ (Choi et al.
 2007).
@@
 (2012) observed methyl formate with the Atacama Millimeter and sub-millimeter Array (ALMA) and found evidence of rotation toward one of the proto-binary Class 0 sources embedded in IRAS 16293-2422.
-These observations are consistent with an almost edge-on disk.
-When ALMA will be completed, it will be finally possible to spatially resolve these young disks and, for the first time, put stringent constraints on theoretical models.
-As full-operational ALMA is fast approaching, it is important to provide observational predictions based on dynamical models of young protoplanetary disks.
+These observations are consistent with an almost edge-on disc.
+When ALMA will be completed, it will be finally possible to spatially resolve these young discs and, for the first time, put stringent constraints on theoretical models.
+As full-operational ALMA is fast approaching, it is important to provide observational predictions based on dynamical models of young protoplanetary discs.
 
-In this paper, we focus our attention to the young self-gravitating disks of Boley \& Durisen (2008), where episodic heating induced by spiral shocks is present, as this may be a good representation of the earliest phases of protoplanetary disks and an alternative to the young "static" disks studied by, e.g.
+In this paper, we focus our attention to the young self-gravitating discs of Boley \& Durisen (2008), where episodic heating induced by spiral shocks is present, as this may be a good representation of the earliest phases of protoplanetary discs and an alternative to the young "static" discs studied by, e.g.
 Visser et al.
@@
 (2011), the spiral shocks cause desorption of volatiles from dust icy mantles and trigger gas-phase chemical reactions with activation energies, which are inactive at lower temperatures.
-These processes produce clear chemical signatures of the disk dynamics.
-With the use of 3D radiative transfer modeling, we perform simulated ALMA observations of the disk studied by Ilee et al.
-(2011) and identify the best tracers of the physical structure of self-gravitating disks.
+These processes produce clear chemical signatures of the disc dynamics.
+With the use of 3D radiative transfer modeling, we perform simulated ALMA observations of the disc studied by Ilee et al.
+(2011) and identify the best tracers of the physical structure of self-gravitating discs.
 The physical, chemical and radiative transfer models are described in Sect\,\ref{sec:description_model}.
@@
 
-The physical model used to simulate the emission from a young protoplanetary disc is a hybrid model obtained from embedding a gravitationally unstable protoplanetary disk  within an envelope with characteristics similar to the well-studied pre-stellar core L1544, as derived by Keto \& Caselli (2010; hereafter KC2010).
+The physical model used to simulate the emission from a young protoplanetary disc is a hybrid model obtained from embedding a gravitationally unstable protoplanetary disc  within an envelope with characteristics similar to the well-studied pre-stellar core L1544, as derived by Keto \& Caselli (2010; hereafter KC2010).
 The KC2010 model follows the dynamical, chemical and thermal evolution of a contracting Bonnor-Ebert (Bonnor 1956; Ebert 1957) sphere with total mass of 10\,M$_{\odot}$, until it reaches the density, temperature and velocity profiles which best match observations.
@@
  \label{fig:l1544_model}
- \caption{Model of the pre-stellar core L1544 used as the envelope of the young protoplanetary disk in the hybrid model.
+ \caption{Model of the pre-stellar core L1544 used as the envelope of the young protoplanetary disc in the hybrid model.
 Showing temperature (red) and dust (green) temperature in kelvin, log number density (blue) in cm$^{-3}$ and inward velocity$\times$100 (cyan) in m$\,$s$^{-1}$.
@@
 
-%-describe the physical structure of the disk (density and temperature) -- one figure showing the physical structure and the kinematics (2-panels figure)
-The pre-stellar core structure is maintained down to a radius of 80\,AU, within which the young protoplanetary disk has been plugged in.
-The disk structure is derived by the hydrodynamic model of Boley(2007) and Boley (2009).
+%-describe the physical structure of the disc (density and temperature) -- one figure showing the physical structure and the kinematics (2-panels figure)
+The pre-stellar core structure is maintained down to a radius of 80\,AU, within which the young protoplanetary disc has been plugged in.
+The disc structure is derived by the hydrodynamic model of Boley(2007) and Boley (2009).
 The particular model considered here (as well as in Ilee et al.
@@
 2011 for details).
-The simple chemistry in the KC2010 model, adopted here as the envelope of the protoplanetary disk, does not provide detailed abundances of molecular species (besides CO and H$_2$O, see also Caselli et al.
+The simple chemistry in the KC2010 model, adopted here as the envelope of the protoplanetary disc, does not provide detailed abundances of molecular species (besides CO and H$_2$O, see also Caselli et al.
 2012).
@@
 In addition radative transfer simulations are limited to are limited to molecules where the collisional and Einstein co-efficients are known.
-Lines for these molecules were simulated with LIME for freqencies 50$\sim$500$\,$GHz, with focus on lines which could be observed in ALMA band 7.
+Lines for these molecules were simulated with LIME for freqencies 50$\sim$500$\,$GHz, with focus on lines which could be observed in ALMA band 7 and molecules which are not typically seen in outflows, which havent been included in these simulations and could potentially contaminate disc observations.
 The results presented in this section represent those lines which show dectectable emission/absorption which can be used to trace either spiral structure or rotation.\newline
@@
 
-%- current status (Cycle 1) - Figure
-%OCS + C18O + H2CO + HNO/CS/
-%- final status - Figure
+In order to make predictions on the observability of the synthetic brightness maps created by LIME, CASA (common astronomy software applications) was used to simulate observing these with the completed ALMA in it's most extended comfiguration for a total time of four hours.
 
@@
 
- \caption{continuum emission at 337GHz simulated for ALMA most extended configuration}
+ \caption{Continuum emission at 337GHz simulated for ALMA most extended configuration}
 \end{figure}
@@
 \begin{figure}
- \includegraphics[width=54mm]{Figures/sim/casa_OCS_28-27_pv.png}
+ \includegraphics[width=54mm]{Figures/sim/casa_imageOCS_28-27_30deg_composite_ALMAwidth_big_dirty_PV_centre.png}
 
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/casa_OCS_28-27_mom0.png}
+ \includegraphics[width=84mm]{Figures/sim/casa_imageOCS_28-27_30deg_composite_ALMAwidth_big_dirty_contSub.png}
 
@@
 \begin{figure}
- \includegraphics[width=54mm]{Figures/sim/casa_C17O_3-2_pv.png}
+ \includegraphics[width=54mm]{Figures/sim/casa_imageC17O_3-2_30deg_composite_ALMAwidth_dirty_PV_centre.png}
 
@@
  \caption{C17O 3-2 30 deg integrated intensity simulated for ALMA most extended configuration}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=63mm]{Figures/sim/casa_imageHCOp_1-0_30deg_composite_ALMAwidth_dirty_PV_centre.png}
+
+ \caption{HCO$^+$ 1-0 30 deg PV through centre simulated for ALMA most extended configuration}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/casa_imageHCOp_1-0_30deg_composite_ALMAwidth_dirty_contSub.png}
+
+ \caption{HCO$^+$ 1-0 30 deg integrated intensity simulated for ALMA most extended configuration}
 \end{figure}
@@
 Rotation curves can be gathered from these observations even with spiral structure\newline
-Outflows could contaminate measurements of rotation curves meaning that speices  which commonly trace outflows, such as C$^{16}$O and HC$^{16}$O$^+$ are not going to be good tracers of disc rotation.
-However speices such as OCS and C$^{18}$O which are not seen in outflows can be used to trace disc rotation.
+Outflows could contaminate measurements of rotation curves meaning that speices  which commonly trace outflows, such as CO and HCO$^+$ are not going to be good tracers of disc rotation.
+However speices such as OCS and C$^{18}$O which are not commonly seen in outflows (Yildiz et al 2012,)can be used to trace disc rotation.
 

### 2012-12-13 paper.tex
added comments from paola, some new figure arrangements

@@
 
-\title[Simulated observations of young protoplanetary discs]{Young protoplanetary discs}
+\title[Young protoplanetary discs]{Simulated observations of young protoplanetary discs}
 \author[Tom  Douglas, Paola Caselli, Et al.]{Tom Douglas$^{1}$\thanks{E-mail:
-pytd@leeds.ac.uk}, Paola Caselli$^{1}$, Et al.\\
-$^{1}$School of Physics and Astronomy, University of Leeds, Leeds LS2 9JT, UK}
+pytd@leeds.ac.uk}, Paola Caselli$^{1}$, Aaron Boley$^{2}$, Richard Durisen$^{3}$,\newline Tom Hartquist$^{1}$, John Ilee$^{1}$, Jonathon Rawlings$^{4}$ \\
+$^{1}$School of Physics and Astronomy, University of Leeds, Leeds LS2 9JT, UK \\
+$^{2}$Department of Astronomy, University of Florida, 211 Bryant Space Center, PO Box 112055, USA\\
+$^{3}$Department of Astronomy, Indiana University, 727 East 3rd Street, Swain West 319, Bloomington, IN 47405, USA\\
+%$^{4}$Department of Physics & Astronomy, University College London, London WC1E 6BT, UK\\
+}
 \begin{document}
@@
 \begin{abstract}
-Abstract here
+The formation and earliest stages of protoplanetary discs are still lacking observational constraints.
+ALMA will soon revolutionize this field, so it is important to provide predictions and help the interpretation of future high sensitivity and high angular resolution observations.
+Here we present simulated ALMA observations of a relatively massive (0.39 M$_{\odot}$) self-gravitating disc embedded in a 10\,M$_{\odot}$ envelope with a structure similar to the pre-stellar core L1544.
+We focus on simple species and conclude that OCS is among the best tracers to measure the disc structure and kinematics.
 \end{abstract}
@@
 These observations are consistent with an almost edge-on disc.
+Persson et al.
+(2012) observed H$_2^{18}$O with ALMA toward the same source and found evidence of relatively large ($\ga$100\,K) excitation temperatures, as well as a HDO/H$_2$O abundance ratio close to that measured on Earth's oceans and Jupiter-family comets (Hartogh et al.
+2011).
 When ALMA will be completed, it will be finally possible to spatially resolve these young discs and, for the first time, put stringent constraints on theoretical models.
@@
 The pre-stellar core model adopted here contains slight modifications due to the inclusion of oxygen cooling in the outer regions of the cloud, where CO is mostly photodissociated (Keto et al., in preparation), and it is shown in Fig.\,\ref{fig:l1544_model}.
-\newline
+[NOTE: BESIDES THE PROBLEM WITH THE FIGURE NUMBER, YOU NEED TO READJUST FIGURES, AS THIS ONE IS THE FIRST ONE THAT YOU DESCRIBE, SO IT SHOULD BE NUMBER 1] \newline
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/model/L1544model_used_legend.png}
+ \label{fig:l1544_model}
+ \caption{[NOTE: YOU NEED TO ADD LABELS AND UNITS TO THE AXES!!] Model of the pre-stellar core L1544 used as the envelope of the young protoplanetary disc in the hybrid model.
+Showing temperature (red) and dust (green) temperature in kelvin, log number density (blue) in cm$^{-3}$ and inward velocity$\times$100 (cyan) in m$\,$s$^{-1}$.
+Adapted from Keto \& Caselli (2010) and Keto et al.
+(2012, in preparation).}
+\end{figure}
 
@@
  \label{rhoT} 
- \caption{Left: A 3D plot of log number density (m$^{-3}$) showing the spiral structure in the xy plane and scale height of the disc.
+ \caption{Left: A 3D plot of log number density (cm$^{-3}$) showing the spiral structure in the xy plane and scale height of the disc.
 Right: The 3D temperature structure of the disc; regions cooler than 40 degrees are not shown in 3D, demonstrating the narrow central region containing hot material.}
@@
  \label{Chemistry} 
- \caption{Column densities of H$_2$CO, OCS and HCO$^+$ used in the disc model. Figure adapted from Ilee at al. (2011)}
+ \caption{Column densities of OCS, H$_2$CO and HCO$^+$ used in the disc model. Figure adapted from Ilee at al. (2011) [SHOULD WE ALSO ADD C18O COLUMN DENSITY AS WE WANT TO DISCUSS THAT LATER ?? ]}
 \end{figure*}
-
-\begin{figure}
- \includegraphics[width=84mm]{Figures/model/L1544model_used.png}
- \label{fig:l1544_model}
- \caption{Model of the pre-stellar core L1544 used as the envelope of the young protoplanetary disc in the hybrid model.
-Showing temperature (red) and dust (green) temperature in kelvin, log number density (blue) in cm$^{-3}$ and inward velocity$\times$100 (cyan) in m$\,$s$^{-1}$.
-Adapted from Keto \& Caselli (2010) and Keto et al.
-(2012, in preparation).}
-\end{figure}
 
@@
 2011) is a 0.39$\,\rm{M}_\odot$ self-gravitating disc featuring prominent spiral arms.
-H$_2$ number densities in the disc range from 10$^{10}$-10$^{19}\,\rm{m}^{-3}$, and temperatures range from 30-400 K (figure \ref{rhoT}).
+H$_2$ number densities in the disc range from 10$^{4}$-10$^{13}\,\rm{cm}^{-3}$, and temperatures range from 30-400 K (figure \ref{rhoT}).
 The dust and gas temperatures in the disc are assumed to be in equilibrium.
@@
 The gas/dust mass ratio was assumed to be 1/100 throughout both sections model and the opacities were given by the model of dust grains with thick icy mantles and 10$^6\,$yr coagulation from Ossenkopf and Henning (1994).
-THe gas number density and temperature structure are displayed in Fig.
+The gas number density and temperature structure are displayed in Fig.
 XX.
@@
 These abundances were interpolated onto a 51$^3$ grid covering the disc with cells of size 2.2$\times$2.2$\times$0.22$\,$au.
-Fig.
-XX shows a sample of column density maps from Ilee et al.
-(2011), pointing out the different regions traced by H$_2$CO and OCS, which mostly probe the central warm regions, and HCO$^+$, which preferentially trace the outer spiral pattern as in the central region is destroyed by water molecules (see Ilee et al.
-2011 for details).
+From Ilee et al.
+(2011) we selected the three species which appear to trace different regions of the disc : the inner 30\,AU (OCS), the inner 60\,AU (H$_2$CO) and the region between $\simeq$20 and 60\,AU (HCO$^+$) and one which traces the entirity of the disc (C$^{18}$O).
+As explained by Ilee et al.
+(2011),  H$_2$CO and OCS mostly probe the central warm regions, where icy mantles evaporate, whereas HCO$^+$ preferentially traces the outer spiral pattern as in the central region it is destroyed by water molecules.
 The simple chemistry in the KC2010 model, adopted here as the envelope of the protoplanetary disc, does not provide detailed abundances of molecular species (besides CO and H$_2$O, see also Caselli et al.
 2012).
-As discussed in the result section (Sec.\,\ref{sec:model_results}), rough guesses have been made based on values measured toward similar object.
+As discussed in the result section (Sec.\,\ref{sec:model_results}), rough guesses have been made based on values measured toward similar objects.
 
@@
 The radiative transfer program used, LIME (Brinch \&Hogerheijde 2010), calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3D model.
-The method of selecting these points is given in the griding section.
+The method of selecting these points is given in the grid-construction section.
 At each of these points, the density of the main collision partner (H$_2$), gas and dust temperatures, velocity, molecular abundances and turbulent velocity are taken from the model.
@@
 This is repeated 20 times with the populations of each level converging towards a single value.
-This number of iterations is sufficient for the signal to noise ratio of the level populations (as defined in Brinch \&Hogerheijde 2010) to exceed 1000 in 99\% of the points \newline
+This number of iterations is sufficient for the signal to noise ratio of the level populations (as defined in Brinch \&Hogerheijde 2010) to exceed 1000 in 99\% of the points.
+[NOTE: WHY DO WE NEED TO REACH SUCH A HIGH S/N?
+--- it isn't s/n in the usual sense, it's a measurement of how converged the model is, defined in brinch 2010 as change in populations this iteration / std-dev of change in pops over last 5 iterations] \newline
+After 20 iterations of updateing the level populations the model is ray-traced in order to produce synthetic brighness maps.
+In order to minimise the ``blockyness'' of the output images, resulting from the grid construction, the average of ten seperate runs was taken (figure \ref{averages}).
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/average_comparison.png}
+ \label{averages}
+ \caption{A plot showing the difference between a single LIME continuum image at 300$\,$GHz (right) and the average of ten such images from different runs of the same model in LIME (left).}
+\end{figure}
 
@@
  \label{points}
- \caption{A histogram of the point distribution throughout the model. The disc and envelope can be seen as two separate entities which have to be sampled using different point distributions}
-\end{figure}
-
-\subsection{Grid Construction} \label{subsec:gridding}
-In order to construct the grid, points are randomly selected from the volume then have the density and molecular density at the point compared against a reference point in order to decide if the point is to be accepted or not.
-Grid points are selected at random in cylindrical co-ordinates, linearly spaced in z and $\phi$ and logarithmically spaced in r.
-For each point to be selected, a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) as a threshold.
-After selection of random co-ordinates, the hydrogen density and molecular density at the point (n and m, respectively) are compared against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$).
-If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use, if not then another r, $\phi$, z co-ordinate is selected.
-The weighting function and point distribution were selected empirically to sample all the scales while ensuring that the majority of points are located in the inner disc where the density is higher.
-20\% of these points are forced to be at radii greater than $\sqrt{R_{min}R_{max}}$ (where $R_{min}$ and $R_{max}$ are the inner and outer radius of the model) in order to stop too many of the selecected points clustering in the high density disc and leaving the envelope undersampled.
-In addiation to this method of selection, 5\% of the points are linearly distributed in x, y and z with no bias with regards to density or abundance.
-This provides a minimum level of sampling for the large low density regions in the outer parts of the simulated volume.
-See figure \ref{points} for an example of the points distribution in r, z.
-\newline
-
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/average_comparison.png}
- \label{averages}
- \caption{A plot showing the difference between a single LIME continuum image at 300$\,$GHz (right) and the average of ten such images from different runs of the same model in LIME (left).}
+ \caption{A 2D histogram of the point distribution throughout the model. The disc and envelope can be seen as two separate entities which have to be sampled using different point distributions}
 \end{figure}
@@
 
-Simulated molecules were confined to speices where the chemical abundance in the disc and envelope are known, or have simulated abundances.
+[NOTE: I SUGGEST TO:
+
+1.
+SHOW THE MOMENT 0 AND 1 ONLY MAPS OF C18O, OCS, H2CO AND HCO+ + SPECTRA TOWARD THE CENTER AND +/- 30 AU (FOR EACH SPECIES, YOU CAN DO A 3-PANEL FIGURE SHOWING THE TWO MOMENTS AND A PANEL WITH THE 3 SPECTRA AT DIFFERENT LOCATIONS)
++  THE CONTINUUM MAP 
+3. SHOW THE SIMULATED ALMA OBSERVATIONS (SAME STYLE AS BEFORE) AND ALSO SHOW A SEPARATE FIGURE WITH THE PV DIAGRAMS OF ALL SPECIES. 
+]
+
+[NOTE: THE FOLLOWING PARAGRAPH IS NOT CLEAR AT ALL !!!
+PLEASE RE-WRITE MAKING SURE THAT THE SENTENCES MAKE SENSE AND THERE ARE NO TYPOS.
+PLEASE MAKE THE FIGURES AS SUGGESTED AND THEN RE-WRITE THIS PART.]
+%Simulated molecules were confined to speices where the chemical abundance in the disc and envelope are known, or have simulated abundances.
 In addition radative transfer simulations are limited to are limited to molecules where the collisional and Einstein co-efficients are known.
@@
 (Note the moment 1 and 0 maps were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in some PV diagrams as the strong absorption feature at all positions around zero velocity, moment 1 maps are shown with a cutoff of 1/1000 of the peak emission/absorption value)\newline
+%
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_contSub.png}
+%
+% \caption{CO J=3-2 Continuum subtracted mom0}
+%\end{figure}
+%
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_mom1.png}
+%
+% \caption{CO J=3-2 moment 1 map}
+ %\end{figure}
+%
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_PV_centre.png}
+%
+% \caption{CO J=3-2 PV through y=0''}
+%\end{figure}
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_contSub.png}
-
- \caption{CO J=3-2 Continuum subtracted mom0}
-\end{figure}
-
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_mom1.png}
-
- \caption{CO J=3-2 moment 1 map}
-\end{figure}
-
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_PV_centre.png}
-
- \caption{CO J=3-2 PV through y=0''}
-\end{figure}
-
-Figures 6,7 and 8 show synthetic images of the CO J=3-2 line at 345.8$\,$GHz.
+%Figures 6,7 and 8 show synthetic images of the CO J=3-2 line at 345.8$\,$GHz.
 As the upper level for this line is at 33$\,$K above the ground state this transition should be excited through out disc.
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageOCS_28-27_30deg_composite_contSub.png}
- \label{OCS_mom0}
- \caption{OCS 28-27 Continuum subtracted mom0}
+ \includegraphics[width=84mm]{Figures/sim/continuum.png}
+ \label{points}
+ \caption{A 300$\,$GHz continuum image of the model, created from the average of ten LIME runs.}
 \end{figure}
+
+\begin{figure*}
+ \includegraphics[width=168mm]{Figures/sim/imageOCS_28-27_30deg_composite_all.png}
+ \label{OCS_all}
+ \caption{OCS 28-27 {\bf Left:} Continuum subtracted integrated intensity map, {\bf Centre:} Continuum subtracted spectra from Y=0'', X=+0.1'' (bottom), X=-0.1'' (centre) and X=0'' (top) spaced by 10$\,$K for clarity, {\bf Right:} Intensity weighted velocity map}
+\end{figure*}
 
@@
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageH2CO_4-0-4->3-0-3_30deg_contSub.png}
-
- \caption{H$_2$CO 4$\,$0$\,$4 - 3$\,$0$\,$3 Continuum subtracted mom0}
-\end{figure}
-
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageH2CO_4-0-4->3-0-3_30deg_mom1.png}
-
- \caption{H$_2$CO 4$\,$0$\,$4 - 3$\,$0$\,$3 PV through centre}
-\end{figure}
+\begin{figure*}
+ \includegraphics[width=168mm]{Figures/sim/imageH2CO_4-0-4--3-0-3_composite_all.png}
+ \label{h2co_all}
+ \caption{H$_2$CO 4$_{0\,4}$ - 3$_{\,0\,3}$ {\bf Left:} Continuum subtracted integrated intensity map, {\bf Centre:} Continuum subtracted spectra from Y=0'', X=+0.1'' (bottom), X=-0.1'' (centre) and X=0'' (top) spaced by 50$\,$K for clarity, {\bf Right:} Intensity weighted velocity map}
+\end{figure*}
 
@@
 
- \caption{H$_2$CO 4$\,$0$\,$4 - 3$\,$0$\,$3 PV through centre}
+ \caption{H$_2$CO 4$_{0\,4}$ - 3$_{\,0\,3}$ PV through centre}
 \end{figure}
@@
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageHCOp_1-0_30deg_contSub.png}
-
- \caption{HCO$^+$ 1-0 Continuum subtracted mom0}
-\end{figure}
-
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageHCOp_1-0_30deg_mom1.png}
-
- \caption{HCO$^+$ 1-0 mom1map}
-\end{figure}
+\begin{figure*}
+ \includegraphics[width=168mm]{Figures/sim/imageHCOp_1-0_30deg_composite_all.png}
+ \label{h2co_all}
+ \caption{HCO$^+$ 1-0 {\bf Left:} Continuum subtracted integrated intensity map, {\bf Centre:} Continuum subtracted spectra from Y=0'', X=+0.4'' (bottom), X=-0.4'' (centre) and X=0'' (top) spaced by 40$\,$K for clarity, {\bf Right:} Intensity weighted velocity map}
+\end{figure*}
 
@@
 \appendix
+
+\section{Grid Construction} \label{sec:gridding} 
+In order to construct the grid, candidate points are randomly selected from the volume to be simulated.
+These candidates then have their density and molecular density compared against a reference point in order to decide if the point is to be used in the grid or not.
+[NOTE: THIS FIRST SENTENCE DOES NOT MAKE SENSE.
+PLEASE RE-WRITE IT AND MAKE SURE THAT IT IS CLEAR AND THERE ARE NO TYPOS.] Candidate grid points are selected at random in cylindrical co-ordinates, linearly spaced in z and $\phi$ and logarithmically spaced in r.
+For each point to be selected, a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) as a threshold.
+After selection of random co-ordinates, the hydrogen density and molecular density at the candidate point (n and m, respectively) are compared against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$).
+If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use, otherwise another r, $\phi$, z co-ordinate is selected and this becomes the candidate point.
+The function comparing the candidate point to the reference point and the candidate point distribution were selected empirically to sample all the scales while ensuring that the majority of points are located in the inner disc where the density is higher.
+20\% of these points are forced to be at radii greater than $\sqrt{R_{min}R_{max}}$ (where $R_{min}$ and $R_{max}$ are the inner and outer radius of the model) in order to stop too many of the selecected points clustering in the high density disc and leaving the envelope undersampled.
+In addiation to this method of selection, 5\% of the points are linearly distributed in x, y and z with no bias with regards to density or abundance.
+This provides a minimum level of sampling for the large low density regions in the outer parts of the simulated volume.
+See figure \ref{points} for an example of the points distribution in r, z.
+\newline
 

### 2012-12-17 paper.tex
some small changes

@@
 \begin{figure*}
- \includegraphics[width=168mm]{Figures/model/rhoT2.png}
+ \includegraphics[width=168mm]{Figures/model/rhoT2.eps}
  \label{rhoT} 
@@
 The simulations done are focused upon frequencies within ALMA band 7, selected to give the best trade off between resolution and sensitivity for early ALMA science {\bf IS BAND 7 STILL THE BEST FOR US TO LOOK AT SEEING AS WE ARE NOW LOOKING AT ALMA FULL CAPABILITY RATHER THAN CYCLE1?}.
-(Note the moment 1 and 0 maps were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in some PV diagrams as the strong absorption feature at all positions around zero velocity, moment 1 maps are shown with a cutoff of 1/1000 of the peak emission/absorption value)\newline
+(Note the moment 1 and 0 maps were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in some PV diagrams as the strong absorption feature at all positions around zero velocity, moment 1 maps are shown with a cutoff of 1/100 of the peak emission/absorption value)\newline
 %
@@
 \begin{figure}
+  \showthe\columnwidth % Use this to determine the width of the figure.
   \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_PV_centre.png}
-
   \caption{C18O 3-2 75 deg PV through centre}

### 2012-12-19 paper.tex
now using eps rather than png

@@
 \author[Tom  Douglas, Paola Caselli, Et al.]{Tom Douglas$^{1}$\thanks{E-mail:
-pytd@leeds.ac.uk}, Paola Caselli$^{1}$, Aaron Boley$^{2}$, Richard Durisen$^{3}$,\newline Tom Hartquist$^{1}$, John Ilee$^{1}$, Jonathon Rawlings$^{4}$ \\
+pytd@leeds.ac.uk}, Paola Caselli$^{1}$, Aaron Boley$^{2}$, Richard Durisen$^{3}$, Tom Hartquist$^{1}$, John Ilee$^{1}$, Jonathon Rawlings$^{4}$ \\
 $^{1}$School of Physics and Astronomy, University of Leeds, Leeds LS2 9JT, UK \\
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/model/L1544model_used_legend.png}
+ \includegraphics[width=84mm]{Figures/model/L1544model_used_legend.eps}
  \label{fig:l1544_model}
- \caption{[NOTE: YOU NEED TO ADD LABELS AND UNITS TO THE AXES!!] Model of the pre-stellar core L1544 used as the envelope of the young protoplanetary disc in the hybrid model.
+ \caption{Model of the pre-stellar core L1544 used as the envelope of the young protoplanetary disc in the hybrid model.
 Showing temperature (red) and dust (green) temperature in kelvin, log number density (blue) in cm$^{-3}$ and inward velocity$\times$100 (cyan) in m$\,$s$^{-1}$.
@@
 \begin{figure*}
- \includegraphics[width=168mm]{Figures/model/columnDensities2.png}
+ \includegraphics[width=168mm]{Figures/model/columnDensities2.eps}
  \label{Chemistry} 
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/model/rotational_velocities.png}
+ \includegraphics[width=84mm]{Figures/model/rotational_velocities.eps}
  \label{velocity}
@@
 This is repeated 20 times with the populations of each level converging towards a single value.
-This number of iterations is sufficient for the signal to noise ratio of the level populations (as defined in Brinch \&Hogerheijde 2010) to exceed 1000 in 99\% of the points.
-[NOTE: WHY DO WE NEED TO REACH SUCH A HIGH S/N?
---- it isn't s/n in the usual sense, it's a measurement of how converged the model is, defined in brinch 2010 as change in populations this iteration / std-dev of change in pops over last 5 iterations] \newline
+This number of iterations is sufficient for the signal to noise ratio of the level populations (as defined in Brinch \&Hogerheijde 2010) to exceed 1000 in 99\% of the points, ensuring that the simulation has converged on a stable level population.
+\newline
 After 20 iterations of updateing the level populations the model is ray-traced in order to produce synthetic brighness maps.
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/average_comparison.png}
+ \includegraphics[width=84mm]{Figures/sim/average_comparison.eps}
  \label{averages}
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/model/Lime_grid3.png}
+ \includegraphics[width=84mm]{Figures/model/Lime_grid3.eps}
  \label{grid}
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/model/lime_points_rz_histo.png}
+ \includegraphics[width=84mm]{Figures/model/lime_points_rz_histo.eps}
  \label{points}
@@
 
-[NOTE: I SUGGEST TO:
-
-1.
-SHOW THE MOMENT 0 AND 1 ONLY MAPS OF C18O, OCS, H2CO AND HCO+ + SPECTRA TOWARD THE CENTER AND +/- 30 AU (FOR EACH SPECIES, YOU CAN DO A 3-PANEL FIGURE SHOWING THE TWO MOMENTS AND A PANEL WITH THE 3 SPECTRA AT DIFFERENT LOCATIONS)
-+  THE CONTINUUM MAP 
-3. SHOW THE SIMULATED ALMA OBSERVATIONS (SAME STYLE AS BEFORE) AND ALSO SHOW A SEPARATE FIGURE WITH THE PV DIAGRAMS OF ALL SPECIES. 
-]
-
-[NOTE: THE FOLLOWING PARAGRAPH IS NOT CLEAR AT ALL !!!
-PLEASE RE-WRITE MAKING SURE THAT THE SENTENCES MAKE SENSE AND THERE ARE NO TYPOS.
-PLEASE MAKE THE FIGURES AS SUGGESTED AND THEN RE-WRITE THIS PART.]
-%Simulated molecules were confined to speices where the chemical abundance in the disc and envelope are known, or have simulated abundances.
-In addition radative transfer simulations are limited to are limited to molecules where the collisional and Einstein co-efficients are known.
-Lines for these molecules were simulated with LIME for freqencies 50$\sim$500$\,$GHz, with focus on lines which could be observed in ALMA band 7 and molecules which are not typically seen in outflows, which havent been included in these simulations and could potentially contaminate disc observations.
+Simulations are limited to molecules for which we have abundances in both the disc and envelope, and also have calculated Einstein and collisional co-efficients.
+The Molecular data used is from the lamda database (reference?
+http://home.strw.leidenuniv.nl/$\sim$moldata/).
+Lines for the molecules which satisfy these conditions were simulated with LIME for freqencies between 50$\sim$500$\,$GHz, with a focus on lines which could be observed in ALMA band 7 and molecules which are not typically seen in outflows.
 The results presented in this section represent those lines which show dectectable emission/absorption which can be used to trace either spiral structure or rotation.\newline
 
-%Figures showing the RT results in a few molecules/transitions (CO, HCO$^+$, HCN, OCS, H2CO, NH3 --- maybe H2O,H2$^{18}$O [to try first])
-The results of these simulations for the molecules OCS, HCO$^+$, H$_2$CO and isotopologues of CO are shown here, other molecules simulated but not shown include HCN, HNC, HNO, HCS$^+$ and  CS.
+Transitions focused upon are CO 3-2 (and isotopologues) at 345.8GHz with an upper energy level of 33.2K, HCO+ 1-0 at 89.2GHZ and 4.3K, OCS 28-27 at 340.4GHz and 237.0K and H2CO $4_{04}$-3$_{03}$ at 290.6GHz and 34.9K {\bf maybe worth including a higher frequency line as well?
+maybe CS at ~650GHz}.
+Other molecules simulated but not shown include HCN, HNC, HNO, HCS$^+$ and CS.\newline
+
 For the purpose of simulating observations the model was placed at roughly the distance of nearby low-mass star forming regions (100$\,$pc) and is inclined at 30$^\circ$ to edge on.
 From these observations integrated intensity, intensity weighted velocity and position velocity diagrams through the centre of the model were created.
-The simulations done are focused upon frequencies within ALMA band 7, selected to give the best trade off between resolution and sensitivity for early ALMA science {\bf IS BAND 7 STILL THE BEST FOR US TO LOOK AT SEEING AS WE ARE NOW LOOKING AT ALMA FULL CAPABILITY RATHER THAN CYCLE1?}.
+The simulations done are focused upon frequencies within ALMA band 7, selected to give the best trade off between resolution and sensitivity for early ALMA science.
 (Note the moment 1 and 0 maps were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in some PV diagrams as the strong absorption feature at all positions around zero velocity, moment 1 maps are shown with a cutoff of 1/100 of the peak emission/absorption value)\newline
-%
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_contSub.png}
-%
-% \caption{CO J=3-2 Continuum subtracted mom0}
-%\end{figure}
-%
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_mom1.png}
-%
-% \caption{CO J=3-2 moment 1 map}
- %\end{figure}
-%
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_PV_centre.png}
-%
-% \caption{CO J=3-2 PV through y=0''}
-%\end{figure}
-
-%Figures 6,7 and 8 show synthetic images of the CO J=3-2 line at 345.8$\,$GHz.
-As the upper level for this line is at 33$\,$K above the ground state this transition should be excited through out disc.
-given the large and uniform nature of the abundance of CO in the disc this line will be optically thick and this is only mapping the outer regions of the disc.
-In common with most transitions simulated, the line is seen almost exclusively in absorption against the disc continuum.
-The region of emission in the centre is where there is no continuum background to be absorbed.
-Some indications of spiral structure can be seen but are indistinct.
-{\bf not sure how useful these are, might be worth cutting them?}\newline
 
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/continuum.png}
+ \includegraphics[width=84mm]{Figures/sim/continuum.eps}
  \label{points}
@@
 \begin{figure*}
- \includegraphics[width=168mm]{Figures/sim/imageOCS_28-27_30deg_composite_all.png}
+ \includegraphics[width=168mm]{Figures/sim/imageOCS_28-27_30deg_composite_all.eps}
  \label{OCS_all}
- \caption{OCS 28-27 {\bf Left:} Continuum subtracted integrated intensity map, {\bf Centre:} Continuum subtracted spectra from Y=0'', X=+0.1'' (bottom), X=-0.1'' (centre) and X=0'' (top) spaced by 10$\,$K for clarity, {\bf Right:} Intensity weighted velocity map}
+ \caption{OCS 28-27 {\bf Left:} Continuum subtracted integrated intensity map, {\bf Right:} Intensity weighted velocity map}
 \end{figure*}
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageOCS_28-27_30deg_composite_PV_centre.png}
+ \includegraphics[width=84mm]{Figures/sim/imageOCS_28-27_30deg_composite_PV_centre.eps}
 
@@
 \begin{figure*}
- \includegraphics[width=168mm]{Figures/sim/imageH2CO_4-0-4--3-0-3_composite_all.png}
+ \includegraphics[width=168mm]{Figures/sim/imageH2CO_4-0-4--3-0-3_30deg_composite_all.eps}
  \label{h2co_all}
- \caption{H$_2$CO 4$_{0\,4}$ - 3$_{\,0\,3}$ {\bf Left:} Continuum subtracted integrated intensity map, {\bf Centre:} Continuum subtracted spectra from Y=0'', X=+0.1'' (bottom), X=-0.1'' (centre) and X=0'' (top) spaced by 50$\,$K for clarity, {\bf Right:} Intensity weighted velocity map}
+ \caption{H$_2$CO 4$_{0\,4}$ - 3$_{\,0\,3}$ {\bf Left:} Continuum subtracted integrated intensity map, {\bf Right:} Intensity weighted velocity map}
 \end{figure*}
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageH2CO_4-0-4->3-0-3_30deg_PV_centre.png}
+ \includegraphics[width=84mm]{Figures/sim/imageH2CO_4-0-4--3-0-3_30deg_composite_PV_centre.eps}
 
@@
 \begin{figure*}
- \includegraphics[width=168mm]{Figures/sim/imageHCOp_1-0_30deg_composite_all.png}
+ \includegraphics[width=168mm]{Figures/sim/imageHCOp_1-0_30deg_composite_all.eps}
  \label{h2co_all}
- \caption{HCO$^+$ 1-0 {\bf Left:} Continuum subtracted integrated intensity map, {\bf Centre:} Continuum subtracted spectra from Y=0'', X=+0.4'' (bottom), X=-0.4'' (centre) and X=0'' (top) spaced by 40$\,$K for clarity, {\bf Right:} Intensity weighted velocity map}
+ \caption{HCO$^+$ 1-0 {\bf Left:} Continuum subtracted integrated intensity map, {\bf Right:} Intensity weighted velocity map}
 \end{figure*}
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageHCOp_1-0_30deg_PV_centre.png}
+ \includegraphics[width=84mm]{Figures/sim/imageHCOp_1-0_30deg_composite_PV_centre.eps}
 
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/casa_cont_337GHz.png}
+ \includegraphics[width=84mm]{Figures/sim/casa_cont_337GHz.eps}
 
@@
 \begin{figure}
- \includegraphics[width=54mm]{Figures/sim/casa_imageOCS_28-27_30deg_composite_ALMAwidth_big_dirty_PV_centre.png}
+ \includegraphics[width=54mm]{Figures/sim/casa_imageOCS_28-27_30deg_composite_ALMAwidth_big_dirty_PV_centre.eps}
 
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/casa_imageOCS_28-27_30deg_composite_ALMAwidth_big_dirty_contSub.png}
+ \includegraphics[width=84mm]{Figures/sim/casa_imageOCS_28-27_30deg_composite_ALMAwidth_big_dirty_contSub.eps}
 
@@
 \begin{figure}
- \includegraphics[width=54mm]{Figures/sim/casa_imageC17O_3-2_30deg_composite_ALMAwidth_dirty_PV_centre.png}
+ \includegraphics[width=84mm]{Figures/sim/casa_HCOp_spectra_40_AUsplit.eps}
 
- \caption{C17O 3-2 30 deg PV through centre simulated for ALMA most extended configuration}
+ \caption{HCO$^+$ 1-0 30 deg spectra at Y=0, X=+40AU (bottom), 0AU (middle) and -40AU (Top)}
 \end{figure}
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/casa_C17O_3-2_mom0.png}
+ \includegraphics[width=54mm]{Figures/sim/casa_imageC17O_3-2_30deg_composite_ALMAwidth_dirty_PV_centre.eps}
 
- \caption{C17O 3-2 30 deg integrated intensity simulated for ALMA most extended configuration}
+ \caption{C$^{17}$O 3-2 30 deg PV through centre simulated for ALMA most extended configuration}
 \end{figure}
@@
 \begin{figure}
- \includegraphics[width=63mm]{Figures/sim/casa_imageHCOp_1-0_30deg_composite_ALMAwidth_dirty_PV_centre.png}
+ \includegraphics[width=84mm]{Figures/sim/casa_C17O_3-2_mom0.eps}
+
+ \caption{C$^{17}$O 3-2 30 deg integrated intensity simulated for ALMA most extended configuration}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/casa_C17O_spectra_20AUsplit.eps}
+
+ \caption{C$^{17}$O 1-0 30 deg spectra at Y=0, X=+20AU (bottom), 0AU (middle) and -20AU (Top)}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=63mm]{Figures/sim/casa_imageHCOp_1-0_30deg_composite_ALMAwidth_dirty_PV_centre.eps}
 
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/casa_imageHCOp_1-0_30deg_composite_ALMAwidth_dirty_contSub.png}
+ \includegraphics[width=84mm]{Figures/sim/casa_imageHCOp_1-0_30deg_composite_ALMAwidth_dirty_contSub.eps}
 
  \caption{HCO$^+$ 1-0 30 deg integrated intensity simulated for ALMA most extended configuration}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/casa_OCS_spectra_10AUsplit.eps}
+
+ \caption{OCS 28-27 30 deg spectra at Y=0, X=+10AU (bottom), 0AU (middle) and -10AU (Top)}
 \end{figure}
@@
 Outflows could contaminate measurements of rotation curves meaning that speices  which commonly trace outflows, such as CO and HCO$^+$ are not going to be good tracers of disc rotation.
-However speices such as OCS and C$^{18}$O which are not commonly seen in outflows (Yildiz et al 2012,)can be used to trace disc rotation.
+However speices such as OCS and C$^{18}$O which are not commonly seen in outflows (e.g.
+van der Tak et al.
+2003, Stanke et al.
+2007, Yildiz et al 2012, Ren et al.
+2011)can be used to trace disc rotation.
 
@@
 These candidates then have their density and molecular density compared against a reference point in order to decide if the point is to be used in the grid or not.
-[NOTE: THIS FIRST SENTENCE DOES NOT MAKE SENSE.
-PLEASE RE-WRITE IT AND MAKE SURE THAT IT IS CLEAR AND THERE ARE NO TYPOS.] Candidate grid points are selected at random in cylindrical co-ordinates, linearly spaced in z and $\phi$ and logarithmically spaced in r.
+Candidate grid points are selected at random in cylindrical co-ordinates, linearly spaced in z and $\phi$ and logarithmically spaced in r.
 For each point to be selected, a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) as a threshold.
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_contSub.png}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_contSub.eps}
 
@@
 %\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_mom1.png}
+% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_mom1.eps}
 %
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_PV_centre.png}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_PV_centre.eps}
 
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_contSub.png}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_contSub.eps}
 
@@
 %\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_mom1.png}
+% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_mom1.eps}
 %
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_PV_centre.png}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_PV_centre.eps}
 
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_contSub.png}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_contSub.eps}
 
@@
 %\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_mom1.png}
+% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_mom1.eps}
 %
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_PV_centre.png}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_PV_centre.eps}
 
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_contSub.png}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_contSub.eps}
 
@@
 %\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_mom1.png}
+% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_mom1.eps}
 %
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_PV_centre.png}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_PV_centre.eps}
 
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_contSub.png}
+ \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_contSub.eps}
 
@@
 %\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_mom1.png}
+% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_mom1.eps}
 %
@@
 \begin{figure}
-  \showthe\columnwidth % Use this to determine the width of the figure.
-  \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_PV_centre.png}
+%  \showthe\columnwidth % Use this to determine the width of the figure.
+  \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_PV_centre.eps}
   \caption{C18O 3-2 75 deg PV through centre}

### 2013-01-11 paper.tex
more figures a few tweaks to the text

@@
 \title[Young protoplanetary discs]{Simulated observations of young protoplanetary discs}
+%authors arent splitting over 2 lines so rawlings is pushed off the edge
 \author[Tom Douglas, Paola Caselli, Et al.]{Tom Douglas$^{1}$\thanks{E-mail:
@@
 2012), are challenging.
-The use of sensitive interferometers is needed to achieve high angular resolution and spatially/spectrally disentangle the various (disc + envelope + outflow) components as well to filter out the extended emission tracing envelope material.
+The use of sensitive interferometers is needed to achieve high angular resolution and spatially/spectrally disentangle the various disc, envelope and outflow components as well to filter out the extended emission tracing envelope material.
 
@@
 Pineda et al.
-(2012) observed methyl formate with the Atacama Millimeter and sub-millimeter Array (ALMA) and found evidence of rotation toward one of the proto-binary Class 0 sources embedded in IRAS 16293-2422.
+(2012) observed methyl formate with the Atacama Millimetre and millimetre Array (ALMA) and found evidence of rotation toward one of the proto-binary Class 0 sources embedded in IRAS 16293-2422.
 These observations are consistent with an almost edge-on disc.
@@
 
-In this paper, we focus our attention to the young self-gravitating discs of Boley \& Durisen (2008), where episodic heating induced by spiral shocks is present, as this may be a good representation of the earliest phases of protoplanetary discs and an alternative to the young "static" discs studied by, e.g.
+Previous work on simulating observations of gravitationally unstable discs have performed calculations of the continuum radiative transfer in order to look at the structure of the disc to detect disc fragmentation (Ruge et al.
+2012) or have used the local thermodynamic equilibrium (LTE) approximation in order to estimate the molecular line emission for an unembedded disc (Krumholtz et al.
+2007).
+
+In this paper, we focus our attention to the young self-gravitating discs of Boley \& Durisen (2008), where episodic heating induced by spiral shocks is present, as this may be a good representation of the earliest phases of protoplanetary discs and an alternative to the young ``static'' discs studied by, e.g.
 Visser et al.
@@
 As shown by Ilee et al.
-(2011), the spiral shocks cause desorption of volatiles from dust icy mantles and trigger gas-phase chemical reactions with activation energies, which are inactive at lower temperatures.
+(2011), the spiral shocks cause desorption of volatiles from dust icy mantles and trigger gas-phase chemical reactions with activation energies, too high to occur at lower temperatures.
 These processes produce clear chemical signatures of the disc dynamics.
-With the use of 3D radiative transfer modeling, we perform simulated ALMA observations of the disc studied by Ilee et al.
+With the use of 3D radiative transfer modelling, we perform simulated ALMA observations of the disc studied by Ilee et al.
 (2011) and identify the best tracers of the physical structure of self-gravitating discs.
@@
 The physical model used to simulate the emission from a young protoplanetary disc is a hybrid model obtained from embedding a gravitationally unstable protoplanetary disc  within an envelope with characteristics similar to the well-studied pre-stellar core L1544, as derived by Keto \& Caselli (2010; hereafter KC2010).
-The KC2010 model follows the dynamical, chemical and thermal evolution of a contracting Bonnor-Ebert (Bonnor 1956; Ebert 1957) sphere with total mass of 10\,M$_{\odot}$, until it reaches the density, temperature and velocity profiles which best match observations.
+The KC2010 model follows the dynamical, chemical and thermal evolution of a contracting Bonnor-Ebert sphere (Bonnor 1956; Ebert 1957) with total mass of 10\,M$_{\odot}$, until it reaches the density, temperature and velocity profiles which best match observations.
 The pre-stellar core model adopted here contains slight modifications due to the inclusion of oxygen cooling in the outer regions of the cloud, where CO is mostly photodissociated (Keto et al., in preparation), and it is shown in Fig.\,\ref{fig:l1544_model}.
-[NOTE: BESIDES THE PROBLEM WITH THE FIGURE NUMBER, YOU NEED TO READJUST FIGURES, AS THIS ONE IS THE FIRST ONE THAT YOU DESCRIBE, SO IT SHOULD BE NUMBER 1] \newline
+\newline
 
 \begin{figure}
- \includegraphics[width=84mm]{Figures/model/L1544model_used_legend.eps}
+ \includegraphics[width=84mm]{Figures/model/L1544model_used_legend_small.eps}
  \label{fig:l1544_model}
@@
  \label{rhoT} 
- \caption{Left: A 3D plot of log number density (cm$^{-3}$) showing the spiral structure in the xy plane and scale height of the disc.
-Right: The 3D temperature structure of the disc; regions cooler than 40 degrees are not shown in 3D, demonstrating the narrow central region containing hot material.}
+ \caption{{\bf Left:} A 3D plot of log number density (cm$^{-3}$) showing the spiral structure in the xy plane and scale height of the disc.
+{\bf Right:} The 3D temperature structure of the disc; regions cooler than 40 degrees are not shown in 3D, demonstrating the narrow central region containing hot material.}
 \end{figure*}
@@
 From Ilee et al.
-(2011) we selected the three species which appear to trace different regions of the disc : the inner 30\,AU (OCS), the inner 60\,AU (H$_2$CO) and the region between $\simeq$20 and 60\,AU (HCO$^+$) and one which traces the entirity of the disc (C$^{18}$O).
+(2011) we selected the three species which appear to trace different regions of the disc : the inner 30\,AU (OCS), the inner 60\,AU (H$_2$CO) and the region between $\simeq$20 and 60\,AU (HCO$^+$) and one which traces the entirety of the disc (C$^{18}$O).
 As explained by Ilee et al.
@@
 
-%NOTE: WE SHOULD TALK ABOUT THESE SPECIES AFTER WE SHOW WHICH SPECIES WE SELECT FOR THE RADIATIVE TRANSFER. 
-%Abundances in the envelope model were as follows:\newline
-
-%(tableify this?)
-%HCO$^+$: As the H$_2$O profile from Caselli et al. (2012, submitted) scaled so that the maximum abundance is 10$^{-8}$\newline
-%HNO: Constant abundance of 5$\times$10$^{-11}$\newline
-%HCS$^+$: Constant abundance of 10$^{-11}$\newline
-%OCS: Constant abundance of 10$^{-9}$\newline
-%H$_2$CO: 1.5$\times$10$^{-9}$ decreased by a factor of 40 at radii less than 8250au (Young et al 2004)\newline
-%CS:  3$\times$10$^{-9}$ decreased by a factor of 10,000 at radii less than 6700au (Tafalla, santiago-garcia and myers 2006)\newline
-%CO: As the H2O profile from Caselli (2012, submitted) scaled so that the maximum abundance is CO maximum ***which is....***\newline
-
 \subsection{The radiative transfer code} \label{subsec:radiative_transfer_code}
+%-describe the RT used (LIME) 
 %-describe the RT used (LIME) 
@@
 These points are then smoothed by Lloyds algorithm (Lloyd 1982) in order to minimise the variation in distance between points whilst keeping the same underlying distribution.
-These points are then connected by Delaunay triangulation \footnote{In three dimensions this means that if four points are conneted into a tetrahedron, the sphere circumscribing these four points contains no other points.
+These points are then connected by Delaunay triangulation \footnote{In three dimensions this means that if four points are connected into a tetrahedron, the sphere circumscribing these four points contains no other points.
 It can be shown that this connection is unique for a given set of points.} and it is down these paths that photon propagation is restricted (figures \ref{grid}).
@@
 \newline
-After 20 iterations of updateing the level populations the model is ray-traced in order to produce synthetic brighness maps.
-In order to minimise the ``blockyness'' of the output images, resulting from the grid construction, the average of ten seperate runs was taken (figure \ref{averages}).
+After 20 iterations of updating the level populations the model is ray-traced in order to produce synthetic brightness maps.
+In order to minimise the artifacts in the output images, resulting from the grid construction, the average of ten separate runs was taken (figure \ref{averages}).
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/average_comparison.eps}
- \label{averages}
- \caption{A plot showing the difference between a single LIME continuum image at 300$\,$GHz (right) and the average of ten such images from different runs of the same model in LIME (left).}
-\end{figure}
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/average_comparison.eps}
+% \label{averages}
+% \caption{A plot showing the difference between a single LIME continuum image at 300$\,$GHz (right) and the average of ten such images from different runs of the same model in LIME (left).}
+%\end{figure}
 
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/model/lime_points_rz_histo.eps}
+ \includegraphics[width=84mm]{Figures/model/lime_points_rz_histo2.eps}
  \label{points}
@@
 
-Simulations are limited to molecules for which we have abundances in both the disc and envelope, and also have calculated Einstein and collisional co-efficients.
+Simulations are limited to molecules for which we have abundances in both the disc and envelope, and also have calculated Einstein and collisional coefficients.
 The Molecular data used is from the lamda database (reference?
 http://home.strw.leidenuniv.nl/$\sim$moldata/).
-Lines for the molecules which satisfy these conditions were simulated with LIME for freqencies between 50$\sim$500$\,$GHz, with a focus on lines which could be observed in ALMA band 7 and molecules which are not typically seen in outflows.
-The results presented in this section represent those lines which show dectectable emission/absorption which can be used to trace either spiral structure or rotation.\newline
+Lines for the molecules which satisfy these conditions were simulated with LIME for frequencies between 50$\sim$500$\,$GHz, with a focus on lines which could be observed in ALMA band 7 and molecules which are not typically seen in outflows.
+The results presented in this section represent those lines which show detectable emission/absorption which can be used to trace either spiral structure or rotation.\newline
 
 Transitions focused upon are CO 3-2 (and isotopologues) at 345.8GHz with an upper energy level of 33.2K, HCO+ 1-0 at 89.2GHZ and 4.3K, OCS 28-27 at 340.4GHz and 237.0K and H2CO $4_{04}$-3$_{03}$ at 290.6GHz and 34.9K {\bf maybe worth including a higher frequency line as well?
-maybe CS at ~650GHz}.
+CS at ~650GHz?}.
 Other molecules simulated but not shown include HCN, HNC, HNO, HCS$^+$ and CS.\newline
@@
 The simulations done are focused upon frequencies within ALMA band 7, selected to give the best trade off between resolution and sensitivity for early ALMA science.
-(Note the moment 1 and 0 maps were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in some PV diagrams as the strong absorption feature at all positions around zero velocity, moment 1 maps are shown with a cutoff of 1/100 of the peak emission/absorption value)\newline
+(Note the moment 1 and 0 maps were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in some PV diagrams as the strong absorption feature at all positions around zero velocity, moment 1 maps are shown with a cut-off of 1/100 of the peak emission/absorption value)\newline
 
@@
  \label{OCS_all}
- \caption{OCS 28-27 {\bf Left:} Continuum subtracted integrated intensity map, {\bf Right:} Intensity weighted velocity map}
+ \caption{OCS 28-27 {\bf Left:} Continuum subtracted integrated intensity map showing clearly differentiated spiral structure in the inner regions of the disc, {\bf Right:} Intensity weighted velocity map}
 \end{figure*}
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageOCS_28-27_30deg_composite_PV_centre.eps}
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/imageOCS_28-27_30deg_composite_PV_centre.eps}
+% \caption{OCS 28-27 position-velocity diagram through centre}
+%\end{figure}
 
- \caption{OCS 28-27 PV through centre}
-\end{figure}
+OCS traces only the innermost region of the disc and can be used to examine the central regions.
+As OCS is not seen in outflows it can be used to view rotation of the central part of the disc without risk of contamination.
+As the excitation energy for the high J transitions of OCS is much higher than the other lines under consideration it is only excited in the hottest densest regions.
+As a result of this the spiral structure is clearer in OCS than in most transitions, with the low density regions between spiral arms showing no emission or absorption(see figure \ref{ocs_all}).
+The majority of the OCS is visible in absorption against the bright continuum emission from the disc midplane.
+The exception to this in the centre of the disc and is an effect of the inclination angle, whereby the line of sight passes through gas above the midplane and then through the hole in the centre of the disc.
 
-After looking at a variety of lines which could be observed of ALMA band 6 or 7 (211-275$\,$GHz and 275-373$\,$GHz) we found that the OCS lines in alma band 7 (22-21 through 30-29) with upper energy levels between 161 and 271 K above the ground state provide a way to trace hot shocked gas in spiral arms without resolving structure.
-Figures \ref{OCS_mom0} \& \ref{smoothOCS_mom0} show the integrated intensity of the OCS J=28-27 line in the model described previously and one where the disc section of the model is an axis-symmetric model created by taking the azimuthal average of density, temperature and molecular abundance.
-The order of magnitude difference in the line intensity provides a method to detect hot dense gas without being able to resolve the spiral structure spatially.\newline
-%
 %\begin{figure}
@@
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageH2CO_4-0-4--3-0-3_30deg_composite_PV_centre.eps}
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/imageH2CO_4-0-4--3-0-3_30deg_composite_PV_centre.eps}
+% \caption{H$_2$CO 4$_{0\,4}$ - 3$_{\,0\,3}$ PV through centre}
+%\end{figure}
 
- \caption{H$_2$CO 4$_{0\,4}$ - 3$_{\,0\,3}$ PV through centre}
-\end{figure}
-
-More complex molecules such as H$_2$CO with many closely spaced spectral lines can be used to gain an estimate on the temperature of a region.\newline
+The abundance H$_2$CO molecule is fairly typical of the molecules simulated in Ilee (2011) in that it traces the spiral structure roughly the inner 2/3$^{rd}s$ of the disc.
+The spiral structure of the disc can be seen clearly in the integrated intensity map and its rotation of detected out to larger radii than is possible with the OCS and is more visible between spiral arms but is otherwise simimlar in morphology.
 
@@
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageHCOp_1-0_30deg_composite_PV_centre.eps}
-
- \caption{HCO$^+$ 1-0 pv through centre, with the rotation curve from figure \ref{velocity} for comparison}
-\end{figure}
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/imageHCOp_1-0_30deg_composite_PV_centre.eps}
+% \caption{HCO$^+$ 1-0 pv through centre, with the rotation curve from figure \ref{velocity} for comparison}
+%\end{figure}
 
@@
 In all the simulations except HCO$^+$ we see molecular lines in absorption throughout the majority of the disc and in some cases a small amount of emission towards the centre.
-Molecular lines throughout the plane of the disc show up in absorption against the continuum emission of the shock heated, dense midplane.
+Molecular lines throughout the plane of the disc show up in absorption against the continuum emission of the shock heated, dense mid-plane.
 
@@
 
-In order to make predictions on the observability of the synthetic brightness maps created by LIME, CASA (common astronomy software applications) was used to simulate observing these with the completed ALMA in it's most extended comfiguration for a total time of four hours.
+In order to make predictions on the observability of the synthetic brightness maps created by LIME, CASA (common astronomy software applications) was used to simulate observing these with the completed ALMA in its most extended comfiguration for a total time of four hours.
 
@@
 
+PV diagrams allow us to reconstruct the rotation of the disc.
+ALMA has enough resolution and sensitivity to see spiral structure clearly in continuum emission but also in CO isotopologues and marginally in OCS.
+
 \section{Discussion and conclusions} \label{sec:discussion}
@@
 \section{Grid Construction} \label{sec:gridding}
+
 In order to construct the grid, candidate points are randomly selected from the volume to be simulated.
@@
 The function comparing the candidate point to the reference point and the candidate point distribution were selected empirically to sample all the scales while ensuring that the majority of points are located in the inner disc where the density is higher.
-20\% of these points are forced to be at radii greater than $\sqrt{R_{min}R_{max}}$ (where $R_{min}$ and $R_{max}$ are the inner and outer radius of the model) in order to stop too many of the selecected points clustering in the high density disc and leaving the envelope undersampled.
-In addiation to this method of selection, 5\% of the points are linearly distributed in x, y and z with no bias with regards to density or abundance.
+20\% of these points are forced to be at radii greater than $\sqrt{R_{min}R_{max}}$ (where $R_{min}$ and $R_{max}$ are the inner and outer radius of the model) in order to stop too many of the selected points clustering in the high density disc and leaving the envelope under sampled.
+In addition to this method of selection, 5\% of the points are linearly distributed in x, y and z with no bias with regards to density or abundance.
 This provides a minimum level of sampling for the large low density regions in the outer parts of the simulated volume.
@@
 
-Figures showing different inclinations  
+Figures showing different inclinations {\bf (will redo these for compound images soon)}
 \begin{figure}

### 2013-01-21 paper.tex
figures pretty much sorted

@@
  \includegraphics[width=168mm]{Figures/sim/imageHCOp_1-0_30deg_composite_all.eps}
- \label{h2co_all}
+ \label{hco+_all}
  \caption{HCO$^+$ 1-0 {\bf Left:} Continuum subtracted integrated intensity map, {\bf Right:} Intensity weighted velocity map}
@@
 
-\begin{figure}
- \includegraphics[width=54mm]{Figures/sim/casa_imageOCS_28-27_30deg_composite_ALMAwidth_big_dirty_PV_centre.eps}
+%\begin{figure}
+%\includegraphics[width=54mm]{Figures/sim/casa_imageOCS_28-27_30deg_composite_ALMAwidth_big_dirty_PV_centre.eps}
+% \caption{OCS 28-29 pv diagram simulated for ALMA most extended configuration}
+%\end{figure}
 
- \caption{OCS 28-29 pv diagram simulated for ALMA most extended configuration}
-\end{figure}
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/casa_OCS_26-25_30deg_contSub.eps}
+%
+% \caption{OCS 28-29 integrated intesity simulated for ALMA most extended configuration, contours %starting at 3$\sigma$ and increasing in intervals of 3$\sigma$}
+%\end{figure}
+%
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/casa_H2CO_404-303_30deg_contSub.eps}
+%
+% \caption{H$_2$CO 4$_{04}$-3$_{03}$ integrated intesity simulated for ALMA most extended configuration, %contours starting at 5$\sigma$ and increasing in intervals of 5$\sigma$}
+%\end{figure}
+%
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/casa_HCOp_spectra_40_AUsplit.eps}
+%
+% \caption{HCO$^+$ 1-0 30 deg spectra at Y=0, X=+40AU (bottom), 0AU (middle) and -40AU (Top)}
+%\end{figure}
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/casa_imageOCS_28-27_30deg_composite_ALMAwidth_big_dirty_contSub.eps}
+\begin{figure*}
+ \includegraphics[width=168mm]{Figures/sim/channel_map-1.eps} 
+ \label{h2co_chanmap}
+ \caption{H$_2$CO 4$_{04}$-3$_{03}$ channel maps as simulated by CASA.
+H$_2$CO line in contours starting at 0.35 mJy$\,$beam$^{-1}\,$km$\,$s$^{-1}$ (absorption in red, emission in blue).
+Overlaid on the continuum emission.
+Each map integrates over 2.4 km$\,$s$^{-1}$ with the top left from -10.8 to -8.4 km$\,$s$^{-1}$ to the bottom left ranging from 8.4 to 10.8 km$\,$s$^{-1}$}
+\end{figure*}
 
- \caption{OCS 28-29 integrated intesity simulated for ALMA most extended configuration}
-\end{figure}
+%\begin{figure}
+%\includegraphics[width=54mm]{Figures/sim/casa_imageC17O_3-2_30deg_composite_ALMAwidth_dirty_PV_centre.eps}
+% \caption{C$^{17}$O 3-2 30 deg PV through centre simulated for ALMA most extended configuration}
+%\end{figure}
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/casa_HCOp_spectra_40_AUsplit.eps}
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/casa_C17O_3-2_30deg_contSub.eps}
+%
+% \caption{C$^{17}$O 3-2 30 deg integrated intensity simulated for ALMA most extended configuration, %contours starting at 3$\sigma$ and increasing in intervals of 3$\sigma$}
+%\end{figure}
 
- \caption{HCO$^+$ 1-0 30 deg spectra at Y=0, X=+40AU (bottom), 0AU (middle) and -40AU (Top)}
-\end{figure}
+\begin{figure*}
+ \includegraphics[width=168mm]{Figures/sim/casa_all_30deg_contSub.eps}
 
-\begin{figure}
- \includegraphics[width=54mm]{Figures/sim/casa_imageC17O_3-2_30deg_composite_ALMAwidth_dirty_PV_centre.eps}
+ \caption{C$^{17}$O 3-2 30 deg integrated intensity simulated for ALMA most extended configuration, contours starting at 3$\sigma$ and increasing in intervals of 3$\sigma$}
+\end{figure*}
 
- \caption{C$^{17}$O 3-2 30 deg PV through centre simulated for ALMA most extended configuration}
-\end{figure}
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/casa_C17O_spectra_20AUsplit.eps}
+%
+% \caption{C$^{17}$O 1-0 30 deg spectra at Y=0, X=+20AU (bottom), 0AU (middle) and -20AU (Top)}
+%\end{figure}
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/casa_C17O_3-2_mom0.eps}
+%\begin{figure}
+%\includegraphics[width=63mm]{Figures/sim/casa_imageHCOp_1-0_30deg_composite_ALMAwidth_dirty_PV_centre.eps}
+% \caption{HCO$^+$ 1-0 30 deg PV through centre simulated for ALMA most extended configuration}
+%\end{figure}
 
- \caption{C$^{17}$O 3-2 30 deg integrated intensity simulated for ALMA most extended configuration}
-\end{figure}
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/casa_HCOp_3-2_30deg_contSub.eps}
+%
+% \caption{HCO$^+$ 3-2 30 deg integrated intensity simulated for ALMA most extended configuration. %Contours start at 3$\sigma$ and increase in steps of 3$\sigma$}
+%\end{figure}
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/casa_C17O_spectra_20AUsplit.eps}
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/casa_H2CO_404-303_30deg_contSub.eps}
+%
+% \caption{H$_2$CO 404-303 30 deg integrated intensity simulated for ALMA most extended configuration. Contours start at 5$\sigma$ and increase in steps of 10$\sigma$}
+%\end{figure}
 
- \caption{C$^{17}$O 1-0 30 deg spectra at Y=0, X=+20AU (bottom), 0AU (middle) and -20AU (Top)}
-\end{figure}
+\begin{figure*}
+ \includegraphics[width=198mm]{Figures/sim/casa_all_30deg_PV_rotCurve.eps}
 
-\begin{figure}
- \includegraphics[width=63mm]{Figures/sim/casa_imageHCOp_1-0_30deg_composite_ALMAwidth_dirty_PV_centre.eps}
+ \caption{PVs with model rotation curve}
+\end{figure*}
 
- \caption{HCO$^+$ 1-0 30 deg PV through centre simulated for ALMA most extended configuration}
-\end{figure}
+\begin{figure*}
+ \includegraphics[width=168mm]{Figures/sim/casa_all_spectra.eps}
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/casa_imageHCOp_1-0_30deg_composite_ALMAwidth_dirty_contSub.eps}
+ \caption{Spectra, H$_2$CO 20AU split, C$^{17}$O 28AU split, OCS 10AU split, HCO$^+$ 38AU split}
+\end{figure*}
 
- \caption{HCO$^+$ 1-0 30 deg integrated intensity simulated for ALMA most extended configuration}
-\end{figure}
-
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/casa_OCS_spectra_10AUsplit.eps}
-
- \caption{OCS 28-27 30 deg spectra at Y=0, X=+10AU (bottom), 0AU (middle) and -10AU (Top)}
-\end{figure}
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/casa_OCS_spectra_10AUsplit.eps}
+%
+% \caption{OCS 28-27 30 deg spectra at Y=0, X=+10AU (bottom), 0AU (middle) and -10AU (Top)}
+%\end{figure}
 
@@
 
-Figures showing different inclinations {\bf (will redo these for compound images soon)}
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_contSub.eps}
+Figures showing different inclinations 
+\begin{figure*}
+ \includegraphics[width=198mm]{Figures/sim/imageC17O_3-2_15deg_all.eps}
 
- \caption{C18O 3-2 15 deg Continuum subtracted mom0}
-\end{figure}
+ \caption{C$^{17}$O 3-2 15 deg Continuum subtracted mom0}
+\end{figure*}
+
+\begin{figure*}
+ \includegraphics[width=198mm]{Figures/sim/imageC17O_3-2_45deg_all.eps}
+
+ \caption{C$^{17}$O 3-2 45 deg Continuum subtracted mom0}
+\end{figure*}
+
+\begin{figure*}
+ \includegraphics[width=198mm]{Figures/sim/imageC17O_3-2_75deg_all.eps}
+
+ \caption{C$^{17}$O 3-2 75 deg Continuum subtracted mom0}
+\end{figure*}
 
 %\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_mom1.eps}
+% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_contSub.eps}
 %
-% \caption{C18O 3-2 15 deg mom1map}
+% \caption{C18O 3-2 15 deg Continuum subtracted mom0}
 %\end{figure}
-
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_PV_centre.eps}
-
- \caption{C18O 3-2 PV 15 deg through centre}
-\end{figure}
-
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_contSub.eps}
-
- \caption{C18O 3-2  30 deg Continuum subtracted mom0}
-\end{figure}
+%
+%%\begin{figure}
+%% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_mom1.eps}
+%%
+%% \caption{C18O 3-2 15 deg mom1map}
+%%\end{figure}
+%
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_PV_centre.eps}
+%
+% \caption{C18O 3-2 PV 15 deg through centre}
+%\end{figure}
+%
+%
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_contSub.eps}
+%
+% \caption{C18O 3-2  30 deg Continuum subtracted mom0}
+%\end{figure}
 
@@
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_PV_centre.eps}
-
- \caption{C18O 3-2 30 deg PV through centre}
-\end{figure}
-
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_contSub.eps}
-
- \caption{C18O 3-2 45 deg Continuum subtracted mom0}
-\end{figure}
-
 %\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_mom1.eps}
+% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_PV_centre.eps}
 %
-% \caption{C18O 3-2 45 deg mom1map}
+% \caption{C18O 3-2 30 deg PV through centre}
 %\end{figure}
-
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_PV_centre.eps}
-
- \caption{C18O 3-2 45 deg PV through centre}
-\end{figure}
-
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_contSub.eps}
-
- \caption{C18O 3-2 60 deg Continuum subtracted mom0}
-\end{figure}
-
+%
 %\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_mom1.eps}
+% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_contSub.eps}
 %
-% \caption{C18O 3-2 60 deg mom1map}
+% \caption{C18O 3-2 45 deg Continuum subtracted mom0}
 %\end{figure}
-
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_PV_centre.eps}
-
- \caption{C18O 3-2 60 deg PV through centre}
-\end{figure}
-
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_contSub.eps}
-
- \caption{C18O 3-2 75 deg Continuum subtracted mom0}
-\end{figure}
-
+%
+%%\begin{figure}
+%% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_mom1.eps}
+%%
+%% \caption{C18O 3-2 45 deg mom1map}
+%%\end{figure}
+%
 %\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_mom1.eps}
+% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_PV_centre.eps}
 %
-% \caption{C18O 3-2 75 deg mom1map}
+% \caption{C18O 3-2 45 deg PV through centre}
 %\end{figure}
-
-\begin{figure}
-%  \showthe\columnwidth % Use this to determine the width of the figure.
-  \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_PV_centre.eps}
-  \caption{C18O 3-2 75 deg PV through centre}
-\end{figure}
+%
+%
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_contSub.eps}
+%
+% \caption{C18O 3-2 60 deg Continuum subtracted mom0}
+%\end{figure}
+%
+%%\begin{figure}
+%% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_mom1.eps}
+%%
+%% \caption{C18O 3-2 60 deg mom1map}
+%%\end{figure}
+%
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_PV_centre.eps}
+%
+% \caption{C18O 3-2 60 deg PV through centre}
+%\end{figure}
+%
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_contSub.eps}
+%
+% \caption{C18O 3-2 75 deg Continuum subtracted mom0}
+%\end{figure}
+%
+%%\begin{figure}
+%% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_mom1.eps}
+%%
+%% \caption{C18O 3-2 75 deg mom1map}
+%%\end{figure}
+%
+%\begin{figure}
+%%  \showthe\columnwidth % Use this to determine the width of the figure.
+%  \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_PV_centre.eps}
+%  \caption{C18O 3-2 75 deg PV through centre}
+%\end{figure}
 

### 2013-01-21 paper.tex
authors corrected and a few minor fig changes

@@
 \usepackage{float}
+\usepackage{wasysym}
+\usepackage{stmaryrd}
+\usepackage{txfonts}
+\usepackage{natbib}
+\usepackage{color}
+\usepackage{colortbl}
+\usepackage{multirow}
+
+% Journal Definitions
+\def   \aj {{\rm {AJ}}}
+\def   \araa {{\rm {ARA\&A}}}
+\def   \apj {{\rm {ApJ}}}
+\def   \icarus {{\rm {Icarus}}}
+\def   \apjs {{\rm {ApJS}}}
+\def   \apss {{\rm {Ap\&SS}}}
+\def   \aap {{\rm {A\&A}}}
+\def   \aapr {{\rm {A\&AR}}}
+\def   \aaps {{\rm {A\&AS}}}
+\def   \baas {{\rm {BAAS}}}
+\def   \memras {{\rm {MmRAS}}}
+\def   \mnras {{\rm {MNRAS}}}
+\def   \prl {{\rm {Phys. Rev. Lett.}}}
+\def   \jqsrt {{\rm {Journal of Quantitative Spectroscopy and Radiative Transfer}}}
+\def   \apjl{\rm {ApJL}}
+\def   \nat{\rm {Nat.}}
 
@@
 
-\title[Young protoplanetary discs]{Simulated observations of young protoplanetary discs}
-%authors arent splitting over 2 lines so rawlings is pushed off the edge
-\author[Tom Douglas, Paola Caselli, Et al.]{Tom Douglas$^{1}$\thanks{E-mail:
-pytd@leeds.ac.uk}, Paola Caselli$^{1}$, Aaron Boley$^{2}$, Richard Durisen$^{3}$, Tom Hartquist$^{1}$, John Ilee$^{1}$, Jonathon Rawlings$^{4}$ \\
-$^{1}$School of Physics and Astronomy, University of Leeds, Leeds LS2 9JT, UK \\
-$^{2}$Department of Astronomy, University of Florida, 211 Bryant Space Center, PO Box 112055, USA\\
-$^{3}$Department of Astronomy, Indiana University, 727 East 3rd Street, Swain West 319, Bloomington, IN 47405, USA\\
+\title[Young protoplanetary discs]{Simulated Observations of Young Protoplanetary Discs}
+%%authors arent splitting over 2 lines so rawlings is pushed off the edge
+%\author[Tom Douglas, Paola Caselli, Et al.]{Tom Douglas$^{1}$\thanks{E-mail:
+%pytd@leeds.ac.uk}, Paola Caselli$^{1}$, Aaron Boley$^{2}$, Richard Durisen$^{3}$, Tom Hartquist$^{1}$, %John Ilee$^{1}$, Jonathon Rawlings$^{4}$ \\
+%$^{1}$School of Physics and Astronomy, University of Leeds, Leeds LS2 9JT, UK \\
+%$^{2}$Department of Astronomy, University of Florida, 211 Bryant Space Center, PO Box 112055, USA\\
+%$^{3}$Department of Astronomy, Indiana University, 727 East 3rd Street, Swain West 319, Bloomington, IN %47405, USA\\
+%%$^{4}$Department of Physics & Astronomy, University College London, London WC1E 6BT, UK\\
+%}
+
+\author[T.~A.~Douglas et al.]
+{\parbox{\textwidth}{Tom Douglas$^{1}$\thanks{E-mail: \texttt{pytd@leeds.ac.uk}},
+Paola Caselli$^{1}$,
+Aaron Boley$^{2}$,
+Richard Durisen$^{3}$,
+Tom Hartquist$^{1}$,
+John Ilee$^{1}$ and
+Jonathon Rawlings$^{4}$\\
+\vspace{0.1cm}\\
+{\small{\it$^{1}$School of Physics and Astronomy, University of Leeds, Leeds LS2 9JT, UK}} \\
+{\small{\it$^{2}$Department of Astronomy, University of Florida, 211 Bryant Space Center, PO Box 112055, USA}}\\
+{\small{\it$^{3}$Department of Astronomy, Indiana University, 727 East 3rd Street, Swain West 319, Bloomington, IN 47405, USA}}\\
+{\small{\it$^{4}$Department of Physics \& Astronomy, University College London, London WC1E 6BT, UK}}\\}}
+
+%{\parbox{\textwidth}{
+%$^{1}$School of Physics and Astronomy, University of Leeds, Leeds LS2 9JT, UK \\
+%$^{2}$Department of Astronomy, University of Florida, 211 Bryant Space Center, PO Box 112055, USA\\
+%$^{3}$Department of Astronomy, Indiana University, 727 East 3rd Street, Swain West 319, Bloomington, IN %47405, USA\\
 %$^{4}$Department of Physics & Astronomy, University College London, London WC1E 6BT, UK\\
-}
+%}}
+
 \begin{document}
 
-\date{In original form 2012}
+\date{In original form 2013}
 
@@
 \begin{figure*}
- \includegraphics[width=168mm]{Figures/model/rhoT2.eps}
+ \includegraphics[width=168mm]{Figures/model/rhoT6.eps}
  \label{rhoT} 
@@
  \caption{H$_2$CO 4$_{04}$-3$_{03}$ channel maps as simulated by CASA.
-H$_2$CO line in contours starting at 0.35 mJy$\,$beam$^{-1}\,$km$\,$s$^{-1}$ (absorption in red, emission in blue).
+H$_2$CO line in contours starting at 0.35 mJy$\,$beam$^{-1}\,$km$\,$s$^{-1}$ (absorption in blue, emission in red).
 Overlaid on the continuum emission.

### 2013-01-22 paper.tex

@@
 
-Transitions focused upon are CO 3-2 (and isotopologues) at 345.8GHz with an upper energy level of 33.2K, HCO+ 1-0 at 89.2GHZ and 4.3K, OCS 28-27 at 340.4GHz and 237.0K and H2CO $4_{04}$-3$_{03}$ at 290.6GHz and 34.9K {\bf maybe worth including a higher frequency line as well?
+Transitions focused upon are CO 3-2 (and isotopologues) at 345.8GHz with an upper energy level of 33.2K, HCO+ 3-2 at 267GHZ and 25.7K, OCS 26-25 at 316GHz and 205K and H2CO $4_{04}$-3$_{03}$ at 290GHz and 34.9K {\bf maybe worth including a higher frequency line as well?
 CS at ~650GHz?}.
@@
 From these observations integrated intensity, intensity weighted velocity and position velocity diagrams through the centre of the model were created.
-The simulations done are focused upon frequencies within ALMA band 7, selected to give the best trade off between resolution and sensitivity for early ALMA science.
+The simulations were focused upon frequencies within ALMA band 7, selected to give the best trade off between resolution and sensitivity for early ALMA science.
 (Note the moment 1 and 0 maps were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in some PV diagrams as the strong absorption feature at all positions around zero velocity, moment 1 maps are shown with a cut-off of 1/100 of the peak emission/absorption value)\newline
@@
 
-In order to make predictions on the observability of the synthetic brightness maps created by LIME, CASA (common astronomy software applications) was used to simulate observing these with the completed ALMA in its most extended comfiguration for a total time of four hours.
+In order to make predictions on the observability of the synthetic brightness maps created by LIME, CASA (common astronomy software applications) was used to simulate observing these with the completed ALMA in configuration 26 of 28 for a total time of four hours, giving a beam size of between 0.02 and 0.03 arcseconds.
+In order to clean the images which featured mainly absorption the sky model used was the output of the lime simulations with the continuum subtracted and then the image inverted.
+The simulated images were cleaned down to a 3\sigma level with \sigma given by the online alma sensitivity calculator (ref).
 

### 2013-01-22 paper_pc.tex

@@
 
-\title[Simulated observations of young protoplanetary disks]{Young protoplanetary disks}
+\title[Young protoplanetary discs]{Simulated observations of young protoplanetary discs}
 \author[Tom  Douglas, Paola Caselli, Et al.]{Tom Douglas$^{1}$\thanks{E-mail:
-pytd@leeds.ac.uk}, Paola Caselli$^{1}$\\
-$^{1}$School of Physics and Astronomy, University of Leeds, Leeds LS2 9JT, UK}
+pytd@leeds.ac.uk}, Paola Caselli$^{1}$, Aaron Boley$^{2}$, Richard Durisen$^{3}$,\\ Tom Hartquist$^{1}$, Ilee$^{1}$, Rawlings$^{4}$ \\
+$^{1}$School of Physics and Astronomy, University of Leeds, Leeds LS2 9JT, UK\\
+%$^{2}$Department of Astronomy, University of Florida, 211 Bryant Space Center, PO Box 112055, USA\\
+%$^{3}$Department of Astronomy, Indiana University, 727 East 3rd Street, Swain West 319, Bloomington, IN 47405, USA\\
+%$^{4}$Department of Physics & Astronomy, University College London, London WC1E 6BT, UK
+}
 \begin{document}
@@
 (2012) observed methyl formate with the Atacama Millimeter and sub-millimeter Array (ALMA) and found evidence of rotation toward one of the proto-binary Class 0 sources embedded in IRAS 16293-2422.
-These observations are consistent with an almost edge-on disk.
-When ALMA will be completed, it will be finally possible to spatially resolve these young disks and, for the first time, put stringent constraints on theoretical models.
-As full-operational ALMA is fast approaching, it is important to provide observational predictions based on dynamical models of young protoplanetary disks.
+These observations are consistent with an almost edge-on disc.
+Persson et al.
+(2012) observed H$_2^{18}$O with ALMA toward the same source and found evidence of relatively large ($\ga$100\,K) excitation temperatures, as well as a HDO/H$_2$O abundance ratio close to that measured on Earth's oceans and Jupiter-family comets (Hartogh et al.
+2011).
+When ALMA will be completed, it will be finally possible to spatially resolve these young discs and, for the first time, put stringent constraints on theoretical models.
+As full-operational ALMA is fast approaching, it is important to provide observational predictions based on dynamical models of young protoplanetary discs.
 
-In this paper, we focus our attention to the young self-gravitating disks of Boley \& Durisen (2008), where episodic heating induced by spiral shocks is present, as this may be a good representation of the earliest phases of protoplanetary disks and an alternative to the young "static" disks studied by, e.g.
+In this paper, we focus our attention to the young self-gravitating discs of Boley \& Durisen (2008), where episodic heating induced by spiral shocks is present, as this may be a good representation of the earliest phases of protoplanetary discs and an alternative to the young "static" discs studied by, e.g.
 Visser et al.
@@
 Discussions and conclusions can be found in Sect.\,\ref{sec:discussion}.
-
-%1. description of what has been done so far on the modelling and radiative transfer of disks (this includes also more evolved disks -- Visser et al., Walsh et al., Aikawa et al. ..)
-%2. focus on the young disks (work done by Machida et al., Dapp, Basu \& Kunz 2012, .. for their formation; work by Boley et al. on the physical evolution ; Ilee et al. for chemistry) 
-%3.
-previous attempts to observe these young disks: (a) simulations (Cossins et al.
-2010); (b) observations: Fuente et al.
-2010 (AB Aur); Jorgensen \& van Dishoeck (H$_2^{18}$O and the HDO/H$_2$O ratio); Pineda et al.
-(2012); other papers talking about "hot corinos" (Bottinelli et al.
-....)
 
@@
 
-%-describe the envelope structure (pre-stellar core)
-
-The physical model used to simulate the emission from a young protoplanetary disc is a hybrid model obtained from embedding a gravitationally unstable protoplanetary disk  within an envelope with characteristics similar to the well-studied pre-stellar core L1544, as derived by Keto \& Caselli (2010; hereafter KC2010).
+The physical model used to simulate the emission from a young protoplanetary disc is a hybrid model obtained from embedding a gravitationally unstable protoplanetary disc  within an envelope with characteristics similar to the well-studied pre-stellar core L1544, as derived by Keto \& Caselli (2010; hereafter KC2010).
 The KC2010 model follows the dynamical, chemical and thermal evolution of a contracting Bonnor-Ebert (Bonnor 1956; Ebert 1957) sphere with total mass of 10\,M$_{\odot}$, until it reaches the density, temperature and velocity profiles which best match observations.
 The pre-stellar core model adopted here contains slight modifications due to the inclusion of oxygen cooling in the outer regions of the cloud, where CO is mostly photodissociated (Keto et al., in preparation), and it is shown in Fig.\,\ref{fig:l1544_model}.
-\newline
+[NOTE: BESIDES THE PROBLEM WITH THE FIGURE NUMBER, YOU NEED TO READJUST FIGURES, AS THIS ONE IS THE FIRST ONE THAT YOU DESCRIBE, SO IT SHOULD BE NUMBER 1] \newline
 
 \begin{figure}
- \includegraphics[width=84mm]{Figures/model/L1544model_used.png}
+ \includegraphics[width=84mm]{Figures/model/L1544model_used_legend.png}
  \label{fig:l1544_model}
- \caption{Model of the pre-stellar core L1544 used as the envelope of the young protoplanetary disk in the hybrid model.
+ \caption{[NOTE: YOU NEED TO ADD LABELS AND UNITS TO THE AXES!!] Model of the pre-stellar core L1544 used as the envelope of the young protoplanetary disc in the hybrid model.
 Showing temperature (red) and dust (green) temperature in kelvin, log number density (blue) in cm$^{-3}$ and inward velocity$\times$100 (cyan) in m$\,$s$^{-1}$.
@@
  \label{Chemistry} 
- \caption{Column densities of H$_2$CO, OCS and HCO$^+$ used in the disc model. Figure adapted from Ilee at al. (2011)}
+ \caption{Column densities of H$_2$CO, OCS and HCO$^+$ used in the disc model. Figure adapted from Ilee at al. (2011) [SHOULD WE ALSO ADD C18O COLUMN DENSITY AS WE WANT TO DISCUSS THAT LATER ?? ]}
 \end{figure*}
@@
 
-%-describe the physical structure of the disk (density and temperature) -- one figure showing the physical structure and the kinematics (2-panels figure)
-The pre-stellar core structure is maintained down to a radius of 80\,AU, within which the young protoplanetary disk has been plugged in.
-The disk structure is derived by the hydrodynamic model of Boley(2007) and Boley (2009).
+%-describe the physical structure of the disc (density and temperature) -- one figure showing the physical structure and the kinematics (2-panels figure)
+The pre-stellar core structure is maintained down to a radius of 80\,AU, within which the young protoplanetary disc has been plugged in.
+The disc structure is derived by the hydrodynamic model of Boley(2007) and Boley (2009).
 The particular model considered here (as well as in Ilee et al.
 2011) is a 0.39$\,\rm{M}_\odot$ self-gravitating disc featuring prominent spiral arms.
-H$_2$ number densities in the disc range from 10$^{10}$-10$^{19}\,\rm{m}^{-3}$, and temperatures range from 30-400 K (figure \ref{rhoT}).
+H$_2$ number densities in the disc range from 10$^{4}$-10$^{13}\,\rm{cm}^{-3}$, and temperatures range from 30-400 K (figure \ref{rhoT}).
 The dust and gas temperatures in the disc are assumed to be in equilibrium.
@@
 These abundances were interpolated onto a 51$^3$ grid covering the disc with cells of size 2.2$\times$2.2$\times$0.22$\,$au.
-Fig.
-XX shows a sample of column density maps from Ilee et al.
-(2011), pointing out the different regions traced by H$_2$CO and OCS, which mostly probe the central warm regions, and HCO$^+$, which preferentially trace the outer spiral pattern as in the central region is destroyed by water molecules (see Ilee et al.
-2011 for details).
-The simple chemistry in the KC2010 model, adopted here as the envelope of the protoplanetary disk, does not provide detailed abundances of molecular species (besides CO and H$_2$O, see also Caselli et al.
+From Ilee et al.
+(2011) we selected the three species which appear to trace different regions of the disc : the inner 30\,AU (OCS), the inner 60\,AU (H$_2$CO) and the region between $\simeq$20 and 60\,AU (HCO$^+$) and one which traces the entirity of the disc (C$^{18}$O).
+As explained by Ilee et al.
+(2011),  H$_2$CO and OCS mostly probe the central warm regions, where icy mantles evaporate, whereas HCO$^+$ preferentially traces the outer spiral pattern as in the central region it is destroyed by water molecules.
+The simple chemistry in the KC2010 model, adopted here as the envelope of the protoplanetary disc, does not provide detailed abundances of molecular species (besides CO and H$_2$O, see also Caselli et al.
 2012).
-As discussed in the result section (Sec.\,\ref{sec:model_results}), rough guesses have been made based on values measured toward similar object.
+As discussed in the result section (Sec.\,\ref{sec:model_results}), rough guesses have been made based on values measured toward similar objects.
 
@@
 The radiative transfer program used, LIME (Brinch \&Hogerheijde 2010), calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3D model.
-The method of selecting these points is given in the griding section (NOTE: WHERE IS THE GRIDING SECTION?).
+The method of selecting these points is given in the grid-construction section.
 At each of these points, the density of the main collision partner (H$_2$), gas and dust temperatures, velocity, molecular abundances and turbulent velocity are taken from the model.
 These points are then smoothed by Lloyds algorithm (Lloyd 1982) in order to minimise the variation in distance between points whilst keeping the same underlying distribution.
-These points are then connected by Delaunay triangulation (NOTE: YOU NEED TO EXPLAIN THIS - MAYBE IN A FOOTNOTE) and it is down these paths that photon propagation is restricted (figures \ref{grid}).
+These points are then connected by Delaunay triangulation \footnote{In three dimensions this means that if four points are conneted into a tetrahedron, the sphere circumscribing these four points contains no other points.
+It can be shown that this connection is unique for a given set of points.} and it is down these paths that photon propagation is restricted (figures \ref{grid}).
 The level populations of the selected molecules are calculated at each of these points from collisional and radiative (de)excitation and the local radiation field is calculated.
-This is repeated 20 times with the populations of each level converging towards a single value.\newline
+This is repeated 20 times with the populations of each level converging towards a single value.
+This number of iterations is sufficient for the signal to noise ratio of the level populations (as defined in Brinch \&Hogerheijde 2010) to exceed 1000 in 99\% of the points.
+[NOTE: WHY DO WE NEED TO REACH SUCH A HIGH S/N?
+--- it isnt s/n in the usual sense, it's a measurement of how converged the model is, defined in brinch 2010 as change in populations this iteration / std-dev of change in pops over last 5 iterations] \newline
 
@@
  \label{points}
- \caption{A histogram of the point distribution throughout the model.}
-\end{figure}
-
-In order to construct the grid, points are randomly selected from the volume, then compared against a reference point (NOTE: WHAT IS THE COMPARISON FOR?).
-Grid points are selected at random in cylindrical co-ordinates, linearly spaced in z and $\phi$ and logarithmically spaced in r.
-For each point to be selected, a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) as a threshold.
-After selection of random co-ordinates, the hydrogen density and molecular density at the point (n and m, respectively) are compared against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$).
-If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use, if not then another r, $\phi$, z co-ordinate is selected.
-The weighting function and griding functions (NOTE: CAN YOU PLEASE EXPLAIN WHAT A GRIDING FUNCTION IS?) were selected empirically to sample all the scales while ensuring that the majority of points are located into the inner disc (where the density is higher --IS THIS LAST STATEMENT, WHICH I JUST ADDED, CORRECT?).
-20\% of these points are forced to be at radii greater than $\sqrt{R_{min}R_{max}}$ (where $R_{min}$ and $R_{max}$ are the inner and outer radius of the model) in order to stop too many of the selecected points clustering in the high density disc and leaving the envelope undersampled.
-In addiation to this method of selection, 5\% of the points are linearly distributed in x, y and z with no bias with regards to density or abundance.
-This provides a minimum level of sampling for the large low density regions in the outer parts of the simulated volume.
-See figure \ref{points} for example of the points distribution in r, z.
-\newline
-
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/average_comparison.png}
- \label{averages}
- \caption{A plot showing the difference between a single LIME continuum image at 300$\,$GHz (right) and the average of ten such images from different runs of the same model in LIME (left).}
+ \caption{A 2D histogram of the point distribution throughout the model. The disc and envelope can be seen as two separate entities which have to be sampled using different point distributions}
 \end{figure}
@@
 
-NOTE: YOU NEED TO ADD A LITTLE HISTORY ON WHY YOU SELECTED THESE SPECIES TO DO THE RADIATIVE TRANSFER. CAN YOU PLEASE RESTRUCTURE THIS SECTION ?
+[NOTE: I SUGGEST TO:
+
+1.
+SHOW THE MOMENT 0 AND 1 ONLY MAPS OF C18O, OCS, H2CO AND HCO+ + SPECTRA TOWARD THE CENTER AND +/- 30 AU (FOR EACH SPECIES, YOU CAN DO A 3-PANEL FIGURE SHOWING THE TWO MOMENTS AND A PANEL WITH THE 3 SPECTRA AT DIFFERENT LOCATIONS)
++  THE CONTINUUM MAP 
+3. SHOW THE SIMULATED ALMA OBSERVATIONS (SAME STYLE AS BEFORE) AND ALSO SHOW A SEPARATE FIGURE WITH THE PV DIAGRAMS OF ALL SPECIES. 
+]
+
+[NOTE: THE FOLLOWING PARAGRAPH IS NOT CLEAR AT ALL !!!
+PLEASE RE-WRITE MAKING SURE THAT THE SENTENCES MAKE SENSE AND THERE ARE NO TYPOS.
+PLEASE MAKE THE FIGURES AS SUGGESTED AND THEN RE-WRITE THIS PART.]
+Simulated molecules were confined to speices where the chemical abundance in the disc and envelope are known, or have simulated abundances.
+In addition radative transfer simulations are limited to are limited to molecules where the collisional and Einstein co-efficients are known.
+Lines for these molecules were simulated with LIME for freqencies 50$\sim$500$\,$GHz, with focus on lines which could be observed in ALMA band 7 and molecules which are not typically seen in outflows, which havent been included in these simulations and could potentially contaminate disc observations.
+The results presented in this section represent those lines which show dectectable emission/absorption which can be used to trace either spiral structure or rotation.\newline
+
 %Figures showing the RT results in a few molecules/transitions (CO, HCO$^+$, HCN, OCS, H2CO, NH3 --- maybe H2O,H2$^{18}$O [to try first])
 The results of these simulations for the molecules OCS, HCO$^+$, H$_2$CO and isotopologues of CO are shown here, other molecules simulated but not shown include HCN, HNC, HNO, HCS$^+$ and  CS.
-For the purpose of simulating observations the model was placed at roughly the distance of nearby low-mass star forming regions (100$\,$pc) and is inclined 30$^\circ$ to edge on.
+For the purpose of simulating observations the model was placed at roughly the distance of nearby low-mass star forming regions (100$\,$pc) and is inclined at 30$^\circ$ to edge on.
 From these observations integrated intensity, intensity weighted velocity and position velocity diagrams through the centre of the model were created.
-The simulations done are focused upon frequencies within ALMA band 7, selected to give the best trade off between resolution and sensitivity for early ALMA science.
+The simulations done are focused upon frequencies within ALMA band 7, selected to give the best trade off between resolution and sensitivity for early ALMA science {\bf IS BAND 7 STILL THE BEST FOR US TO LOOK AT SEEING AS WE ARE NOW LOOKING AT ALMA FULL CAPABILITY RATHER THAN CYCLE1?}.
 (Note the moment 1 and 0 maps were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in some PV diagrams as the strong absorption feature at all positions around zero velocity, moment 1 maps are shown with a cutoff of 1/1000 of the peak emission/absorption value)\newline
+%
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_contSub.png}
+%
+% \caption{CO J=3-2 Continuum subtracted mom0}
+%\end{figure}
+%
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_mom1.png}
+%
+% \caption{CO J=3-2 moment 1 map}
+ %\end{figure}
+%
+%\begin{figure}
+% \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_PV_centre.png}
+%
+% \caption{CO J=3-2 PV through y=0''}
+%\end{figure}
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_contSub.png}
-
- \caption{CO J=3-2 Continuum subtracted mom0}
-\end{figure}
-
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_mom1.png}
-
- \caption{CO J=3-2 moment 1 map}
-\end{figure}
-
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageCO_3-2_30deg_PV_centre.png}
-
- \caption{CO J=3-2 PV through y=0''}
-\end{figure}
-
-Figures 6,7 and 8 show synthetic images of the CO J=3-2 line at 345.8$\,$GHz.
+%Figures 6,7 and 8 show synthetic images of the CO J=3-2 line at 345.8$\,$GHz.
 As the upper level for this line is at 33$\,$K above the ground state this transition should be excited through out disc.
@@
 Some indications of spiral structure can be seen but are indistinct.
-***not sure how useful these are, might be worth cutting them?***\newline
+{\bf not sure how useful these are, might be worth cutting them?}\newline
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/imageOCS_28-27_30deg_composite_contSub.png}
+\begin{figure*}
+ \includegraphics[width=168mm]{Figures/sim/imageOCS_28-27_30deg_composite_all.png}
  \label{OCS_mom0}
- \caption{OCS 28-27 Continuum subtracted mom0}
-\end{figure}
+ \caption{OCS 28-27 {\bf Left:} Continuum subtracted integrated intensity map, {\bf Centre:} Continuum subtracted spectra from Y=0'', X=+0.1'' (bottom) X=-0.1'' (centre) and X=0'' (top) spaced by 10$\,$K for clarity, {\bf Right:} Intensity weighted velocity map}
+\end{figure*}
 
@@
 
+\begin{figure}
+ \includegraphics[width=63mm]{Figures/sim/casa_imageHCOp_1-0_30deg_composite_ALMAwidth_dirty_PV_centre.png}
+
+ \caption{HCO$^+$ 1-0 30 deg PV through centre simulated for ALMA most extended configuration}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/casa_imageHCOp_1-0_30deg_composite_ALMAwidth_dirty_contSub.png}
+
+ \caption{HCO$^+$ 1-0 30 deg integrated intensity simulated for ALMA most extended configuration}
+\end{figure}
+
 \section{Discussion and conclusions} \label{sec:discussion}
@@
 The quiescent nature of the envelope around such discs only obscures them within $\pm\,0.5 km\,s^{-1}$.\newline
-Hot, shocked gas can be detected in such a disc without resolving it by observing OCS transitions between 26-27 to 30-29.\newline
 One assumption made in this model is that the gas and dust are in thermal equilibrium.If they are not and the dust is significantly cooler than the gas then transitions may not show up in absorption.\newline
-The mass of the disc used (0.4$\,\rm{M}_\odot$) is on the high end for early discs (citations for estimate of early class 1 disc masses).\newline 
+%The mass of the disc used (0.4$\,\rm{M}_\odot$) is on the high end for early discs (citations for estimate of early class 1 disc masses).\newline
 In the model spirals shock heat the mid-plane layer and the colder more diffuse gas absorbs the continuum from it, this results in molecular lines being seen in absorbtion whenever lines of sight pass through the cold diffuse gas at larger heights on to the hot dense midplane of the disc.
 Rotation curves can be gathered from these observations even with spiral structure\newline
+Outflows could contaminate measurements of rotation curves meaning that speices  which commonly trace outflows, such as CO and HCO$^+$ are not going to be good tracers of disc rotation.
+However speices such as OCS and C$^{18}$O which are not commonly seen in outflows (Yildiz et al 2012,)can be used to trace disc rotation.
 
@@
 \appendix
+
+\section{Grid Construction} \label{sec:gridding} 
+In order to construct the grid, candidate points are randomly selected from the volume to be simulated.
+These candidates then have their density and molecular density compared against a reference point in order to decide if the point is to be used in the grid or not.
+[NOTE: THIS FIRST SENTENCE DOES NOT MAKE SENSE.
+PLEASE RE-WRITE IT AND MAKE SURE THAT IT IS CLEAR AND THERE ARE NO TYPOS.] Candidate grid points are selected at random in cylindrical co-ordinates, linearly spaced in z and $\phi$ and logarithmically spaced in r.
+For each point to be selected, a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) as a threshold.
+After selection of random co-ordinates, the hydrogen density and molecular density at the candidate point (n and m, respectively) are compared against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$).
+If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use, otherwise another r, $\phi$, z co-ordinate is selected and this becomes the candidate point.
+The function comparing the candidate point to the reference point and the candidate point distribution were selected empirically to sample all the scales while ensuring that the majority of points are located in the inner disc where the density is higher.
+20\% of these points are forced to be at radii greater than $\sqrt{R_{min}R_{max}}$ (where $R_{min}$ and $R_{max}$ are the inner and outer radius of the model) in order to stop too many of the selecected points clustering in the high density disc and leaving the envelope undersampled.
+In addiation to this method of selection, 5\% of the points are linearly distributed in x, y and z with no bias with regards to density or abundance.
+This provides a minimum level of sampling for the large low density regions in the outer parts of the simulated volume.
+See figure \ref{points} for an example of the points distribution in r, z.
+\newline
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/average_comparison.png}
+ \label{averages}
+ \caption{A plot showing the difference between a single LIME continuum image at 300$\,$GHz (right) and the average of ten such images from different runs of the same model in LIME (left).}
+\end{figure}
 

### 2013-01-22 paper.tex
text changes

@@
 The formation and earliest stages of protoplanetary discs are still lacking observational constraints.
-ALMA will soon revolutionize this field, so it is important to provide predictions and help the interpretation of future high sensitivity and high angular resolution observations.
+ALMA will soon revolutionise this field, so it is important to provide predictions and help the interpretation of future high sensitivity and high angular resolution observations.
 Here we present simulated ALMA observations of a relatively massive (0.39 M$_{\odot}$) self-gravitating disc embedded in a 10\,M$_{\odot}$ envelope with a structure similar to the pre-stellar core L1544.
@@
 As a result of this the spiral structure is clearer in OCS than in most transitions, with the low density regions between spiral arms showing no emission or absorption(see figure \ref{ocs_all}).
-The majority of the OCS is visible in absorption against the bright continuum emission from the disc midplane.
-The exception to this in the centre of the disc and is an effect of the inclination angle, whereby the line of sight passes through gas above the midplane and then through the hole in the centre of the disc.
+The majority of the OCS is visible in absorption against the bright continuum emission from the disc mid-plane.
+The exception to this in the centre of the disc and is an effect of the inclination angle, whereby the line of sight passes through gas above the mid-plane and then through the hole in the centre of the disc.
 
@@
 The abundance H$_2$CO molecule is fairly typical of the molecules simulated in Ilee (2011) in that it traces the spiral structure roughly the inner 2/3$^{rd}s$ of the disc.
-The spiral structure of the disc can be seen clearly in the integrated intensity map and its rotation of detected out to larger radii than is possible with the OCS and is more visible between spiral arms but is otherwise simimlar in morphology.
+The spiral structure of the disc can be seen clearly in the integrated intensity map and its rotation of detected out to larger radii than is possible with the OCS and is more visible between spiral arms but is otherwise similar in morphology.
 
@@
 
-In order to make predictions on the observability of the synthetic brightness maps created by LIME, CASA (common astronomy software applications) was used to simulate observing these with the completed ALMA in configuration 26 of 28 for a total time of four hours, giving a beam size of between 0.02 and 0.03 arcseconds.
+In order to make predictions on the observability of the synthetic brightness maps created by LIME, CASA (common astronomy software applications) was used to simulate observing these with the completed ALMA in configuration 26 of 28 for a total time of six hours, giving a beam size of between 0.02 and 0.03 arcseconds.
 In order to clean the images which featured mainly absorption the sky model used was the output of the lime simulations with the continuum subtracted and then the image inverted.
-The simulated images were cleaned down to a 3\sigma level with \sigma given by the online alma sensitivity calculator (ref).
+The simulated images were cleaned down to a 3\sigma level with \sigma given by the on-line ALMA sensitivity calculator (ref).
+
+Sensitivities:
+C17O J=$3\rightarrow2$ at 337.06GHz \sigma=0.0270$\,$mJy$\,$beam$^{-1}$
+OCS J=$26\rightarrow25$ at 316.15GHz \sigma=0.0275$\,$mJy$\,$beam$^{-1}$
+HCO$^+$ J=$3\rightarrow2$ at 267.56GHz \sigma=0.0176$\,$mJy$\,$beam$^{-1}$
+H$_2$CO J=$4_{04}\rightarrow3_{03}$ at 290.62GHz \sigma=0.0228$\,$mJy$\,$beam$^{-1}$
 
@@
 
- \caption{C$^{17}$O 3-2 30 deg integrated intensity simulated for ALMA most extended configuration, contours starting at 3$\sigma$ and increasing in intervals of 3$\sigma$}
+ \caption{Integrated intesity maps for the simulated observations of:{\bf Top Left:} H$_2$CO 4$_{04}$\rightarow3$_{03}$, {\bf Top Right:}C$^{17}$O 3\rightarrow2, {\bf Bottom Left:} OCS 26\rightarrow25 and {\bf Bottom Right:} HCO$^+$ 3\rightarrow2.
+contours start at 3$\sigma$ and increasing in intervals of 3$\sigma$ for each of the maps except the H$_2$CO which starts at 5\sigma and increases in intervals of 5\sigma}
 \end{figure*}
+
+The simulated integrated intesity maps demonstrate how different species allow observations to trace different regions of the disc, from OCS tracing the innermost regions to HCO$^+$ showing the outer regions which are less bright in the continuum.
 
@@
 
- \caption{PVs with model rotation curve}
+ \caption{Position velocity diagrams for each of the species simulated with CASA. The green curve on each diagram is the best fit curve to the azimuthally averaged rotation profile from figure 4.}
 \end{figure*}
@@
 
- \caption{Spectra, H$_2$CO 20AU split, C$^{17}$O 28AU split, OCS 10AU split, HCO$^+$ 38AU split}
+ \caption{Spectra for each of the simulated species.
+In each diagram the three spectra are taken from positions on the Y=0 axis, one is at X=0 (green) and the other 2 are from x=\pm N (plus blue, minus red) where N is different for each species.
+the values for N are: H$_2$CO 20AU, C$^{17}$O 28AU, OCS 10AU, HCO$^+$ 38AU.
+{\bf maybe should put stars or something on the mom0 maps to show these locations?}}
 \end{figure*}
@@
 %The mass of the disc used (0.4$\,\rm{M}_\odot$) is on the high end for early discs (citations for estimate of early class 1 disc masses).\newline
-In the model spirals shock heat the mid-plane layer and the colder more diffuse gas absorbs the continuum from it, this results in molecular lines being seen in absorbtion whenever lines of sight pass through the cold diffuse gas at larger heights on to the hot dense midplane of the disc.
+In the model spirals shock heat the mid-plane layer and the colder more diffuse gas absorbs the continuum from it, this results in molecular lines being seen in absorption whenever lines of sight pass through the cold diffuse gas at larger heights on to the hot dense mid-plane of the disc.
 Rotation curves can be gathered from these observations even with spiral structure\newline
-Outflows could contaminate measurements of rotation curves meaning that speices  which commonly trace outflows, such as CO and HCO$^+$ are not going to be good tracers of disc rotation.
-However speices such as OCS and C$^{18}$O which are not commonly seen in outflows (e.g.
+Outflows could contaminate measurements of rotation curves meaning that species  which commonly trace outflows, such as CO and HCO$^+$ are not going to be good tracers of disc rotation.
+However species such as OCS and C$^{18}$O which are not commonly seen in outflows (e.g.
 van der Tak et al.
@@
 
-\section[]{Other Inclinations}
+\section{Other Inclinations} \label{sec:other_inc}
 

### 2013-01-22 paper.tex

@@
 In order to clean the images which featured mainly absorption the sky model used was the output of the lime simulations with the continuum subtracted and then the image inverted.
-The simulated images were cleaned down to a 3\sigma level with \sigma given by the on-line ALMA sensitivity calculator (ref).
+The simulated images were cleaned down to a 3$\sigma$level with $\sigma$given by the on-line ALMA sensitivity calculator (ref).
 
 Sensitivities:
-C17O J=$3\rightarrow2$ at 337.06GHz \sigma=0.0270$\,$mJy$\,$beam$^{-1}$
-OCS J=$26\rightarrow25$ at 316.15GHz \sigma=0.0275$\,$mJy$\,$beam$^{-1}$
-HCO$^+$ J=$3\rightarrow2$ at 267.56GHz \sigma=0.0176$\,$mJy$\,$beam$^{-1}$
-H$_2$CO J=$4_{04}\rightarrow3_{03}$ at 290.62GHz \sigma=0.0228$\,$mJy$\,$beam$^{-1}$
+C17O J=$3\rightarrow2$ at 337.06GHz $\sigma$=0.0270$\,$mJy$\,$beam$^{-1}$
+OCS J=$26\rightarrow25$ at 316.15GHz $\sigma$=0.0275$\,$mJy$\,$beam$^{-1}$
+HCO$^+$ J=$3\rightarrow2$ at 267.56GHz $\sigma$=0.0176$\,$mJy$\,$beam$^{-1}$
+H$_2$CO J=$4_{04}\rightarrow3_{03}$ at 290.62GHz $\sigma$=0.0228$\,$mJy$\,$beam$^{-1}$
 
@@
 
- \caption{Integrated intesity maps for the simulated observations of:{\bf Top Left:} H$_2$CO 4$_{04}$\rightarow3$_{03}$, {\bf Top Right:}C$^{17}$O 3\rightarrow2, {\bf Bottom Left:} OCS 26\rightarrow25 and {\bf Bottom Right:} HCO$^+$ 3\rightarrow2.
-contours start at 3$\sigma$ and increasing in intervals of 3$\sigma$ for each of the maps except the H$_2$CO which starts at 5\sigma and increases in intervals of 5\sigma}
+ \caption{Integrated intesity maps for the simulated observations of:{\bf Top Left:} H$_2$CO 4$_{04}\rightarrow$3$_{03}$, {\bf Top Right:}C$^{17}$O 3$\rightarrow$2, {\bf Bottom Left:} OCS 26$\rightarrow$25 and {\bf Bottom Right:} HCO$^+$ 3$\rightarrow$2.
+contours start at 3$\sigma$ and increasing in intervals of 3$\sigma$ for each of the maps except the H$_2$CO which starts at 5$\sigma$ and increases in intervals of 5$\sigma$.}
 \end{figure*}
@@
  \caption{Spectra for each of the simulated species.
-In each diagram the three spectra are taken from positions on the Y=0 axis, one is at X=0 (green) and the other 2 are from x=\pm N (plus blue, minus red) where N is different for each species.
+In each diagram the three spectra are taken from positions on the Y=0 axis, one is at X=0 (green) and the other 2 are from x=$\pm$ N (plus blue, minus red) where N is different for each species.
 the values for N are: H$_2$CO 20AU, C$^{17}$O 28AU, OCS 10AU, HCO$^+$ 38AU.

### 2013-01-22 paper.tex
tweaks to lime mom1 maps

@@
 The simulations were focused upon frequencies within ALMA band 7, selected to give the best trade off between resolution and sensitivity for early ALMA science.
-(Note the moment 1 and 0 maps were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in some PV diagrams as the strong absorption feature at all positions around zero velocity, moment 1 maps are shown with a cut-off of 1/100 of the peak emission/absorption value)\newline
+(Note the moment 1 and 0 maps were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in some PV diagrams as the strong absorption feature at all positions around zero velocity, moment 1 maps are shown with a cut-off of 3$\sigma$ as defined in section \ref{alma_predicions})\newline
 
@@
 \begin{figure*}
- \includegraphics[width=168mm]{Figures/sim/imageOCS_28-27_30deg_composite_all.eps}
+ \includegraphics[width=168mm]{Figures/sim/imageOCS_26-25_30deg_composite_all.eps}
  \label{OCS_all}
@@
 \begin{figure*}
- \includegraphics[width=168mm]{Figures/sim/imageHCOp_1-0_30deg_composite_all.eps}
+ \includegraphics[width=168mm]{Figures/sim/imageHCOp_3-2_30deg_all.eps}
  \label{hco+_all}
- \caption{HCO$^+$ 1-0 {\bf Left:} Continuum subtracted integrated intensity map, {\bf Right:} Intensity weighted velocity map}
+ \caption{HCO$^+$ 3-2 {\bf Left:} Continuum subtracted integrated intensity map, {\bf Right:} Intensity weighted velocity map}
 \end{figure*}

### 2013-01-22 paper.tex
x

--- 2013-01-22 paper.tex
@@
 
-Sensitivities:
+Sensitivities:\newline
 C17O J=$3\rightarrow2$ at 337.06GHz $\sigma$=0.0270$\,$mJy$\,$beam$^{-1}$

### 2013-01-23 paper.tex
more text added

--- 2013-01-22 paper.tex
@@
 2011).
+Zapata et al.
+(2013) used ALMA to observe a disc of size $\sim$50$\,$AU in the other Class 0 source in IRAS 16293-2422 and detected infall towards this disc as inverse P-Cygni profiles in HCN and CH$_3$OH.
 When ALMA will be completed, it will be finally possible to spatially resolve these young discs and, for the first time, put stringent constraints on theoretical models.
@@
 
-Previous work on simulating observations of gravitationally unstable discs have performed calculations of the continuum radiative transfer in order to look at the structure of the disc to detect disc fragmentation (Ruge et al.
+Previous work on simulating observations of gravitationally unstable discs have performed calculations of the continuum radiative transfer in order to look at the structure of the disc and detect disc fragmentation (Ruge et al.
 2012) or have used the local thermodynamic equilibrium (LTE) approximation in order to estimate the molecular line emission for an unembedded disc (Krumholtz et al.
@@
 (2011) and identify the best tracers of the physical structure of self-gravitating discs.
-The physical, chemical and radiative transfer models are described in Sect\,\ref{sec:description_model}.
-Radiative transfer results are in Sect.\,\ref{sec:model_results}, while ALMA simulated observations are in Sec.\,\ref{sec:alma_predictions}.
+The physical, chemical and radiative transfer models are described in Sect.\,\ref{sec:description_model}.
+Radiative transfer results are in Sect.\,\ref{sec:model_results}, while ALMA simulated observations are in Sect.\,\ref{sec:alma_predictions}.
 Discussions and conclusions can be found in Sect.\,\ref{sec:discussion}.
@@
 The KC2010 model follows the dynamical, chemical and thermal evolution of a contracting Bonnor-Ebert sphere (Bonnor 1956; Ebert 1957) with total mass of 10\,M$_{\odot}$, until it reaches the density, temperature and velocity profiles which best match observations.
-The pre-stellar core model adopted here contains slight modifications due to the inclusion of oxygen cooling in the outer regions of the cloud, where CO is mostly photodissociated (Keto et al., in preparation), and it is shown in Fig.\,\ref{fig:l1544_model}.
+The pre-stellar core model adopted here contains slight modifications due to the inclusion of oxygen cooling in the outer regions of the cloud, where CO is mostly dissociated (Keto et al., in preparation), and it is shown in Fig.\,\ref{fig:l1544_model}.
 \newline
@@
  \includegraphics[width=84mm]{Figures/model/L1544model_used_legend_small.eps}
- \label{fig:l1544_model}
  \caption{Model of the pre-stellar core L1544 used as the envelope of the young protoplanetary disc in the hybrid model.
@@
 Adapted from Keto \& Caselli (2010) and Keto et al.
-(2012, in preparation).}
+(2013, in preparation).}
+ \label{fig:l1544_model}
 \end{figure}
@@
  \includegraphics[width=168mm]{Figures/model/rhoT6.eps}
- \label{rhoT} 
  \caption{{\bf Left:} A 3D plot of log number density (cm$^{-3}$) showing the spiral structure in the xy plane and scale height of the disc.
 {\bf Right:} The 3D temperature structure of the disc; regions cooler than 40 degrees are not shown in 3D, demonstrating the narrow central region containing hot material.}
+ \label{rhoT} 
 \end{figure*}
@@
  \includegraphics[width=168mm]{Figures/model/columnDensities2.eps}
+ \caption{Column densities of OCS, H$_2$CO and HCO$^+$ used in the disc model. Figure adapted from Ilee at al. (2011) [SHOULD WE ALSO ADD C18O COLUMN DENSITY AS WE WANT TO DISCUSS THAT LATER ?? ]}
  \label{Chemistry} 
- \caption{Column densities of OCS, H$_2$CO and HCO$^+$ used in the disc model. Figure adapted from Ilee at al. (2011) [SHOULD WE ALSO ADD C18O COLUMN DENSITY AS WE WANT TO DISCUSS THAT LATER ?? ]}
 \end{figure*}
@@
  \includegraphics[width=84mm]{Figures/model/rotational_velocities.eps}
+ \caption{Azimuthaly averaged rotational velocity in the disc mid-plane with best fit curve}
  \label{velocity}
- \caption{Azimuthaly averaged rotational velocity in the disc mid-plane with best fit curve}
 \end{figure}
 
-%-describe the physical structure of the disc (density and temperature) -- one figure showing the physical structure and the kinematics (2-panels figure)
 The pre-stellar core structure is maintained down to a radius of 80\,AU, within which the young protoplanetary disc has been plugged in.
@@
 The dust and gas temperatures in the disc are assumed to be in equilibrium.
-The model is sampled over a regular grid of size 256$\times$256$\times$64 with spatial resolution of 0.5$\,$au in x, y and z.
+The model is sampled over a regular grid of size 256$\times$256$\times$64 with spatial resolution of 0.5$\,$AU in x, y and z.
 The gas/dust mass ratio was assumed to be 1/100 throughout both sections model and the opacities were given by the model of dust grains with thick icy mantles and 10$^6\,$yr coagulation from Ossenkopf and Henning (1994).
-The gas number density and temperature structure are displayed in Fig.
-XX.
+The gas number density and temperature structure are displayed in Figure \ref{rhoT}.
 \newline
 
-%The majority of the mass lies in the mid-plane of the disc.
-For the models using a smoothed disc the same physical and chemical model is used but with the temperature, density and abundance averaged in $\phi$.
-The gas/dust mass ratio was assumed to be 1/100 throughout both sections model and the opacities were given by the model of dust grains with thick icy mantles and 10$^6\,$yr coagulation from Ossenkopf and Henning (1994)\newline
-
-%-describe the chemistry  - refer to Ilee et al. which have been taken as input to the rad transfer (RT) code
 Chemical abundances in the disc were taken from Ilee et.
@@
 The abundances of 125 species related by 1334 reactions were followed through the time evolution of the disc.
-These abundances were interpolated onto a 51$^3$ grid covering the disc with cells of size 2.2$\times$2.2$\times$0.22$\,$au.
+These abundances were interpolated onto a 51$^3$ grid covering the disc with cells of size 2.2$\times$2.2$\times$0.22$\,$AU.
 From Ilee et al.
-(2011) we selected the three species which appear to trace different regions of the disc : the inner 30\,AU (OCS), the inner 60\,AU (H$_2$CO) and the region between $\simeq$20 and 60\,AU (HCO$^+$) and one which traces the entirety of the disc (C$^{18}$O).
+(2011) we selected the three species which appear to trace different regions of the disc : the inner 20\,AU (OCS), the inner 40\,AU (H$_2$CO) and the region between $\simeq$40 and 60\,AU (HCO$^+$) and one which traces the entirety of the disc (C$^{17}$O).
 As explained by Ilee et al.
@@
 At each of these points, the density of the main collision partner (H$_2$), gas and dust temperatures, velocity, molecular abundances and turbulent velocity are taken from the model.
-These points are then smoothed by Lloyds algorithm (Lloyd 1982) in order to minimise the variation in distance between points whilst keeping the same underlying distribution.
+These points are then smoothed by Lloyd's algorithm (Lloyd 1982) in order to minimise the variation in distance between points whilst keeping the same underlying distribution.
 These points are then connected by Delaunay triangulation \footnote{In three dimensions this means that if four points are connected into a tetrahedron, the sphere circumscribing these four points contains no other points.
@@
 
-Transitions focused upon are CO 3-2 (and isotopologues) at 345.8GHz with an upper energy level of 33.2K, HCO+ 3-2 at 267GHZ and 25.7K, OCS 26-25 at 316GHz and 205K and H2CO $4_{04}$-3$_{03}$ at 290GHz and 34.9K {\bf maybe worth including a higher frequency line as well?
+Transitions focused upon are CO 3-2 (and isotopologues) at 345.8GHz with an upper energy level of 33.2K, HCO$^+$ 3-2 at 267GHZ and 25.7K, OCS 26-25 at 316GHz and 205K and H$_2$CO $4_{04}$-3$_{03}$ at 290GHz and 34.9K {\bf maybe worth including a higher frequency line as well?
 CS at ~650GHz?}.
@@
 The simulations were focused upon frequencies within ALMA band 7, selected to give the best trade off between resolution and sensitivity for early ALMA science.
-(Note the moment 1 and 0 maps were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in some PV diagrams as the strong absorption feature at all positions around zero velocity, moment 1 maps are shown with a cut-off of 1/100 of the peak emission/absorption value)\newline
+(Note the moment 1 and 0 maps were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in some PV diagrams as the strong absorption feature at all positions around zero velocity, moment 1 maps are shown with a cut-off of 3$\sigma$ as described in section \ref{sec:alma_predictions})\newline
 
@@
 
-OCS traces only the innermost region of the disc and can be used to examine the central regions.
+OCS traces only the innermost region of the disc and can be used to examine the central regions (figure \ref{OCS_all}).
 As OCS is not seen in outflows it can be used to view rotation of the central part of the disc without risk of contamination.
 As the excitation energy for the high J transitions of OCS is much higher than the other lines under consideration it is only excited in the hottest densest regions.
-As a result of this the spiral structure is clearer in OCS than in most transitions, with the low density regions between spiral arms showing no emission or absorption(see figure \ref{ocs_all}).
+As a result of this the spiral structure is clearer in OCS than in most transitions, with the low density regions between spiral arms showing no emission or absorption(see figure \ref{OCS_all}).
 The majority of the OCS is visible in absorption against the bright continuum emission from the disc mid-plane.
@@
  \includegraphics[width=168mm]{Figures/sim/imageH2CO_4-0-4--3-0-3_30deg_composite_all.eps}
+ \caption{H$_2$CO 4$_{0\,4}$ - 3$_{\,0\,3}$ {\bf Left:} Continuum subtracted integrated intensity map, {\bf Right:} Intensity weighted velocity map}
  \label{h2co_all}
- \caption{H$_2$CO 4$_{0\,4}$ - 3$_{\,0\,3}$ {\bf Left:} Continuum subtracted integrated intensity map, {\bf Right:} Intensity weighted velocity map}
 \end{figure*}
@@
 
-The abundance H$_2$CO molecule is fairly typical of the molecules simulated in Ilee (2011) in that it traces the spiral structure roughly the inner 2/3$^{rd}s$ of the disc.
+The abundance of the H$_2$CO molecule is fairly typical of the molecules simulated in Ilee (2011) in that it traces the spiral structure roughly the inner 2/3$^{rd}s$ of the disc.
 The spiral structure of the disc can be seen clearly in the integrated intensity map and its rotation of detected out to larger radii than is possible with the OCS and is more visible between spiral arms but is otherwise similar in morphology.
@@
 \begin{figure*}
- \includegraphics[width=168mm]{Figures/sim/imageHCOp_1-0_30deg_composite_all.eps}
+  \includegraphics[width=168mm]{Figures/sim/imageHCOp_1-0_30deg_composite_all.eps}  \caption{HCO$^+$ 1-0 {\bf Left:} Continuum subtracted integrated intensity map, {\bf Right:} Intensity weighted velocity map}
   \label{hco+_all}
- \caption{HCO$^+$ 1-0 {\bf Left:} Continuum subtracted integrated intensity map, {\bf Right:} Intensity weighted velocity map}
 \end{figure*}
@@
 In these colder less dense regions we see the molecular lines in emission rather than absorption.
-Figure \ref{hcop_pv} shows the rotation curve of the model as shown in figure \ref{velocity} against the HCO$^+$ J=1-0 line emission.
-It is clear that from observations such as these the rotation curve of a disc could be reconstructed.\newline
+\newline
+%Figure \ref{hcop_pv} shows the rotation curve of the model as shown in figure \ref{velocity} against the HCO$^+$ J=1-0 line emission.
+It is clear that from observations such as these the rotation curve of a disc
 
@@
 Sensitivities:\newline
-C17O J=$3\rightarrow2$ at 337.06GHz $\sigma$=0.0270$\,$mJy$\,$beam$^{-1}$
-OCS J=$26\rightarrow25$ at 316.15GHz $\sigma$=0.0275$\,$mJy$\,$beam$^{-1}$
-HCO$^+$ J=$3\rightarrow2$ at 267.56GHz $\sigma$=0.0176$\,$mJy$\,$beam$^{-1}$
-H$_2$CO J=$4_{04}\rightarrow3_{03}$ at 290.62GHz $\sigma$=0.0228$\,$mJy$\,$beam$^{-1}$
+C17O J=3$\rightarrow$2 at 337.06GHz $\sigma$=0.0270$\,$mJy$\,$beam$^{-1}$ \newline
+OCS J=26$\rightarrow$25 at 316.15GHz $\sigma$=0.0275$\,$mJy$\,$beam$^{-1}$ \newline
+HCO$^+$ J=3$\rightarrow$2 at 267.56GHz $\sigma$=0.0176$\,$mJy$\,$beam$^{-1}$ \newline
+H$_2$CO J=4$_{04}\rightarrow$3$_{03}$ at 290.62GHz $\sigma$=0.0228$\,$mJy$\,$beam$^{-1}$ \newline
 
@@
  \caption{Continuum emission at 337GHz simulated for ALMA most extended configuration}
+ \label{continuum}
 \end{figure}
@@
  \includegraphics[width=168mm]{Figures/sim/channel_map-1.eps} 
- \label{h2co_chanmap}
  \caption{H$_2$CO 4$_{04}$-3$_{03}$ channel maps as simulated by CASA.
@@
 Each map integrates over 2.4 km$\,$s$^{-1}$ with the top left from -10.8 to -8.4 km$\,$s$^{-1}$ to the bottom left ranging from 8.4 to 10.8 km$\,$s$^{-1}$}
+ \label{h2co_chanmap}
 \end{figure*}
+
+Figure \ref{h2co_chanmap} shows a channel map of the H$_2$CO 4$_{04}$-$3_{03}$ line overlaid on the 1$\,$mm continuum emission.
+From this it can be seen that the absorption features trace the disc spiral structure whilst line emission emanates from gaps in the disc where there is less continuum to be absorbed.{\bf not sure what else to say about channel map ask paola}
 
@@
  \includegraphics[width=168mm]{Figures/sim/casa_all_30deg_contSub.eps}
-
- \caption{Integrated intesity maps for the simulated observations of:{\bf Top Left:} H$_2$CO 4$_{04}\rightarrow$3$_{03}$, {\bf Top Right:}C$^{17}$O 3$\rightarrow$2, {\bf Bottom Left:} OCS 26$\rightarrow$25 and {\bf Bottom Right:} HCO$^+$ 3$\rightarrow$2.
+ \caption{Integrated intensity maps for the simulated observations of:{\bf Top Left:} H$_2$CO 4$_{04}\rightarrow$3$_{03}$, {\bf Top Right:}C$^{17}$O 3$\rightarrow$2, {\bf Bottom Left:} OCS 26$\rightarrow$25 and {\bf Bottom Right:} HCO$^+$ 3$\rightarrow$2.
 contours start at 3$\sigma$ and increasing in intervals of 3$\sigma$ for each of the maps except the H$_2$CO which starts at 5$\sigma$ and increases in intervals of 5$\sigma$.}
+\label{mom0_maps}
 \end{figure*}
 
-The simulated integrated intesity maps demonstrate how different species allow observations to trace different regions of the disc, from OCS tracing the innermost regions to HCO$^+$ showing the outer regions which are less bright in the continuum.
+Figure \ref{mom0_maps} shows the simulated integrated intensity maps demonstrate how different species allow observations to trace different regions of the disc, from OCS tracing the innermost regions to HCO$^+$ showing the outer regions which are less bright in the continuum.
+ALMA has enough resolution and sensitivity to see spiral structure clearly in continuum emission but also in CO isotopologues and marginally in H$_2$CO.
 
@@
  \includegraphics[width=198mm]{Figures/sim/casa_all_30deg_PV_rotCurve.eps}
+ \caption{Position velocity diagrams for each of the species simulated with CASA.
+The green curve on each diagram is the best fit curve to the azimuthally averaged rotation profile from figure 4.{\bf *****labels of h2co and ocs are wrong way round*****}}
+ \label{pvs}
+\end{figure*}
 
- \caption{Position velocity diagrams for each of the species simulated with CASA. The green curve on each diagram is the best fit curve to the azimuthally averaged rotation profile from figure 4.}
-\end{figure*}
+Figure \ref{pvs} shows position-velocity diagrams of the simulated lines, allowing us to reconstruct the rotation of the disc.
+The curve also shown in these figures is the best fit rotation curve of the physical model (see figure \ref{velocity}), showing that the rotation profile of the disc can be well constrained using kinematic information gathered from species tracing different regions of the disc.
 
@@
 In each diagram the three spectra are taken from positions on the Y=0 axis, one is at X=0 (green) and the other 2 are from x=$\pm$ N (plus blue, minus red) where N is different for each species.
-the values for N are: H$_2$CO 20AU, C$^{17}$O 28AU, OCS 10AU, HCO$^+$ 38AU.
+the values for N are: OCS 10AU, H$_2$CO 20AU, C$^{17}$O 28AU, HCO$^+$ 38AU.
 {\bf maybe should put stars or something on the mom0 maps to show these locations?}}
+ \label{spectra}
 \end{figure*}
+
+Figure \ref{spectra} shows spectra from the lines simulated, one from the centre of the image and one on each side of the disc along the Y=0 axis.
+The most notable thing about these is, despite the fact that the spectra are equally spaced about the centre of the disc, they are not symmetric.
+Most noticeably in the C$^{17}$O the spectrum from the +X side of the disc is shows significantly more absorption than that of the -X side.
+In the OCS lines, the two sides are not moving with equal velocities and the line widths and shapes are markedly different.
+These can be atributed to the non-axissymmetric nature of the model.
+%Spectra show stuff, i guess? not really sure if this adds anything to the pv diagrams.
 
@@
 
-PV diagrams allow us to reconstruct the rotation of the disc.
-ALMA has enough resolution and sensitivity to see spiral structure clearly in continuum emission but also in CO isotopologues and marginally in OCS.
-
 \section{Discussion and conclusions} \label{sec:discussion}
@@
 The quiescent nature of the envelope around such discs only obscures them within $\pm\,0.5 km\,s^{-1}$.\newline
-One assumption made in this model is that the gas and dust are in thermal equilibrium.If they are not and the dust is significantly cooler than the gas then transitions may not show up in absorption.\newline
+One assumption made in this model is that the gas and dust are in thermal equilibrium in the disc.
+If they are not and the dust is significantly cooler than the gas then transitions may not show up in absorption.\newline
 %The mass of the disc used (0.4$\,\rm{M}_\odot$) is on the high end for early discs (citations for estimate of early class 1 disc masses).\newline

### 2013-01-24 paper.tex
figs edited, text slightly changed

@@
 John Ilee$^{1}$ and
-Jonathon Rawlings$^{4}$\\
+Jonathan Rawlings$^{4}$\\
 \vspace{0.1cm}\\
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/model/Lime_grid3.eps}
+ \includegraphics[width=84mm]{Figures/model/grid.eps}%Lime_grid3.eps
  \label{grid}
@@
 Simulations are limited to molecules for which we have abundances in both the disc and envelope, and also have calculated Einstein and collisional coefficients.
-The Molecular data used is from the lamda database (reference?
-http://home.strw.leidenuniv.nl/$\sim$moldata/).
+The Molecular data used is from the lamda database (Sch\"oier et al.
+(2005) http://home.strw.leidenuniv.nl/$\sim$moldata/).
 Lines for the molecules which satisfy these conditions were simulated with LIME for frequencies between 50$\sim$500$\,$GHz, with a focus on lines which could be observed in ALMA band 7 and molecules which are not typically seen in outflows.
@@
  \includegraphics[width=84mm]{Figures/sim/continuum.eps}
- \label{points}
- \caption{A 300$\,$GHz continuum image of the model, created from the average of ten LIME runs.}
+ \caption{{\bf Left:}A 300$\,$GHz continuum image of the model, created from the average of ten LIME runs.
+{\bf Right:} the output of a single radiative transfer simulation, with artefacts due to finite gridding.}
+ \label{averages}
 \end{figure}
@@
 \begin{figure*}
- \includegraphics[width=168mm]{Figures/sim/imageOCS_28-27_30deg_composite_all.eps}
+ \includegraphics[width=168mm]{Figures/sim/imageOCS_26-25_30deg_all.eps}
+ \caption{OCS 28-27 {\bf Left:} Continuum subtracted integrated intensity map showing clearly differentiated spiral structure in the inner regions of the disc, {\bf Right:} Intensity weighted velocity map}
  \label{OCS_all}
- \caption{OCS 28-27 {\bf Left:} Continuum subtracted integrated intensity map showing clearly differentiated spiral structure in the inner regions of the disc, {\bf Right:} Intensity weighted velocity map}
 \end{figure*}
@@
 \begin{figure*}
-  \includegraphics[width=168mm]{Figures/sim/imageHCOp_1-0_30deg_composite_all.eps}  \caption{HCO$^+$ 1-0 {\bf Left:} Continuum subtracted integrated intensity map, {\bf Right:} Intensity weighted velocity map}
+  \includegraphics[width=168mm]{Figures/sim/imageHCOp_3-2_30deg_all.eps}  \caption{HCO$^+$ 3-2 {\bf Left:} Continuum subtracted integrated intensity map, {\bf Right:} Intensity weighted velocity map}
   \label{hco+_all}
@@
 
-In order to make predictions on the observability of the synthetic brightness maps created by LIME, CASA (common astronomy software applications) was used to simulate observing these with the completed ALMA in configuration 26 of 28 for a total time of six hours, giving a beam size of between 0.02 and 0.03 arcseconds.
+In order to make predictions on the observability of the synthetic brightness maps CASA (common astronomy software applications) was used to simulate their observtion with the completed ALMA in configuration 26 of 28, giving a beam size of between 0.02 and 0.03 arcseconds.
+As the weakest lines studied in the model are of the order of 0.1-0.2$\,$mJy$\,$beam$^{-1}$ at this resolution, sensitivities of the order of 0.02$\,$mJy$\,$beam$^{-1}$ are required.
+This requires around 6 hours of integration time, the exact sensitivities are give in table \ref{sigmas}.
+
+\begin{table}
+ \centering
+ \begin{minipage}{80mm}
+   \caption{Sensitivities of ALMA given 6 hours integration time. As calculated by the ALMA on-line sensitivity calculator.}
+   \label{sigmas}
+   \begin{tabular}{c||c|c|c}
+     \hline
+     Species & Transition & Frequency & Sensitivity\\
+     \hline
+     C$^{17}$O & J=3$\rightarrow$2 & 337.06GHz & 0.0270$\,$mJy$\,$beam$^{-1}$ \\
+     OCS & J=26$\rightarrow$25 & 316.15GHz & 0.0275$\,$mJy$\,$beam$^{-1}$ \\
+     HCO$^+$ & J=3$\rightarrow$2 & 267.56GHz & 0.0176$\,$mJy$\,$beam$^{-1}$ \\
+     H$_2$CO & 4$_{04}\rightarrow$3$_{03}$ & 290.62GHz & 0.0228$\,$mJy$\,$beam$^{-1}$ \\
+     \hline
+   \end{tabular}
+ \end{minipage}
+\end{table}
+
  In order to clean the images which featured mainly absorption the sky model used was the output of the lime simulations with the continuum subtracted and then the image inverted.
-The simulated images were cleaned down to a 3$\sigma$level with $\sigma$given by the on-line ALMA sensitivity calculator (ref).
-
-Sensitivities:\newline
-C17O J=3$\rightarrow$2 at 337.06GHz $\sigma$=0.0270$\,$mJy$\,$beam$^{-1}$ \newline
-OCS J=26$\rightarrow$25 at 316.15GHz $\sigma$=0.0275$\,$mJy$\,$beam$^{-1}$ \newline
-HCO$^+$ J=3$\rightarrow$2 at 267.56GHz $\sigma$=0.0176$\,$mJy$\,$beam$^{-1}$ \newline
-H$_2$CO J=4$_{04}\rightarrow$3$_{03}$ at 290.62GHz $\sigma$=0.0228$\,$mJy$\,$beam$^{-1}$ \newline
+The simulated images were cleaned down to a 3$\sigma$level with $\sigma$ given in table \ref{sigmas}.
 
@@
 Figure \ref{h2co_chanmap} shows a channel map of the H$_2$CO 4$_{04}$-$3_{03}$ line overlaid on the 1$\,$mm continuum emission.
-From this it can be seen that the absorption features trace the disc spiral structure whilst line emission emanates from gaps in the disc where there is less continuum to be absorbed.{\bf not sure what else to say about channel map ask paola}
+From this it can be seen that the absorption features trace the disc spiral structure whilst line emission emanates from gaps in the disc where there is less continuum to be absorbed.
 
@@
  \caption{Integrated intensity maps for the simulated observations of:{\bf Top Left:} H$_2$CO 4$_{04}\rightarrow$3$_{03}$, {\bf Top Right:}C$^{17}$O 3$\rightarrow$2, {\bf Bottom Left:} OCS 26$\rightarrow$25 and {\bf Bottom Right:} HCO$^+$ 3$\rightarrow$2.
-contours start at 3$\sigma$ and increasing in intervals of 3$\sigma$ for each of the maps except the H$_2$CO which starts at 5$\sigma$ and increases in intervals of 5$\sigma$.}
+contours start at 3$\sigma$ and increasing in intervals of 3$\sigma$ for each of the maps except the H$_2$CO which starts at 5$\sigma$ and increases in intervals of 5$\sigma$.
+Emission is in red contours, absorption in blue.}
 \label{mom0_maps}

### 2013-02-04 paper.tex
added next lot of PC comments

@@
 
-\date{In original form 2013}
+\date{Jan 2013}
 
@@
 ALMA will soon revolutionise this field, so it is important to provide predictions and help the interpretation of future high sensitivity and high angular resolution observations.
-Here we present simulated ALMA observations of a relatively massive (0.39 M$_{\odot}$) self-gravitating disc embedded in a 10\,M$_{\odot}$ envelope with a structure similar to the pre-stellar core L1544.
-We focus on simple species and conclude that OCS is among the best tracers to measure the disc structure and kinematics.
+Here we present simulated ALMA observations based on radiative transfer modelling of a relatively massive (0.39 M$_{\odot}$) self-gravitating disc embedded in a 10\,M$_{\odot}$ dense core, with structure similar to the pre-stellar core L1544.
+We focus on simple species and conclude that OCS, C$^{17}$O, H$_2$CO and HCO$^+$ lines together allow measurements of the disc structure and kinematics at all scales.
 \end{abstract}
@@
 2011; Machida et al.
-2011; Braiding \& Wardle 2012).
-The reason for this is that young protostars are surrounded by thick envelopes and power energetic outflows, thus observations of the young discs, predicted to have sizes of about 100\,AU and masses as large as 10\% the original core mass (e.g.
+2011; Braiding \& Wardle 2012; Joos et al.
+2013).
+The reason for this is that young protostars are surrounded by thick envelopes and power energetic outflows.
+Thus, observations of the young discs, predicted to have sizes of about 100\,AU and masses as large as 10\% the original core mass (e.g.
 Joos et al.
@@
 (2000), recent interferometric observations have discovered compact embedded discs in a sample of Class 0 (Andr\'e et al.
-2000) sources, finding masses between 0.4 and  $>$1 M$_{\odot}$ (Jorgensen et al.
+2000) sources, finding masses between 0.4 and  $>$1 M$_{\odot}$ (J\o rgensen et al.
 2007, 2009; Enoch et al.
@@
 
-Previous work on simulating observations of gravitationally unstable discs have performed calculations of the continuum radiative transfer in order to look at the structure of the disc and detect disc fragmentation (Ruge et al.
+%Previous work on simulating observations of gravitationally unstable discs have performed calculations of the continuum radiative transfer in order to look at the structure of the disc and detect disc fragmentation (Ruge et al.
 2012) or have used the local thermodynamic equilibrium (LTE) approximation in order to estimate the molecular line emission for an unembedded disc (Krumholtz et al.
@@
 
-In this paper, we focus our attention to the young self-gravitating discs of Boley \& Durisen (2008), where episodic heating induced by spiral shocks is present, as this may be a good representation of the earliest phases of protoplanetary discs and an alternative to the young ``static'' discs studied by, e.g.
-Visser et al.
+Simulated observations of gravitationally unstable discs have already been performed to study the continuum emission and measure the structure and possible fragmentation (Cossins et al.
+2010; Ruge et al.
+2013).
+Molecular line emission from massive discs has been simulated by Krumholz et al.
+(2007), assuming local thermodynamic equilibrium (LTE).
+In this paper, we focus on the self-gravitating discs of Boley \& Durisen (2008), where episodic heating induced by spiral shocks is present.
+This may be a good representation of the earliest phases of protoplanetary discs and an alternative to the young ``static'' discs studied by, e.g., Visser et al.
 (2009, 2011).
 As shown by Ilee et al.
-(2011), the spiral shocks cause desorption of volatiles from dust icy mantles and trigger gas-phase chemical reactions with activation energies, too high to occur at lower temperatures.
+(2011; hereafter I2011), the spiral shocks cause desorption of volatiles from dust icy mantles and trigger gas-phase chemical reactions with activation energies, too high to occur at lower temperatures.
 These processes produce clear chemical signatures of the disc dynamics.
-With the use of 3D radiative transfer modelling, we perform simulated ALMA observations of the disc studied by Ilee et al.
-(2011) and identify the best tracers of the physical structure of self-gravitating discs.
+With the use of 3D radiative transfer modelling, we perform simulated ALMA observations of the disc studied by I2011 and identify the best tracers of the physical structure of self-gravitating discs.
 The physical, chemical and radiative transfer models are described in Sect.\,\ref{sec:description_model}.
@@
 
-The physical model used to simulate the emission from a young protoplanetary disc is a hybrid model obtained from embedding a gravitationally unstable protoplanetary disc  within an envelope with characteristics similar to the well-studied pre-stellar core L1544, as derived by Keto \& Caselli (2010; hereafter KC2010).
+The physical model used to simulate the emission from a young protoplanetary disc is a hybrid model obtained from embedding a gravitationally unstable protoplanetary disc  within a dense core with characteristics similar to the well-studied pre-stellar core L1544, (Keto \& Caselli 2010; hereafter KC2010).
 The KC2010 model follows the dynamical, chemical and thermal evolution of a contracting Bonnor-Ebert sphere (Bonnor 1956; Ebert 1957) with total mass of 10\,M$_{\odot}$, until it reaches the density, temperature and velocity profiles which best match observations.
-The pre-stellar core model adopted here contains slight modifications due to the inclusion of oxygen cooling in the outer regions of the cloud, where CO is mostly dissociated (Keto et al., in preparation), and it is shown in Fig.\,\ref{fig:l1544_model}.
+The pre-stellar core model adopted here contains slight modifications due to the inclusion of oxygen cooling in the outer regions of the cloud, where CO is mostly photodissociated (Caselli et al.
+2012; Keto et al.
+in preparation), and it is shown in Fig.\,\ref{fig:l1544_model}.
 \newline
@@
  \caption{Model of the pre-stellar core L1544 used as the envelope of the young protoplanetary disc in the hybrid model.
-Showing temperature (red) and dust (green) temperature in kelvin, log number density (blue) in cm$^{-3}$ and inward velocity$\times$100 (cyan) in m$\,$s$^{-1}$.
+Showing temperature (green) and dust (red) temperature in kelvin, log number density (blue) in cm$^{-3}$ and inward velocity$\times$100 (cyan) in m$\,$s$^{-1}$.
 Adapted from Keto \& Caselli (2010) and Keto et al.
@@
  \caption{{\bf Left:} A 3D plot of log number density (cm$^{-3}$) showing the spiral structure in the xy plane and scale height of the disc.
-{\bf Right:} The 3D temperature structure of the disc; regions cooler than 40 degrees are not shown in 3D, demonstrating the narrow central region containing hot material.}
+{\bf Right:} The 3D temperature structure of the disc; regions cooler than 40 degrees are not shown in 3D, highlighting the narrow central region containing hot material.}
  \label{rhoT} 
@@
  \includegraphics[width=168mm]{Figures/model/columnDensities2.eps}
- \caption{Column densities of OCS, H$_2$CO and HCO$^+$ used in the disc model. Figure adapted from Ilee at al. (2011) [SHOULD WE ALSO ADD C18O COLUMN DENSITY AS WE WANT TO DISCUSS THAT LATER ?? ]}
+ \caption{Column densities of OCS, H$_2$CO and HCO$^+$ used in the disc model. Figure adapted from I2011 [SHOULD WE ALSO ADD C17O COLUMN DENSITY AS WE WANT TO DISCUSS THAT LATER ?? ]}
  \label{Chemistry} 
@@
 The pre-stellar core structure is maintained down to a radius of 80\,AU, within which the young protoplanetary disc has been plugged in.
-The disc structure is derived by the hydrodynamic model of Boley(2007) and Boley (2009).
-The particular model considered here (as well as in Ilee et al.
-2011) is a 0.39$\,\rm{M}_\odot$ self-gravitating disc featuring prominent spiral arms.
+The disc structure is derived by the hydrodynamic model of Boley (2007) and Boley (2009).
+The particular model considered here (as well as in I2011) is a 0.39$\,\rm{M}_\odot$ self-gravitating disc featuring prominent spiral arms.
 H$_2$ number densities in the disc range from 10$^{4}$-10$^{13}\,\rm{cm}^{-3}$, and temperatures range from 30-400 K (figure \ref{rhoT}).
 The dust and gas temperatures in the disc are assumed to be in equilibrium.
-The model is sampled over a regular grid of size 256$\times$256$\times$64 with spatial resolution of 0.5$\,$AU in x, y and z.
-The gas/dust mass ratio was assumed to be 1/100 throughout both sections model and the opacities were given by the model of dust grains with thick icy mantles and 10$^6\,$yr coagulation from Ossenkopf and Henning (1994).
-The gas number density and temperature structure are displayed in Figure \ref{rhoT}.
-\newline
+The underlying model from which the radiative transefer grid is sampled is a regular grid of size 256$\times$256$\times$64 with spatial resolution of 0.5$\,$AU in x, y and z.
+The gas/dust mass ratio was assumed to be 1/100 throughout both sections model and the opacities were adopted from Ossenkops and Henning (1994) and refer to dust grains with thick icy mantles and 10$^6$ yr coagulation history.\newline
 
-Chemical abundances in the disc were taken from Ilee et.
-al (2011) which followed the changes of chemical abundances of trace particles moving through the disc as it evolved.
-The abundances of 125 species related by 1334 reactions were followed through the time evolution of the disc.
+Chemical abundances in the disc were taken from I2011 who followed gas-grain chemical processes during the dynamical evolution of the disc.
+The abundances of 125 species related by 1334 reactions were calculated through the time evolution of the disc.
 These abundances were interpolated onto a 51$^3$ grid covering the disc with cells of size 2.2$\times$2.2$\times$0.22$\,$AU.
-From Ilee et al.
-(2011) we selected the three species which appear to trace different regions of the disc : the inner 20\,AU (OCS), the inner 40\,AU (H$_2$CO) and the region between $\simeq$40 and 60\,AU (HCO$^+$) and one which traces the entirety of the disc (C$^{17}$O).
-As explained by Ilee et al.
-(2011),  H$_2$CO and OCS mostly probe the central warm regions, where icy mantles evaporate, whereas HCO$^+$ preferentially traces the outer spiral pattern as in the central region it is destroyed by water molecules.
+From I2011 we selected the four species which appear to trace different regions of the disc: the inner 20\,AU (OCS), the inner 40\,AU (H$_2$CO),  the region between $\simeq$40 and 60\,AU (HCO$^+$) (see figure \ref{Chemistry}) and one which traces the entirety of the disc (C$^{17}$O).
+As explained by I2011,  H$_2$CO and OCS mostly probe the central warm regions, where icy mantles evaporate, whereas HCO$^+$ preferentially traces the outer spiral pattern as in the central region it is destroyed by water molecules and transformed into H$_3$O$^+$ and CO.
 The simple chemistry in the KC2010 model, adopted here as the envelope of the protoplanetary disc, does not provide detailed abundances of molecular species (besides CO and H$_2$O, see also Caselli et al.
@@
 As discussed in the result section (Sec.\,\ref{sec:model_results}), rough guesses have been made based on values measured toward similar objects.
+The molecular data used is from the lamda database (Sch\"oier et al.
+(2005) http://home.strw.leidenuniv.nl/$\sim$moldata/)
 
@@
 %-describe the RT used (LIME) 
-The radiative transfer program used, LIME (Brinch \&Hogerheijde 2010), calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3D model.
-The method of selecting these points is given in the grid-construction section.
-At each of these points, the density of the main collision partner (H$_2$), gas and dust temperatures, velocity, molecular abundances and turbulent velocity are taken from the model.
+The radiative transfer program used is LIME (Brinch \&Hogerheijde 2010),which  calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3D model.
+The method of selecting these points is given in the grid-construction section (section \ref{gridding}).
+At each of these points, the density of the main collision partner (H$_2$), gas and dust temperatures, velocity, molecular abundances and turbulent velocity are specified.
 These points are then smoothed by Lloyd's algorithm (Lloyd 1982) in order to minimise the variation in distance between points whilst keeping the same underlying distribution.
@@
 This number of iterations is sufficient for the signal to noise ratio of the level populations (as defined in Brinch \&Hogerheijde 2010) to exceed 1000 in 99\% of the points, ensuring that the simulation has converged on a stable level population.
-\newline
-After 20 iterations of updating the level populations the model is ray-traced in order to produce synthetic brightness maps.
+After 20 iterations the model is ray-traced in order to produce synthetic brightness maps.
 In order to minimise the artifacts in the output images, resulting from the grid construction, the average of ten separate runs was taken (figure \ref{averages}).
@@
  \label{grid}
- \caption{A plot of the points selected by the griding process and the paths down which photons can propagate overlaid on a smoothed density model.
+ \caption{A plot of the points selected by the griding process and the paths down which photons can propagate overlaid on the density distribution (in m$^{-3}$).
 The points are more concentrated at small radii and in the densest regions.}
-\end{figure}
-
-\begin{figure}
- \includegraphics[width=84mm]{Figures/model/lime_points_rz_histo2.eps}
- \label{points}
- \caption{A 2D histogram of the point distribution throughout the model. The disc and envelope can be seen as two separate entities which have to be sampled using different point distributions}
 \end{figure}
@@
 Simulations are limited to molecules for which we have abundances in both the disc and envelope, and also have calculated Einstein and collisional coefficients.
-The Molecular data used is from the lamda database (Sch\"oier et al.
-(2005) http://home.strw.leidenuniv.nl/$\sim$moldata/).
-Lines for the molecules which satisfy these conditions were simulated with LIME for frequencies between 50$\sim$500$\,$GHz, with a focus on lines which could be observed in ALMA band 7 and molecules which are not typically seen in outflows.
-The results presented in this section represent those lines which show detectable emission/absorption which can be used to trace either spiral structure or rotation.\newline
+We focus on the frequency range available with ALMA, with particular attention to band 7, which offers the best trade off between resolution and sensitivity.
+The results presented in this section are limited to those lines which show detectable emission/absorption which can be used to trace either spiral structure or rotation.\newline
 
-Transitions focused upon are CO 3-2 (and isotopologues) at 345.8GHz with an upper energy level of 33.2K, HCO$^+$ 3-2 at 267GHZ and 25.7K, OCS 26-25 at 316GHz and 205K and H$_2$CO $4_{04}$-3$_{03}$ at 290GHz and 34.9K {\bf maybe worth including a higher frequency line as well?
-CS at ~650GHz?}.
+We considered C$^{17}$O 3-2 at 337.1GHz with an upper energy level of $E_u$=32.3K, HCO$^+$ 3-2 at 267GHZ and $E_u$=25.7K, OCS 26-25 at 316GHz and $E_u$=205K and H$_2$CO $4_{04}$-3$_{03}$ at 290GHz and $E_u$=34.9K.
 Other molecules simulated but not shown include HCN, HNC, HNO, HCS$^+$ and CS.\newline
 
-For the purpose of simulating observations the model was placed at roughly the distance of nearby low-mass star forming regions (100$\,$pc) and is inclined at 30$^\circ$ to edge on.
-From these observations integrated intensity, intensity weighted velocity and position velocity diagrams through the centre of the model were created.
+To simulate observations, the model was placed at roughly the distance of nearby low-mass star forming regions (100$\,$pc) and the disc is inclined at 30$^\circ$ to edge on.
+From these simulated observations, integrated intensity, intensity weighted velocity and position velocity diagrams through the centre of the model were created.
 The simulations were focused upon frequencies within ALMA band 7, selected to give the best trade off between resolution and sensitivity for early ALMA science.
-(Note the moment 1 and 0 maps were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in some PV diagrams as the strong absorption feature at all positions around zero velocity, moment 1 maps are shown with a cut-off of 3$\sigma$ as described in section \ref{sec:alma_predictions})\newline
+(Note the integrated intensity and intensity weighted velocity maps (figures \ref{OCS_all} - \ref{hcop+_all} and \ref{mom0_maps}) were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in some PV diagrams  (figure \ref{PVs}) as the strong absorption feature at all positions around zero velocity, moment 1 maps are shown with a cut-off of 3$\sigma$ as described in section \ref{sec:alma_predictions})\newline
 
@@
 
-OCS traces only the innermost region of the disc and can be used to examine the central regions (figure \ref{OCS_all}).
-As OCS is not seen in outflows it can be used to view rotation of the central part of the disc without risk of contamination.
-As the excitation energy for the high J transitions of OCS is much higher than the other lines under consideration it is only excited in the hottest densest regions.
-As a result of this the spiral structure is clearer in OCS than in most transitions, with the low density regions between spiral arms showing no emission or absorption(see figure \ref{OCS_all}).
-The majority of the OCS is visible in absorption against the bright continuum emission from the disc mid-plane.
-The exception to this in the centre of the disc and is an effect of the inclination angle, whereby the line of sight passes through gas above the mid-plane and then through the hole in the centre of the disc.
+OCS traces only the innermost 20$\,$AU of the disc and can be used to examine the central regions (figure \ref{OCS_all}).
+As OCS is not seen in outflows (e.g.
+Stanke 07, Van der Tak 03) it can be used to view rotation of the central part of the disc without risk of contamination from emission from shocked material.
+The OCS line, which has the highest excitation among the selected transitions, well traces the hottest and densest regions of the disc.
+As a result, the spiral structure is best seen in OCS (26 - 25), as shown in figure \ref{OCS_all}.
+The majority of the OCS line is visible in absorption against the bright continuum emission from the disc mid-plane.
+The exception to this is towards the centre of the disc where the hole in the hot, dense midplane means that there is little continuum to be absorbed.
 
@@
 
-The abundance of the H$_2$CO molecule is fairly typical of the molecules simulated in Ilee (2011) in that it traces the spiral structure roughly the inner 2/3$^{rd}s$ of the disc.
-The spiral structure of the disc can be seen clearly in the integrated intensity map and its rotation of detected out to larger radii than is possible with the OCS and is more visible between spiral arms but is otherwise similar in morphology.
+The abundance of the H$_2$CO molecule is typical of the majority of the molecules simulated in I2011 in that it traces the spiral structure roughly the inner 40$\,$AU of the disc.
+The spiral structure of the disc can be seen clearly in the integrated intensity map and its rotation of detected out to larger radii than is possible with the OCS (figure \ref{h2co_all}).
+As with the OCS line, the majority of the H$_2$CO is seen in absorption against the disc mid-plane continuum with the central region seen in emission.
+Unlike the OCS however, the H$_2$CO extends out to large enough radii to be present in the voids between spiral arms.
+In these regions the H$_2$CO line can be seen in emission, this can be seen most clearly in the H$_2$CO channel map (figure \ref{h2co_chanmap}).
 
@@
 
-Some molecules such as HCO$^+$ trace only the outer regions of the disc (Ilee 2011) and so can be used to look at the extended velocity and physical structure.
-In these colder less dense regions we see the molecular lines in emission rather than absorption.
-\newline
+HCO$^+$ in unique in the molecules simulated in I2011 in that it traces only the outer regions of the disc, and so can be used to look at the extended velocity and physical structure.
+In figure \ref{hco+_all} we can see that the HCO$^+$ line shows the outer edges of the spiral arms in absorption, but also shows emission from the diffuse gas further out in the disc.
+This allows the velocity structure of the disc measured out to larger radii.\newline
 %Figure \ref{hcop_pv} shows the rotation curve of the model as shown in figure \ref{velocity} against the HCO$^+$ J=1-0 line emission.
@@
 
-In all the simulations except HCO$^+$ we see molecular lines in absorption throughout the majority of the disc and in some cases a small amount of emission towards the centre.
+%With the exception of HCO$^+$, molecular lines are seen in absorption throughout the majority of the disc and in some cases a small amount of emission towards the centre.
 Molecular lines throughout the plane of the disc show up in absorption against the continuum emission of the shock heated, dense mid-plane.
@@
 
-Figure \ref{h2co_chanmap} shows a channel map of the H$_2$CO 4$_{04}$-$3_{03}$ line overlaid on the 1$\,$mm continuum emission.
+Figure \ref{h2co_chanmap} shows a channel map of the H$_2$CO 4$_{04}$-$3_{03}$ line overlaid on the 1$\,$mm continuum emission (figure \ref{continuum}).
 From this it can be seen that the absorption features trace the disc spiral structure whilst line emission emanates from gaps in the disc where there is less continuum to be absorbed.
@@
 \begin{figure*}
- \includegraphics[width=168mm]{Figures/sim/casa_all_30deg_contSub.eps}
+ \includegraphics[width=168mm]{Figures/sim/casa_all_30deg_contSub_nums.eps}
  \caption{Integrated intensity maps for the simulated observations of:{\bf Top Left:} H$_2$CO 4$_{04}\rightarrow$3$_{03}$, {\bf Top Right:}C$^{17}$O 3$\rightarrow$2, {\bf Bottom Left:} OCS 26$\rightarrow$25 and {\bf Bottom Right:} HCO$^+$ 3$\rightarrow$2.
 contours start at 3$\sigma$ and increasing in intervals of 3$\sigma$ for each of the maps except the H$_2$CO which starts at 5$\sigma$ and increases in intervals of 5$\sigma$.
-Emission is in red contours, absorption in blue.}
+Emission is in red contours, absorption in blue.
+The numbers refer to the spectra shown in figure \ref{spectra}.}
 \label{mom0_maps}
@@
  \includegraphics[width=198mm]{Figures/sim/casa_all_30deg_PV_rotCurve.eps}
- \caption{Position velocity diagrams for each of the species simulated with CASA.
-The green curve on each diagram is the best fit curve to the azimuthally averaged rotation profile from figure 4.{\bf *****labels of h2co and ocs are wrong way round*****}}
+ \caption{Position velocity diagrams for each of the species simulated with CASA. The green curve on each diagram is the best fit curve to the azimuthally averaged rotation profile from figure 4.}
  \label{pvs}
@@
 the values for N are: OCS 10AU, H$_2$CO 20AU, C$^{17}$O 28AU, HCO$^+$ 38AU.
-{\bf maybe should put stars or something on the mom0 maps to show these locations?}}
+The locations for these spectra are given in figure \ref{mom0_maps}, the red green and blue curves are taken from the locations marked 1, 2 and 3 respectively.}
  \label{spectra}
@@
 These can be atributed to the non-axissymmetric nature of the model.
-%Spectra show stuff, i guess? not really sure if this adds anything to the pv diagrams.
 
@@
 Outflows could contaminate measurements of rotation curves meaning that species  which commonly trace outflows, such as CO and HCO$^+$ are not going to be good tracers of disc rotation.
-However species such as OCS and C$^{18}$O which are not commonly seen in outflows (e.g.
+However species such as OCS and C$^{17}$O which are not commonly seen in outflows (e.g.
 van der Tak et al.
@@
 \newline
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/model/lime_points_rz_histo2.eps}
+ \caption{A 2D histogram of the point distribution throughout the model. The disc and envelope can be seen as two separate entities which have to be sampled using different point distributions}
+ \label{points}
+\end{figure}
 

### 2013-02-07 paper.tex
tidied up model descriptions and discussion

@@
 Here we present simulated ALMA observations based on radiative transfer modelling of a relatively massive (0.39 M$_{\odot}$) self-gravitating disc embedded in a 10\,M$_{\odot}$ dense core, with structure similar to the pre-stellar core L1544.
-We focus on simple species and conclude that OCS, C$^{17}$O, H$_2$CO and HCO$^+$ lines together allow measurements of the disc structure and kinematics at all scales.
+We focus on simple species and conclude that OCS, C$^{17}$O, H$_2$CO and HCO$^+$ lines together allow for measurements of the disc structure and kinematics at all scales.
 \end{abstract}
@@
 The use of sensitive interferometers is needed to achieve high angular resolution and spatially/spectrally disentangle the various disc, envelope and outflow components as well to filter out the extended emission tracing envelope material.
+\newline
 
@@
 As full-operational ALMA is fast approaching, it is important to provide observational predictions based on dynamical models of young protoplanetary discs.
-
-%Previous work on simulating observations of gravitationally unstable discs have performed calculations of the continuum radiative transfer in order to look at the structure of the disc and detect disc fragmentation (Ruge et al.
-2012) or have used the local thermodynamic equilibrium (LTE) approximation in order to estimate the molecular line emission for an unembedded disc (Krumholtz et al.
-2007).
+\newline
 
@@
  \includegraphics[width=84mm]{Figures/model/L1544model_used_legend_small.eps}
- \caption{Model of the pre-stellar core L1544 used as the envelope of the young protoplanetary disc in the hybrid model.
-Showing temperature (green) and dust (red) temperature in kelvin, log number density (blue) in cm$^{-3}$ and inward velocity$\times$100 (cyan) in m$\,$s$^{-1}$.
-Adapted from Keto \& Caselli (2010) and Keto et al.
+ \caption{The spherically symmetric model of the pre-stellar core L1544 used as the envelope of the young protoplanetary disc in the hybrid model.
+Showing temperature (green) and dust (red) temperature in kelvin, log number density (blue) in cm$^{-3}$ and inward velocity / 100 (cyan) in m$\,$s$^{-1}$.
+Adapted from KC2010 and Keto et al.
 (2013, in preparation).}
@@
  \includegraphics[width=168mm]{Figures/model/columnDensities2.eps}
- \caption{Column densities of OCS, H$_2$CO and HCO$^+$ used in the disc model. Figure adapted from I2011 [SHOULD WE ALSO ADD C17O COLUMN DENSITY AS WE WANT TO DISCUSS THAT LATER ?? ]}
+ \caption{Column densities of OCS, H$_2$CO,HCO$^+$ and CO used in the disc model. Figure adapted from I2011}
  \label{Chemistry} 
@@
 The dust and gas temperatures in the disc are assumed to be in equilibrium.
-The underlying model from which the radiative transefer grid is sampled is a regular grid of size 256$\times$256$\times$64 with spatial resolution of 0.5$\,$AU in x, y and z.
+The underlying model is sampled as a regular grid of size 256$\times$256$\times$64 with spatial resolution of 0.5$\,$AU in x, y and z.
 The gas/dust mass ratio was assumed to be 1/100 throughout both sections model and the opacities were adopted from Ossenkops and Henning (1994) and refer to dust grains with thick icy mantles and 10$^6$ yr coagulation history.\newline
@@
 These abundances were interpolated onto a 51$^3$ grid covering the disc with cells of size 2.2$\times$2.2$\times$0.22$\,$AU.
-From I2011 we selected the four species which appear to trace different regions of the disc: the inner 20\,AU (OCS), the inner 40\,AU (H$_2$CO),  the region between $\simeq$40 and 60\,AU (HCO$^+$) (see figure \ref{Chemistry}) and one which traces the entirety of the disc (C$^{17}$O).
+From I2011 we selected the four species which appear to trace different regions of the disc: the inner 20\,AU (OCS), the inner 40\,AU (H$_2$CO),  the region between $\simeq$40 and 60\,AU (HCO$^+$) and one which traces the entirety of the disc (C$^{17}$O) (see figure \ref{Chemistry}, the abundance model used for C$^{17}$O was the CO model reduced by a factor of 1792, the ratio of $^{16}$O to $^{17}$O in the local ISM, Wilson \& Rood 1994).
 As explained by I2011,  H$_2$CO and OCS mostly probe the central warm regions, where icy mantles evaporate, whereas HCO$^+$ preferentially traces the outer spiral pattern as in the central region it is destroyed by water molecules and transformed into H$_3$O$^+$ and CO.
@@
 The molecular data used is from the lamda database (Sch\"oier et al.
-(2005) http://home.strw.leidenuniv.nl/$\sim$moldata/)
+(2005) http://home.strw.leidenuniv.nl/$\sim$moldata/).
 
@@
 %-describe the RT used (LIME) 
-The radiative transfer program used is LIME (Brinch \&Hogerheijde 2010),which  calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3D model.
+The radiative transfer program used is LIME (Brinch \& Hogerheijde 2010),which  calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3D model.
 The method of selecting these points is given in the grid-construction section (section \ref{gridding}).
@@
 These points are then connected by Delaunay triangulation \footnote{In three dimensions this means that if four points are connected into a tetrahedron, the sphere circumscribing these four points contains no other points.
-It can be shown that this connection is unique for a given set of points.} and it is down these paths that photon propagation is restricted (figures \ref{grid}).
+It can be shown that this connection is unique for a given set of points.} and it is down these paths that photon propagation is restricted (figure \ref{grid}).
 The level populations of the selected molecules are calculated at each of these points from collisional and radiative (de)excitation and the local radiation field is calculated.
@@
 
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/average_comparison.eps}
-% \label{averages}
-% \caption{A plot showing the difference between a single LIME continuum image at 300$\,$GHz (right) and the average of ten such images from different runs of the same model in LIME (left).}
-%\end{figure}
-
 \begin{figure}
  \includegraphics[width=84mm]{Figures/model/grid.eps}%Lime_grid3.eps
+ \caption{A plot of the points selected by the griding process and the paths down which photons can propagate overlaid on the density distribution (in m$^{-3}$, as used in LIME).
+The points are more concentrated at small radii and in the densest regions.}
  \label{grid}
- \caption{A plot of the points selected by the griding process and the paths down which photons can propagate overlaid on the density distribution (in m$^{-3}$).
-The points are more concentrated at small radii and in the densest regions.}
 \end{figure}
@@
 The simulations were focused upon frequencies within ALMA band 7, selected to give the best trade off between resolution and sensitivity for early ALMA science.
-(Note the integrated intensity and intensity weighted velocity maps (figures \ref{OCS_all} - \ref{hcop+_all} and \ref{mom0_maps}) were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in some PV diagrams  (figure \ref{PVs}) as the strong absorption feature at all positions around zero velocity, moment 1 maps are shown with a cut-off of 3$\sigma$ as described in section \ref{sec:alma_predictions})\newline
+(Note the integrated intensity and intensity weighted velocity maps (figures \ref{sim_all} and \ref{mom0_maps}) were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in some PV diagrams  (figure \ref{pvs}) as the strong absorption feature at all positions around zero velocity, moment 1 maps are shown with a cut-off of 3$\sigma$ as described in section \ref{sec:alma_predictions})\newline
 
@@
 \begin{figure*}
- \includegraphics[width=168mm]{Figures/sim/imageOCS_26-25_30deg_all.eps}
- \caption{OCS 28-27 {\bf Left:} Continuum subtracted integrated intensity map showing clearly differentiated spiral structure in the inner regions of the disc, {\bf Right:} Intensity weighted velocity map}
- \label{OCS_all}
+ \includegraphics[width=150mm]{Figures/sim/imageALL_30deg_all.eps}
+ \caption{{\bf Left:}Continuum subtracted integrated intensity maps, {\bf Right:} Intensity weighted velocity maps.
+The spiral structure in different regions of the disc is highlighted by looking at different molecular lines.
+From top to bottom the lines displayed are: OCS 26$\rightarrow$25, H$_2$CO 4$_{04}$$\rightarrow$3$_{03}$, C$^{17}$O 3$\rightarrow$2 and HCO$^+$ 3$\rightarrow$2.
+All maps are integrated over -12.5 to -0.5 and 0.5 to 12.5 in order to avoid the envelope contribution.}
+ \label{sim_all}
 \end{figure*}
 
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageOCS_28-27_30deg_composite_PV_centre.eps}
-% \caption{OCS 28-27 position-velocity diagram through centre}
-%\end{figure}
-
-OCS traces only the innermost 20$\,$AU of the disc and can be used to examine the central regions (figure \ref{OCS_all}).
+OCS traces only the innermost 20$\,$AU of the disc and can be used to examine the central regions (figure \ref{sim_all}).
 As OCS is not seen in outflows (e.g.
 Stanke 07, Van der Tak 03) it can be used to view rotation of the central part of the disc without risk of contamination from emission from shocked material.
-The OCS line, which has the highest excitation among the selected transitions, well traces the hottest and densest regions of the disc.
-As a result, the spiral structure is best seen in OCS (26 - 25), as shown in figure \ref{OCS_all}.
+The OCS line, which has the highest upper energy level among the selected transitions, traces the hottest and densest regions of the disc.
+As a result, the innermost spiral structure is best seen in OCS (26 - 25), as shown in figure \ref{sim_all}.
 The majority of the OCS line is visible in absorption against the bright continuum emission from the disc mid-plane.
-The exception to this is towards the centre of the disc where the hole in the hot, dense midplane means that there is little continuum to be absorbed.
+The exception to this is towards the centre of the disc where the hole in the hot, dense midplane means that there is little continuum to be absorbed.\newline
 
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imagesmoothedOCS_28-27_30deg_contSub.png}
-% \label{smoothOCS_mom0}
-% \caption{SmoothedOCS 28-27 Continuum subtracted mom0}
-%\end{figure}
+The abundance of the H$_2$CO molecule is typical of the majority of the molecules simulated in I2011 in that it traces the spiral structure of the inner $\sim$40$\,$AU of the disc.
+The spiral structure of the disc can be seen clearly in the integrated intensity map and its rotation of detected out to larger radii than is possible with the OCS (figure \ref{sim_all}).
+As with the OCS line, the majority of the H$_2$CO 4$_{04}$-3$_{03}$ line is seen in absorption against the disc mid-plane continuum with the central region seen in emission.
+Unlike the OCS however, the H$_2$CO extends out to large enough radii to be present in the voids between spiral arms.
+In these regions the H$_2$CO line can be seen in emission, this can be seen most clearly in the H$_2$CO channel map (figure \ref{h2co_chanmap}).\newline
 
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imagesmoothedOCS_28-27_30deg_PV_centre.png}
-%
-% \caption{SmoothedOCS 28-27 PV through centre}
-%\end{figure}
-
-\begin{figure*}
- \includegraphics[width=168mm]{Figures/sim/imageH2CO_4-0-4--3-0-3_30deg_composite_all.eps}
- \caption{H$_2$CO 4$_{0\,4}$ - 3$_{\,0\,3}$ {\bf Left:} Continuum subtracted integrated intensity map, {\bf Right:} Intensity weighted velocity map}
- \label{h2co_all}
-\end{figure*}
-
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageH2CO_4-0-4--3-0-3_30deg_composite_PV_centre.eps}
-% \caption{H$_2$CO 4$_{0\,4}$ - 3$_{\,0\,3}$ PV through centre}
-%\end{figure}
-
-The abundance of the H$_2$CO molecule is typical of the majority of the molecules simulated in I2011 in that it traces the spiral structure roughly the inner 40$\,$AU of the disc.
-The spiral structure of the disc can be seen clearly in the integrated intensity map and its rotation of detected out to larger radii than is possible with the OCS (figure \ref{h2co_all}).
-As with the OCS line, the majority of the H$_2$CO is seen in absorption against the disc mid-plane continuum with the central region seen in emission.
-Unlike the OCS however, the H$_2$CO extends out to large enough radii to be present in the voids between spiral arms.
-In these regions the H$_2$CO line can be seen in emission, this can be seen most clearly in the H$_2$CO channel map (figure \ref{h2co_chanmap}).
-
-\begin{figure*}
-  \includegraphics[width=168mm]{Figures/sim/imageHCOp_3-2_30deg_all.eps}  \caption{HCO$^+$ 3-2 {\bf Left:} Continuum subtracted integrated intensity map, {\bf Right:} Intensity weighted velocity map}
-  \label{hco+_all}
-\end{figure*}
-
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageHCOp_1-0_30deg_composite_PV_centre.eps}
-% \caption{HCO$^+$ 1-0 pv through centre, with the rotation curve from figure \ref{velocity} for comparison}
-%\end{figure}
-
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageHCOp_3-2_30deg_PV_centre_2.png}
-% \label{hcop_pv}
-% \caption{HCO$^+$ 3-2 PV through centre with rotation curve from figure \ref{velocity} *** should the velocities in this be reduced by cos(30) as we're not in the plane of rotation? ***}
-%\end{figure}
+The fractional abundace of C$^{17}$O is constant at 2$\times$10$^{-8}$ across the disc, meaning the C$^{17}$O line is the most accurate in reproducing the physical structure of the disc.
+Like H$_2$CO, C$^{17}$O shows emission in voids between spiral arms.
+The C$^{17}$O line is visible from inner edge of the disc to its outer edge.
+Like OCS, C$^{17}$O is not seen in outflows (e.g.
+yildiz et al.
+2012) and so rotation seen in C$^{17}$O lines should only be due to rotation from the disc and not contamination from outflows.\newline
 
 HCO$^+$ in unique in the molecules simulated in I2011 in that it traces only the outer regions of the disc, and so can be used to look at the extended velocity and physical structure.
-In figure \ref{hco+_all} we can see that the HCO$^+$ line shows the outer edges of the spiral arms in absorption, but also shows emission from the diffuse gas further out in the disc.
-This allows the velocity structure of the disc measured out to larger radii.\newline
-%Figure \ref{hcop_pv} shows the rotation curve of the model as shown in figure \ref{velocity} against the HCO$^+$ J=1-0 line emission.
-It is clear that from observations such as these the rotation curve of a disc
-
-%With the exception of HCO$^+$, molecular lines are seen in absorption throughout the majority of the disc and in some cases a small amount of emission towards the centre.
-Molecular lines throughout the plane of the disc show up in absorption against the continuum emission of the shock heated, dense mid-plane.
+In figure \ref{sim_all} we can see that the HCO$^+$ line shows the outer edges of the spiral arms in absorption, but also shows emission from the diffuse gas further out in the disc.
+This allows the velocity structure of the disc measured out to larger radii.
+This allows constraints to be placed on the rotation of the disc out to larger raddi than other molecules.
 
@@
 As the weakest lines studied in the model are of the order of 0.1-0.2$\,$mJy$\,$beam$^{-1}$ at this resolution, sensitivities of the order of 0.02$\,$mJy$\,$beam$^{-1}$ are required.
-This requires around 6 hours of integration time, the exact sensitivities are give in table \ref{sigmas}.
-
+This requires around 6 hours of integration time.
+The exact sensitivities are give in table \ref{sigmas}.
 \begin{table}
@@
  \begin{minipage}{80mm}
-   \caption{Sensitivities of ALMA given 6 hours integration time. As calculated by the ALMA on-line sensitivity calculator.}
+   \caption{Sensitivities of ALMA given 6 hours integration time with velocity resolution of $\sim$400$\,$ms$^{-1}$. As calculated by the ALMA on-line sensitivity calculator.}
    \label{sigmas}
@@
 \end{table}
-
 In order to clean the images which featured mainly absorption the sky model used was the output of the lime simulations with the continuum subtracted and then the image inverted.
-The simulated images were cleaned down to a 3$\sigma$level with $\sigma$ given in table \ref{sigmas}.
+The simulated images were cleaned down to a 3$\sigma$ level with $\sigma$ given in table \ref{sigmas}.\newline
 
@@
 
-%\begin{figure}
-%\includegraphics[width=54mm]{Figures/sim/casa_imageOCS_28-27_30deg_composite_ALMAwidth_big_dirty_PV_centre.eps}
-% \caption{OCS 28-29 pv diagram simulated for ALMA most extended configuration}
-%\end{figure}
-
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/casa_OCS_26-25_30deg_contSub.eps}
-%
-% \caption{OCS 28-29 integrated intesity simulated for ALMA most extended configuration, contours %starting at 3$\sigma$ and increasing in intervals of 3$\sigma$}
-%\end{figure}
-%
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/casa_H2CO_404-303_30deg_contSub.eps}
-%
-% \caption{H$_2$CO 4$_{04}$-3$_{03}$ integrated intesity simulated for ALMA most extended configuration, %contours starting at 5$\sigma$ and increasing in intervals of 5$\sigma$}
-%\end{figure}
-%
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/casa_HCOp_spectra_40_AUsplit.eps}
-%
-% \caption{HCO$^+$ 1-0 30 deg spectra at Y=0, X=+40AU (bottom), 0AU (middle) and -40AU (Top)}
-%\end{figure}
-
 \begin{figure*}
@@
 H$_2$CO line in contours starting at 0.35 mJy$\,$beam$^{-1}\,$km$\,$s$^{-1}$ (absorption in blue, emission in red).
-Overlaid on the continuum emission.
+Overlaid on the 1mm continuum emission.
 Each map integrates over 2.4 km$\,$s$^{-1}$ with the top left from -10.8 to -8.4 km$\,$s$^{-1}$ to the bottom left ranging from 8.4 to 10.8 km$\,$s$^{-1}$}
@@
 Figure \ref{h2co_chanmap} shows a channel map of the H$_2$CO 4$_{04}$-$3_{03}$ line overlaid on the 1$\,$mm continuum emission (figure \ref{continuum}).
-From this it can be seen that the absorption features trace the disc spiral structure whilst line emission emanates from gaps in the disc where there is less continuum to be absorbed.
-
-%\begin{figure}
-%\includegraphics[width=54mm]{Figures/sim/casa_imageC17O_3-2_30deg_composite_ALMAwidth_dirty_PV_centre.eps}
-% \caption{C$^{17}$O 3-2 30 deg PV through centre simulated for ALMA most extended configuration}
-%\end{figure}
-
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/casa_C17O_3-2_30deg_contSub.eps}
-%
-% \caption{C$^{17}$O 3-2 30 deg integrated intensity simulated for ALMA most extended configuration, %contours starting at 3$\sigma$ and increasing in intervals of 3$\sigma$}
-%\end{figure}
+From this it can be seen that the absorption features trace the disc spiral structure whilst line emission emanates from gaps in the disc where there is less continuum to be absorbed.\newline
 
@@
 
-Figure \ref{mom0_maps} shows the simulated integrated intensity maps demonstrate how different species allow observations to trace different regions of the disc, from OCS tracing the innermost regions to HCO$^+$ showing the outer regions which are less bright in the continuum.
-ALMA has enough resolution and sensitivity to see spiral structure clearly in continuum emission but also in CO isotopologues and marginally in H$_2$CO.
-
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/casa_C17O_spectra_20AUsplit.eps}
-%
-% \caption{C$^{17}$O 1-0 30 deg spectra at Y=0, X=+20AU (bottom), 0AU (middle) and -20AU (Top)}
-%\end{figure}
-
-%\begin{figure}
-%\includegraphics[width=63mm]{Figures/sim/casa_imageHCOp_1-0_30deg_composite_ALMAwidth_dirty_PV_centre.eps}
-% \caption{HCO$^+$ 1-0 30 deg PV through centre simulated for ALMA most extended configuration}
-%\end{figure}
-
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/casa_HCOp_3-2_30deg_contSub.eps}
-%
-% \caption{HCO$^+$ 3-2 30 deg integrated intensity simulated for ALMA most extended configuration. %Contours start at 3$\sigma$ and increase in steps of 3$\sigma$}
-%\end{figure}
-
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/casa_H2CO_404-303_30deg_contSub.eps}
-%
-% \caption{H$_2$CO 404-303 30 deg integrated intensity simulated for ALMA most extended configuration. Contours start at 5$\sigma$ and increase in steps of 10$\sigma$}
-%\end{figure}
+Figure \ref{mom0_maps} shows the simulated integrated intensity maps, which demonstrate how different species allow observations to trace different regions of the disc, from OCS tracing the innermost regions to HCO$^+$ showing the outer regions which are less bright in the continuum.
+ALMA has enough resolution and sensitivity to see spiral structure clearly in continuum emission but also in CO isotopologues and marginally in H$_2$CO.\newline
 
@@
 Figure \ref{pvs} shows position-velocity diagrams of the simulated lines, allowing us to reconstruct the rotation of the disc.
-The curve also shown in these figures is the best fit rotation curve of the physical model (see figure \ref{velocity}), showing that the rotation profile of the disc can be well constrained using kinematic information gathered from species tracing different regions of the disc.
-
+The curve also shown in these figures is the best fit rotation curve of the physical model (see figure \ref{velocity}), showing that the rotation profile of the disc can be well constrained using kinematic information gathered from species tracing different regions of the disc.\newline
 \begin{figure*}
@@
 
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/casa_OCS_spectra_10AUsplit.eps}
-%
-% \caption{OCS 28-27 30 deg spectra at Y=0, X=+10AU (bottom), 0AU (middle) and -10AU (Top)}
-%\end{figure}
-
 \section{Discussion and conclusions} \label{sec:discussion}
 
-In this paper we have performed radiative transfer simulations of a hybrid model comprising a 0.4$\, M_\odot$ self gravitating disc with radius 64$\,AU$ showing spiral density waves, surrounded by an envelope simulated as a collapsing 10$\,M_\odot$ BE-sphere.
-CASA simulations show that at a distance of 100$\,$pc both spatial resolution of the spirals in such a disc and extraction of kinematic and temperature from molecular lines are possible in ALMA band 7.
-Our simulations show that many  molecular species are predominantly seen in absorption towards the centre of  self-gravitating protoplanetary discs.
-The quiescent nature of the envelope around such discs only obscures them within $\pm\,0.5 km\,s^{-1}$.\newline
+In this paper we have presented radiative transfer simulations of a hybrid model comprising a 0.4$\, M_\odot$ self gravitating disc with radius 64$\,AU$ showing spiral density waves, surrounded by an envelope simulated as a collapsing 10$\,M_\odot$ BE-sphere.
+The main results of these simulations are as follows:\newline
+
+$\bullet$ CASA simulations of this model show that at a distance of 100$\,$pc extraction of kinematic and structural information from continuum and some molecular lines are possible in ALMA band 7.\newline
+$\bullet$ Our simulations show that many molecular species are predominantly seen in absorption against the hot mid-plane of self-gravitating protoplanetary discs, with emission only being seen where voids in the structure of the disc do not provide a bright continuum source to be absorbed.\newline
+$\bullet$ The quiescent nature of the envelope around such discs only obscures lines within $\pm\,$0.5 km$\,$s$^{-1}$ of the systematic velocity.\newline 
+$\bullet$ The lines studied (OCS 26$\rightarrow$25, H$_2$CO 4$_{04}$$\rightarrow$3$_{03}$, C$^{17}$O 3$\rightarrow$2 and HCO$^+$ 3$\rightarrow$2) taken togther allow all regions of the disc to be sampled and the rotation of the disc to be constrained from the inner edge to the outer edge.\newline
+
 One assumption made in this model is that the gas and dust are in thermal equilibrium in the disc.
 If they are not and the dust is significantly cooler than the gas then transitions may not show up in absorption.\newline
-%The mass of the disc used (0.4$\,\rm{M}_\odot$) is on the high end for early discs (citations for estimate of early class 1 disc masses).\newline
-In the model spirals shock heat the mid-plane layer and the colder more diffuse gas absorbs the continuum from it, this results in molecular lines being seen in absorption whenever lines of sight pass through the cold diffuse gas at larger heights on to the hot dense mid-plane of the disc.
-Rotation curves can be gathered from these observations even with spiral structure\newline
+The mass of the disc used (0.4$\,\rm{M}_\odot$) is on the high end for early discs (citations for estimate of early class 0 disc masses).
 Outflows could contaminate measurements of rotation curves meaning that species  which commonly trace outflows, such as CO and HCO$^+$ are not going to be good tracers of disc rotation.
@@
 2007, Yildiz et al 2012, Ren et al.
-2011)can be used to trace disc rotation.
+2011)can be used to trace disc rotation.\newline
+
+We have shown that observations of young, gravitationally-unstable protoplanetary discs can be both seen and differentiated from smooth/stable discs by ALMA.
+Using a range of molecular lines would allow such observations to be able to determine both the structure and the kinematics of such a disc.
 

### 2013-02-07 paper.tex
spell checked

@@
  \caption{{\bf Left:}A 300$\,$GHz continuum image of the model, created from the average of ten LIME runs.
-{\bf Right:} the output of a single radiative transfer simulation, with artefacts due to finite gridding.}
+{\bf Right:} the output of a single radiative transfer simulation, with artifacts due to finite griding.}
  \label{averages}
@@
 The majority of the OCS line is visible in absorption against the bright continuum emission from the disc mid-plane.
-The exception to this is towards the centre of the disc where the hole in the hot, dense midplane means that there is little continuum to be absorbed.\newline
+The exception to this is towards the centre of the disc where the hole in the hot, dense mid-plane means that there is little continuum to be absorbed.\newline
 
@@
 
-The fractional abundace of C$^{17}$O is constant at 2$\times$10$^{-8}$ across the disc, meaning the C$^{17}$O line is the most accurate in reproducing the physical structure of the disc.
+The fractional abundance of C$^{17}$O is constant at 2$\times$10$^{-8}$ across the disc, meaning the C$^{17}$O line is the most accurate in reproducing the physical structure of the disc.
 Like H$_2$CO, C$^{17}$O shows emission in voids between spiral arms.
@@
 Like OCS, C$^{17}$O is not seen in outflows (e.g.
-yildiz et al.
+Yildiz et al.
 2012) and so rotation seen in C$^{17}$O lines should only be due to rotation from the disc and not contamination from outflows.\newline
@@
 This allows the velocity structure of the disc measured out to larger radii.
-This allows constraints to be placed on the rotation of the disc out to larger raddi than other molecules.
+This allows constraints to be placed on the rotation of the disc out to larger radii than other molecules.
 
@@
 
-In order to make predictions on the observability of the synthetic brightness maps CASA (common astronomy software applications) was used to simulate their observtion with the completed ALMA in configuration 26 of 28, giving a beam size of between 0.02 and 0.03 arcseconds.
+In order to make predictions on the observability of the synthetic brightness maps CASA (common astronomy software applications) was used to simulate their observation with the completed ALMA in configuration 26 of 28, giving a beam size of between 0.02 and 0.03 arcseconds.
 As the weakest lines studied in the model are of the order of 0.1-0.2$\,$mJy$\,$beam$^{-1}$ at this resolution, sensitivities of the order of 0.02$\,$mJy$\,$beam$^{-1}$ are required.
@@
 In the OCS lines, the two sides are not moving with equal velocities and the line widths and shapes are markedly different.
-These can be atributed to the non-axissymmetric nature of the model.
+These can be attributed to the non-axissymmetric nature of the model.
 
@@
 $\bullet$ The quiescent nature of the envelope around such discs only obscures lines within $\pm\,$0.5 km$\,$s$^{-1}$ of the systematic velocity.\newline 
-$\bullet$ The lines studied (OCS 26$\rightarrow$25, H$_2$CO 4$_{04}$$\rightarrow$3$_{03}$, C$^{17}$O 3$\rightarrow$2 and HCO$^+$ 3$\rightarrow$2) taken togther allow all regions of the disc to be sampled and the rotation of the disc to be constrained from the inner edge to the outer edge.\newline
+$\bullet$ The lines studied (OCS 26$\rightarrow$25, H$_2$CO 4$_{04}$$\rightarrow$3$_{03}$, C$^{17}$O 3$\rightarrow$2 and HCO$^+$ 3$\rightarrow$2) taken together allow all regions of the disc to be sampled and the rotation of the disc to be constrained from the inner edge to the outer edge.\newline
 

### 2013-02-07 paper.tex
minor tweaks

@@
 From these simulated observations, integrated intensity, intensity weighted velocity and position velocity diagrams through the centre of the model were created.
-The simulations were focused upon frequencies within ALMA band 7, selected to give the best trade off between resolution and sensitivity for early ALMA science.
+We focus on the frequency range available with ALMA, with particular attention to band 7, which offers the best trade off between resolution and sensitivity.
 (Note the integrated intensity and intensity weighted velocity maps (figures \ref{sim_all} and \ref{mom0_maps}) were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in some PV diagrams  (figure \ref{pvs}) as the strong absorption feature at all positions around zero velocity, moment 1 maps are shown with a cut-off of 3$\sigma$ as described in section \ref{sec:alma_predictions})\newline
@@
 From top to bottom the lines displayed are: OCS 26$\rightarrow$25, H$_2$CO 4$_{04}$$\rightarrow$3$_{03}$, C$^{17}$O 3$\rightarrow$2 and HCO$^+$ 3$\rightarrow$2.
-All maps are integrated over -12.5 to -0.5 and 0.5 to 12.5 in order to avoid the envelope contribution.}
+All maps are integrated over -12.5 to -0.5 and 0.5 to 12.5 km$\,$s$^{-1}$ in order to avoid the envelope contribution.}
  \label{sim_all}

### 2013-02-20 paper.tex
included PC 4th set of changes

@@
 \author[T.~A.~Douglas et al.]
-{\parbox{\textwidth}{Tom Douglas$^{1}$\thanks{E-mail: \texttt{pytd@leeds.ac.uk}},
-Paola Caselli$^{1}$,
-Aaron Boley$^{2}$,
-Richard Durisen$^{3}$,
-Tom Hartquist$^{1}$,
-John Ilee$^{1}$ and
-Jonathan Rawlings$^{4}$\\
+{\parbox{\textwidth}{T. A. Douglas$^{1}$\thanks{E-mail: \texttt{pytd@leeds.ac.uk}},
+P. Caselli$^{1}$,
+J. D. Ilee$^{1}$,
+A. C. Boley$^{2}$,
+T. W. Hartquist$^{1}$,
+R. Durisen$^{3}$, and
+J. Rawlings$^{4}$\\
 \vspace{0.1cm}\\
@@
 (2000), Looney et al.
-(2000), recent interferometric observations have discovered compact embedded discs in a sample of Class 0 (Andr\'e et al.
-2000) sources, finding masses between 0.4 and  $>$1 M$_{\odot}$ (J\o rgensen et al.
+(2000), recent interferometric observations have discovered compact embedded discs in a sample of Class 0 sources (Andr\'e et al.
+2000), finding masses between 0.4 and  $>$1 M$_{\odot}$ (J\o rgensen et al.
 2007, 2009; Enoch et al.
 2011).
-A 130\,AU disc was discovered toward a Class 0 source in Perseus, using Jansky Very Large Array (JVLA) observations of NH$_3$ (Choi et al.
+A 130\,AU disc was discovered toward a Class 0 source in Perseus, using the Jansky Very Large Array (JVLA) to observe NH$_3$ (Choi et al.
 2007).
 Pineda et al.
-(2012) observed methyl formate with the Atacama Millimetre and millimetre Array (ALMA) and found evidence of rotation toward one of the proto-binary Class 0 sources embedded in IRAS 16293-2422.
+(2012) observed methyl formate (HCOOCH$_3$) with the Atacama Large Millimetre/sub-millimetre Array (ALMA) and found evidence of rotation toward one of the proto-binary Class 0 sources embedded in IRAS 16293-2422.
 These observations are consistent with an almost edge-on disc.
@@
 (2013) used ALMA to observe a disc of size $\sim$50$\,$AU in the other Class 0 source in IRAS 16293-2422 and detected infall towards this disc as inverse P-Cygni profiles in HCN and CH$_3$OH.
-When ALMA will be completed, it will be finally possible to spatially resolve these young discs and, for the first time, put stringent constraints on theoretical models.
+When ALMA is completed, it will be finally possible to spatially resolve these young discs and, for the first time, put stringent constraints on the theoretical models mentioned previously.
 As full-operational ALMA is fast approaching, it is important to provide observational predictions based on dynamical models of young protoplanetary discs.
@@
 
-Simulated observations of gravitationally unstable discs have already been performed to study the continuum emission and measure the structure and possible fragmentation (Cossins et al.
+Simulated observations of gravitationally unstable discs have already been performed to study the continuum emission, measure the structure and investigate possible fragmentation (Cossins et al.
 2010; Ruge et al.
@@
 
-The physical model used to simulate the emission from a young protoplanetary disc is a hybrid model obtained from embedding a gravitationally unstable protoplanetary disc  within a dense core with characteristics similar to the well-studied pre-stellar core L1544, (Keto \& Caselli 2010; hereafter KC2010).
+To describe the full physical enviroment which we expect these young discs to occur in, we combine the disc model from I2011 with a model of a dense core with characteristics similar to the well-studied pre-stellar core L1544 (Keto \& Caselli 2010; hereafter KC2010).
 The KC2010 model follows the dynamical, chemical and thermal evolution of a contracting Bonnor-Ebert sphere (Bonnor 1956; Ebert 1957) with total mass of 10\,M$_{\odot}$, until it reaches the density, temperature and velocity profiles which best match observations.
@@
 2012; Keto et al.
-in preparation), and it is shown in Fig.\,\ref{fig:l1544_model}.
+in preparation).
+Figure \ref{fig:l1544_model} shows the physical parameters of the core model.
 \newline
@@
  \caption{The spherically symmetric model of the pre-stellar core L1544 used as the envelope of the young protoplanetary disc in the hybrid model.
-Showing temperature (green) and dust (red) temperature in kelvin, log number density (blue) in cm$^{-3}$ and inward velocity / 100 (cyan) in m$\,$s$^{-1}$.
+Showing gas (green) and dust (red) temperature in kelvin, log number density (blue) in cm$^{-3}$ and inward velocity / 10 (cyan) in m$\,$s$^{-1}$.
 Adapted from KC2010 and Keto et al.
@@
  \caption{{\bf Left:} A 3D plot of log number density (cm$^{-3}$) showing the spiral structure in the xy plane and scale height of the disc.
-{\bf Right:} The 3D temperature structure of the disc; regions cooler than 40 degrees are not shown in 3D, highlighting the narrow central region containing hot material.}
+{\bf Right:} The 3D temperature (K) structure of the disc; regions cooler than 40$\,$K are not shown in 3D, highlighting the narrow central region containing hot material.}
  \label{rhoT} 
@@
  \includegraphics[width=168mm]{Figures/model/columnDensities2.eps}
- \caption{Column densities of OCS, H$_2$CO,HCO$^+$ and CO used in the disc model. Figure adapted from I2011}
+ \caption{Column densities of OCS, H$_2$CO,HCO$^+$ and CO used in the disc model. Figure adapted from I2011.}
  \label{Chemistry} 
@@
  \includegraphics[width=84mm]{Figures/model/rotational_velocities.eps}
- \caption{Azimuthaly averaged rotational velocity in the disc mid-plane with best fit curve}
+ \caption{Azimuthaly averaged rotational velocity in the disc mid-plane with best fit curve.}
  \label{velocity}
@@
 
-The pre-stellar core structure is maintained down to a radius of 80\,AU, within which the young protoplanetary disc has been plugged in.
+The pre-stellar core structure is maintained down to a radius of 80\,AU, within which the model of the young protoplanetary disc is used.
 The disc structure is derived by the hydrodynamic model of Boley (2007) and Boley (2009).
-The particular model considered here (as well as in I2011) is a 0.39$\,\rm{M}_\odot$ self-gravitating disc featuring prominent spiral arms.
+The particular model considered here (as well as in I2011) is a 0.39$\,\rm{M}_\odot$ self-gravitating Keplerian disc (figure \ref{velocity}) featuring prominent spiral arms.
 H$_2$ number densities in the disc range from 10$^{4}$-10$^{13}\,\rm{cm}^{-3}$, and temperatures range from 30-400 K (figure \ref{rhoT}).
@@
 The underlying model is sampled as a regular grid of size 256$\times$256$\times$64 with spatial resolution of 0.5$\,$AU in x, y and z.
-The gas/dust mass ratio was assumed to be 1/100 throughout both sections model and the opacities were adopted from Ossenkops and Henning (1994) and refer to dust grains with thick icy mantles and 10$^6$ yr coagulation history.\newline
+The gas/dust mass ratio was assumed to be 1/100 throughout the disc and the envelope.
+The opacities were adopted from Ossenkops and Henning (1994) and refer to dust grains with thick icy mantles and 10$^6$ yr coagulation history.\newline
 
@@
 2012).
-As discussed in the result section (Sec.\,\ref{sec:model_results}), rough guesses have been made based on values measured toward similar objects.
-The molecular data used is from the lamda database (Sch\"oier et al.
-(2005) http://home.strw.leidenuniv.nl/$\sim$moldata/).
+As discussed in the result section \ref{sec:model_results}, approximations have been made based on values measured toward similar objects.
+The molecular data used is from the LAMDA (Leiden Atomic and Molecular DAtabase) database (Sch\"oier et al.
+(2005; http://home.strw.leidenuniv.nl/$\sim$moldata/).
 
@@
 %-describe the RT used (LIME) 
-The radiative transfer program used is LIME (Brinch \& Hogerheijde 2010),which  calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3D model.
-The method of selecting these points is given in the grid-construction section (section \ref{gridding}).
+The radiative transfer program used is LIME (LIne Modeling Engine; Brinch \& Hogerheijde 2010), which  calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3D model.
+The method of selecting these points is given in appendix  \ref{sec:gridding}).
 At each of these points, the density of the main collision partner (H$_2$), gas and dust temperatures, velocity, molecular abundances and turbulent velocity are specified.
@@
 After 20 iterations the model is ray-traced in order to produce synthetic brightness maps.
-In order to minimise the artifacts in the output images, resulting from the grid construction, the average of ten separate runs was taken (figure \ref{averages}).
+In order to minimise the artifacts in the output images, resulting from the grid construction, the average of ten separate runs was taken (Figure \ref{averages}).
 
@@
  \includegraphics[width=84mm]{Figures/model/grid.eps}%Lime_grid3.eps
- \caption{A plot of the points selected by the griding process and the paths down which photons can propagate overlaid on the density distribution (in m$^{-3}$, as used in LIME).
+ \caption{A plot of the points selected by the gridding process and the paths down which photons can propagate overlaid on the density distribution (in m$^{-3}$, as used in LIME).
 The points are more concentrated at small radii and in the densest regions.}
@@
 
-We considered C$^{17}$O 3-2 at 337.1GHz with an upper energy level of $E_u$=32.3K, HCO$^+$ 3-2 at 267GHZ and $E_u$=25.7K, OCS 26-25 at 316GHz and $E_u$=205K and H$_2$CO $4_{04}$-3$_{03}$ at 290GHz and $E_u$=34.9K.
-Other molecules simulated but not shown include HCN, HNC, HNO, HCS$^+$ and CS.\newline
+We considered C$^{17}$O 3$\rightarrow$2 at 337.1$\,$GHz with an upper energy level of $E_u$=32.3K, HCO$^+$ 3$\rightarrow$2 at 267$\,$GHz and $E_u$=25.7K, OCS 26$\rightarrow$25 at 316$\,$GHz and $E_u$=205K and H$_2$CO 4$_{04}\rightarrow$3$_{03}$ at 290$\,$GHz and $E_u$=34.9K.\newline
 
@@
 From these simulated observations, integrated intensity, intensity weighted velocity and position velocity diagrams through the centre of the model were created.
-We focus on the frequency range available with ALMA, with particular attention to band 7, which offers the best trade off between resolution and sensitivity.
-(Note the integrated intensity and intensity weighted velocity maps (figures \ref{sim_all} and \ref{mom0_maps}) were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in some PV diagrams  (figure \ref{pvs}) as the strong absorption feature at all positions around zero velocity, moment 1 maps are shown with a cut-off of 3$\sigma$ as described in section \ref{sec:alma_predictions})\newline
+(The integrated intensity and intensity weighted velocity maps (figures \ref{sim_all} and \ref{mom0_maps}) were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope.
+This can be seen in some PV diagrams  (figure \ref{pvs}) as the strong absorption feature at all positions around zero velocity.
+Moment 1 maps are shown with a cut-off of 3$\sigma$ as described in section \ref{sec:alma_predictions})\newline
 
@@
  \caption{{\bf Left:}A 300$\,$GHz continuum image of the model, created from the average of ten LIME runs.
-{\bf Right:} the output of a single radiative transfer simulation, with artifacts due to finite griding.}
+{\bf Right:} the output of a single radiative transfer simulation, with artifacts due to finite gridding.}
  \label{averages}
@@
  \includegraphics[width=150mm]{Figures/sim/imageALL_30deg_all.eps}
- \caption{{\bf Left:}Continuum subtracted integrated intensity maps, {\bf Right:} Intensity weighted velocity maps.
+ \caption{{\bf Left:} Continuum subtracted integrated intensity maps.
+{\bf Right:} Intensity weighted velocity maps.
 The spiral structure in different regions of the disc is highlighted by looking at different molecular lines.
@@
 
-The abundance of the H$_2$CO molecule is typical of the majority of the molecules simulated in I2011 in that it traces the spiral structure of the inner $\sim$40$\,$AU of the disc.
-The spiral structure of the disc can be seen clearly in the integrated intensity map and its rotation of detected out to larger radii than is possible with the OCS (figure \ref{sim_all}).
-As with the OCS line, the majority of the H$_2$CO 4$_{04}$-3$_{03}$ line is seen in absorption against the disc mid-plane continuum with the central region seen in emission.
-Unlike the OCS however, the H$_2$CO extends out to large enough radii to be present in the voids between spiral arms.
-In these regions the H$_2$CO line can be seen in emission, this can be seen most clearly in the H$_2$CO channel map (figure \ref{h2co_chanmap}).\newline
+The abundance of the H$_2$CO molecule traces the spiral structure of the inner $\sim$40$\,$AU of the disc.
+The spiral structure of the disc can be seen clearly in the integrated intensity map and its rotation is detected out to larger radii than is possible with the OCS line (figure \ref{sim_all}).
+As with the OCS line, the majority of the H$_2$CO 4$_{04}\rightarrow$3$_{03}$, is seen in absorption against the disc mid-plane continuum, with the central region seen in emission.
+Unlike the OCS however, the H$_2$CO extends out to large enough radii to be present in the voids between the outer parts spiral arms.
+In these regions, the H$_2$CO line can be seen in emission.\newline
 
@@
 Like H$_2$CO, C$^{17}$O shows emission in voids between spiral arms.
-The C$^{17}$O line is visible from inner edge of the disc to its outer edge.
+The C$^{17}$O line is visible from the inner edge of the disc to its outer edge.
 Like OCS, C$^{17}$O is not seen in outflows (e.g.
@@
 This allows the velocity structure of the disc measured out to larger radii.
-This allows constraints to be placed on the rotation of the disc out to larger radii than other molecules.
+This allows constraints to be placed on the rotation of the disc out to larger radii than with other molecules.
 
-\section{ALMA Predictions} \label{sec:alma_predictions}
+\section{Predictions for ALMA} \label{sec:alma_predictions}
 
-In order to make predictions on the observability of the synthetic brightness maps CASA (common astronomy software applications) was used to simulate their observation with the completed ALMA in configuration 26 of 28, giving a beam size of between 0.02 and 0.03 arcseconds.
+In order to make predictions on the observability of the synthetic brightness maps, the Common Astronomy Software Applications package (CASA) was used to simulate their observation with the completed ALMA in the 26th most extended comfiguration (out of a total of 28), with a longest baseline of 14.4km and giving beam sizes of between 0.02 and 0.03 arcseconds at the simulated frequencies.
 As the weakest lines studied in the model are of the order of 0.1-0.2$\,$mJy$\,$beam$^{-1}$ at this resolution, sensitivities of the order of 0.02$\,$mJy$\,$beam$^{-1}$ are required.
-This requires around 6 hours of integration time.
-The exact sensitivities are give in table \ref{sigmas}.
+This implies around 6 hours of integration time.
+The exact sensitivities are given in Table \ref{sigmas}.
 \begin{table}
@@
      \hline
-     C$^{17}$O & J=3$\rightarrow$2 & 337.06GHz & 0.0270$\,$mJy$\,$beam$^{-1}$ \\
-     OCS & J=26$\rightarrow$25 & 316.15GHz & 0.0275$\,$mJy$\,$beam$^{-1}$ \\
-     HCO$^+$ & J=3$\rightarrow$2 & 267.56GHz & 0.0176$\,$mJy$\,$beam$^{-1}$ \\
+     C$^{17}$O & 3$\rightarrow$2 & 337.06GHz & 0.0270$\,$mJy$\,$beam$^{-1}$ \\
+     OCS & 26$\rightarrow$25 & 316.15GHz & 0.0275$\,$mJy$\,$beam$^{-1}$ \\
+     HCO$^+$ & 3$\rightarrow$2 & 267.56GHz & 0.0176$\,$mJy$\,$beam$^{-1}$ \\
      H$_2$CO & 4$_{04}\rightarrow$3$_{03}$ & 290.62GHz & 0.0228$\,$mJy$\,$beam$^{-1}$ \\
@@
 \end{table}
-In order to clean the images which featured mainly absorption the sky model used was the output of the lime simulations with the continuum subtracted and then the image inverted.
+In order to clean the images, which featured mainly absorption, the sky model used was the output of the LIME simulations with the continuum subtracted and then the image inverted.
 The simulated images were cleaned down to a 3$\sigma$ level with $\sigma$ given in table \ref{sigmas}.\newline
@@
 
- \caption{Continuum emission at 337GHz simulated for ALMA most extended configuration}
+ \caption{CASA simulation on the continuum emission of the model at 337GHz, using the same ALMA configuration as used for the molecular lines.}
  \label{continuum}
@@
  \includegraphics[width=168mm]{Figures/sim/channel_map-1.eps} 
- \caption{H$_2$CO 4$_{04}$-3$_{03}$ channel maps as simulated by CASA.
-H$_2$CO line in contours starting at 0.35 mJy$\,$beam$^{-1}\,$km$\,$s$^{-1}$ (absorption in blue, emission in red).
+ \caption{H$_2$CO 4$_{04}\rightarrow$3$_{03}$ channel maps as simulated by CASA.
+The contours start at 0.35 mJy$\,$beam$^{-1}\,$km$\,$s$^{-1}$  and are in steps of 0.35 mJy$\,$beam$^{-1}\,$km$\,$s$^{-1}$ (absorption in blue, emission in red).
 Overlaid on the 1mm continuum emission.
@@
 
-Figure \ref{h2co_chanmap} shows a channel map of the H$_2$CO 4$_{04}$-$3_{03}$ line overlaid on the 1$\,$mm continuum emission (figure \ref{continuum}).
-From this it can be seen that the absorption features trace the disc spiral structure whilst line emission emanates from gaps in the disc where there is less continuum to be absorbed.\newline
+Figure \ref{h2co_chanmap} shows a channel map of the H$_2$CO 4$_{04}\rightarrow$3$_{03}$ line overlaid on the 1$\,$mm continuum emission (figure \ref{continuum}).
+From this it can be seen that the absorption features trace the disc spiral structure whilst line emission emanates from gaps in the outer disc where there is less continuum to be absorbed.\newline
 
@@
  \includegraphics[width=168mm]{Figures/sim/casa_all_30deg_contSub_nums.eps}
- \caption{Integrated intensity maps for the simulated observations of:{\bf Top Left:} H$_2$CO 4$_{04}\rightarrow$3$_{03}$, {\bf Top Right:}C$^{17}$O 3$\rightarrow$2, {\bf Bottom Left:} OCS 26$\rightarrow$25 and {\bf Bottom Right:} HCO$^+$ 3$\rightarrow$2.
+ \caption{Integrated intensity maps for the simulated observations of: {\bf Top Left:} H$_2$CO 4$_{04}\rightarrow$3$_{03}$, {\bf Top Right:} C$^{17}$O 3$\rightarrow$2, {\bf Bottom Left:} OCS 26$\rightarrow$25 and {\bf Bottom Right:} HCO$^+$ 3$\rightarrow$2.
 contours start at 3$\sigma$ and increasing in intervals of 3$\sigma$ for each of the maps except the H$_2$CO which starts at 5$\sigma$ and increases in intervals of 5$\sigma$.
 Emission is in red contours, absorption in blue.
-The numbers refer to the spectra shown in figure \ref{spectra}.}
+The numbers refer to the spectra shown in figure \ref{spectra}.
+{\bf need to discuss how to do this, i dont like the idea of coloured dots as the spectra are also in red and blue and would get confused with the contours}}
 \label{mom0_maps}
@@
 
-Figure \ref{mom0_maps} shows the simulated integrated intensity maps, which demonstrate how different species allow observations to trace different regions of the disc, from OCS tracing the innermost regions to HCO$^+$ showing the outer regions which are less bright in the continuum.
+Figure \ref{mom0_maps} shows the simulated integrated intensity maps, which demonstrate how lines from different species allow observations to trace different regions of the disc, from the OCS line tracing the innermost regions, to the HCO$^+$ line showing the outer regions which are less bright in the continuum.
 ALMA has enough resolution and sensitivity to see spiral structure clearly in continuum emission but also in CO isotopologues and marginally in H$_2$CO.\newline
@@
 \begin{figure*}
- \includegraphics[width=198mm]{Figures/sim/casa_all_30deg_PV_rotCurve.eps}
- \caption{Position velocity diagrams for each of the species simulated with CASA. The green curve on each diagram is the best fit curve to the azimuthally averaged rotation profile from figure 4.}
+ \includegraphics[width=198mm]{Figures/sim/casa_all_30deg_PV_rotCurve_small.eps}
+ \caption{Position velocity diagrams for each of the lines simulated with CASA. The green curve on each diagram is the best fit curve to the azimuthally averaged rotation profile from figure 4.}
  \label{pvs}
@@
 Figure \ref{pvs} shows position-velocity diagrams of the simulated lines, allowing us to reconstruct the rotation of the disc.
-The curve also shown in these figures is the best fit rotation curve of the physical model (see figure \ref{velocity}), showing that the rotation profile of the disc can be well constrained using kinematic information gathered from species tracing different regions of the disc.\newline
+The green curves in each panel of figure \ref{pvs} display the best fit rotation curve of the physical model (see figure \ref{velocity}), showing that the rotation profile of the disc can be well constrained using kinematic information gathered from species tracing different regions of the disc.\newline
+
 \begin{figure*}
  \includegraphics[width=168mm]{Figures/sim/casa_all_spectra.eps}
-
- \caption{Spectra for each of the simulated species.
-In each diagram the three spectra are taken from positions on the Y=0 axis, one is at X=0 (green) and the other 2 are from x=$\pm$ N (plus blue, minus red) where N is different for each species.
-the values for N are: OCS 10AU, H$_2$CO 20AU, C$^{17}$O 28AU, HCO$^+$ 38AU.
-The locations for these spectra are given in figure \ref{mom0_maps}, the red green and blue curves are taken from the locations marked 1, 2 and 3 respectively.}
+ \caption{Spectra for each of the simulated species at the positions indicated by the numbers in figure \ref{mom0_maps}, the red green and blue curves are taken from the locations marked 1, 2 and 3 respectively.
+In each diagram, the three spectra are taken from positions on the Y=0 axis, one is at X=0 (green) and the other 2 are from x=$\pm$ N (plus blue, minus red) where N is the distance from the centre: 10 AU for OCS, 20 AU for H2CO, 28 AU for C17O, 38 AU for HCO+.}
  \label{spectra}
@@
 Figure \ref{spectra} shows spectra from the lines simulated, one from the centre of the image and one on each side of the disc along the Y=0 axis.
-The most notable thing about these is, despite the fact that the spectra are equally spaced about the centre of the disc, they are not symmetric.
-Most noticeably in the C$^{17}$O the spectrum from the +X side of the disc is shows significantly more absorption than that of the -X side.
+As with all the CASA simulated images, these spectra have a total bandwidth of 938$\,$MHz, giving velocity resolutions of between 418 and 527 ms$^{-1}$.
+The most notable thing about these spectral features is that they are not symmetric about the disk centre.
+For example, C17O(3$\rightarrow$2) has a significantly stronger blueshifted absorption, due to the presence of a spiral arm along the same line of sight.
 In the OCS lines, the two sides are not moving with equal velocities and the line widths and shapes are markedly different.
-These can be attributed to the non-axissymmetric nature of the model.
+These can be attributed to the non-axisymmetric nature of the model.
 
@@
 
-In this paper we have presented radiative transfer simulations of a hybrid model comprising a 0.4$\, M_\odot$ self gravitating disc with radius 64$\,AU$ showing spiral density waves, surrounded by an envelope simulated as a collapsing 10$\,M_\odot$ BE-sphere.
-The main results of these simulations are as follows:\newline
-
-$\bullet$ CASA simulations of this model show that at a distance of 100$\,$pc extraction of kinematic and structural information from continuum and some molecular lines are possible in ALMA band 7.\newline
-$\bullet$ Our simulations show that many molecular species are predominantly seen in absorption against the hot mid-plane of self-gravitating protoplanetary discs, with emission only being seen where voids in the structure of the disc do not provide a bright continuum source to be absorbed.\newline
-$\bullet$ The quiescent nature of the envelope around such discs only obscures lines within $\pm\,$0.5 km$\,$s$^{-1}$ of the systematic velocity.\newline 
-$\bullet$ The lines studied (OCS 26$\rightarrow$25, H$_2$CO 4$_{04}$$\rightarrow$3$_{03}$, C$^{17}$O 3$\rightarrow$2 and HCO$^+$ 3$\rightarrow$2) taken together allow all regions of the disc to be sampled and the rotation of the disc to be constrained from the inner edge to the outer edge.\newline
+In this paper we have presented radiative transfer simulations of a hybrid model comprising a 0.39$\, M_\odot$ self gravitating disc with radius 64$\,AU$ showing spiral density waves, surrounded by an envelope simulated as a contracting 10$\,M_\odot$ BE-sphere.
+The main results of these simulations are as follows:\\
+$\bullet$ CASA simulations of this model show that at a distance of 100$\,$pc, extraction of kinematics and structural information from the continuum and molecular lines is possible with ALMA band 7.\\
+$\bullet$ Our simulations show that molecular features are predominantly seen in absorption against the hot mid-plane of self-gravitating protoplanetary discs, with emission only being seen where voids in the structure of the disc do not provide a bright continuum source to be absorbed.\\
+$\bullet$ The quiescent nature of the envelope around such discs only obscures lines within $\pm\,$0.5 km$\,$s$^{-1}$ of the systematic velocity.\\
+$\bullet$ The lines studied (OCS 26$\rightarrow$25, H$_2$CO 4$_{04}$$\rightarrow$3$_{03}$, C$^{17}$O 3$\rightarrow$2 and HCO$^+$ 3$\rightarrow$2) taken together allow all regions of the disc to be sampled and the rotation of the disc to be constrained from the inner edge to the outer edge.\\
 
 One assumption made in this model is that the gas and dust are in thermal equilibrium in the disc.
-If they are not and the dust is significantly cooler than the gas then transitions may not show up in absorption.\newline
-The mass of the disc used (0.4$\,\rm{M}_\odot$) is on the high end for early discs (citations for estimate of early class 0 disc masses).
+If they are not and the dust is significantly cooler than the gas then transitions may not show up in absorption.
+However, the large volume densities are expected to provide an efficient dust-gas coupling.\newline
 Outflows could contaminate measurements of rotation curves meaning that species  which commonly trace outflows, such as CO and HCO$^+$ are not going to be good tracers of disc rotation.
@@
 2007, Yildiz et al 2012, Ren et al.
-2011)can be used to trace disc rotation.\newline
+2011) can be used to trace disc rotation.\newline
 
-We have shown that observations of young, gravitationally-unstable protoplanetary discs can be both seen and differentiated from smooth/stable discs by ALMA.
-Using a range of molecular lines would allow such observations to be able to determine both the structure and the kinematics of such a disc.
+We have shown that observations of young, gravitationally-unstable protoplanetary discs can be both seen and differentiated from the envelope.
+Using a range of molecular lines in band 7, would allow such observations to be able to determine both the structure and the kinematics of such a disc.
 
 \section*{Acknowledgements}
+PC and TWH acknowledge support of successive rolling grants awarded by the UK Science and Technology Funding Council. 
+TAD and JDI acknowledge studentships from the Science and Technology Facilities Council of the United Kingdom (STFC).
 
-stuff here
 \newpage
@@
  \includegraphics[width=84mm]{Figures/model/lime_points_rz_histo2.eps}
- \caption{A 2D histogram of the point distribution throughout the model. The disc and envelope can be seen as two separate entities which have to be sampled using different point distributions}
+ \caption{A 2D histogram of the point distribution throughout the model. The disc and envelope can be seen as two separate entities which have to be sampled using different point distributions.}
  \label{points}
@@
 
- \caption{C$^{17}$O 3-2 15 deg Continuum subtracted mom0}
+ \caption{C$^{17}$O 3$\rightarrow$2 inclined at 15$^\circ$ to edge on.
+The three panels are: {\bf left:} Continuum subtracted integrated intensity map (in K$\,$km$\,$s$^{-1}$).
+{\bf Centre:} Intensity weighted velocity map (in km$\,$s$^{-1}$).
+{\bf Right:} Position-velocity diagram with intensities in K.}
 \end{figure*}
@@
 
- \caption{C$^{17}$O 3-2 45 deg Continuum subtracted mom0}
+ \caption{C$^{17}$O 3$\rightarrow$2 inclined at 45$^\circ$ to edge on.
+The three panels are: {\bf left:} Continuum subtracted integrated intensity map (in K$\,$km$\,$s$^{-1}$).
+{\bf Centre:} Intensity weighted velocity map (in km$\,$s$^{-1}$).
+{\bf Right:} Position-velocity diagram with intensities in K.}
 \end{figure*}
@@
 
- \caption{C$^{17}$O 3-2 75 deg Continuum subtracted mom0}
+ \caption{C$^{17}$O 3$\rightarrow$2 inclined at 75$^\circ$ to edge on.
+The three panels are: {\bf left:} Continuum subtracted integrated intensity map (in K$\,$km$\,$s$^{-1}$).
+{\bf Centre:} Intensity weighted velocity map (in km$\,$s$^{-1}$).
+{\bf Right:} Position-velocity diagram with intensities in K.}
 \end{figure*}

### 2013-02-20 paper.tex
corrections done

@@
 
-\title[Young protoplanetary discs]{Simulated Observations of Young Protoplanetary Discs}
+\title[Young protoplanetary discs]{Simulated Observations of Young Gravitationally Unstable Protoplanetary Discs}
 %%authors arent splitting over 2 lines so rawlings is pushed off the edge
@@
 These processes produce clear chemical signatures of the disc dynamics.
-With the use of 3D radiative transfer modelling, we perform simulated ALMA observations of the disc studied by I2011 and identify the best tracers of the physical structure of self-gravitating discs.
+With the use of non-LTE 3D radiative transfer modelling, we perform simulated ALMA observations of the disc studied by I2011 and identify the best tracers of the physical structure of self-gravitating discs.
 The physical, chemical and radiative transfer models are described in Sect.\,\ref{sec:description_model}.
@@
 
-\subsection{Physical and chemical structure} \label{subsec:physical_structure}
+\subsection{Physical structure} \label{subsec:physical_structure}
 
@@
 The gas/dust mass ratio was assumed to be 1/100 throughout the disc and the envelope.
-The opacities were adopted from Ossenkops and Henning (1994) and refer to dust grains with thick icy mantles and 10$^6$ yr coagulation history.\newline
+The dust opacities were adopted from Ossenkopf and Henning (1994) and refer to dust grains with thick icy mantles and 10$^6$ yr coagulation history.\newline
 
+\subsection{Chemical structure} \label{subsec:chemical_structure}
 Chemical abundances in the disc were taken from I2011 who followed gas-grain chemical processes during the dynamical evolution of the disc.
@@
 Simulations are limited to molecules for which we have abundances in both the disc and envelope, and also have calculated Einstein and collisional coefficients.
+In the envelope the HCO$^+$ abundance profile follows the H$_2$O profile of L1544 (Caselli et al.
+2012), scaled so the maximum is 1$\times$10$^{-8}$ (because photo-disassoc and freeze out are in similar places, need ref).
+The H$_2$CO has a step profile abundance with a fractional abundance of 1.5$\times$10$^{-8}$ at radii greater than 0.04$\,$pc and 1.5$\times$10$^{9}$ inside it (Young et al.
+2004), OCS has a constant abundance of 1.9$\times$10$^{-9}$ (Ren et al.
+2011) and C$^{17}$O uses the CO profile of L1544 of KC2010 divided by 1792.
 We focus on the frequency range available with ALMA, with particular attention to band 7, which offers the best trade off between resolution and sensitivity.
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/casa_cont_337GHz.eps}
+ \includegraphics[width=84mm]{Figures/sim/casa_cont_300GHz_invert.eps}
 
- \caption{CASA simulation on the continuum emission of the model at 337GHz, using the same ALMA configuration as used for the molecular lines.}
+ \caption{CASA simulation on the continuum emission of the model at 300GHz, using the same ALMA configuration as used for the molecular lines.
+The size of the beam at 300GHz is shown in the lower left corner.}
  \label{continuum}
@@
  \caption{Spectra for each of the simulated species at the positions indicated by the numbers in figure \ref{mom0_maps}, the red green and blue curves are taken from the locations marked 1, 2 and 3 respectively.
-In each diagram, the three spectra are taken from positions on the Y=0 axis, one is at X=0 (green) and the other 2 are from x=$\pm$ N (plus blue, minus red) where N is the distance from the centre: 10 AU for OCS, 20 AU for H2CO, 28 AU for C17O, 38 AU for HCO+.}
+In each diagram, the three spectra are taken from positions on the Y=0 axis, one is at X=0 (green) and the other 2 are from x=$\pm$ N (plus blue, minus red) where N is the distance from the centre: 10 AU for OCS, 20 AU for H$_2$CO, 28 AU for C$^{17}$O, 38 AU for HCO$^+$.}
  \label{spectra}
@@
 However, the large volume densities are expected to provide an efficient dust-gas coupling.\newline
-Outflows could contaminate measurements of rotation curves meaning that species  which commonly trace outflows, such as CO and HCO$^+$ are not going to be good tracers of disc rotation.
-However species such as OCS and C$^{17}$O which are not commonly seen in outflows (e.g.
-van der Tak et al.
-2003, Stanke et al.
-2007, Yildiz et al 2012, Ren et al.
-2011) can be used to trace disc rotation.\newline
+Outflows could contaminate measurements of rotation curves, meaning that species  which commonly trace outflows, such as CO and HCO$^+$ are not going to be good tracers of disc rotation.
+However species such as OCS and C$^{17}$O, which are not commonly seen in outflows, can be used to trace disc rotation.\newline
 
@@
 
-Figures showing different inclinations 
+Simulations at inclinations other than 30$^\circ$ were also performed with C$^{17}$O in order to demonstate that these results could be replicated over a range of inclination angles.
+Figures B1-3 show the C$^{17}$O 3$\rightarrow$2 line in the same phisical model but at 15$^\circ$, 45$^\circ$ and 75$^\circ$ to egde on.
+At 15$^\circ$ to edge on we can still see some structure in the integrated intensity map but also the structure is visible in the position velocity diagram.
+At larger incliations it gets more difficult to obtain any kinematic information but the physical structure of the disc becomes clearer.
+
 \begin{figure*}
- \includegraphics[width=198mm]{Figures/sim/imageC17O_3-2_15deg_all.eps}
+ \includegraphics[width=164mm]{Figures/sim/imageC17O_3-2_15deg_all.eps}
 
@@
 \begin{figure*}
- \includegraphics[width=198mm]{Figures/sim/imageC17O_3-2_45deg_all.eps}
+ \includegraphics[width=164mm]{Figures/sim/imageC17O_3-2_45deg_all.eps}
 
@@
 \begin{figure*}
- \includegraphics[width=198mm]{Figures/sim/imageC17O_3-2_75deg_all.eps}
+ \includegraphics[width=164mm]{Figures/sim/imageC17O_3-2_75deg_all.eps}
 

### 2013-02-22 paper.tex
tweaks

@@
 \def   \nat{\rm {Nat.}}
+\def   \pasj{\rm {PASJ}}
 
@@
 \begin{keywords}
-circumstellar matter -- infrared: stars.
+Stars: Circumstellar Matter -- infrared; Stars: Formation -- infrared; Planetary Systems: Protoplanetary Discs.
 \end{keywords}
@@
 
-The formation and early evolution of protoplanetary discs around solar-type and low-mass protostars has little observational support, despite of the fast growing list of theoretical models on the dynamical evolution of star forming dense cores (e.g.
-Krasnopolsky et al.
-2011; Machida et al.
-2011; Braiding \& Wardle 2012; Joos et al.
-2013).
+The formation and early evolution of protoplanetary discs around solar-type and low-mass protostars has little observational support, despite of the fast growing list of theoretical models on the dynamical evolution of star forming dense cores \citep[e.g.]{Krasnopolsky2011,Machida2011,Braiding2012,Joos2013}.
 The reason for this is that young protostars are surrounded by thick envelopes and power energetic outflows.
 Thus, observations of the young discs, predicted to have sizes of about 100\,AU and masses as large as 10\% the original core mass (e.g.
-Joos et al.
-2012), are challenging.
+\citealt{Joos2012}), are challenging.
 The use of sensitive interferometers is needed to achieve high angular resolution and spatially/spectrally disentangle the various disc, envelope and outflow components as well to filter out the extended emission tracing envelope material.
@@
 
-After the pioneer work of, e.g., Chandler et al.
-(1995), Brown et al.
-(2000), Looney et al.
-(2000), recent interferometric observations have discovered compact embedded discs in a sample of Class 0 sources (Andr\'e et al.
-2000), finding masses between 0.4 and  $>$1 M$_{\odot}$ (J\o rgensen et al.
-2007, 2009; Enoch et al.
-2011).
-A 130\,AU disc was discovered toward a Class 0 source in Perseus, using the Jansky Very Large Array (JVLA) to observe NH$_3$ (Choi et al.
-2007).
-Pineda et al.
-(2012) observed methyl formate (HCOOCH$_3$) with the Atacama Large Millimetre/sub-millimetre Array (ALMA) and found evidence of rotation toward one of the proto-binary Class 0 sources embedded in IRAS 16293-2422.
+After the pioneer work of, e.g., \citet{Chandler1995,Brown2000,Looney2000}, recent interferometric observations have discovered compact embedded discs in a sample of Class 0 sources \citep{Andre1999}), finding masses between 0.4 and  $>$1 M$_{\odot}$ \citep{Jorgensen2007,Jorgensen2009,Enoch2011}.
+A 130\,AU disc was discovered toward a Class 0 source in Perseus, using the Jansky Very Large Array (JVLA) to observe NH$_3$ \citep{Choi2007}.
+\citet{Pineda2012} observed methyl formate (HCOOCH$_3$) with the Atacama Large Millimetre/sub-millimetre Array (ALMA) and found evidence of rotation toward one of the proto-binary Class 0 sources embedded in IRAS 16293-2422.
 These observations are consistent with an almost edge-on disc.
-Persson et al.
-(2012) observed H$_2^{18}$O with ALMA toward the same source and found evidence of relatively large ($\ga$100\,K) excitation temperatures, as well as a HDO/H$_2$O abundance ratio close to that measured on Earth's oceans and Jupiter-family comets (Hartogh et al.
-2011).
-Zapata et al.
-(2013) used ALMA to observe a disc of size $\sim$50$\,$AU in the other Class 0 source in IRAS 16293-2422 and detected infall towards this disc as inverse P-Cygni profiles in HCN and CH$_3$OH.
+\citet{Persson2012} observed H$_2^{18}$O with ALMA toward the same source and found evidence of relatively large ($\ga$100\,K) excitation temperatures, as well as a HDO/H$_2$O abundance ratio close to that measured on Earth's oceans and Jupiter-family comets \citep{Hartogh2012}.
+\citet{Zapata2013} used ALMA to observe a disc of size $\sim$50$\,$AU in the other Class 0 source in IRAS 16293-2422 and detected infall towards this disc as inverse P-Cygni profiles in HCN and CH$_3$OH.
 When ALMA is completed, it will be finally possible to spatially resolve these young discs and, for the first time, put stringent constraints on the theoretical models mentioned previously.
@@
 
-Simulated observations of gravitationally unstable discs have already been performed to study the continuum emission, measure the structure and investigate possible fragmentation (Cossins et al.
-2010; Ruge et al.
-2013).
-Molecular line emission from massive discs has been simulated by Krumholz et al.
-(2007), assuming local thermodynamic equilibrium (LTE).
-In this paper, we focus on the self-gravitating discs of Boley \& Durisen (2008), where episodic heating induced by spiral shocks is present.
-This may be a good representation of the earliest phases of protoplanetary discs and an alternative to the young ``static'' discs studied by, e.g., Visser et al.
-(2009, 2011).
-As shown by Ilee et al.
-(2011; hereafter I2011), the spiral shocks cause desorption of volatiles from dust icy mantles and trigger gas-phase chemical reactions with activation energies, too high to occur at lower temperatures.
+Simulated observations of gravitationally unstable discs have already been performed to study the continuum emission, measure the structure and investigate possible fragmentation \citep{Cossins2010,Ruge2013}.
+Molecular line emission from massive discs has been simulated by \citet{Krumholz2007}, assuming local thermodynamic equilibrium (LTE).
+In this paper, we focus on the self-gravitating discs of \citet{Boley2008}, where episodic heating induced by spiral shocks is present.
+This may be a good representation of the earliest phases of protoplanetary discs and an alternative to the young ``static'' discs studied by, e.g., \citet{Visser2009,Visser2011}.
+As shown by \citet{Ilee2011}, hereafter I2011, the spiral shocks cause desorption of volatiles from dust icy mantles and trigger gas-phase chemical reactions with activation energies, too high to occur at lower temperatures.
 These processes produce clear chemical signatures of the disc dynamics.
@@
 
-To describe the full physical enviroment which we expect these young discs to occur in, we combine the disc model from I2011 with a model of a dense core with characteristics similar to the well-studied pre-stellar core L1544 (Keto \& Caselli 2010; hereafter KC2010).
-The KC2010 model follows the dynamical, chemical and thermal evolution of a contracting Bonnor-Ebert sphere (Bonnor 1956; Ebert 1957) with total mass of 10\,M$_{\odot}$, until it reaches the density, temperature and velocity profiles which best match observations.
-The pre-stellar core model adopted here contains slight modifications due to the inclusion of oxygen cooling in the outer regions of the cloud, where CO is mostly photodissociated (Caselli et al.
-2012; Keto et al.
-in preparation).
+To describe the full physical enviroment which we expect these young discs to occur in, we combine the disc model from I2011 with a model of a dense core with characteristics similar to the well-studied pre-stellar core L1544 \citep{Keto2010}, hereafter KC2010.
+The KC2010 model follows the dynamical, chemical and thermal evolution of a contracting Bonnor-Ebert sphere \citep{Bonnor1956,Ebert1957} with total mass of 10\,M$_{\odot}$, until it reaches the density, temperature and velocity profiles which best match observations.
+The pre-stellar core model adopted here contains slight modifications due to the inclusion of oxygen cooling in the outer regions of the cloud, where CO is mostly photodissociated \citep{Caselli2012}.
 Figure \ref{fig:l1544_model} shows the physical parameters of the core model.
@@
 The pre-stellar core structure is maintained down to a radius of 80\,AU, within which the model of the young protoplanetary disc is used.
-The disc structure is derived by the hydrodynamic model of Boley (2007) and Boley (2009).
+The disc structure is derived by the hydrodynamic model of \citet{Boley2007,Boley2009}.
 The particular model considered here (as well as in I2011) is a 0.39$\,\rm{M}_\odot$ self-gravitating Keplerian disc (figure \ref{velocity}) featuring prominent spiral arms.
@@
 These abundances were interpolated onto a 51$^3$ grid covering the disc with cells of size 2.2$\times$2.2$\times$0.22$\,$AU.
-From I2011 we selected the four species which appear to trace different regions of the disc: the inner 20\,AU (OCS), the inner 40\,AU (H$_2$CO),  the region between $\simeq$40 and 60\,AU (HCO$^+$) and one which traces the entirety of the disc (C$^{17}$O) (see figure \ref{Chemistry}, the abundance model used for C$^{17}$O was the CO model reduced by a factor of 1792, the ratio of $^{16}$O to $^{17}$O in the local ISM, Wilson \& Rood 1994).
+From I2011 we selected the four species which appear to trace different regions of the disc: the inner 20\,AU (OCS), the inner 40\,AU (H$_2$CO),  the region between $\simeq$40 and 60\,AU (HCO$^+$) and one which traces the entirety of the disc (C$^{17}$O) (see figure \ref{Chemistry}, the abundance model used for C$^{17}$O was the CO model reduced by a factor of 1792, the ratio of $^{16}$O to $^{17}$O in the local ISM, \citet{Wilson1994}.
 As explained by I2011,  H$_2$CO and OCS mostly probe the central warm regions, where icy mantles evaporate, whereas HCO$^+$ preferentially traces the outer spiral pattern as in the central region it is destroyed by water molecules and transformed into H$_3$O$^+$ and CO.
-The simple chemistry in the KC2010 model, adopted here as the envelope of the protoplanetary disc, does not provide detailed abundances of molecular species (besides CO and H$_2$O, see also Caselli et al.
-2012).
+The simple chemistry in the KC2010 model, adopted here as the envelope of the protoplanetary disc, does not provide detailed abundances of molecular species (besides CO and H$_2$O, see also \cite{Caselli2012}).
 As discussed in the result section \ref{sec:model_results}, approximations have been made based on values measured toward similar objects.
@@
 %-describe the RT used (LIME) 
-The radiative transfer program used is LIME (LIne Modeling Engine; Brinch \& Hogerheijde 2010), which  calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3D model.
+The radiative transfer program used is LIME (LIne Modeling Engine; \cite{Brinch2010}), which  calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3D model.
 The method of selecting these points is given in appendix  \ref{sec:gridding}).
 At each of these points, the density of the main collision partner (H$_2$), gas and dust temperatures, velocity, molecular abundances and turbulent velocity are specified.
-These points are then smoothed by Lloyd's algorithm (Lloyd 1982) in order to minimise the variation in distance between points whilst keeping the same underlying distribution.
+These points are then smoothed by Lloyd's algorithm \citep{Lloyd1982} in order to minimise the variation in distance between points whilst keeping the same underlying distribution.
 These points are then connected by Delaunay triangulation \footnote{In three dimensions this means that if four points are connected into a tetrahedron, the sphere circumscribing these four points contains no other points.
@@
 This is repeated 20 times with the populations of each level converging towards a single value.
-This number of iterations is sufficient for the signal to noise ratio of the level populations (as defined in Brinch \&Hogerheijde 2010) to exceed 1000 in 99\% of the points, ensuring that the simulation has converged on a stable level population.
+This number of iterations is sufficient for the signal to noise ratio of the level populations (as defined in \cite{Brinch2010} to exceed 1000 in 99\% of the points, ensuring that the simulation has converged on a stable level population.
 After 20 iterations the model is ray-traced in order to produce synthetic brightness maps.
@@
 Simulations are limited to molecules for which we have abundances in both the disc and envelope, and also have calculated Einstein and collisional coefficients.
-In the envelope the HCO$^+$ abundance profile follows the H$_2$O profile of L1544 (Caselli et al.
-2012), scaled so the maximum is 1$\times$10$^{-8}$ (because photo-disassoc and freeze out are in similar places, need ref).
-The H$_2$CO has a step profile abundance with a fractional abundance of 1.5$\times$10$^{-8}$ at radii greater than 0.04$\,$pc and 1.5$\times$10$^{9}$ inside it (Young et al.
-2004), OCS has a constant abundance of 1.9$\times$10$^{-9}$ (Ren et al.
-2011) and C$^{17}$O uses the CO profile of L1544 of KC2010 divided by 1792.
+In the envelope the HCO$^+$ abundance profile follows the H$_2$O profile of L1544 \citep{Caselli2012}, scaled so the maximum is 1$\times$10$^{-8}$ (because photo-disassoc and freeze out are in similar places, {\bf need ref for this}).
+The H$_2$CO has a step profile abundance with a fractional abundance of 1.5$\times$10$^{-8}$ at radii greater than 0.04$\,$pc and 1.5$\times$10$^{9}$ inside it \citep{Young2004}, OCS has a constant abundance of 1.9$\times$10$^{-9}$ \citep{Ren2011} and C$^{17}$O uses the CO profile of L1544 of KC2010 divided by 1792.
 We focus on the frequency range available with ALMA, with particular attention to band 7, which offers the best trade off between resolution and sensitivity.
@@
 The most notable thing about these spectral features is that they are not symmetric about the disk centre.
-For example, C17O(3$\rightarrow$2) has a significantly stronger blueshifted absorption, due to the presence of a spiral arm along the same line of sight.
+For example, C$^{17}$O(3$\rightarrow$2) has a significantly stronger blueshifted absorption, due to the presence of a spiral arm along the same line of sight.
 In the OCS lines, the two sides are not moving with equal velocities and the line widths and shapes are markedly different.
@@
 
-\newpage
+\bibliographystyle{apalike} 
+\bibliography{new_bib}
 

### 2013-03-01 paper.tex
pre-comments

@@
 \usepackage{wasysym}
-\usepackage{stmaryrd}
+%\usepackage{stmaryrd}
 \usepackage{txfonts}
@@
 T. W. Hartquist$^{1}$,
-R. Durisen$^{3}$, and
-J. Rawlings$^{4}$\\
+R. H. Durisen$^{3}$, and
+J. C. Rawlings$^{4}$\\
 \vspace{0.1cm}\\
@@
 The formation and earliest stages of protoplanetary discs are still lacking observational constraints.
-ALMA will soon revolutionise this field, so it is important to provide predictions and help the interpretation of future high sensitivity and high angular resolution observations.
+ALMA will soon revolutionize this field, so it is important to provide predictions and help the interpretation of future high sensitivity and high angular resolution observations.
 Here we present simulated ALMA observations based on radiative transfer modelling of a relatively massive (0.39 M$_{\odot}$) self-gravitating disc embedded in a 10\,M$_{\odot}$ dense core, with structure similar to the pre-stellar core L1544.
-We focus on simple species and conclude that OCS, C$^{17}$O, H$_2$CO and HCO$^+$ lines together allow for measurements of the disc structure and kinematics at all scales.
+We focus on simple species and conclude that  C$^{17}$O 3$\rightarrow$2, HCO$^+$ 3$\rightarrow$2, OCS 26$\rightarrow$25 and H$_2$CO 4$_{04}\rightarrow$3$_{03}$ lines together allow for measurements of the disc structure and kinematics at all scales.
 \end{abstract}
@@
 
-The formation and early evolution of protoplanetary discs around solar-type and low-mass protostars has little observational support, despite of the fast growing list of theoretical models on the dynamical evolution of star forming dense cores \citep[e.g.]{Krasnopolsky2011,Machida2011,Braiding2012,Joos2013}.
+The formation and early evolution of protoplanetary discs around solar-type and low-mass protostars has little observational support, despite of the fast growing list of theoretical models on the dynamical evolution of star forming dense cores (e.g.
+\citealt{Krasnopolsky2011,Machida2011,Braiding2012,Joos2013}).
 The reason for this is that young protostars are surrounded by thick envelopes and power energetic outflows.
@@
 
-After the pioneer work of, e.g., \citet{Chandler1995,Brown2000,Looney2000}, recent interferometric observations have discovered compact embedded discs in a sample of Class 0 sources \citep{Andre1999}), finding masses between 0.4 and  $>$1 M$_{\odot}$ \citep{Jorgensen2007,Jorgensen2009,Enoch2011}.
+After the pioneer work of, e.g., \citet{Chandler1995,Brown2000,Looney2000}, recent interferometric observations have discovered compact embedded discs in a sample of Class 0 sources \citep{Andre1999}, finding masses between 0.4 and  $>$1 M$_{\odot}$ \citep{Jorgensen2007,Jorgensen2009,Enoch2011}.
 A 130\,AU disc was discovered toward a Class 0 source in Perseus, using the Jansky Very Large Array (JVLA) to observe NH$_3$ \citep{Choi2007}.
@@
 
-To describe the full physical enviroment which we expect these young discs to occur in, we combine the disc model from I2011 with a model of a dense core with characteristics similar to the well-studied pre-stellar core L1544 \citep{Keto2010}, hereafter KC2010.
+To appropriately describe the environment within which a young protoplanetary disc is embedded, we combine the disc model from I2011 with a model of a dense core with characteristics similar to the well-studied pre-stellar core L1544 (\citealt{Keto2010}, hereafter KC2010).
 The KC2010 model follows the dynamical, chemical and thermal evolution of a contracting Bonnor-Ebert sphere \citep{Bonnor1956,Ebert1957} with total mass of 10\,M$_{\odot}$, until it reaches the density, temperature and velocity profiles which best match observations.
@@
  \label{fig:l1544_model}
+\end{figure}
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/model/rotational_velocities.eps}
+ \caption{Azimuthaly averaged rotational velocity in the disc mid-plane with best fit curve.}
+ \label{velocity}
 \end{figure}
@@
 
-\begin{figure}
- \includegraphics[width=84mm]{Figures/model/rotational_velocities.eps}
- \caption{Azimuthaly averaged rotational velocity in the disc mid-plane with best fit curve.}
- \label{velocity}
-\end{figure}
-
 The pre-stellar core structure is maintained down to a radius of 80\,AU, within which the model of the young protoplanetary disc is used.
-The disc structure is derived by the hydrodynamic model of \citet{Boley2007,Boley2009}.
+The disc structure is derived by the hydrodynamic model of \citet{Boley2007} and  \citet{Boley2009}.
 The particular model considered here (as well as in I2011) is a 0.39$\,\rm{M}_\odot$ self-gravitating Keplerian disc (figure \ref{velocity}) featuring prominent spiral arms.
@@
 The abundances of 125 species related by 1334 reactions were calculated through the time evolution of the disc.
-These abundances were interpolated onto a 51$^3$ grid covering the disc with cells of size 2.2$\times$2.2$\times$0.22$\,$AU.
-From I2011 we selected the four species which appear to trace different regions of the disc: the inner 20\,AU (OCS), the inner 40\,AU (H$_2$CO),  the region between $\simeq$40 and 60\,AU (HCO$^+$) and one which traces the entirety of the disc (C$^{17}$O) (see figure \ref{Chemistry}, the abundance model used for C$^{17}$O was the CO model reduced by a factor of 1792, the ratio of $^{16}$O to $^{17}$O in the local ISM, \citet{Wilson1994}.
+These abundances were interpolated onto a 51$^3$ grid covering the disc with cells of size 2.2$\times$2.2$\times$0.22$\,$AU$^2$.
+From I2011 we selected the four species which appear to trace different regions of the disc: the inner 20\,AU (OCS), the inner 40\,AU (H$_2$CO),  the region between $\simeq$40 and 60\,AU (HCO$^+$) and one which traces the entirety of the disc (C$^{17}$O) (see figure \ref{Chemistry}).
+The abundance model used for C$^{17}$O was the CO model reduced by a factor of 1792, the ratio of $^{16}$O to $^{17}$O in the local ISM \citep{Wilson1994}.
 As explained by I2011,  H$_2$CO and OCS mostly probe the central warm regions, where icy mantles evaporate, whereas HCO$^+$ preferentially traces the outer spiral pattern as in the central region it is destroyed by water molecules and transformed into H$_3$O$^+$ and CO.
@@
 The molecular data used is from the LAMDA (Leiden Atomic and Molecular DAtabase) database (Sch\"oier et al.
-(2005; http://home.strw.leidenuniv.nl/$\sim$moldata/).
+2005; http://home.strw.leidenuniv.nl/$\sim$moldata/).
 
@@
 The radiative transfer program used is LIME (LIne Modeling Engine; \cite{Brinch2010}), which  calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3D model.
-The method of selecting these points is given in appendix  \ref{sec:gridding}).
+The method of selecting these points is given in appendix  \ref{sec:gridding}.
 At each of these points, the density of the main collision partner (H$_2$), gas and dust temperatures, velocity, molecular abundances and turbulent velocity are specified.
@@
 Simulations are limited to molecules for which we have abundances in both the disc and envelope, and also have calculated Einstein and collisional coefficients.
-In the envelope the HCO$^+$ abundance profile follows the H$_2$O profile of L1544 \citep{Caselli2012}, scaled so the maximum is 1$\times$10$^{-8}$ (because photo-disassoc and freeze out are in similar places, {\bf need ref for this}).
-The H$_2$CO has a step profile abundance with a fractional abundance of 1.5$\times$10$^{-8}$ at radii greater than 0.04$\,$pc and 1.5$\times$10$^{9}$ inside it \citep{Young2004}, OCS has a constant abundance of 1.9$\times$10$^{-9}$ \citep{Ren2011} and C$^{17}$O uses the CO profile of L1544 of KC2010 divided by 1792.
+In the envelope, the HCO$^+$ abundance profile follows the H$_2$O profile of L1544 \citep{Caselli2012}, scaled so the maximum is 1$\times$10$^{-8}$ (assuming, for simplicity, that photodissociation and freeze-out affect these two species in a similar way).For H$_2$CO, a step profile was considered, with a fractional abundance of 1.5$\times$10$^{-8}$ at radii greater than 0.04$\,$pc and 1.5$\times$10$^{-9}$ inside it \citep{Young2004}.
+For OCS we adopted a constant abundance of 1.9$\times$10$^{-9}$ \citep{Ren2011}.
+The C$^{17}$O abundance profile in the envelope follows the CO profile calculated for L1544 by KC2010, scaled by the 17O/16O elemental abundance.
+
 We focus on the frequency range available with ALMA, with particular attention to band 7, which offers the best trade off between resolution and sensitivity.
+Thus, we consider C$^{17}$O(3$\rightarrow$2), HCO$^+$(3$\rightarrow$2), OCS (26$\rightarrow$25) and H$_2$CO(4$_{04}\rightarrow$3$_{03}$).
+The frequencies and upper level energies of these transitions are in table \ref{sigmas}.
 The results presented in this section are limited to those lines which show detectable emission/absorption which can be used to trace either spiral structure or rotation.\newline
 
-We considered C$^{17}$O 3$\rightarrow$2 at 337.1$\,$GHz with an upper energy level of $E_u$=32.3K, HCO$^+$ 3$\rightarrow$2 at 267$\,$GHz and $E_u$=25.7K, OCS 26$\rightarrow$25 at 316$\,$GHz and $E_u$=205K and H$_2$CO 4$_{04}\rightarrow$3$_{03}$ at 290$\,$GHz and $E_u$=34.9K.\newline
+%We considered C$^{17}$O 3$\rightarrow$2 at 337.1$\,$GHz with an upper energy level of $E_u$=32.3K, HCO$^+$ 3$\rightarrow$2 at 267$\,$GHz and $E_u$=25.7K, OCS 26$\rightarrow$25 at 316$\,$GHz and $E_u$=205K and H$_2$CO 4$_{04}\rightarrow$3$_{03}$ at 290$\,$GHz and $E_u$=34.9K.\newline
 
 To simulate observations, the model was placed at roughly the distance of nearby low-mass star forming regions (100$\,$pc) and the disc is inclined at 30$^\circ$ to edge on.
-From these simulated observations, integrated intensity, intensity weighted velocity and position velocity diagrams through the centre of the model were created.
-(The integrated intensity and intensity weighted velocity maps (figures \ref{sim_all} and \ref{mom0_maps}) were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope.
+From these simulated observations, integrated intensity maps, intensity weighted velocity maps and position velocity diagrams were created.
+The integrated intensity and intensity weighted velocity maps (figures \ref{sim_all} and \ref{mom0_maps}) were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope.
 This can be seen in some PV diagrams  (figure \ref{pvs}) as the strong absorption feature at all positions around zero velocity.
-Moment 1 maps are shown with a cut-off of 3$\sigma$ as described in section \ref{sec:alma_predictions})\newline
+Moment 1 maps are shown with a cut-off of 3$\sigma$ as described in section \ref{sec:alma_predictions}.\newline
 
@@
 
-OCS traces only the innermost 20$\,$AU of the disc and can be used to examine the central regions (figure \ref{sim_all}).
+OCS 26$\rightarrow$25 traces only the innermost 20$\,$AU of the disc and can be used to examine the central regions (figure \ref{sim_all}).
 As OCS is not seen in outflows (e.g.
-Stanke 07, Van der Tak 03) it can be used to view rotation of the central part of the disc without risk of contamination from emission from shocked material.
+\citealt{Stanke2007}, \citealt{VDTak2003}) it can be used to view rotation of the central part of the disc without risk of contamination from emission from shocked material along the outflow.
 The OCS line, which has the highest upper energy level among the selected transitions, traces the hottest and densest regions of the disc.
@@
 The majority of the OCS line is visible in absorption against the bright continuum emission from the disc mid-plane.
-The exception to this is towards the centre of the disc where the hole in the hot, dense mid-plane means that there is little continuum to be absorbed.\newline
+The exception to this is towards the centre of the disc where the hole in the hot, dense mid-plane means that there is little continuum to be absorbed.
+However, because of the presence of the protostar and other hot material within the central hole, not considered in our simple model, we expect absorption to also be observed toward the central region of the disc.\newline
 
-The abundance of the H$_2$CO molecule traces the spiral structure of the inner $\sim$40$\,$AU of the disc.
-The spiral structure of the disc can be seen clearly in the integrated intensity map and its rotation is detected out to larger radii than is possible with the OCS line (figure \ref{sim_all}).
+The abundance of the H$_2$CO molecule traces the spiral structure of the inner $\sim$40$\,$AU of the disc, ehich can be seen in the integrated intensity map and its rotation is detected out to larger radii than is possible with the OCS line (figure \ref{sim_all}).
 As with the OCS line, the majority of the H$_2$CO 4$_{04}\rightarrow$3$_{03}$, is seen in absorption against the disc mid-plane continuum, with the central region seen in emission.
@@
 
-The fractional abundance of C$^{17}$O is constant at 2$\times$10$^{-8}$ across the disc, meaning the C$^{17}$O line is the most accurate in reproducing the physical structure of the disc.
+The fractional abundance of C$^{17}$O is constant at 2$\times$10$^{-8}$ across the disc, so that the selected C$^{17}$O line is the most accurate in reproducing the physical structure of the disc.
 Like H$_2$CO, C$^{17}$O shows emission in voids between spiral arms.
 The C$^{17}$O line is visible from the inner edge of the disc to its outer edge.
-Like OCS, C$^{17}$O is not seen in outflows (e.g.
-Yildiz et al.
-2012) and so rotation seen in C$^{17}$O lines should only be due to rotation from the disc and not contamination from outflows.\newline
+Like OCS, C$^{17}$O is not seen in outflows \citep{Yildiz2012}, so we do not expect contamination.\newline
 
 HCO$^+$ in unique in the molecules simulated in I2011 in that it traces only the outer regions of the disc, and so can be used to look at the extended velocity and physical structure.
-In figure \ref{sim_all} we can see that the HCO$^+$ line shows the outer edges of the spiral arms in absorption, but also shows emission from the diffuse gas further out in the disc.
-This allows the velocity structure of the disc measured out to larger radii.
+In figure \ref{sim_all} we can see that the HCO$^+$ line shows the outer edges of the spiral arms in absorption, but it also shows emission from the diffuse gas further out in the disc.
+This allows the velocity structure of the disc to be measured out to larger radii.
 This allows constraints to be placed on the rotation of the disc out to larger radii than with other molecules.
@@
 
-In order to make predictions on the observability of the synthetic brightness maps, the Common Astronomy Software Applications package (CASA) was used to simulate their observation with the completed ALMA in the 26th most extended comfiguration (out of a total of 28), with a longest baseline of 14.4km and giving beam sizes of between 0.02 and 0.03 arcseconds at the simulated frequencies.
+In order to make predictions on the observability of the synthetic brightness maps, the Common Astronomy Software Applications package (CASA) was used to simulate their observation with the completed ALMA in the 26th most extended configuration (out of a total of 28), with the longest baseline of 14.4km and giving beam sizes between 0.02 and 0.03 arcseconds at the selected frequencies, giving a beam size close to the size of the spiral structure in the disc.
 As the weakest lines studied in the model are of the order of 0.1-0.2$\,$mJy$\,$beam$^{-1}$ at this resolution, sensitivities of the order of 0.02$\,$mJy$\,$beam$^{-1}$ are required.
@@
 The exact sensitivities are given in Table \ref{sigmas}.
-\begin{table}
+\begin{table*}
  \centering
  \begin{minipage}{80mm}
-   \caption{Sensitivities of ALMA given 6 hours integration time with velocity resolution of $\sim$400$\,$ms$^{-1}$. As calculated by the ALMA on-line sensitivity calculator.}
+   \caption{Line sensitivities obtained with ALMA after 6 hours integration time with velocity resolution of $\sim$400$\,$ms$^{-1}$. As calculated by the ALMA on-line sensitivity calculator.}
    \label{sigmas}
-   \begin{tabular}{c||c|c|c}
+   \begin{tabular}{c||c|c|c|c}
      \hline
-     Species & Transition & Frequency & Sensitivity\\
+     Species & Transition & Frequency & Upper energy level & Sensitivity\\
      \hline
-     C$^{17}$O & 3$\rightarrow$2 & 337.06GHz & 0.0270$\,$mJy$\,$beam$^{-1}$ \\
-     OCS & 26$\rightarrow$25 & 316.15GHz & 0.0275$\,$mJy$\,$beam$^{-1}$ \\
-     HCO$^+$ & 3$\rightarrow$2 & 267.56GHz & 0.0176$\,$mJy$\,$beam$^{-1}$ \\
-     H$_2$CO & 4$_{04}\rightarrow$3$_{03}$ & 290.62GHz & 0.0228$\,$mJy$\,$beam$^{-1}$ \\
+     C$^{17}$O & 3$\rightarrow$2 & 337.06GHz & 32.3$\,$K & 0.0270$\,$mJy$\,$beam$^{-1}$ \\
+     OCS & 26$\rightarrow$25 & 316.15GHz & 25.7$\,$K & 0.0275$\,$mJy$\,$beam$^{-1}$ \\
+     HCO$^+$ & 3$\rightarrow$2 & 267.56GHz & 205$\,$K & 0.0176$\,$mJy$\,$beam$^{-1}$ \\
+     H$_2$CO & 4$_{04}\rightarrow$3$_{03}$ & 34.9$\,$K & 290.62GHz & 0.0228$\,$mJy$\,$beam$^{-1}$ \\
      \hline
@@
  \end{minipage}
-\end{table}
-In order to clean the images, which featured mainly absorption, the sky model used was the output of the LIME simulations with the continuum subtracted and then the image inverted.
-The simulated images were cleaned down to a 3$\sigma$ level with $\sigma$ given in table \ref{sigmas}.\newline
+\end{table*}
+In order to clean the images, which featured mainly absorption, the sky model used was the output of the LIME simulations with the continuum subtracted and then the spectrum inverted.
+The simulated images were cleaned down to a 3$\sigma$ level with $\sigma$ (the sensitivity) given in table \ref{sigmas}.\newline
 
@@
 
-Figure \ref{h2co_chanmap} shows a channel map of the H$_2$CO 4$_{04}\rightarrow$3$_{03}$ line overlaid on the 1$\,$mm continuum emission (figure \ref{continuum}).
-From this it can be seen that the absorption features trace the disc spiral structure whilst line emission emanates from gaps in the outer disc where there is less continuum to be absorbed.\newline
+Figure \ref{continuum} Shows the 1mm continuum emission and beam size in this configuration of ALMA.
+
+Figure \ref{h2co_chanmap} shows a channel map of the H$_2$CO 4$_{04}\rightarrow$3$_{03}$ line overlaid on the 1$\,$mm continuum emission.
+From this it can be seen that the absorption features trace the disc spiral structure whilst the line emission emanates from gaps in the outer disc, where there is less continuum to be absorbed.\newline
 
 \begin{figure*}
- \includegraphics[width=168mm]{Figures/sim/casa_all_30deg_contSub_nums.eps}
+ \includegraphics[width=168mm]{Figures/sim/casa_all_30deg_contSub_dots.eps}
  \caption{Integrated intensity maps for the simulated observations of: {\bf Top Left:} H$_2$CO 4$_{04}\rightarrow$3$_{03}$, {\bf Top Right:} C$^{17}$O 3$\rightarrow$2, {\bf Bottom Left:} OCS 26$\rightarrow$25 and {\bf Bottom Right:} HCO$^+$ 3$\rightarrow$2.
-contours start at 3$\sigma$ and increasing in intervals of 3$\sigma$ for each of the maps except the H$_2$CO which starts at 5$\sigma$ and increases in intervals of 5$\sigma$.
+Contours start at 3$\sigma$ and increasing in intervals of 3$\sigma$ for each of the maps except the H$_2$CO which starts at 5$\sigma$ and increases in intervals of 5$\sigma$.
 Emission is in red contours, absorption in blue.
-The numbers refer to the spectra shown in figure \ref{spectra}.
-{\bf need to discuss how to do this, i dont like the idea of coloured dots as the spectra are also in red and blue and would get confused with the contours}}
+The dots refer to the spectra shown in figure \ref{spectra}.}
 \label{mom0_maps}
@@
 
-Figure \ref{mom0_maps} shows the simulated integrated intensity maps, which demonstrate how lines from different species allow observations to trace different regions of the disc, from the OCS line tracing the innermost regions, to the HCO$^+$ line showing the outer regions which are less bright in the continuum.
+Figure \ref{mom0_maps} shows the simulated integrated intensity maps, which demonstrates how lines from different species allow observations to trace different regions of the disc, from the OCS line tracing the innermost regions, to the HCO$^+$ line showing the outer regions which are less bright in the continuum.
 ALMA has enough resolution and sensitivity to see spiral structure clearly in continuum emission but also in CO isotopologues and marginally in H$_2$CO.\newline
@@
 
-Figure \ref{pvs} shows position-velocity diagrams of the simulated lines, allowing us to reconstruct the rotation of the disc.
+Figure \ref{pvs} shows position-velocity diagrams of the lines simulated, allowing us to reconstruct the rotation of the disc.
 The green curves in each panel of figure \ref{pvs} display the best fit rotation curve of the physical model (see figure \ref{velocity}), showing that the rotation profile of the disc can be well constrained using kinematic information gathered from species tracing different regions of the disc.\newline
@@
 \begin{figure*}
- \includegraphics[width=168mm]{Figures/sim/casa_all_spectra.eps}
- \caption{Spectra for each of the simulated species at the positions indicated by the numbers in figure \ref{mom0_maps}, the red green and blue curves are taken from the locations marked 1, 2 and 3 respectively.
+ \includegraphics[width=168mm]{Figures/sim/casa_all_spectra2.eps}
+ \caption{Simulated spectra for each of the selected transitions at the positions indicated by the coloured dots in figure \ref{mom0_maps}, the pink, green and cyan curves are taken from the locations marked the dot of the same colour respectively.
 In each diagram, the three spectra are taken from positions on the Y=0 axis, one is at X=0 (green) and the other 2 are from x=$\pm$ N (plus blue, minus red) where N is the distance from the centre: 10 AU for OCS, 20 AU for H$_2$CO, 28 AU for C$^{17}$O, 38 AU for HCO$^+$.}
@@
 
-\section{Discussion and conclusions} \label{sec:discussion}
+\section{Conclusions} \label{sec:discussion}
 
@@
 Outflows could contaminate measurements of rotation curves, meaning that species  which commonly trace outflows, such as CO and HCO$^+$ are not going to be good tracers of disc rotation.
-However species such as OCS and C$^{17}$O, which are not commonly seen in outflows, can be used to trace disc rotation.\newline
-
-We have shown that observations of young, gravitationally-unstable protoplanetary discs can be both seen and differentiated from the envelope.
-Using a range of molecular lines in band 7, would allow such observations to be able to determine both the structure and the kinematics of such a disc.
+However species such as OCS and C$^{17}$O, which are not commonly seen in outflows, can be used to trace disc rotation and structure.\newline
 
@@
 These candidates then have their density and molecular density compared against a reference point in order to decide if the point is to be used in the grid or not.
-Candidate grid points are selected at random in cylindrical co-ordinates, linearly spaced in z and $\phi$ and logarithmically spaced in r.
+Candidate grid points are selected at random in cylindrical coordinates, linearly spaced in z and $\phi$ and logarithmically spaced in r.
 For each point to be selected, a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) as a threshold.
-After selection of random co-ordinates, the hydrogen density and molecular density at the candidate point (n and m, respectively) are compared against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$).
+After selection of random coordinates, the hydrogen density and molecular density at the candidate point (n and m, respectively) are compared against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$).
 If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use, otherwise another r, $\phi$, z co-ordinate is selected and this becomes the candidate point.
@@
 
-Simulations at inclinations other than 30$^\circ$ were also performed with C$^{17}$O in order to demonstate that these results could be replicated over a range of inclination angles.
+Simulations at inclinations other than 30$^\circ$ were also performed with C$^{17}$O.
 Figures B1-3 show the C$^{17}$O 3$\rightarrow$2 line in the same phisical model but at 15$^\circ$, 45$^\circ$ and 75$^\circ$ to egde on.
-At 15$^\circ$ to edge on we can still see some structure in the integrated intensity map but also the structure is visible in the position velocity diagram.
+At 15$^\circ$ to edge on we can still see some structure in the integrated intensity map and the structure is also visible in the position velocity diagram.
 At larger incliations it gets more difficult to obtain any kinematic information but the physical structure of the disc becomes clearer.

### 2013-03-01 young_pp_discs.tex
renamed

--- 2013-03-01 paper.tex
@@
 The gas/dust mass ratio was assumed to be 1/100 throughout the disc and the envelope.
-The dust opacities were adopted from Ossenkopf and Henning (1994) and refer to dust grains with thick icy mantles and 10$^6$ yr coagulation history.\newline
+The dust opacities were adopted from \citet{Ossenkopf1994} and refer to dust grains with thick icy mantles and 10$^6$ yr coagulation history.\newline
 
@@
      HCO$^+$ & 3$\rightarrow$2 & 267.56GHz & 205$\,$K & 0.0176$\,$mJy$\,$beam$^{-1}$ \\
-     H$_2$CO & 4$_{04}\rightarrow$3$_{03}$ & 34.9$\,$K & 290.62GHz & 0.0228$\,$mJy$\,$beam$^{-1}$ \\
+     H$_2$CO & 4$_{04}\rightarrow$3$_{03}$ &  290.62GHz & 34.9$\,$K & 0.0228$\,$mJy$\,$beam$^{-1}$ \\
      \hline
@@
 
- \caption{CASA simulation on the continuum emission of the model at 300GHz, using the same ALMA configuration as used for the molecular lines.
+ \caption{CASA simulation of the continuum emission of the model at 300GHz, using the same ALMA configuration as used for the molecular lines.
 The size of the beam at 300GHz is shown in the lower left corner.}

### 2013-03-07 young_pp_discs.tex
minor comment changes

@@
 R. H. Durisen$^{3}$, and
-J. C. Rawlings$^{4}$\\
+J. M. C. Rawlings$^{4}$\\
 \vspace{0.1cm}\\
-{\small{\it$^{1}$School of Physics and Astronomy, University of Leeds, Leeds LS2 9JT, UK}} \\
-{\small{\it$^{2}$Department of Astronomy, University of Florida, 211 Bryant Space Center, PO Box 112055, USA}}\\
-{\small{\it$^{3}$Department of Astronomy, Indiana University, 727 East 3rd Street, Swain West 319, Bloomington, IN 47405, USA}}\\
+{\small{\it$^{1}$School of Physics and Astronomy, University of Leeds, Leeds LS2 9JT, UK,}} \\
+{\small{\it$^{2}$Department of Astronomy, University of Florida, 211 Bryant Space Center, PO Box 112055, USA,}}\\
+{\small{\it$^{3}$Department of Astronomy, Indiana University, 727 East 3rd Street, Swain West 319, Bloomington, IN 47405, USA,}}\\
 {\small{\it$^{4}$Department of Physics \& Astronomy, University College London, London WC1E 6BT, UK}}\\}}
@@
 The formation and earliest stages of protoplanetary discs are still lacking observational constraints.
-ALMA will soon revolutionize this field, so it is important to provide predictions and help the interpretation of future high sensitivity and high angular resolution observations.
+ALMA will soon revolutionize this field, therefore it is important to provide predictions and help the interpretation of future high sensitivity and high angular resolution observations.
 Here we present simulated ALMA observations based on radiative transfer modelling of a relatively massive (0.39 M$_{\odot}$) self-gravitating disc embedded in a 10\,M$_{\odot}$ dense core, with structure similar to the pre-stellar core L1544.
@@
 The reason for this is that young protostars are surrounded by thick envelopes and power energetic outflows.
-Thus, observations of the young discs, predicted to have sizes of about 100\,AU and masses as large as 10\% the original core mass (e.g.
+Thus, observations of the young discs, predicted to have sizes of about 100\,au and masses as large as 10\% the original core mass (e.g.
 \citealt{Joos2012}), are challenging.
 The use of sensitive interferometers is needed to achieve high angular resolution and spatially/spectrally disentangle the various disc, envelope and outflow components as well to filter out the extended emission tracing envelope material.
-\newline
+\smallskip
 
 After the pioneer work of, e.g., \citet{Chandler1995,Brown2000,Looney2000}, recent interferometric observations have discovered compact embedded discs in a sample of Class 0 sources \citep{Andre1999}, finding masses between 0.4 and  $>$1 M$_{\odot}$ \citep{Jorgensen2007,Jorgensen2009,Enoch2011}.
-A 130\,AU disc was discovered toward a Class 0 source in Perseus, using the Jansky Very Large Array (JVLA) to observe NH$_3$ \citep{Choi2007}.
+A 130\,au disc was discovered toward a Class 0 source in Perseus, using the Jansky Very Large Array (JVLA) to observe NH$_3$ \citep{Choi2007}.
 \citet{Pineda2012} observed methyl formate (HCOOCH$_3$) with the Atacama Large Millimetre/sub-millimetre Array (ALMA) and found evidence of rotation toward one of the proto-binary Class 0 sources embedded in IRAS 16293-2422.
@@
 \citet{Persson2012} observed H$_2^{18}$O with ALMA toward the same source and found evidence of relatively large ($\ga$100\,K) excitation temperatures, as well as a HDO/H$_2$O abundance ratio close to that measured on Earth's oceans and Jupiter-family comets \citep{Hartogh2012}.
-\citet{Zapata2013} used ALMA to observe a disc of size $\sim$50$\,$AU in the other Class 0 source in IRAS 16293-2422 and detected infall towards this disc as inverse P-Cygni profiles in HCN and CH$_3$OH.
+\citet{Zapata2013} used ALMA to observe a disc of size $\sim$50$\,$au in the other Class 0 source in IRAS 16293-2422 and detected infall towards this disc as inverse P-Cygni profiles in HCN and CH$_3$OH.
 When ALMA is completed, it will be finally possible to spatially resolve these young discs and, for the first time, put stringent constraints on the theoretical models mentioned previously.
 As full-operational ALMA is fast approaching, it is important to provide observational predictions based on dynamical models of young protoplanetary discs.
-\newline
+\smallskip
 
@@
 Figure \ref{fig:l1544_model} shows the physical parameters of the core model.
-\newline
+\smallskip
 
@@
 
-The pre-stellar core structure is maintained down to a radius of 80\,AU, within which the model of the young protoplanetary disc is used.
+The pre-stellar core structure is maintained down to a radius of 80\,au, within which the model of the young protoplanetary disc is used.
 The disc structure is derived by the hydrodynamic model of \citet{Boley2007} and  \citet{Boley2009}.
@@
 The dust and gas temperatures in the disc are assumed to be in equilibrium.
-The underlying model is sampled as a regular grid of size 256$\times$256$\times$64 with spatial resolution of 0.5$\,$AU in x, y and z.
+The underlying model is sampled as a regular grid of size 256$\times$256$\times$64 with spatial resolution of 0.5$\,$au in $x$, $y$ and $z$.
 The gas/dust mass ratio was assumed to be 1/100 throughout the disc and the envelope.
-The dust opacities were adopted from \citet{Ossenkopf1994} and refer to dust grains with thick icy mantles and 10$^6$ yr coagulation history.\newline
+The dust opacities were adopted from \citet{Ossenkopf1994} and refer to dust grains with thick icy mantles and 10$^6$ yr coagulation history.
+In the dense conditions of the protoplanetary disc could be encouraging the dust grains to agglomerate and increase the size of the ice mantle through freeze out of volitiles.
+This could lead to changes in the dust opacity, however we have not attempted to include these effects in our model.\smallskip
 
@@
 The abundances of 125 species related by 1334 reactions were calculated through the time evolution of the disc.
-These abundances were interpolated onto a 51$^3$ grid covering the disc with cells of size 2.2$\times$2.2$\times$0.22$\,$AU$^2$.
-From I2011 we selected the four species which appear to trace different regions of the disc: the inner 20\,AU (OCS), the inner 40\,AU (H$_2$CO),  the region between $\simeq$40 and 60\,AU (HCO$^+$) and one which traces the entirety of the disc (C$^{17}$O) (see figure \ref{Chemistry}).
+These abundances were interpolated onto a 51$^3$ grid covering the disc with cells of size 2.2$\times$2.2$\times$0.22$\,$au$^2$.
+From I2011 we selected the four species which appear to trace different regions of the disc: the inner 20\,au (OCS), the inner 40\,au (H$_2$CO),  the region between $\simeq$40 and 60\,au (HCO$^+$) and one which traces the entirety of the disc (C$^{17}$O) (see figure \ref{Chemistry}).
 The abundance model used for C$^{17}$O was the CO model reduced by a factor of 1792, the ratio of $^{16}$O to $^{17}$O in the local ISM \citep{Wilson1994}.
@@
 \subsection{The radiative transfer code} \label{subsec:radiative_transfer_code}
-%-describe the RT used (LIME) 
-%-describe the RT used (LIME) 
 The radiative transfer program used is LIME (LIne Modeling Engine; \cite{Brinch2010}), which  calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3D model.
@@
 These points are then smoothed by Lloyd's algorithm \citep{Lloyd1982} in order to minimise the variation in distance between points whilst keeping the same underlying distribution.
-These points are then connected by Delaunay triangulation \footnote{In three dimensions this means that if four points are connected into a tetrahedron, the sphere circumscribing these four points contains no other points.
+These points are then connected by Delaunay triangulation\footnote{For three dimensions, Delaunay trianglulating means that if four points are connected into a tetrahedron, the sphere circumscribing these four points contains no other points.
 It can be shown that this connection is unique for a given set of points.} and it is down these paths that photon propagation is restricted (figure \ref{grid}).
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/model/grid.eps}%Lime_grid3.eps
- \caption{A plot of the points selected by the gridding process and the paths down which photons can propagate overlaid on the density distribution (in m$^{-3}$, as used in LIME).
-The points are more concentrated at small radii and in the densest regions.}
+ \includegraphics[width=84mm]{Figures/model/lime2.eps}%Lime_grid3.eps
+ \caption{A plot of the points selected by the gridding process and the paths down which photons can propagate colour coded by the density distribution (in m$^{-3}$, as used in LIME).
+The points are more concentrated at small radii and in the most dense regions.}
  \label{grid}
@@
 The C$^{17}$O abundance profile in the envelope follows the CO profile calculated for L1544 by KC2010, scaled by the 17O/16O elemental abundance.
+\smallskip
 
@@
 The frequencies and upper level energies of these transitions are in table \ref{sigmas}.
-The results presented in this section are limited to those lines which show detectable emission/absorption which can be used to trace either spiral structure or rotation.\newline
+The results presented in this section are limited to those lines which show detectable emission/absorption which can be used to trace either spiral structure or rotation.\smallskip
 
-%We considered C$^{17}$O 3$\rightarrow$2 at 337.1$\,$GHz with an upper energy level of $E_u$=32.3K, HCO$^+$ 3$\rightarrow$2 at 267$\,$GHz and $E_u$=25.7K, OCS 26$\rightarrow$25 at 316$\,$GHz and $E_u$=205K and H$_2$CO 4$_{04}\rightarrow$3$_{03}$ at 290$\,$GHz and $E_u$=34.9K.\newline
+%We considered C$^{17}$O 3$\rightarrow$2 at 337.1$\,$GHz with an upper energy level of $E_u$=32.3K, HCO$^+$ 3$\rightarrow$2 at 267$\,$GHz and $E_u$=25.7K, OCS 26$\rightarrow$25 at 316$\,$GHz and $E_u$=205K and H$_2$CO 4$_{04}\rightarrow$3$_{03}$ at 290$\,$GHz and $E_u$=34.9K.\smallskip
 
@@
 From these simulated observations, integrated intensity maps, intensity weighted velocity maps and position velocity diagrams were created.
-The integrated intensity and intensity weighted velocity maps (figures \ref{sim_all} and \ref{mom0_maps}) were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope.
-This can be seen in some PV diagrams  (figure \ref{pvs}) as the strong absorption feature at all positions around zero velocity.
-Moment 1 maps are shown with a cut-off of 3$\sigma$ as described in section \ref{sec:alma_predictions}.\newline
+The integrated intensity and intensity weighted velocity maps (figures \ref{sim_all} and \ref{mom0_maps}) were created by integrating between -12.5 to -0.5$\,$km$\,$s$^{-1}$ and +0.5 to +12.5$\,$km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope.
+This can be seen in some PV diagrams  (Figure \ref{pvs}) as the strong absorption feature at all positions around zero velocity.
+Moment 1 maps are shown with a cut-off of 3$\sigma$ as described in section \ref{sec:alma_predictions}.\smallskip
 
@@
 
-OCS 26$\rightarrow$25 traces only the innermost 20$\,$AU of the disc and can be used to examine the central regions (figure \ref{sim_all}).
+OCS 26$\rightarrow$25 traces only the innermost 20$\,$au of the disc and can be used to examine the central regions (figure \ref{sim_all}).
 As OCS is not seen in outflows (e.g.
@@
 The exception to this is towards the centre of the disc where the hole in the hot, dense mid-plane means that there is little continuum to be absorbed.
-However, because of the presence of the protostar and other hot material within the central hole, not considered in our simple model, we expect absorption to also be observed toward the central region of the disc.\newline
+However, because of the presence of the protostar and other hot material within the central hole, not considered in our simple model, we expect absorption to also be observed toward the central region of the disc.\smallskip
 
-The abundance of the H$_2$CO molecule traces the spiral structure of the inner $\sim$40$\,$AU of the disc, ehich can be seen in the integrated intensity map and its rotation is detected out to larger radii than is possible with the OCS line (figure \ref{sim_all}).
+The abundance of the H$_2$CO molecule traces the spiral structure of the inner $\sim$40$\,$au of the disc, which can be seen in the integrated intensity map and its rotation is detected out to larger radii than is possible with the OCS line (figure \ref{sim_all}).
 As with the OCS line, the majority of the H$_2$CO 4$_{04}\rightarrow$3$_{03}$, is seen in absorption against the disc mid-plane continuum, with the central region seen in emission.
 Unlike the OCS however, the H$_2$CO extends out to large enough radii to be present in the voids between the outer parts spiral arms.
-In these regions, the H$_2$CO line can be seen in emission.\newline
+In these regions, the H$_2$CO line can be seen in emission.\smallskip
 
@@
 The C$^{17}$O line is visible from the inner edge of the disc to its outer edge.
-Like OCS, C$^{17}$O is not seen in outflows \citep{Yildiz2012}, so we do not expect contamination.\newline
+Like OCS, C$^{17}$O is not seen in outflows \citep{Yildiz2012}, so we do not expect contamination.\smallskip
 
@@
 In order to clean the images, which featured mainly absorption, the sky model used was the output of the LIME simulations with the continuum subtracted and then the spectrum inverted.
-The simulated images were cleaned down to a 3$\sigma$ level with $\sigma$ (the sensitivity) given in table \ref{sigmas}.\newline
+The simulated images were cleaned down to a 3$\sigma$ level with $\sigma$ (the sensitivity) given in table \ref{sigmas}.\smallskip
 
@@
 Figure \ref{h2co_chanmap} shows a channel map of the H$_2$CO 4$_{04}\rightarrow$3$_{03}$ line overlaid on the 1$\,$mm continuum emission.
-From this it can be seen that the absorption features trace the disc spiral structure whilst the line emission emanates from gaps in the outer disc, where there is less continuum to be absorbed.\newline
+From this it can be seen that the absorption features trace the disc spiral structure whilst the line emission emanates from gaps in the outer disc, where there is less continuum to be absorbed.\smallskip
 
@@
 Figure \ref{mom0_maps} shows the simulated integrated intensity maps, which demonstrates how lines from different species allow observations to trace different regions of the disc, from the OCS line tracing the innermost regions, to the HCO$^+$ line showing the outer regions which are less bright in the continuum.
-ALMA has enough resolution and sensitivity to see spiral structure clearly in continuum emission but also in CO isotopologues and marginally in H$_2$CO.\newline
+ALMA has enough resolution and sensitivity to see spiral structure clearly in continuum emission but also in CO isotopologues and marginally in H$_2$CO.\smallskip
 
 \begin{figure*}
- \includegraphics[width=198mm]{Figures/sim/casa_all_30deg_PV_rotCurve_small.eps}
+ \includegraphics[width=180mm]{Figures/sim/casa_all_30deg_PV_rotCurve_small.eps}
  \caption{Position velocity diagrams for each of the lines simulated with CASA. The green curve on each diagram is the best fit curve to the azimuthally averaged rotation profile from figure 4.}
@@
 Figure \ref{pvs} shows position-velocity diagrams of the lines simulated, allowing us to reconstruct the rotation of the disc.
-The green curves in each panel of figure \ref{pvs} display the best fit rotation curve of the physical model (see figure \ref{velocity}), showing that the rotation profile of the disc can be well constrained using kinematic information gathered from species tracing different regions of the disc.\newline
+The green curves in each panel of figure \ref{pvs} display the best fit rotation curve of the physical model (see figure \ref{velocity}), showing that the rotation profile of the disc can be well constrained using kinematic information gathered from species tracing different regions of the disc.\smallskip
 
@@
  \includegraphics[width=168mm]{Figures/sim/casa_all_spectra2.eps}
- \caption{Simulated spectra for each of the selected transitions at the positions indicated by the coloured dots in figure \ref{mom0_maps}, the pink, green and cyan curves are taken from the locations marked the dot of the same colour respectively.
-In each diagram, the three spectra are taken from positions on the Y=0 axis, one is at X=0 (green) and the other 2 are from x=$\pm$ N (plus blue, minus red) where N is the distance from the centre: 10 AU for OCS, 20 AU for H$_2$CO, 28 AU for C$^{17}$O, 38 AU for HCO$^+$.}
+ \caption{Simulated spectra for each of the selected transitions at the positions indicated by the coloured dots in figure \ref{mom0_maps}, the pink, green and cyan curves are taken from the locations marked by the dot of the same colour.
+In each diagram, the three spectra are taken from three positions on the Y=0 axis, one is at X=0 (green) and the other 2 are from x=$\pm$ N (plus blue, minus red) where N is the distance from the centre: 10 au for OCS, 20 au for H$_2$CO, 28 au for C$^{17}$O, 38 au for HCO$^+$.}
  \label{spectra}
@@
 
-In this paper we have presented radiative transfer simulations of a hybrid model comprising a 0.39$\, M_\odot$ self gravitating disc with radius 64$\,AU$ showing spiral density waves, surrounded by an envelope simulated as a contracting 10$\,M_\odot$ BE-sphere.
+In this paper we have presented radiative transfer simulations of a hybrid model comprising a 0.39$\, M_\odot$ self gravitating disc with radius 64$\,$au showing spiral density waves, surrounded by an envelope simulated as a contracting 10$\,M_\odot$ BE-sphere.
 The main results of these simulations are as follows:\\
@@
 If they are not and the dust is significantly cooler than the gas then transitions may not show up in absorption.
-However, the large volume densities are expected to provide an efficient dust-gas coupling.\newline
+However, the large volume densities are expected to provide an efficient dust-gas coupling.
 Outflows could contaminate measurements of rotation curves, meaning that species  which commonly trace outflows, such as CO and HCO$^+$ are not going to be good tracers of disc rotation.
-However species such as OCS and C$^{17}$O, which are not commonly seen in outflows, can be used to trace disc rotation and structure.\newline
+However species such as OCS and C$^{17}$O, which are not commonly seen in outflows, can be used to trace disc rotation and structure.\smallskip
 
@@
 See figure \ref{points} for an example of the points distribution in r, z.
-\newline
+\smallskip
 
@@
 Simulations at inclinations other than 30$^\circ$ were also performed with C$^{17}$O.
-Figures B1-3 show the C$^{17}$O 3$\rightarrow$2 line in the same phisical model but at 15$^\circ$, 45$^\circ$ and 75$^\circ$ to egde on.
+Figures B1-3 show the C$^{17}$O 3$\rightarrow$2 line in the same phisical model but at 15$^\circ$, 30$^\circ$, 45$^\circ$ and 75$^\circ$ to egde on.
 At 15$^\circ$ to edge on we can still see some structure in the integrated intensity map and the structure is also visible in the position velocity diagram.
@@
 \begin{figure*}
- \includegraphics[width=164mm]{Figures/sim/imageC17O_3-2_15deg_all.eps}
+ \includegraphics[width=164mm]{Figures/sim/appendix_inclinations2.eps}
 
- \caption{C$^{17}$O 3$\rightarrow$2 inclined at 15$^\circ$ to edge on.
-The three panels are: {\bf left:} Continuum subtracted integrated intensity map (in K$\,$km$\,$s$^{-1}$).
+ \caption{C$^{17}$O 3$\rightarrow$2 {\bf left:} Continuum subtracted integrated intensity map (in K$\,$km$\,$s$^{-1}$).
 {\bf Centre:} Intensity weighted velocity map (in km$\,$s$^{-1}$).
-{\bf Right:} Position-velocity diagram with intensities in K.}
+{\bf Right:} Position-velocity diagram with intensities in K.
+The inclinations shown from top to bottom are 75$^\circ$, 45$^\circ$, 30$^\circ$ and 15$^\circ$ to edge on.}
 \end{figure*}
 
-\begin{figure*}
- \includegraphics[width=164mm]{Figures/sim/imageC17O_3-2_45deg_all.eps}
-
- \caption{C$^{17}$O 3$\rightarrow$2 inclined at 45$^\circ$ to edge on.
-The three panels are: {\bf left:} Continuum subtracted integrated intensity map (in K$\,$km$\,$s$^{-1}$).
-{\bf Centre:} Intensity weighted velocity map (in km$\,$s$^{-1}$).
-{\bf Right:} Position-velocity diagram with intensities in K.}
-\end{figure*}
-
-\begin{figure*}
- \includegraphics[width=164mm]{Figures/sim/imageC17O_3-2_75deg_all.eps}
-
- \caption{C$^{17}$O 3$\rightarrow$2 inclined at 75$^\circ$ to edge on.
-The three panels are: {\bf left:} Continuum subtracted integrated intensity map (in K$\,$km$\,$s$^{-1}$).
-{\bf Centre:} Intensity weighted velocity map (in km$\,$s$^{-1}$).
-{\bf Right:} Position-velocity diagram with intensities in K.}
-\end{figure*}
+%\begin{figure*}
+% \includegraphics[width=164mm]{Figures/sim/imageC17O_3-2_45deg_all.eps}
+%
+% \caption{C$^{17}$O 3$\rightarrow$2 inclined at 45$^\circ$ to edge on.
+The three panels are: %{\bf left:} Continuum subtracted integrated intensity map (in K$\,$km$\,$s$^{-1}$).
+{\bf %Centre:} Intensity weighted velocity map (in km$\,$s$^{-1}$).
+{\bf Right:} Position-velocity %diagram with intensities in K.}
+%\end{figure*}
+%
+%\begin{figure*}
+% \includegraphics[width=164mm]{Figures/sim/imageC17O_3-2_75deg_all.eps}
+%
+% \caption{C$^{17}$O 3$\rightarrow$2 inclined at 75$^\circ$ to edge on.
+The three panels are: %{\bf left:} Continuum subtracted integrated intensity map (in K$\,$km$\,$s$^{-1}$).
+{\bf %Centre:} Intensity weighted velocity map (in km$\,$s$^{-1}$).
+{\bf Right:} Position-velocity %diagram with intensities in K.}
+%\end{figure*}
 

### 2013-03-11 young_pp_discs.tex
added 15 deg casa sims to body, re-working main text

@@
 To appropriately describe the environment within which a young protoplanetary disc is embedded, we combine the disc model from I2011 with a model of a dense core with characteristics similar to the well-studied pre-stellar core L1544 (\citealt{Keto2010}, hereafter KC2010).
+Although L1544 does not appear to contain a central protostar and disc itself, other similar dense cores such as L1521F contain a central object which appears to be a low mass protostar and disc \citep{Bourke2006} whilest having around half the mass of L1544.
 The KC2010 model follows the dynamical, chemical and thermal evolution of a contracting Bonnor-Ebert sphere \citep{Bonnor1956,Ebert1957} with total mass of 10\,M$_{\odot}$, until it reaches the density, temperature and velocity profiles which best match observations.
@@
 The disc structure is derived by the hydrodynamic model of \citet{Boley2007} and  \citet{Boley2009}.
-The particular model considered here (as well as in I2011) is a 0.39$\,\rm{M}_\odot$ self-gravitating Keplerian disc (figure \ref{velocity}) featuring prominent spiral arms.
+The particular model considered here (as well as in I2011) is a 0.39$\,\rm{M}_\odot$ self-gravitating Keplerian disc (figure \ref{velocity}) featuring prominent spiral arms, rotating around a 1$\,$M$_\odot$ mass protostar (which is not included in the model).
 H$_2$ number densities in the disc range from 10$^{4}$-10$^{13}\,\rm{cm}^{-3}$, and temperatures range from 30-400 K (figure \ref{rhoT}).
@@
 As discussed in the result section \ref{sec:model_results}, approximations have been made based on values measured toward similar objects.
-The molecular data used is from the LAMDA (Leiden Atomic and Molecular DAtabase) database (Sch\"oier et al.
+The molecular data used is from the Leiden Atomic and Molecular DAtabase (LAMDA) (Sch\"oier et al.
 2005; http://home.strw.leidenuniv.nl/$\sim$moldata/).
@@
  \includegraphics[width=84mm]{Figures/model/lime2.eps}%Lime_grid3.eps
- \caption{A plot of the points selected by the gridding process and the paths down which photons can propagate colour coded by the density distribution (in m$^{-3}$, as used in LIME).
-The points are more concentrated at small radii and in the most dense regions.}
+ \caption{A plot of the points selected by the gridding process and the paths down which photons can propagate for points in the central r,$\theta$ plane.
+The points are colour coded by the density distribution (in m$^{-3}$, as used in LIME) and are more concentrated at small radii and in the most dense regions.
+The circular high density region in the centre is the disc model and is 128$\,$au in diameter.}
  \label{grid}
+\end{figure}
+
+\subsection{Grid construction} \label{subsec:gridding}
+In order to construct the grid, candidate points are randomly selected from the volume to be simulated.
+These candidates then have their density and molecular density compared against a reference point in order to decide if the point is to be used in the grid or not.
+Candidate grid points are selected at random in cylindrical coordinates, linearly spaced in z and $\phi$ and logarithmically spaced in r.
+For each point to be selected, a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) as a threshold.
+After selection of random coordinates, the hydrogen density and molecular density at the candidate point (n and m, respectively) are compared against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$).
+If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use, otherwise another r, $\phi$, z co-ordinate is selected and this becomes the candidate point.
+The function comparing the candidate point to the reference point and the candidate point distribution were selected empirically to sample all the scales while ensuring that the majority of points are located in the inner disc where the density is higher.
+20\% of these points are forced to be at radii greater than $\sqrt{R_{min}R_{max}}$ (where $R_{min}$ and $R_{max}$ are the inner and outer radius of the model) in order to stop too many of the selected points clustering in the high density disc and leaving the envelope under sampled.
+In addition to this method of selection, 5\% of the points are linearly distributed in x, y and z with no bias with regards to density or abundance.
+This provides a minimum level of sampling for the large low density regions in the outer parts of the simulated volume.
+See figure \ref{points} for an example of the points distribution in r, z.
+\smallskip
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/model/lime_points_rz_histo2.eps}
+ \caption{A 2D histogram of the point distribution throughout the model. The disc and envelope can be seen as two separate entities which have to be sampled using different point distributions.}
+ \label{points}
 \end{figure}
@@
 The C$^{17}$O abundance profile in the envelope follows the CO profile calculated for L1544 by KC2010, scaled by the 17O/16O elemental abundance.
-\smallskip
+These estimates for the abundances in the envelope are simplistic, however, as seen in section \ref{alma_predictions}, the envelope contribution to the line is very narrow, and can be spectrally disentangled from the disc contribution.\smallskip
 
@@
 
-To simulate observations, the model was placed at roughly the distance of nearby low-mass star forming regions (100$\,$pc) and the disc is inclined at 30$^\circ$ to edge on.
+To simulate observations, the model was placed at roughly the distance of nearby low-mass star forming regions (100$\,$pc).
+The inlination angle was varied from 15$^\circ$ to 75$^\circ$ to edge on, we will consider the 30$^\circ$ case as a 'typical' inclination with the 15$^\circ$ inclination discussed in section \ref{alma_predictions}, the other inclinations simulated are shown in appendix \ref{other_inc}.
 From these simulated observations, integrated intensity maps, intensity weighted velocity maps and position velocity diagrams were created.
@@
 The exception to this is towards the centre of the disc where the hole in the hot, dense mid-plane means that there is little continuum to be absorbed.
-However, because of the presence of the protostar and other hot material within the central hole, not considered in our simple model, we expect absorption to also be observed toward the central region of the disc.\smallskip
+However, because of the presence of the protostar and other hot material within 2$\,$au of the protostar, not considered in our simple model, we expect absorption to also be observed toward the central region of the disc.\smallskip
 
@@
 Figure \ref{continuum} Shows the 1mm continuum emission and beam size in this configuration of ALMA.
+The spiral structure of the disc is clearly visible at this inclination and will be clearer the closer the disc is to being face on.
+\smallskip
 
 Figure \ref{h2co_chanmap} shows a channel map of the H$_2$CO 4$_{04}\rightarrow$3$_{03}$ line overlaid on the 1$\,$mm continuum emission.
-From this it can be seen that the absorption features trace the disc spiral structure whilst the line emission emanates from gaps in the outer disc, where there is less continuum to be absorbed.\smallskip
+From this it can be seen that the absorption features trace the disc spiral structure whilst the line emission emanates from gaps in the outer disc, where there is less continuum to be absorbed.
+The central pannel is domminated by the envelope contribution, causing stron absorption through out the disc.
+The other pannels show the line following a rotation profile distorted by the presence of the spiral arms.
+\smallskip
 
@@
 Figure \ref{mom0_maps} shows the simulated integrated intensity maps, which demonstrates how lines from different species allow observations to trace different regions of the disc, from the OCS line tracing the innermost regions, to the HCO$^+$ line showing the outer regions which are less bright in the continuum.
-ALMA has enough resolution and sensitivity to see spiral structure clearly in continuum emission but also in CO isotopologues and marginally in H$_2$CO.\smallskip
+ALMA has enough resolution and sensitivity to see spiral structure clearly in continuum emission but also in CO isotopologues and marginally in H$_2$CO.
+The different molecules can be seen to be tracing different regions of the disc\smallskip
+
+\begin{figure}
+ \includegraphics[width=63mm]{Figures/sim/casa_C17O_15deg_all.eps}
+
+ \caption{CASA simulation of the C17O 3$\rightarrow$2 line inclided at 15$^\circ$ to edge on {\bf Top:} integrated intensity map.
+{\bf bottom:} position velocity diagram.
+In the position velocity diagram the spiral structures can be seen as narrow finger-like structures extending from the origin.}
+ \label{15deg}
+\end{figure}
+
+%\begin{figure}
+%  \centering
+%  \includegraphics[width=42mm]{Figures/sim/casa_C17O_15deg_PV.eps}
+
+%  \caption{CASA simulation of the position velocity diagram of the C17O 3$\rightarrow$2 line inclided at 15$^\circ$ to edge on.}
+%  \label{15deg_pv}
+%\end{figure}
 
@@
 TAD and JDI acknowledge studentships from the Science and Technology Facilities Council of the United Kingdom (STFC).
+The research leading to these results has received funding from the European Union FP7-2011 under grant agreement no 284405.
 
-\bibliographystyle{apalike} 
+\bibliographystyle{mn2e} 
 \bibliography{new_bib}
@@
 \appendix
-
-\section{Grid Construction} \label{sec:gridding}
-
-In order to construct the grid, candidate points are randomly selected from the volume to be simulated.
-These candidates then have their density and molecular density compared against a reference point in order to decide if the point is to be used in the grid or not.
-Candidate grid points are selected at random in cylindrical coordinates, linearly spaced in z and $\phi$ and logarithmically spaced in r.
-For each point to be selected, a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) as a threshold.
-After selection of random coordinates, the hydrogen density and molecular density at the candidate point (n and m, respectively) are compared against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$).
-If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use, otherwise another r, $\phi$, z co-ordinate is selected and this becomes the candidate point.
-The function comparing the candidate point to the reference point and the candidate point distribution were selected empirically to sample all the scales while ensuring that the majority of points are located in the inner disc where the density is higher.
-20\% of these points are forced to be at radii greater than $\sqrt{R_{min}R_{max}}$ (where $R_{min}$ and $R_{max}$ are the inner and outer radius of the model) in order to stop too many of the selected points clustering in the high density disc and leaving the envelope under sampled.
-In addition to this method of selection, 5\% of the points are linearly distributed in x, y and z with no bias with regards to density or abundance.
-This provides a minimum level of sampling for the large low density regions in the outer parts of the simulated volume.
-See figure \ref{points} for an example of the points distribution in r, z.
-\smallskip
-
-\begin{figure}
- \includegraphics[width=84mm]{Figures/model/lime_points_rz_histo2.eps}
- \caption{A 2D histogram of the point distribution throughout the model. The disc and envelope can be seen as two separate entities which have to be sampled using different point distributions.}
- \label{points}
-\end{figure}
 

### 2013-03-12 young_pp_discs.tex
all minor changes done and stared on apendix reworking

@@
 Thus, observations of the young discs, predicted to have sizes of about 100\,au and masses as large as 10\% the original core mass (e.g.
-\citealt{Joos2012}), are challenging.
+\citealt{Joos2012,Hayfield2011,Machida2011}), are challenging.
 The use of sensitive interferometers is needed to achieve high angular resolution and spatially/spectrally disentangle the various disc, envelope and outflow components as well to filter out the extended emission tracing envelope material.
@@
  \includegraphics[width=84mm]{Figures/model/rotational_velocities.eps}
- \caption{Azimuthaly averaged rotational velocity in the disc mid-plane with best fit curve.}
+ \caption{Azimuthaly averaged rotational velocity in the disc mid-plane. The best fit curve follows the equation $\frac{31.5}{\sqrt{x+1.68}}+0.518$ .}
  \label{velocity}
@@
 The pre-stellar core structure is maintained down to a radius of 80\,au, within which the model of the young protoplanetary disc is used.
-The disc structure is derived by the hydrodynamic model of \citet{Boley2007} and  \citet{Boley2009}.
-The particular model considered here (as well as in I2011) is a 0.39$\,\rm{M}_\odot$ self-gravitating Keplerian disc (figure \ref{velocity}) featuring prominent spiral arms, rotating around a 1$\,$M$_\odot$ mass protostar (which is not included in the model).
-H$_2$ number densities in the disc range from 10$^{4}$-10$^{13}\,\rm{cm}^{-3}$, and temperatures range from 30-400 K (figure \ref{rhoT}).
-The dust and gas temperatures in the disc are assumed to be in equilibrium.
-The underlying model is sampled as a regular grid of size 256$\times$256$\times$64 with spatial resolution of 0.5$\,$au in $x$, $y$ and $z$.
-The gas/dust mass ratio was assumed to be 1/100 throughout the disc and the envelope.
+The disc structure used is from the same hydrodynamics simulation described in I2011, which is a 1$\,$M$_\odot$ protostar surrounded by a 0.39$\,$M$_\odot$ disc.
+The system is envisaged to be at a very early stage of evolution and embedded in an envelope.
+The still growing protostar will eventually become an A star through accretion of most of the disc's mass.
+The hydrodynamics simulation is run with a proper equation of state for molecular hydrogen \citet{Boley2007}.
+The star is allowed to move freely in response to disc torques, and radiative cooling is included \citet{Boley2009}.
+The self-gravitating disc exhibits prominent spiral structure, with H2 number densities in the disc ranging from 10$^4$-10$^13$ cm$^{-3}$ and temperatures from 30-400 K (figure \ref{rhoT}).
+For the non-LTE 3D radiative transfer modeling presented here, we interpolate the I2011 simulation output on to a 256$\times$256$\times$64 Cartesian grid with spatial resolution of 0.5$\,$au in x, y, and z and use this to sample the unstructured radiative transfer grid (see section \ref{subsec:gridding}).
+As in the hydrodynamics simulation, the dust and gas temperatures are assumed to be in equilibrium within the disc and a gas to dust mass ratio of 1/100 is used throught the entirity of the model.
 The dust opacities were adopted from \citet{Ossenkopf1994} and refer to dust grains with thick icy mantles and 10$^6$ yr coagulation history.
@@
 As with all the CASA simulated images, these spectra have a total bandwidth of 938$\,$MHz, giving velocity resolutions of between 418 and 527 ms$^{-1}$.
-The most notable thing about these spectral features is that they are not symmetric about the disk centre.
+The most notable thing about these spectral features is that they are not symmetric about the disc centre.
 For example, C$^{17}$O(3$\rightarrow$2) has a significantly stronger blueshifted absorption, due to the presence of a spiral arm along the same line of sight.

### 2013-03-13 young_pp_discs.tex
started transfering 15deg results from the appendix into the body

@@
 Thus, observations of the young discs, predicted to have sizes of about 100\,au and masses as large as 10\% the original core mass (e.g.
-\citealt{Joos2012,Hayfield2011,Machida2011}), are challenging.
+\citealt*{Joos2012,Hayfield2011,Machida2011}), are challenging.
 The use of sensitive interferometers is needed to achieve high angular resolution and spatially/spectrally disentangle the various disc, envelope and outflow components as well to filter out the extended emission tracing envelope material.
@@
 
-After the pioneer work of, e.g., \citet{Chandler1995,Brown2000,Looney2000}, recent interferometric observations have discovered compact embedded discs in a sample of Class 0 sources \citep{Andre1999}, finding masses between 0.4 and  $>$1 M$_{\odot}$ \citep{Jorgensen2007,Jorgensen2009,Enoch2011}.
+After the pioneer work of, e.g., \citet{Chandler1995,Brown2000,Looney2000}, recent interferometric observations have discovered compact embedded discs in a sample of Class 0 sources (as defined by \citealt{Andre1999}), finding masses between 0.4 and  $>$1 M$_{\odot}$ \citep{Jorgensen2007,Jorgensen2009,Enoch2011}.
 A 130\,au disc was discovered toward a Class 0 source in Perseus, using the Jansky Very Large Array (JVLA) to observe NH$_3$ \citep{Choi2007}.
@@
 When ALMA is completed, it will be finally possible to spatially resolve these young discs and, for the first time, put stringent constraints on the theoretical models mentioned previously.
-As full-operational ALMA is fast approaching, it is important to provide observational predictions based on dynamical models of young protoplanetary discs.
+As fully-operational ALMA is fast approaching, it is important to provide observational predictions based on dynamical models of young protoplanetary discs.
 \smallskip
@@
 To appropriately describe the environment within which a young protoplanetary disc is embedded, we combine the disc model from I2011 with a model of a dense core with characteristics similar to the well-studied pre-stellar core L1544 (\citealt{Keto2010}, hereafter KC2010).
-Although L1544 does not appear to contain a central protostar and disc itself, other similar dense cores such as L1521F contain a central object which appears to be a low mass protostar and disc \citep{Bourke2006} whilest having around half the mass of L1544.
+Although L1544 does not appear to contain a central protostar and disc itself, L1521F, a similar dense core, contains a central object which appears to be a low mass protostar and disc \citep{Bourke2006}, whilest having between half and three quarters of the mass of L1544.
 The KC2010 model follows the dynamical, chemical and thermal evolution of a contracting Bonnor-Ebert sphere \citep{Bonnor1956,Ebert1957} with total mass of 10\,M$_{\odot}$, until it reaches the density, temperature and velocity profiles which best match observations.
@@
 The still growing protostar will eventually become an A star through accretion of most of the disc's mass.
-The hydrodynamics simulation is run with a proper equation of state for molecular hydrogen \citet{Boley2007}.
-The star is allowed to move freely in response to disc torques, and radiative cooling is included \citet{Boley2009}.
-The self-gravitating disc exhibits prominent spiral structure, with H2 number densities in the disc ranging from 10$^4$-10$^13$ cm$^{-3}$ and temperatures from 30-400 K (figure \ref{rhoT}).
-For the non-LTE 3D radiative transfer modeling presented here, we interpolate the I2011 simulation output on to a 256$\times$256$\times$64 Cartesian grid with spatial resolution of 0.5$\,$au in x, y, and z and use this to sample the unstructured radiative transfer grid (see section \ref{subsec:gridding}).
+The hydrodynamics simulation is run with a proper equation of state for molecular hydrogen \citep{Boley2007}.
+The star is allowed to move freely in response to disc torques, and radiative cooling is included \citep{Boley2009}.
+The self-gravitating disc exhibits prominent spiral structure, with H$_2$ number densities in the disc ranging from 10$^4$-10$^{13}$ cm$^{-3}$ and temperatures from 30-400 K (figure \ref{rhoT}).
+For the non-LTE 3D radiative transfer modeling presented here, we interpolate the I2011 simulation output on to a 256$\times$256$\times$64 Cartesian grid with spatial resolution of 0.5$\,$au in x, y, and z and sample from this to create the unstructured radiative transfer grid (see section \ref{subsec:gridding}).
 As in the hydrodynamics simulation, the dust and gas temperatures are assumed to be in equilibrium within the disc and a gas to dust mass ratio of 1/100 is used throught the entirity of the model.
@@
 In the dense conditions of the protoplanetary disc could be encouraging the dust grains to agglomerate and increase the size of the ice mantle through freeze out of volitiles.
-This could lead to changes in the dust opacity, however we have not attempted to include these effects in our model.\smallskip
+This could lead to changes in the dust opacity, however we have not attempted to include these effects in our model.
+The dust opacities used in the radiative transfer are not the same as the ones used in the hydrodynamic model (which used the dust opacities of \citealt{DAlessio2001}).
+However the results desciribed here do not depend on the details of the dust opacity and would be qualitatively similar if other opacities were used.\smallskip
 
@@
 Chemical abundances in the disc were taken from I2011 who followed gas-grain chemical processes during the dynamical evolution of the disc.
-The abundances of 125 species related by 1334 reactions were calculated through the time evolution of the disc.
-These abundances were interpolated onto a 51$^3$ grid covering the disc with cells of size 2.2$\times$2.2$\times$0.22$\,$au$^2$.
-From I2011 we selected the four species which appear to trace different regions of the disc: the inner 20\,au (OCS), the inner 40\,au (H$_2$CO),  the region between $\simeq$40 and 60\,au (HCO$^+$) and one which traces the entirety of the disc (C$^{17}$O) (see figure \ref{Chemistry}).
+As described in I2011, the hydrodynamics simulation included Lagrangian tracer fluid elements in addition to solving the equations of hydrodynamics on an Eulerian grid.
+These fluid elements were used to record the thermal history of the gas as material passed through and between spiral structure.
+I2011 used this time evolution information from fluid elements to calculate the abundances of 125 species, related by 1334 reactions.
+These abundances were then interpolated by I2011 on to a Cartesian grid with cell sizes 2.2$\times$2.2$\times$0.22$\,$au in x, y, and z to reveal the morphology of the disk as seen by different molecular species.
+From these we selected the four species which appear to trace different regions of the disc: the inner 20\,au (OCS), the inner 40\,au (H$_2$CO),  the region between $\simeq$40 and 60\,au (HCO$^+$) and one which traces the entirety of the disc (C$^{17}$O) (see figure \ref{Chemistry}).
 The abundance model used for C$^{17}$O was the CO model reduced by a factor of 1792, the ratio of $^{16}$O to $^{17}$O in the local ISM \citep{Wilson1994}.
@@
 The radiative transfer program used is LIME (LIne Modeling Engine; \cite{Brinch2010}), which  calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3D model.
-The method of selecting these points is given in appendix  \ref{sec:gridding}.
-At each of these points, the density of the main collision partner (H$_2$), gas and dust temperatures, velocity, molecular abundances and turbulent velocity are specified.
+The method of selecting these points is given in section \ref{subsec:gridding}.
+At each of these points, the density of the main collision partner (H$_2$), gas and dust temperatures, velocity, molecular abundances and unresolved turbulent velocity are specified.
 These points are then smoothed by Lloyd's algorithm \citep{Lloyd1982} in order to minimise the variation in distance between points whilst keeping the same underlying distribution.
@@
 This is repeated 20 times with the populations of each level converging towards a single value.
-This number of iterations is sufficient for the signal to noise ratio of the level populations (as defined in \cite{Brinch2010} to exceed 1000 in 99\% of the points, ensuring that the simulation has converged on a stable level population.
+This number of iterations is sufficient for the signal to noise ratio of the level populations (as defined in \citealt{Brinch2010}) to exceed 1000 in 99\% of the points, ensuring that the simulation has converged on a stable level population.
 After 20 iterations the model is ray-traced in order to produce synthetic brightness maps.
@@
 These candidates then have their density and molecular density compared against a reference point in order to decide if the point is to be used in the grid or not.
-Candidate grid points are selected at random in cylindrical coordinates, linearly spaced in z and $\phi$ and logarithmically spaced in r.
+Candidate grid points are selected at random in cylindrical coordinates, linearly spaced in z and $\theta$ and logarithmically spaced in r.
 For each point to be selected, a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) as a threshold.
 After selection of random coordinates, the hydrogen density and molecular density at the candidate point (n and m, respectively) are compared against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$).
-If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use, otherwise another r, $\phi$, z co-ordinate is selected and this becomes the candidate point.
-The function comparing the candidate point to the reference point and the candidate point distribution were selected empirically to sample all the scales while ensuring that the majority of points are located in the inner disc where the density is higher.
+If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use, otherwise another r, $\theta$, z co-ordinate is selected and this becomes the candidate point.
+The function comparing the candidate point to the reference point and the candidate point distribution were selected empirically to sample all scales while ensuring that the majority of points are located in the inner disc where the density is higher.
 20\% of these points are forced to be at radii greater than $\sqrt{R_{min}R_{max}}$ (where $R_{min}$ and $R_{max}$ are the inner and outer radius of the model) in order to stop too many of the selected points clustering in the high density disc and leaving the envelope under sampled.
@@
 \smallskip
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/continuum.eps}
+ \caption{{\bf Left:}A 300$\,$GHz continuum image of the model, created from the average of ten LIME runs.
+{\bf Right:} the output of a single radiative transfer simulation, with artifacts due to finite gridding.}
+ \label{averages}
+\end{figure}
 
@@
 For OCS we adopted a constant abundance of 1.9$\times$10$^{-9}$ \citep{Ren2011}.
-The C$^{17}$O abundance profile in the envelope follows the CO profile calculated for L1544 by KC2010, scaled by the 17O/16O elemental abundance.
-These estimates for the abundances in the envelope are simplistic, however, as seen in section \ref{alma_predictions}, the envelope contribution to the line is very narrow, and can be spectrally disentangled from the disc contribution.\smallskip
+The C$^{17}$O abundance profile in the envelope follows the CO profile calculated for L1544 by KC2010, scaled by the $^{17}$O/$^{16}$O elemental abundance.
+These estimates for the abundances in the envelope are simplistic, however, as seen in section \ref{sec:alma_predictions}, the envelope contribution to the line is very narrow, and can be spectrally disentangled from the disc contribution.\smallskip
 
@@
 Thus, we consider C$^{17}$O(3$\rightarrow$2), HCO$^+$(3$\rightarrow$2), OCS (26$\rightarrow$25) and H$_2$CO(4$_{04}\rightarrow$3$_{03}$).
-The frequencies and upper level energies of these transitions are in table \ref{sigmas}.
+The frequencies and upper level energies of these transitions are given in table \ref{sigmas}.
 The results presented in this section are limited to those lines which show detectable emission/absorption which can be used to trace either spiral structure or rotation.\smallskip
@@
 To simulate observations, the model was placed at roughly the distance of nearby low-mass star forming regions (100$\,$pc).
-The inlination angle was varied from 15$^\circ$ to 75$^\circ$ to edge on, we will consider the 30$^\circ$ case as a 'typical' inclination with the 15$^\circ$ inclination discussed in section \ref{alma_predictions}, the other inclinations simulated are shown in appendix \ref{other_inc}.
+The inlination angle was varied from 15$^\circ$ to 75$^\circ$ to edge on, we will consider the 30$^\circ$ case as a 'typical' inclination with the 15$^\circ$ inclination discussed in section \ref{sec:alma_predictions}, the other inclinations simulated are shown in appendix \ref{sec:other_inc}.
 From these simulated observations, integrated intensity maps, intensity weighted velocity maps and position velocity diagrams were created.
-The integrated intensity and intensity weighted velocity maps (figures \ref{sim_all} and \ref{mom0_maps}) were created by integrating between -12.5 to -0.5$\,$km$\,$s$^{-1}$ and +0.5 to +12.5$\,$km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope.
-This can be seen in some PV diagrams  (Figure \ref{pvs}) as the strong absorption feature at all positions around zero velocity.
-Moment 1 maps are shown with a cut-off of 3$\sigma$ as described in section \ref{sec:alma_predictions}.\smallskip
-
-\begin{figure}
- \includegraphics[width=84mm]{Figures/sim/continuum.eps}
- \caption{{\bf Left:}A 300$\,$GHz continuum image of the model, created from the average of ten LIME runs.
-{\bf Right:} the output of a single radiative transfer simulation, with artifacts due to finite gridding.}
- \label{averages}
-\end{figure}
+The integrated intensity, intensity weighted velocity and channel maps (figures \ref{sim_all}, \ref{h2co_chanmap} and \ref{mom0_maps}) were created by integrating between -12.5 to -0.5$\,$km$\,$s$^{-1}$ and +0.5 to +12.5$\,$km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope.
+This can be seen in some PV diagrams as the strong absorption feature at all positions around zero velocity (see section \ref{sec:alma_predictions}).
+Intensity weighted velocity maps are shown with a cut-off of 3$\sigma$ as described in section \ref{sec:alma_predictions}.\smallskip
 
@@
 \citealt{Stanke2007}, \citealt{VDTak2003}) it can be used to view rotation of the central part of the disc without risk of contamination from emission from shocked material along the outflow.
-The OCS line, which has the highest upper energy level among the selected transitions, traces the hottest and densest regions of the disc.
+The OCS lines are unique amongst the lines simulated in that it is not visible throughout all the regions in the disc where it is found, the line is only seen at radii <16$\,au$ whereas the molecules have a significant abundance out to $\sim$30$\,$au.
+This is because the OCS line, which has the highest upper energy level among the selected transitions, traces only the hottest and densest regions of the disc where the high energy states are populated.
 As a result, the innermost spiral structure is best seen in OCS (26 - 25), as shown in figure \ref{sim_all}.
@@
 In figure \ref{sim_all} we can see that the HCO$^+$ line shows the outer edges of the spiral arms in absorption, but it also shows emission from the diffuse gas further out in the disc.
-This allows the velocity structure of the disc to be measured out to larger radii.
-This allows constraints to be placed on the rotation of the disc out to larger radii than with other molecules.
+This allows the velocity structure of the disc to be measured out to larger radii and allows constraints to be placed on the rotation of the disc out to larger radii than with other molecules.
 
@@
 \end{table*}
-In order to clean the images, which featured mainly absorption, the sky model used was the output of the LIME simulations with the continuum subtracted and then the spectrum inverted.
-The simulated images were cleaned down to a 3$\sigma$ level with $\sigma$ (the sensitivity) given in table \ref{sigmas}.\smallskip
+In order to clean the images which featured mainly absorption, the sky model used was the output of the LIME simulations with the continuum subtracted and then the spectrum inverted.
+The simulated images were cleaned down to a 3$\sigma$ level with $\sigma$ (the sensitivity) given in Table \ref{sigmas}.\smallskip
 
@@
 The spiral structure of the disc is clearly visible at this inclination and will be clearer the closer the disc is to being face on.
-\smallskip
+We can get an estimate of the mass from a continuum image such as this using the equation $EQUATION$ \cite{equn_ref} which gives a mass of X showing that Y (continuum mass estimates are good/rubish for discs of this high mass/density).\smallskip
 
@@
 
+Figure \ref{15deg} shows the C$^{17}$O 3$\rightarrow$2 integrated intensity and PV diagram for an inclination angle of 15$^\circ$ to edge on, showing that spiral structure can be seen in the position velocity diagram at low inclinations.
+The ``finger-like'' structures in the PV diagram are similar to those seen in the case of observations of the milky way and of simulations of spirals in the milky way (e.g.
+\citealt{Bissantz2003}).
+Whilest analysis of the detail of the spiral structure (number of arms, pitch angle etc.) would be difficult from such a PV diagram, detecting the presence of spiral waves, and therefore a potentially gravitationally unstable disc, is possible.\smallskip
+
+\begin{figure}
+ \includegraphics[width=84mm]{Figures/sim/casa_C17O_15deg_all2.eps}
+
+ \caption{CASA simulation of the C17O 3$\rightarrow$2 line with the disc inclided at 15$^\circ$ to edge on {\bf Top:} integrated intensity map.
+{\bf bottom:} position velocity diagram.
+In the position velocity diagram the spiral structures can be seen as narrow finger-like structures extending from the origin.}
+ \label{15deg}
+\end{figure}
+
 \begin{figure*}
- \includegraphics[width=168mm]{Figures/sim/casa_all_30deg_contSub_dots.eps}
+ \includegraphics[width=140mm]{Figures/sim/casa_all_30deg_contSub_dots.eps}
  \caption{Integrated intensity maps for the simulated observations of: {\bf Top Left:} H$_2$CO 4$_{04}\rightarrow$3$_{03}$, {\bf Top Right:} C$^{17}$O 3$\rightarrow$2, {\bf Bottom Left:} OCS 26$\rightarrow$25 and {\bf Bottom Right:} HCO$^+$ 3$\rightarrow$2.
@@
 
-Figure \ref{mom0_maps} shows the simulated integrated intensity maps, which demonstrates how lines from different species allow observations to trace different regions of the disc, from the OCS line tracing the innermost regions, to the HCO$^+$ line showing the outer regions which are less bright in the continuum.
+Figure \ref{mom0_maps} shows the simulated integrated intensity maps, which demonstrate how lines from different species allow observations to trace different regions of the disc, from the OCS line tracing the innermost regions, to the HCO$^+$ line showing the outer regions which are less bright in the continuum.
 ALMA has enough resolution and sensitivity to see spiral structure clearly in continuum emission but also in CO isotopologues and marginally in H$_2$CO.
 The different molecules can be seen to be tracing different regions of the disc\smallskip
-
-\begin{figure}
- \includegraphics[width=63mm]{Figures/sim/casa_C17O_15deg_all.eps}
-
- \caption{CASA simulation of the C17O 3$\rightarrow$2 line inclided at 15$^\circ$ to edge on {\bf Top:} integrated intensity map.
-{\bf bottom:} position velocity diagram.
-In the position velocity diagram the spiral structures can be seen as narrow finger-like structures extending from the origin.}
- \label{15deg}
-\end{figure}
-
-%\begin{figure}
-%  \centering
-%  \includegraphics[width=42mm]{Figures/sim/casa_C17O_15deg_PV.eps}
-
-%  \caption{CASA simulation of the position velocity diagram of the C17O 3$\rightarrow$2 line inclided at 15$^\circ$ to edge on.}
-%  \label{15deg_pv}
-%\end{figure}
 
@@
 Figure \ref{spectra} shows spectra from the lines simulated, one from the centre of the image and one on each side of the disc along the Y=0 axis.
-As with all the CASA simulated images, these spectra have a total bandwidth of 938$\,$MHz, giving velocity resolutions of between 418 and 527 ms$^{-1}$.
+As with all the CASA simulated images, these spectra were simulated with an ALMA window of total bandwidth 938$\,$MHz, giving velocity resolutions of between 418 and 527 ms$^{-1}$.
 The most notable thing about these spectral features is that they are not symmetric about the disc centre.
@@
 In this paper we have presented radiative transfer simulations of a hybrid model comprising a 0.39$\, M_\odot$ self gravitating disc with radius 64$\,$au showing spiral density waves, surrounded by an envelope simulated as a contracting 10$\,M_\odot$ BE-sphere.
-The main results of these simulations are as follows:\\
+The main results of these simulations are as follows:\smallskip
 $\bullet$ CASA simulations of this model show that at a distance of 100$\,$pc, extraction of kinematics and structural information from the continuum and molecular lines is possible with ALMA band 7.\\
@@
 $\bullet$ The lines studied (OCS 26$\rightarrow$25, H$_2$CO 4$_{04}$$\rightarrow$3$_{03}$, C$^{17}$O 3$\rightarrow$2 and HCO$^+$ 3$\rightarrow$2) taken together allow all regions of the disc to be sampled and the rotation of the disc to be constrained from the inner edge to the outer edge.\\
+$\bullet$ Spiral structure in young embedded discs are dectectable at a wide range of inclination angles, they can be resolved spatially at angles close to face on and can be infered from position velocity diagrams at low inclination angles.\smallskip
 
@@
 
+Big up results here!!
+
+\smallskip
+
 \section*{Acknowledgements}
@@
 The research leading to these results has received funding from the European Union FP7-2011 under grant agreement no 284405.
+TAD would like to thank Nicol Cunningham for her assistance with CASA and Christian Brinch for his radiative transfer code LIME and for guidance on using it.
 
@@
 
-Simulations at inclinations other than 30$^\circ$ were also performed with C$^{17}$O.
-Figures B1-3 show the C$^{17}$O 3$\rightarrow$2 line in the same phisical model but at 15$^\circ$, 30$^\circ$, 45$^\circ$ and 75$^\circ$ to egde on.
-At 15$^\circ$ to edge on we can still see some structure in the integrated intensity map and the structure is also visible in the position velocity diagram.
-At larger incliations it gets more difficult to obtain any kinematic information but the physical structure of the disc becomes clearer.
-
 \begin{figure*}
- \includegraphics[width=164mm]{Figures/sim/appendix_inclinations2.eps}
+ \includegraphics[width=110mm]{Figures/sim/appendix_inclinations2.eps}
 
@@
 
-%\begin{figure*}
-% \includegraphics[width=164mm]{Figures/sim/imageC17O_3-2_45deg_all.eps}
-%
-% \caption{C$^{17}$O 3$\rightarrow$2 inclined at 45$^\circ$ to edge on.
-The three panels are: %{\bf left:} Continuum subtracted integrated intensity map (in K$\,$km$\,$s$^{-1}$).
-{\bf %Centre:} Intensity weighted velocity map (in km$\,$s$^{-1}$).
-{\bf Right:} Position-velocity %diagram with intensities in K.}
-%\end{figure*}
-%
-%\begin{figure*}
-% \includegraphics[width=164mm]{Figures/sim/imageC17O_3-2_75deg_all.eps}
-%
-% \caption{C$^{17}$O 3$\rightarrow$2 inclined at 75$^\circ$ to edge on.
-The three panels are: %{\bf left:} Continuum subtracted integrated intensity map (in K$\,$km$\,$s$^{-1}$).
-{\bf %Centre:} Intensity weighted velocity map (in km$\,$s$^{-1}$).
-{\bf Right:} Position-velocity %diagram with intensities in K.}
-%\end{figure*}
-
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_contSub.eps}
-%
-% \caption{C18O 3-2 15 deg Continuum subtracted mom0}
-%\end{figure}
-%
-%%\begin{figure}
-%% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_mom1.eps}
-%%
-%% \caption{C18O 3-2 15 deg mom1map}
-%%\end{figure}
-%
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_15deg_PV_centre.eps}
-%
-% \caption{C18O 3-2 PV 15 deg through centre}
-%\end{figure}
-%
-%
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_contSub.eps}
-%
-% \caption{C18O 3-2  30 deg Continuum subtracted mom0}
-%\end{figure}
-
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_mom1.eps}
-%
-% \caption{C18O 3-2 30 deg mom1map}
-%\end{figure}
-
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_30deg_PV_centre.eps}
-%
-% \caption{C18O 3-2 30 deg PV through centre}
-%\end{figure}
-%
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_contSub.eps}
-%
-% \caption{C18O 3-2 45 deg Continuum subtracted mom0}
-%\end{figure}
-%
-%%\begin{figure}
-%% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_mom1.eps}
-%%
-%% \caption{C18O 3-2 45 deg mom1map}
-%%\end{figure}
-%
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_45deg_PV_centre.eps}
-%
-% \caption{C18O 3-2 45 deg PV through centre}
-%\end{figure}
-%
-%
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_contSub.eps}
-%
-% \caption{C18O 3-2 60 deg Continuum subtracted mom0}
-%\end{figure}
-%
-%%\begin{figure}
-%% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_mom1.eps}
-%%
-%% \caption{C18O 3-2 60 deg mom1map}
-%%\end{figure}
-%
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_60deg_PV_centre.eps}
-%
-% \caption{C18O 3-2 60 deg PV through centre}
-%\end{figure}
-%
-%\begin{figure}
-% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_contSub.eps}
-%
-% \caption{C18O 3-2 75 deg Continuum subtracted mom0}
-%\end{figure}
-%
-%%\begin{figure}
-%% \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_mom1.eps}
-%%
-%% \caption{C18O 3-2 75 deg mom1map}
-%%\end{figure}
-%
-%\begin{figure}
-%%  \showthe\columnwidth % Use this to determine the width of the figure.
-%  \includegraphics[width=84mm]{Figures/sim/imageC18O_3-2_75deg_PV_centre.eps}
-%  \caption{C18O 3-2 75 deg PV through centre}
-%\end{figure}
+Simulations at inclinations other than 30$^\circ$ were also performed with C$^{17}$O.
+Figures B1-3 show the C$^{17}$O 3$\rightarrow$2 line in the same phisical model but at 15$^\circ$, 30$^\circ$, 45$^\circ$ and 75$^\circ$ to egde on.
+At 15$^\circ$ to edge on we can still see some structure in the integrated intensity map and the structure is also visible in the position velocity diagram.
+At larger incliations it gets more difficult to obtain any kinematic information but the physical structure of the disc becomes clearer.
 
 \bsp
-%
 \label{lastpage}
-%
 \end{document}

### 2013-03-14 young_pp_discs.tex
nearly done

@@
 In this paper we have presented radiative transfer simulations of a hybrid model comprising a 0.39$\, M_\odot$ self gravitating disc with radius 64$\,$au showing spiral density waves, surrounded by an envelope simulated as a contracting 10$\,M_\odot$ BE-sphere.
-The main results of these simulations are as follows:\smallskip
+The main results of these simulations are as follows:\newline
 $\bullet$ CASA simulations of this model show that at a distance of 100$\,$pc, extraction of kinematics and structural information from the continuum and molecular lines is possible with ALMA band 7.\\
@@
 
-Big up results here!!
+These results demonstrate that with next generation millimetre interferometers we will be able to probe the very earliest stages of circumstellar discs which feed thier growing protostar and eventually could become a planetary system.
+Our results show that these types of observations would be able to dectect whether or not these young disc are gravitationally unstable, which could have significant implications on the evolution of the disc, such as fragmentation and planetesimal formation \cite{Boley2009,Johnson2013,Gibbons2012}, chemical evolution I2011 and other stuff i'd mention if i could get on ads.
 

### 2013-03-14 young_pp_discs.tex
done for now

--- 2013-03-13 young_pp_discs.tex
@@
 The formation and earliest stages of protoplanetary discs are still lacking observational constraints.
-ALMA will soon revolutionize this field, therefore it is important to provide predictions and help the interpretation of future high sensitivity and high angular resolution observations.
+ALMA will soon revolutionise this field, therefore it is important to provide predictions and help the interpretation of future high sensitivity and high angular resolution observations.
 Here we present simulated ALMA observations based on radiative transfer modelling of a relatively massive (0.39 M$_{\odot}$) self-gravitating disc embedded in a 10\,M$_{\odot}$ dense core, with structure similar to the pre-stellar core L1544.
@@
 To appropriately describe the environment within which a young protoplanetary disc is embedded, we combine the disc model from I2011 with a model of a dense core with characteristics similar to the well-studied pre-stellar core L1544 (\citealt{Keto2010}, hereafter KC2010).
-Although L1544 does not appear to contain a central protostar and disc itself, L1521F, a similar dense core, contains a central object which appears to be a low mass protostar and disc \citep{Bourke2006}, whilest having between half and three quarters of the mass of L1544.
+Although L1544 does not appear to contain a central protostar and disc itself, L1521F, a similar dense core, contains a central object which appears to be a low mass protostar and disc \citep{Bourke2006}, whilst having between half and three quarters of the mass of L1544.
 The KC2010 model follows the dynamical, chemical and thermal evolution of a contracting Bonnor-Ebert sphere \citep{Bonnor1956,Ebert1957} with total mass of 10\,M$_{\odot}$, until it reaches the density, temperature and velocity profiles which best match observations.
@@
 The self-gravitating disc exhibits prominent spiral structure, with H$_2$ number densities in the disc ranging from 10$^4$-10$^{13}$ cm$^{-3}$ and temperatures from 30-400 K (figure \ref{rhoT}).
-For the non-LTE 3D radiative transfer modeling presented here, we interpolate the I2011 simulation output on to a 256$\times$256$\times$64 Cartesian grid with spatial resolution of 0.5$\,$au in x, y, and z and sample from this to create the unstructured radiative transfer grid (see section \ref{subsec:gridding}).
-As in the hydrodynamics simulation, the dust and gas temperatures are assumed to be in equilibrium within the disc and a gas to dust mass ratio of 1/100 is used throught the entirity of the model.
+For the non-LTE 3D radiative transfer modelling presented here, we interpolate the I2011 simulation output on to a 256$\times$256$\times$64 Cartesian grid with spatial resolution of 0.5$\,$au in x, y, and z and sample from this to create the unstructured radiative transfer grid (see section \ref{subsec:gridding}).
+As in the hydrodynamics simulation, the dust and gas temperatures are assumed to be in equilibrium within the disc and a gas to dust mass ratio of 1/100 is used throughout the entirety of the model.
 The dust opacities were adopted from \citet{Ossenkopf1994} and refer to dust grains with thick icy mantles and 10$^6$ yr coagulation history.
-In the dense conditions of the protoplanetary disc could be encouraging the dust grains to agglomerate and increase the size of the ice mantle through freeze out of volitiles.
+In the dense conditions of the protoplanetary disc could be encouraging the dust grains to agglomerate and increase the size of the ice mantle through freeze out of volatiles.
 This could lead to changes in the dust opacity, however we have not attempted to include these effects in our model.
 The dust opacities used in the radiative transfer are not the same as the ones used in the hydrodynamic model (which used the dust opacities of \citealt{DAlessio2001}).
-However the results desciribed here do not depend on the details of the dust opacity and would be qualitatively similar if other opacities were used.\smallskip
+However the results described here do not depend on the details of the dust opacity and would be qualitatively similar if other opacities were used.\smallskip
 
@@
 \subsection{The radiative transfer code} \label{subsec:radiative_transfer_code}
-The radiative transfer program used is LIME (LIne Modeling Engine; \cite{Brinch2010}), which  calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3D model.
+The radiative transfer program used is LIME (LIne Modelling Engine; \cite{Brinch2010}), which  calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3D model.
 The method of selecting these points is given in section \ref{subsec:gridding}.
@@
 These points are then smoothed by Lloyd's algorithm \citep{Lloyd1982} in order to minimise the variation in distance between points whilst keeping the same underlying distribution.
-These points are then connected by Delaunay triangulation\footnote{For three dimensions, Delaunay trianglulating means that if four points are connected into a tetrahedron, the sphere circumscribing these four points contains no other points.
+These points are then connected by Delaunay triangulation\footnote{For three dimensions, Delaunay triangulation means that if four points are connected into a tetrahedron, the sphere circumscribing these four points contains no other points.
 It can be shown that this connection is unique for a given set of points.} and it is down these paths that photon propagation is restricted (figure \ref{grid}).
@@
  \includegraphics[width=84mm]{Figures/model/lime2.eps}%Lime_grid3.eps
- \caption{A plot of the points selected by the gridding process and the paths down which photons can propagate for points in the central r,$\theta$ plane.
+ \caption{A plot of the points selected by the griding process and the paths down which photons can propagate for points in the central r,$\theta$ plane.
 The points are colour coded by the density distribution (in m$^{-3}$, as used in LIME) and are more concentrated at small radii and in the most dense regions.
@@
  \caption{{\bf Left:}A 300$\,$GHz continuum image of the model, created from the average of ten LIME runs.
-{\bf Right:} the output of a single radiative transfer simulation, with artifacts due to finite gridding.}
+{\bf Right:} the output of a single radiative transfer simulation, with artifacts due to finite grid-ding.}
  \label{averages}
@@
 To simulate observations, the model was placed at roughly the distance of nearby low-mass star forming regions (100$\,$pc).
-The inlination angle was varied from 15$^\circ$ to 75$^\circ$ to edge on, we will consider the 30$^\circ$ case as a 'typical' inclination with the 15$^\circ$ inclination discussed in section \ref{sec:alma_predictions}, the other inclinations simulated are shown in appendix \ref{sec:other_inc}.
+The inclination angle was varied from 15$^\circ$ to 75$^\circ$ to edge on, we will consider the 30$^\circ$ case as a 'typical' inclination with the 15$^\circ$ inclination discussed in section \ref{sec:alma_predictions}, the other inclinations simulated are shown in appendix \ref{sec:other_inc}.
 From these simulated observations, integrated intensity maps, intensity weighted velocity maps and position velocity diagrams were created.
@@
 The spiral structure of the disc is clearly visible at this inclination and will be clearer the closer the disc is to being face on.
-We can get an estimate of the mass from a continuum image such as this using the equation $EQUATION$ \cite{equn_ref} which gives a mass of X showing that Y (continuum mass estimates are good/rubish for discs of this high mass/density).\smallskip
+We can get an estimate of the mass from a continuum image such as this using the equation $EQUATION$ \cite{equn_ref} which gives a mass of X showing that Y (continuum mass estimates are good/rubbish for discs of this high mass/density).\smallskip
 
@@
 From this it can be seen that the absorption features trace the disc spiral structure whilst the line emission emanates from gaps in the outer disc, where there is less continuum to be absorbed.
-The central pannel is domminated by the envelope contribution, causing stron absorption through out the disc.
-The other pannels show the line following a rotation profile distorted by the presence of the spiral arms.
+The central panel is dominated by the envelope contribution, causing Strong absorption through out the disc.
+The other panels show the line following a rotation profile distorted by the presence of the spiral arms.
 \smallskip
@@
 \citealt{Bissantz2003}).
-Whilest analysis of the detail of the spiral structure (number of arms, pitch angle etc.) would be difficult from such a PV diagram, detecting the presence of spiral waves, and therefore a potentially gravitationally unstable disc, is possible.\smallskip
+Whilst analysis of the detail of the spiral structure (number of arms, pitch angle etc.) would be difficult from such a PV diagram, detecting the presence of spiral waves, and therefore a potentially gravitationally unstable disc, is possible.\smallskip
 
@@
 
- \caption{CASA simulation of the C17O 3$\rightarrow$2 line with the disc inclided at 15$^\circ$ to edge on {\bf Top:} integrated intensity map.
+ \caption{CASA simulation of the C17O 3$\rightarrow$2 line with the disc inclined at 15$^\circ$ to edge on {\bf Top:} integrated intensity map.
 {\bf bottom:} position velocity diagram.
@@
 $\bullet$ The lines studied (OCS 26$\rightarrow$25, H$_2$CO 4$_{04}$$\rightarrow$3$_{03}$, C$^{17}$O 3$\rightarrow$2 and HCO$^+$ 3$\rightarrow$2) taken together allow all regions of the disc to be sampled and the rotation of the disc to be constrained from the inner edge to the outer edge.\\
-$\bullet$ Spiral structure in young embedded discs are dectectable at a wide range of inclination angles, they can be resolved spatially at angles close to face on and can be infered from position velocity diagrams at low inclination angles.\smallskip
+$\bullet$ Spiral structure in young embedded discs are detectable at a wide range of inclination angles, they can be resolved spatially at angles close to face on and can be inferred from position velocity diagrams at low inclination angles.\smallskip
 
@@
 
-Big up results here!!
+These results demonstrate that with next generation millimetre interferometers we will be able to probe the very earliest stages of circumstellar discs which feed their growing protostar and eventually could become a planetary system.
+Our results show that these types of observations would be able to detect whether or not these young disc are gravitationally unstable.
+If such gravitationally instabilities exist they would have significant implications on the evolution of the disc, such as fragmentation and planetesimal formation \citep{Boley2009,Johnson2013,Gibbons2012} and chemical evolution I2011.
 
@@
 Simulations at inclinations other than 30$^\circ$ were also performed with C$^{17}$O.
-Figures B1-3 show the C$^{17}$O 3$\rightarrow$2 line in the same phisical model but at 15$^\circ$, 30$^\circ$, 45$^\circ$ and 75$^\circ$ to egde on.
+Figures B1-3 show the C$^{17}$O 3$\rightarrow$2 line in the same physical model but at 15$^\circ$, 30$^\circ$, 45$^\circ$ and 75$^\circ$ to edge on.
 At 15$^\circ$ to edge on we can still see some structure in the integrated intensity map and the structure is also visible in the position velocity diagram.
-At larger incliations it gets more difficult to obtain any kinematic information but the physical structure of the disc becomes clearer.
+At larger inclinations it gets more difficult to obtain any kinematic information but the physical structure of the disc becomes clearer.
 

### 2013-03-15 young_pp_discs.tex
minor tweaks

@@
 \citealt{Stanke2007}, \citealt{VDTak2003}) it can be used to view rotation of the central part of the disc without risk of contamination from emission from shocked material along the outflow.
-The OCS lines are unique amongst the lines simulated in that it is not visible throughout all the regions in the disc where it is found, the line is only seen at radii <16$\,au$ whereas the molecules have a significant abundance out to $\sim$30$\,$au.
+The OCS lines are unique amongst the lines simulated in that it is not visible throughout all the regions in the disc where it is found, the line is only seen at radii $<$16$\,$au whereas the molecules have a significant abundance out to $\sim$30$\,$au.
 This is because the OCS line, which has the highest upper energy level among the selected transitions, traces only the hottest and densest regions of the disc where the high energy states are populated.
@@
 
-In order to make predictions on the observability of the synthetic brightness maps, the Common Astronomy Software Applications package (CASA) was used to simulate their observation with the completed ALMA in the 26th most extended configuration (out of a total of 28), with the longest baseline of 14.4km and giving beam sizes between 0.02 and 0.03 arcseconds at the selected frequencies, giving a beam size close to the size of the spiral structure in the disc.
+In order to make predictions on the observability of the synthetic brightness maps, the Common Astronomy Software Applications package (CASA) was used to simulate their observation with the completed ALMA in the 26th most extended configuration (out of a total of 28), with the longest baseline of 14.4km and giving beam sizes between 0.02 and 0.03 arcseconds at the selected frequencies.
+This gives a beam size close to the size of the spiral structure in the disc, allowing for the best sensitivity whilst being able to resolve the spiral structure.
 As the weakest lines studied in the model are of the order of 0.1-0.2$\,$mJy$\,$beam$^{-1}$ at this resolution, sensitivities of the order of 0.02$\,$mJy$\,$beam$^{-1}$ are required.
@@
 
- \caption{CASA simulation of the C17O 3$\rightarrow$2 line with the disc inclined at 15$^\circ$ to edge on {\bf Top:} integrated intensity map.
-{\bf bottom:} position velocity diagram.
+ \caption{CASA simulation of the C17O 3$\rightarrow$2 line with the disc inclined at 15$^\circ$ to edge on.
+{\bf Left:} Integrated intensity map.
+{\bf Right:} Position velocity diagram.
 In the position velocity diagram the spiral structures can be seen as narrow finger-like structures extending from the origin.}
@@
 Our results show that these types of observations would be able to detect whether or not these young disc are gravitationally unstable.
-If such gravitationally instabilities exist they would have significant implications on the evolution of the disc, such as fragmentation and planetesimal formation \citep{Boley2009,Johnson2013,Gibbons2012} and chemical evolution I2011.
+If such gravitationally instabilities exist they would have significant implications on the evolution of the disc, such as fragmentation and planetesimal formation \citep{Boley2009,Johnson2013,Gibbons2012} and chemical evolution in the disc (I2011).
 

### 2013-03-18 young_pp_discs.tex
updataed figs, minor text changes

--- 2013-03-14 young_pp_discs.tex
@@
 \citealt*{Joos2012,Hayfield2011,Machida2011}), are challenging.
-The use of sensitive interferometers is needed to achieve high angular resolution and spatially/spectrally disentangle the various disc, envelope and outflow components as well to filter out the extended emission tracing envelope material.
+The use of sensitive interferometers is needed to achieve high angular resolution and spatially/spectrally disentangle the various disc, envelope and outflow components as well to filter out the extended emission tracing the envelope material.
 \smallskip
@@
 To appropriately describe the environment within which a young protoplanetary disc is embedded, we combine the disc model from I2011 with a model of a dense core with characteristics similar to the well-studied pre-stellar core L1544 (\citealt{Keto2010}, hereafter KC2010).
-Although L1544 does not appear to contain a central protostar and disc itself, L1521F, a similar dense core, contains a central object which appears to be a low mass protostar and disc \citep{Bourke2006}, whilst having between half and three quarters of the mass of L1544.
+Although L1544 does not appear to contain a central protostar and disc itself, it is very similar in structure to L1521F,  another dense core in Taurus which hosts a low mass protostar and possibly a disc \citep{Bourke2006}.
 The KC2010 model follows the dynamical, chemical and thermal evolution of a contracting Bonnor-Ebert sphere \citep{Bonnor1956,Ebert1957} with total mass of 10\,M$_{\odot}$, until it reaches the density, temperature and velocity profiles which best match observations.
 The pre-stellar core model adopted here contains slight modifications due to the inclusion of oxygen cooling in the outer regions of the cloud, where CO is mostly photodissociated \citep{Caselli2012}.
-Figure \ref{fig:l1544_model} shows the physical parameters of the core model.
+Fig.
+\ref{fig:l1544_model} shows the physical parameters of the core model.
 \smallskip
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/model/L1544model_used_legend_small.eps}
+ \includegraphics[width=84mm]{Figures/model/L1544model_used_legend_small2.eps}
  \caption{The spherically symmetric model of the pre-stellar core L1544 used as the envelope of the young protoplanetary disc in the hybrid model.
@@
 \begin{figure*}
- \includegraphics[width=168mm]{Figures/model/rhoT6.eps}
+ \includegraphics[width=168mm]{Figures/model/rhoT5.eps}
  \caption{{\bf Left:} A 3D plot of log number density (cm$^{-3}$) showing the spiral structure in the xy plane and scale height of the disc.
@@
 \begin{figure*}
- \includegraphics[width=168mm]{Figures/model/columnDensities2.eps}
- \caption{Column densities of OCS, H$_2$CO,HCO$^+$ and CO used in the disc model. Figure adapted from I2011.}
+ \includegraphics[width=168mm]{Figures/model/columnDensities3.eps}
+ \caption{Column density distributions of OCS, H$_2$CO, HCO$^+$ and CO across the disc, as calculated by I2011.
+Note the different zones traced by the various species, with OCS mostly tracing the inner regions and HCO$^+$ probing the gas at larger radii.}
  \label{Chemistry} 
@@
 The disc structure used is from the same hydrodynamics simulation described in I2011, which is a 1$\,$M$_\odot$ protostar surrounded by a 0.39$\,$M$_\odot$ disc.
+Fig.~\ref{velocity} shows the azimuthally averaged rotational velocity in the disc plane, together with the best fit curve, which will be used in Sec.~\ref{sec:alma_predictions} to compare with position velocity diagrams.
 The system is envisaged to be at a very early stage of evolution and embedded in an envelope.
@@
 The star is allowed to move freely in response to disc torques, and radiative cooling is included \citep{Boley2009}.
-The self-gravitating disc exhibits prominent spiral structure, with H$_2$ number densities in the disc ranging from 10$^4$-10$^{13}$ cm$^{-3}$ and temperatures from 30-400 K (figure \ref{rhoT}).
+The self-gravitating disc exhibits prominent spiral structure, with H$_2$ number densities in the disc ranging from 10$^4$-10$^{13}$ cm$^{-3}$ and temperatures from 30-400 K (fig.
+\ref{rhoT}).
 For the non-LTE 3D radiative transfer modelling presented here, we interpolate the I2011 simulation output on to a 256$\times$256$\times$64 Cartesian grid with spatial resolution of 0.5$\,$au in x, y, and z and sample from this to create the unstructured radiative transfer grid (see section \ref{subsec:gridding}).
-As in the hydrodynamics simulation, the dust and gas temperatures are assumed to be in equilibrium within the disc and a gas to dust mass ratio of 1/100 is used throughout the entirety of the model.
+As in the hydrodynamics simulation, the dust and gas temperatures are assumed to be in equilibrium within the disc and a gas to dust mass ratio of 100 is used throughout the entirety of the model.
 The dust opacities were adopted from \citet{Ossenkopf1994} and refer to dust grains with thick icy mantles and 10$^6$ yr coagulation history.
-In the dense conditions of the protoplanetary disc could be encouraging the dust grains to agglomerate and increase the size of the ice mantle through freeze out of volatiles.
-This could lead to changes in the dust opacity, however we have not attempted to include these effects in our model.
+Although dust grains within the protoplanetary disc are expected to coagulate further,  significantly affecting the opacity, we did not take grain growth into account in our model.
 The dust opacities used in the radiative transfer are not the same as the ones used in the hydrodynamic model (which used the dust opacities of \citealt{DAlessio2001}).
-However the results described here do not depend on the details of the dust opacity and would be qualitatively similar if other opacities were used.\smallskip
+However, the results described here do not depend on the details of the dust opacity used during the hydrodynamic evolution.\smallskip
 
 \subsection{Chemical structure} \label{subsec:chemical_structure}
-Chemical abundances in the disc were taken from I2011 who followed gas-grain chemical processes during the dynamical evolution of the disc.
-As described in I2011, the hydrodynamics simulation included Lagrangian tracer fluid elements in addition to solving the equations of hydrodynamics on an Eulerian grid.
-These fluid elements were used to record the thermal history of the gas as material passed through and between spiral structure.
+Chemical abundances in the disc were taken from I2011, who followed gas-grain chemical processes during the dynamical evolution of the disc.
+As described in I2011, the hydrodynamical simulation included Lagrangian tracer fluid elements in addition to solving the equations of hydrodynamics on an Eulerian grid.
+These fluid elements were used to record the thermal history of the gas as material passed through and between the spiral structure.
 I2011 used this time evolution information from fluid elements to calculate the abundances of 125 species, related by 1334 reactions.
-These abundances were then interpolated by I2011 on to a Cartesian grid with cell sizes 2.2$\times$2.2$\times$0.22$\,$au in x, y, and z to reveal the morphology of the disk as seen by different molecular species.
-From these we selected the four species which appear to trace different regions of the disc: the inner 20\,au (OCS), the inner 40\,au (H$_2$CO),  the region between $\simeq$40 and 60\,au (HCO$^+$) and one which traces the entirety of the disc (C$^{17}$O) (see figure \ref{Chemistry}).
+These abundances were then interpolated by I2011 on to a Cartesian grid with cell sizes 2.2$\times$2.2$\times$0.22$\,$au$^3$ in x, y, and z to reveal the morphology of the disc as seen by different molecular species.
+From these we selected the four species which appear to trace different regions of the disc: the inner 30\,au (OCS), the inner 40\,au (H$_2$CO),  the region between $\simeq$40 and 60\,au (HCO$^+$) and the entirety of the disc (C$^{17}$O) (see fig.
+\ref{Chemistry}).
 The abundance model used for C$^{17}$O was the CO model reduced by a factor of 1792, the ratio of $^{16}$O to $^{17}$O in the local ISM \citep{Wilson1994}.
 As explained by I2011,  H$_2$CO and OCS mostly probe the central warm regions, where icy mantles evaporate, whereas HCO$^+$ preferentially traces the outer spiral pattern as in the central region it is destroyed by water molecules and transformed into H$_3$O$^+$ and CO.
-The simple chemistry in the KC2010 model, adopted here as the envelope of the protoplanetary disc, does not provide detailed abundances of molecular species (besides CO and H$_2$O, see also \cite{Caselli2012}).
-As discussed in the result section \ref{sec:model_results}, approximations have been made based on values measured toward similar objects.
-The molecular data used is from the Leiden Atomic and Molecular DAtabase (LAMDA) (Sch\"oier et al.
-2005; http://home.strw.leidenuniv.nl/$\sim$moldata/).
+The simple chemistry in the KC2010 model, adopted here as the envelope of the protoplanetary disc, does not provide detailed abundances of molecular species (besides CO and H$_2$O, see also \citealt{Caselli2012}).
+As discussed in the results section \ref{sec:model_results}, abundances have been adopted based on values measured toward similar objects.
+The molecular data used here for the radiative transfer is taken from the Leiden Atomic and Molecular DAtabase (LAMDA) (\citealt{Schoier2005} http://home.strw.leidenuniv.nl/$\sim$moldata/).
 
 \subsection{The radiative transfer code} \label{subsec:radiative_transfer_code}
-The radiative transfer program used is LIME (LIne Modelling Engine; \cite{Brinch2010}), which  calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3D model.
+The radiative transfer program used is LIME (LIne Modelling Engine; \citealt{Brinch2010}), which  calculates line intensities based on a weighted sample of randomly chosen points in a continuous 3D model.
 The method of selecting these points is given in section \ref{subsec:gridding}.
@@
 These points are then connected by Delaunay triangulation\footnote{For three dimensions, Delaunay triangulation means that if four points are connected into a tetrahedron, the sphere circumscribing these four points contains no other points.
-It can be shown that this connection is unique for a given set of points.} and it is down these paths that photon propagation is restricted (figure \ref{grid}).
+It can be shown that this connection is unique for a given set of points.} and it is down these paths that photon propagation is restricted (fig.
+\ref{grid}).
 The level populations of the selected molecules are calculated at each of these points from collisional and radiative (de)excitation and the local radiation field is calculated.
@@
 After 20 iterations the model is ray-traced in order to produce synthetic brightness maps.
-In order to minimise the artifacts in the output images, resulting from the grid construction, the average of ten separate runs was taken (Figure \ref{averages}).
+The average of ten separate runs was taken to minimise the artifacts in the output images, resulting from the grid construction (Fig.
+\ref{averages}).
 
 \begin{figure}
- \includegraphics[width=84mm]{Figures/model/lime2.eps}%Lime_grid3.eps
- \caption{A plot of the points selected by the griding process and the paths down which photons can propagate for points in the central r,$\theta$ plane.
+ \includegraphics[width=84mm]{Figures/model/lime3.eps}
+ \caption{A plot of the points selected by the gridding process and the paths down which photons can propagate for points in the central r, $\theta$ plane.
 The points are colour coded by the density distribution (in m$^{-3}$, as used in LIME) and are more concentrated at small radii and in the most dense regions.
@@
 This provides a minimum level of sampling for the large low density regions in the outer parts of the simulated volume.
-See figure \ref{points} for an example of the points distribution in r, z.
+See fig.
+\ref{points} for an example of the points distribution in r, z.
 \smallskip
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/continuum.eps}
- \caption{{\bf Left:}A 300$\,$GHz continuum image of the model, created from the average of ten LIME runs.
-{\bf Right:} the output of a single radiative transfer simulation, with artifacts due to finite grid-ding.}
+ \includegraphics[width=84mm]{Figures/sim/continuum2.eps}
+ \caption{{\bf Left:} A 300$\,$GHz continuum image of the model, created from the average of ten LIME runs.
+{\bf Right:} the output of a single radiative transfer simulation, with artifacts due to finite gridding.}
  \label{averages}
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/model/lime_points_rz_histo2.eps}
+ \includegraphics[width=84mm]{Figures/model/lime_points_rz_histo3.eps}
  \caption{A 2D histogram of the point distribution throughout the model. The disc and envelope can be seen as two separate entities which have to be sampled using different point distributions.}
@@
 Simulations are limited to molecules for which we have abundances in both the disc and envelope, and also have calculated Einstein and collisional coefficients.
-In the envelope, the HCO$^+$ abundance profile follows the H$_2$O profile of L1544 \citep{Caselli2012}, scaled so the maximum is 1$\times$10$^{-8}$ (assuming, for simplicity, that photodissociation and freeze-out affect these two species in a similar way).For H$_2$CO, a step profile was considered, with a fractional abundance of 1.5$\times$10$^{-8}$ at radii greater than 0.04$\,$pc and 1.5$\times$10$^{-9}$ inside it \citep{Young2004}.
+In the envelope, the HCO$^+$ abundance profile follows the H$_2$O profile of L1544 \citep{Caselli2012}, scaled so the maximum is 1$\times$10$^{-8}$ (assuming, for simplicity, that photodissociation and freeze-out affect these two species in a similar way).
+For H$_2$CO, a step profile was considered, with a fractional abundance of 1.5$\times$10$^{-8}$ at radii greater than 0.04$\,$pc and 1.5$\times$10$^{-9}$ inside it \citep{Young2004}.
 For OCS we adopted a constant abundance of 1.9$\times$10$^{-9}$ \citep{Ren2011}.
 The C$^{17}$O abundance profile in the envelope follows the CO profile calculated for L1544 by KC2010, scaled by the $^{17}$O/$^{16}$O elemental abundance.
-These estimates for the abundances in the envelope are simplistic, however, as seen in section \ref{sec:alma_predictions}, the envelope contribution to the line is very narrow, and can be spectrally disentangled from the disc contribution.\smallskip
+These estimates for the abundances in the envelope are simplistic, however, as seen in section \ref{sec:alma_predictions}, the envelope contribution to the line is very limited in velocity and can be spectrally disentangled from the disc contribution.\smallskip
 
@@
 
-%We considered C$^{17}$O 3$\rightarrow$2 at 337.1$\,$GHz with an upper energy level of $E_u$=32.3K, HCO$^+$ 3$\rightarrow$2 at 267$\,$GHz and $E_u$=25.7K, OCS 26$\rightarrow$25 at 316$\,$GHz and $E_u$=205K and H$_2$CO 4$_{04}\rightarrow$3$_{03}$ at 290$\,$GHz and $E_u$=34.9K.\smallskip
-
 To simulate observations, the model was placed at roughly the distance of nearby low-mass star forming regions (100$\,$pc).
-The inclination angle was varied from 15$^\circ$ to 75$^\circ$ to edge on, we will consider the 30$^\circ$ case as a 'typical' inclination with the 15$^\circ$ inclination discussed in section \ref{sec:alma_predictions}, the other inclinations simulated are shown in appendix \ref{sec:other_inc}.
+The inclination angle was varied from 15$^\circ$ to 75$^\circ$ relative to the edge on case.
+In the following, we will show the 30$^\circ$ case, while the 15$^\circ$ is discussed in section \ref{sec:alma_predictions}.
+Other inclinations are shown in appendix \ref{sec:other_inc}.
 From these simulated observations, integrated intensity maps, intensity weighted velocity maps and position velocity diagrams were created.
-The integrated intensity, intensity weighted velocity and channel maps (figures \ref{sim_all}, \ref{h2co_chanmap} and \ref{mom0_maps}) were created by integrating between -12.5 to -0.5$\,$km$\,$s$^{-1}$ and +0.5 to +12.5$\,$km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope.
-This can be seen in some PV diagrams as the strong absorption feature at all positions around zero velocity (see section \ref{sec:alma_predictions}).
+The integrated intensity and  intensity weighted velocity maps (fig.s \ref{sim_all}, and \ref{mom0_maps}) were created by integrating between -12.5 to -0.5$\,$km$\,$s$^{-1}$ and +0.5 to +12.5$\,$km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, which can be seen in some PV diagrams as the strong absorption feature at all positions around zero velocity (see section \ref{sec:alma_predictions}).
 Intensity weighted velocity maps are shown with a cut-off of 3$\sigma$ as described in section \ref{sec:alma_predictions}.\smallskip
@@
 \begin{figure*}
- \includegraphics[width=150mm]{Figures/sim/imageALL_30deg_all.eps}
+ \includegraphics[width=150mm]{Figures/sim/imageALL_30deg_all2.eps}
  \caption{{\bf Left:} Continuum subtracted integrated intensity maps.
@@
 
-OCS 26$\rightarrow$25 traces only the innermost 20$\,$au of the disc and can be used to examine the central regions (figure \ref{sim_all}).
+OCS 26$\rightarrow$25 traces only the innermost 20$\,$au of the disc and can be used to examine the central regions (fig.
+\ref{sim_all}).
 As OCS is not seen in outflows (e.g.
-\citealt{Stanke2007}, \citealt{VDTak2003}) it can be used to view rotation of the central part of the disc without risk of contamination from emission from shocked material along the outflow.
-The OCS lines are unique amongst the lines simulated in that it is not visible throughout all the regions in the disc where it is found, the line is only seen at radii <16$\,au$ whereas the molecules have a significant abundance out to $\sim$30$\,$au.
+\citealt{Stanke2007}, \citealt{VDTak2003}), it can be used to measure the rotation of the central part of the disc without contamination from shocked material along the outflow.
+The OCS lines are unique amongst the lines simulated in that they trace radii $<$16$\,$au, even smaller than the extent of the OCS column density distribution shown in fig.\ref{Chemistry}.
 This is because the OCS line, which has the highest upper energy level among the selected transitions, traces only the hottest and densest regions of the disc where the high energy states are populated.
-As a result, the innermost spiral structure is best seen in OCS (26 - 25), as shown in figure \ref{sim_all}.
+As a result, the innermost spiral structure is best seen in OCS (26$\rightarrow$25), as shown in fig.
+\ref{sim_all}.
 The majority of the OCS line is visible in absorption against the bright continuum emission from the disc mid-plane.
 The exception to this is towards the centre of the disc where the hole in the hot, dense mid-plane means that there is little continuum to be absorbed.
-However, because of the presence of the protostar and other hot material within 2$\,$au of the protostar, not considered in our simple model, we expect absorption to also be observed toward the central region of the disc.\smallskip
+However, this may be an artefact of our simplistic treatment of the inner hole, given that we neglect the presence of the protostar and other hot material within the central 2$\,$au.
+Thus, we expect absorption to be also observed toward the central region of the disc.\smallskip
 
-The abundance of the H$_2$CO molecule traces the spiral structure of the inner $\sim$40$\,$au of the disc, which can be seen in the integrated intensity map and its rotation is detected out to larger radii than is possible with the OCS line (figure \ref{sim_all}).
-As with the OCS line, the majority of the H$_2$CO 4$_{04}\rightarrow$3$_{03}$, is seen in absorption against the disc mid-plane continuum, with the central region seen in emission.
-Unlike the OCS however, the H$_2$CO extends out to large enough radii to be present in the voids between the outer parts spiral arms.
+The abundance of the H$_2$CO molecule traces the spiral structure of the inner $\sim$40$\,$au of the disc, which can be seen in the integrated intensity map, and its rotation is detected out to larger radii compared to the OCS line (fig.
+\ref{sim_all}).
+As with the OCS line, the majority of the H$_2$CO 4$_{04}$$\rightarrow$3$_{03}$, is seen in absorption against the disc mid-plane continuum, with the central region seen in emission.
+However, unlike the OCS, the H$_2$CO extends out to large enough radii to trace the voids between the outer spiral arms.
 In these regions, the H$_2$CO line can be seen in emission.\smallskip
@@
 
-HCO$^+$ in unique in the molecules simulated in I2011 in that it traces only the outer regions of the disc, and so can be used to look at the extended velocity and physical structure.
-In figure \ref{sim_all} we can see that the HCO$^+$ line shows the outer edges of the spiral arms in absorption, but it also shows emission from the diffuse gas further out in the disc.
-This allows the velocity structure of the disc to be measured out to larger radii and allows constraints to be placed on the rotation of the disc out to larger radii than with other molecules.
+The HCO$^+$ line only traces the outer regions of the disc.
+In fig.
+\ref{sim_all} we can see that the HCO$^+$ line shows the outer edges of the spiral arms in absorption, but it also shows emission from the diffuse gas further out in the disc.
+This allows the velocity structure of the disc to be measured out to larger radii, allowing constraints to be placed on the rotation of the disc out to larger radii than with other molecules.
 
@@
 
-In order to make predictions on the observability of the synthetic brightness maps, the Common Astronomy Software Applications package (CASA) was used to simulate their observation with the completed ALMA in the 26th most extended configuration (out of a total of 28), with the longest baseline of 14.4km and giving beam sizes between 0.02 and 0.03 arcseconds at the selected frequencies, giving a beam size close to the size of the spiral structure in the disc.
-As the weakest lines studied in the model are of the order of 0.1-0.2$\,$mJy$\,$beam$^{-1}$ at this resolution, sensitivities of the order of 0.02$\,$mJy$\,$beam$^{-1}$ are required.
+In order to make predictions on the observability of the synthetic brightness maps, the Common Astronomy Software Applications package (CASA) was used to simulate observations with the completed ALMA in the 26th most extended configuration (out of a total of 28).
+The longest baseline of this configuration is 14.4\,km and the beam sizes range between 0.02 and 0.03 arcseconds at the selected frequencies.
+This angular resolution is close to the size of the spiral structure in the disc.
+As the weakest lines studied in the model are of the order of 0.1-0.2$\,$mJy$\,$beam$^{-1}$ at this resolution, Band 7 sensitivities of the order of 0.02$\,$mJy$\,$beam$^{-1}$ are required.
 This implies around 6 hours of integration time.
@@
   \centering
-  \begin{minipage}{80mm}
-    \caption{Line sensitivities obtained with ALMA after 6 hours integration time with velocity resolution of $\sim$400$\,$ms$^{-1}$. As calculated by the ALMA on-line sensitivity calculator.}
+  \begin{minipage}{90mm}
+    \caption{Line sensitivities obtained with ALMA after 6 hours integration time with velocity resolution of 400$\,$m\,s$^{-1}$, using the ALMA on-line sensitivity calculator.}
     \label{sigmas}
@@
       Species & Transition & Frequency & Upper energy level & Sensitivity\\
+                      &                    & (GHz)            & (K)                            & (mJy beam$^{-1}$) \\
       \hline
-      C$^{17}$O & 3$\rightarrow$2 & 337.06GHz & 32.3$\,$K & 0.0270$\,$mJy$\,$beam$^{-1}$ \\
-      OCS & 26$\rightarrow$25 & 316.15GHz & 25.7$\,$K & 0.0275$\,$mJy$\,$beam$^{-1}$ \\
-      HCO$^+$ & 3$\rightarrow$2 & 267.56GHz & 205$\,$K & 0.0176$\,$mJy$\,$beam$^{-1}$ \\
-      H$_2$CO & 4$_{04}\rightarrow$3$_{03}$ &  290.62GHz & 34.9$\,$K & 0.0228$\,$mJy$\,$beam$^{-1}$ \\
+      C$^{17}$O & 3$\rightarrow$2 & 337.06 & 32.3 & 0.0270 \\
+      OCS & 26$\rightarrow$25 & 316.15 & 205 & 0.0275 \\
+      HCO$^+$ & 3$\rightarrow$2 & 267.56 & 25.7 & 0.0176 \\
+      H$_2$CO & 4$_{04}\rightarrow$3$_{03}$ &  290.62 & 34.9 & 0.0228 \\
       \hline
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/casa_cont_300GHz_invert.eps}
+ \includegraphics[width=84mm]{Figures/sim/casa_cont_300GHz_invert2.eps}
 
@@
 \begin{figure*}
- \includegraphics[width=168mm]{Figures/sim/channel_map-1.eps} 
+ \includegraphics[width=168mm]{Figures/sim/channel_map-2.eps} 
  \caption{H$_2$CO 4$_{04}\rightarrow$3$_{03}$ channel maps as simulated by CASA.
@@
 
-Figure \ref{continuum} Shows the 1mm continuum emission and beam size in this configuration of ALMA.
-The spiral structure of the disc is clearly visible at this inclination and will be clearer the closer the disc is to being face on.
-We can get an estimate of the mass from a continuum image such as this using the equation $EQUATION$ \cite{equn_ref} which gives a mass of X showing that Y (continuum mass estimates are good/rubbish for discs of this high mass/density).\smallskip
+Fig.
+\ref{continuum} shows the 1\,mm continuum emission and beam size in the chosen ALMA configuration.
+The spiral structure of the disc is clearly visible at this inclination and and it becomes clearer at angles closer to face-on.
+Integrating the flux from y=0.2 to -0.2 and x=0.4 to -0.4 and using the equation $M=frac{g S_\nu d^2}{\kappa_\nu B_\nu(T_d)}$ where g is the dust/gas mass ratio S$_\nu$ is the integrated flux, d is the distance to the source, $\kappa_\nu$ is the opacity and B$_\nu(T_d)$ is the black body function for a given dust temperature \citep{Beltran2006}.
+From this, a mass measurement of between 0.1$\,$M$_\odot$ and 0.005$\,$M$_\odot$ was obtained assuming temperatures of between 40-400K.
+This underestimates the disc mass by at least a factor of 4 and shows that in such young discs longer wavelength continuum observations may not be neccesary for determining the disc mass.\smallskip
 
-Figure \ref{h2co_chanmap} shows a channel map of the H$_2$CO 4$_{04}\rightarrow$3$_{03}$ line overlaid on the 1$\,$mm continuum emission.
+Fig.
+\ref{h2co_chanmap} shows a channel map of the H$_2$CO 4$_{04}\rightarrow$3$_{03}$ line overlaid on the 1$\,$mm continuum emission.
 From this it can be seen that the absorption features trace the disc spiral structure whilst the line emission emanates from gaps in the outer disc, where there is less continuum to be absorbed.
-The central panel is dominated by the envelope contribution, causing Strong absorption through out the disc.
+The central panel is dominated by the envelope contribution, causing strong absorption through out the disc.
 The other panels show the line following a rotation profile distorted by the presence of the spiral arms.
@@
 
-Figure \ref{15deg} shows the C$^{17}$O 3$\rightarrow$2 integrated intensity and PV diagram for an inclination angle of 15$^\circ$ to edge on, showing that spiral structure can be seen in the position velocity diagram at low inclinations.
-The ``finger-like'' structures in the PV diagram are similar to those seen in the case of observations of the milky way and of simulations of spirals in the milky way (e.g.
+Fig.
+\ref{15deg} shows the C$^{17}$O 3$\rightarrow$2 integrated intensity and PV diagram for an inclination angle of 15$^\circ$ to edge on, showing that spiral structure can be clearly seen in the position velocity diagram even at low inclinations.
+The ``finger-like'' structures in the PV diagram are similar to those seen in observations of the Milky Way and in simulations of spirals in the Milky Way (e.g.
 \citealt{Bissantz2003}).
-Whilst analysis of the detail of the spiral structure (number of arms, pitch angle etc.) would be difficult from such a PV diagram, detecting the presence of spiral waves, and therefore a potentially gravitationally unstable disc, is possible.\smallskip
+Although the detail of the spiral structure (number of arms, pitch angle etc.) is difficult to gauge from such a PV diagram, high spectral and angular resolution observations can definitely unveil their presence and thus find gravitationally unstable discs.
+\smallskip
 
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/casa_C17O_15deg_all2.eps}
+ \includegraphics[width=84mm]{Figures/sim/casa_C17O_15deg_all3.eps}
 
- \caption{CASA simulation of the C17O 3$\rightarrow$2 line with the disc inclined at 15$^\circ$ to edge on {\bf Top:} integrated intensity map.
-{\bf bottom:} position velocity diagram.
-In the position velocity diagram the spiral structures can be seen as narrow finger-like structures extending from the origin.}
+ \caption{CASA simulation of the C$^{17}$O 3$\rightarrow$2 line with the disc inclined at 15$^\circ$ to edge on.
+{\bf Left:} Integrated intensity map.
+{\bf Right:} Position velocity diagram, where the spiral structures can be seen as narrow finger-like structures extending from the origin.}
  \label{15deg}
@@
  \caption{Integrated intensity maps for the simulated observations of: {\bf Top Left:} H$_2$CO 4$_{04}\rightarrow$3$_{03}$, {\bf Top Right:} C$^{17}$O 3$\rightarrow$2, {\bf Bottom Left:} OCS 26$\rightarrow$25 and {\bf Bottom Right:} HCO$^+$ 3$\rightarrow$2.
-Contours start at 3$\sigma$ and increasing in intervals of 3$\sigma$ for each of the maps except the H$_2$CO which starts at 5$\sigma$ and increases in intervals of 5$\sigma$.
+Contours start at 3$\sigma$ and increase in intervals of 3$\sigma$ for each of the maps except the H$_2$CO contours, which start at the 5$\sigma$ level and increase in intervals of 5$\sigma$.
 Emission is in red contours, absorption in blue.
-The dots refer to the spectra shown in figure \ref{spectra}.}
+The dots refer to the spectra shown in fig.
+\ref{spectra}.}
 \label{mom0_maps}
@@
 
-Figure \ref{mom0_maps} shows the simulated integrated intensity maps, which demonstrate how lines from different species allow observations to trace different regions of the disc, from the OCS line tracing the innermost regions, to the HCO$^+$ line showing the outer regions which are less bright in the continuum.
-ALMA has enough resolution and sensitivity to see spiral structure clearly in continuum emission but also in CO isotopologues and marginally in H$_2$CO.
-The different molecules can be seen to be tracing different regions of the disc\smallskip
+Fig.
+\ref{mom0_maps} shows the simulated integrated intensity maps of the disc in the four selected molecular transitions.
+As expected from the radiative transfer results, observations of these transitions can probe different regions of the disc, from the OCS line tracing the innermost regions, to the HCO$^+$ line showing the outer regions.
+Thus, the high sensitivity and angular resolution of ALMA will allow detection of spiral structure both in the continuum emission as well as  in appropriately selected molecular transitions.
+Different molecules can trace different regions of the disc.\smallskip
 
 \begin{figure*}
- \includegraphics[width=180mm]{Figures/sim/casa_all_30deg_PV_rotCurve_small.eps}
- \caption{Position velocity diagrams for each of the lines simulated with CASA. The green curve on each diagram is the best fit curve to the azimuthally averaged rotation profile from figure 4.}
+ \includegraphics[width=180mm]{Figures/sim/casa_all_30deg_PV_rotCurve_small2.eps}
+ \caption{Position velocity diagrams for each of the lines simulated with CASA. The green curve on each diagram is the best fit curve to the azimuthally averaged rotation profile from fig. 4.}
  \label{pvs}
@@
 
-Figure \ref{pvs} shows position-velocity diagrams of the lines simulated, allowing us to reconstruct the rotation of the disc.
-The green curves in each panel of figure \ref{pvs} display the best fit rotation curve of the physical model (see figure \ref{velocity}), showing that the rotation profile of the disc can be well constrained using kinematic information gathered from species tracing different regions of the disc.\smallskip
+Position-velocity diagrams are shown in fig.
+\ref{pvs}.
+These diagrams can be used to reconstruct the rotation of the disc.
+The green curves in each panel of fig.
+\ref{pvs} display the best fit rotation curve of the physical model (see fig.
+\ref{velocity}), showing that the rotation profile of the disc can be well constrained using kinematic information gathered from species tracing different regions of the disc.\smallskip
 
@@
  \includegraphics[width=168mm]{Figures/sim/casa_all_spectra2.eps}
- \caption{Simulated spectra for each of the selected transitions at the positions indicated by the coloured dots in figure \ref{mom0_maps}, the pink, green and cyan curves are taken from the locations marked by the dot of the same colour.
-In each diagram, the three spectra are taken from three positions on the Y=0 axis, one is at X=0 (green) and the other 2 are from x=$\pm$ N (plus blue, minus red) where N is the distance from the centre: 10 au for OCS, 20 au for H$_2$CO, 28 au for C$^{17}$O, 38 au for HCO$^+$.}
+ \caption{Simulated spectra for each of the selected transitions at the positions indicated by the coloured dots in fig.
+\ref{mom0_maps} (the pink, green and cyan curves are taken from the locations marked by the dots of the same colour).
+In each diagram, the three spectra are taken from three positions on the Y=0 axis, one is at X=0 (green) and the other 2 are from x=$\pm$ N (plus yellow, minus pink) where N is the distance from the centre: 10 au for OCS, 20 au for H$_2$CO, 28 au for C$^{17}$O, 38 au for HCO$^+$.}
  \label{spectra}
@@
 
-Figure \ref{spectra} shows spectra from the lines simulated, one from the centre of the image and one on each side of the disc along the Y=0 axis.
-As with all the CASA simulated images, these spectra were simulated with an ALMA window of total bandwidth 938$\,$MHz, giving velocity resolutions of between 418 and 527 ms$^{-1}$.
+Spectra are presented in Fig.
+\ref{spectra}, extracted from the maps in fig.
+\ref{mom0_maps} at the positions indicated by the corresponding coloured dots along the Y=0 axis.
+As with all the CASA simulated images, these spectra were simulated with an ALMA window of total bandwidth 938$\,$MHz, giving velocity resolutions of between 418 and 527\,m\,s$^{-1}$.
 The most notable thing about these spectral features is that they are not symmetric about the disc centre.
-For example, C$^{17}$O(3$\rightarrow$2) has a significantly stronger blueshifted absorption, due to the presence of a spiral arm along the same line of sight.
+For example, C$^{17}$O(3--2) has a significantly stronger blueshifted absorption, due to the presence of a spiral arm along the same line of sight.
 In the OCS lines, the two sides are not moving with equal velocities and the line widths and shapes are markedly different.
@@
 $\bullet$ Our simulations show that molecular features are predominantly seen in absorption against the hot mid-plane of self-gravitating protoplanetary discs, with emission only being seen where voids in the structure of the disc do not provide a bright continuum source to be absorbed.\\
-$\bullet$ The quiescent nature of the envelope around such discs only obscures lines within $\pm\,$0.5 km$\,$s$^{-1}$ of the systematic velocity.\\
+$\bullet$ The quiescent nature of the envelope around such discs only affect lines within $\pm\,$0.5 km$\,$s$^{-1}$ of the LSR velocity.\\
 $\bullet$ The lines studied (OCS 26$\rightarrow$25, H$_2$CO 4$_{04}$$\rightarrow$3$_{03}$, C$^{17}$O 3$\rightarrow$2 and HCO$^+$ 3$\rightarrow$2) taken together allow all regions of the disc to be sampled and the rotation of the disc to be constrained from the inner edge to the outer edge.\\
@@
 However, the large volume densities are expected to provide an efficient dust-gas coupling.
-Outflows could contaminate measurements of rotation curves, meaning that species  which commonly trace outflows, such as CO and HCO$^+$ are not going to be good tracers of disc rotation.
+Outflows could contaminate line profiles of  those species  which commonly trace outflows, such as CO and HCO$^+$.
+In these cases, a detailed study of their line profiles using high spectral resolution should help to disentangle the various kinematic components.
+In the future we will study this, including outflow lobes in the disc/envelope system.
 However species such as OCS and C$^{17}$O, which are not commonly seen in outflows, can be used to trace disc rotation and structure.\smallskip
 
-These results demonstrate that with next generation millimetre interferometers we will be able to probe the very earliest stages of circumstellar discs which feed their growing protostar and eventually could become a planetary system.
-Our results show that these types of observations would be able to detect whether or not these young disc are gravitationally unstable.
-If such gravitationally instabilities exist they would have significant implications on the evolution of the disc, such as fragmentation and planetesimal formation \citep{Boley2009,Johnson2013,Gibbons2012} and chemical evolution I2011.
+These results demonstrate that ALMA will be able to probe the very earliest stages of circumstellar discs which feed the growing protostar and eventually will evolve in a planetary system.
+Our results show that ALMA observations in band 7 will be able to assess whether or not these young discs are gravitationally unstable and test theories of pre-stellar $\rightarrow$ protostellar core evolution.
+If such gravitationally instabilities exist they would have significant implications on the evolution of the disc, such as fragmentation, planetesimal formation \citep{Boley2009,Johnson2013,Gibbons2012} and the chemical evolution in the disc (I2011).
 
@@
 Simulations at inclinations other than 30$^\circ$ were also performed with C$^{17}$O.
-Figures B1-3 show the C$^{17}$O 3$\rightarrow$2 line in the same physical model but at 15$^\circ$, 30$^\circ$, 45$^\circ$ and 75$^\circ$ to edge on.
+Figs.
+B1-3 show the C$^{17}$O 3$\rightarrow$2 line in the same physical model but at 15$^\circ$, 30$^\circ$, 45$^\circ$ and 75$^\circ$ to edge on.
 At 15$^\circ$ to edge on we can still see some structure in the integrated intensity map and the structure is also visible in the position velocity diagram.

### 2013-03-18 young_pp_discs.tex
minor text changes, sending round to authors second time in this form

@@
 The spiral structure of the disc is clearly visible at this inclination and and it becomes clearer at angles closer to face-on.
-Integrating the flux from y=0.2 to -0.2 and x=0.4 to -0.4 and using the equation $M=frac{g S_\nu d^2}{\kappa_\nu B_\nu(T_d)}$ where g is the dust/gas mass ratio S$_\nu$ is the integrated flux, d is the distance to the source, $\kappa_\nu$ is the opacity and B$_\nu(T_d)$ is the black body function for a given dust temperature \citep{Beltran2006}.
-From this, a mass measurement of between 0.1$\,$M$_\odot$ and 0.005$\,$M$_\odot$ was obtained assuming temperatures of between 40-400K.
-This underestimates the disc mass by at least a factor of 4 and shows that in such young discs longer wavelength continuum observations may not be neccesary for determining the disc mass.\smallskip
+Integrating the flux from y=0.2 to -0.2 and x=0.4 to -0.4 and using the equation $M=\frac{g S_\nu d^2}{\kappa_\nu B_\nu(T_d)}$ where g is the gas/dust mass ratio S$_\nu$ is the integrated flux, d is the distance to the source, $\kappa_\nu$ is the dust opacity and B$_\nu(T_d)$ is the black body function for a given dust temperature \citep{Beltran2006}.
+From this, a disc mass measurement of between 0.1$\,$M$_\odot$ and 0.005$\,$M$_\odot$ was obtained, assuming temperatures of between 40-400K, showing that the disc is not optically thin to millimetre wavelengths.
+This underestimate of the disc mass by at least a factor of 4 shows that in young, massive discs such as those we are investigating, longer wavelength continuum observations are neccesary for determining the disc mass.\smallskip
 

### 2013-03-25 young_pp_discs.tex
all changes from co-authors made

@@
 
-\date{Jan 2013}
+\date{Mar 2013}
 
@@
 \begin{abstract}
-The formation and earliest stages of protoplanetary discs are still lacking observational constraints.
-ALMA will soon revolutionise this field, therefore it is important to provide predictions and help the interpretation of future high sensitivity and high angular resolution observations.
+The formation and earliest stages of protoplanetary discs poorly constrained by observations.
+ALMA will soon revolutionise this field.
+Therefore, it is important to provide predictions which will be valuable for the interpretation of future high sensitivity and high angular resolution observations.
 Here we present simulated ALMA observations based on radiative transfer modelling of a relatively massive (0.39 M$_{\odot}$) self-gravitating disc embedded in a 10\,M$_{\odot}$ dense core, with structure similar to the pre-stellar core L1544.
-We focus on simple species and conclude that  C$^{17}$O 3$\rightarrow$2, HCO$^+$ 3$\rightarrow$2, OCS 26$\rightarrow$25 and H$_2$CO 4$_{04}\rightarrow$3$_{03}$ lines together allow for measurements of the disc structure and kinematics at all scales.
+We focus on simple species and conclude that  C$^{17}$O 3$\rightarrow$2, HCO$^+$ 3$\rightarrow$2, OCS 26$\rightarrow$25 and H$_2$CO 4$_{04}\rightarrow$3$_{03}$ lines can be used to probe the disc structure and kinematics at all scales.
 \end{abstract}
@@
 
-The formation and early evolution of protoplanetary discs around solar-type and low-mass protostars has little observational support, despite of the fast growing list of theoretical models on the dynamical evolution of star forming dense cores (e.g.
+Currently few observations constrain the formation and early evolution of protoplanetary discs around solar-type and low-mass protostars, despite of the fast growing list of theoretical models on the dynamical evolution of star forming dense cores (e.
+g.
 \citealt{Krasnopolsky2011,Machida2011,Braiding2012,Joos2013}).
 The reason for this is that young protostars are surrounded by thick envelopes and power energetic outflows.
-Thus, observations of the young discs, predicted to have sizes of about 100\,au and masses as large as 10\% the original core mass (e.g.
-\citealt*{Joos2012,Hayfield2011,Machida2011}), are challenging.
-The use of sensitive interferometers is needed to achieve high angular resolution and spatially/spectrally disentangle the various disc, envelope and outflow components as well to filter out the extended emission tracing the envelope material.
+Thus, observations of the young discs, predicted to have sizes of about 100\,au and masses as large as 10 percent the original core mass (e.
+g.\citealt*{Joos2012,Hayfield2011,Machida2011}), are challenging.
+Sensitive interferometers are needed to achieve high angular resolution and spatially/spectrally disentangle the various disc, envelope and outflow components as well as to filter out the extended emission tracing the envelope material.
 \smallskip
 
-After the pioneer work of, e.g., \citet{Chandler1995,Brown2000,Looney2000}, recent interferometric observations have discovered compact embedded discs in a sample of Class 0 sources (as defined by \citealt{Andre1999}), finding masses between 0.4 and  $>$1 M$_{\odot}$ \citep{Jorgensen2007,Jorgensen2009,Enoch2011}.
-A 130\,au disc was discovered toward a Class 0 source in Perseus, using the Jansky Very Large Array (JVLA) to observe NH$_3$ \citep{Choi2007}.
+After the pioneering work of, e.
+g., \citet{Chandler1995,Brown2000,Looney2000}, recent interferometric observations have discovered compact embedded discs in a sample of Class 0 sources (as defined by \citealt{Andre1999}), finding masses between 0.4 and  $>$1 M$_{\odot}$ \citep{Jorgensen2007,Jorgensen2009,Enoch2011}.
+A 130\,au disc was discovered in NH$_3$ emission toward a Class 0 source in Perseus, with the Jansky Very Large Array (JVLA) \citep{Choi2007}.
 \citet{Pineda2012} observed methyl formate (HCOOCH$_3$) with the Atacama Large Millimetre/sub-millimetre Array (ALMA) and found evidence of rotation toward one of the proto-binary Class 0 sources embedded in IRAS 16293-2422.
@@
 \citet{Persson2012} observed H$_2^{18}$O with ALMA toward the same source and found evidence of relatively large ($\ga$100\,K) excitation temperatures, as well as a HDO/H$_2$O abundance ratio close to that measured on Earth's oceans and Jupiter-family comets \citep{Hartogh2012}.
-\citet{Zapata2013} used ALMA to observe a disc of size $\sim$50$\,$au in the other Class 0 source in IRAS 16293-2422 and detected infall towards this disc as inverse P-Cygni profiles in HCN and CH$_3$OH.
+\citet{Zapata2013} used ALMA to observe a disc of size $\sim$50$\,$au in the other Class 0 source in IRAS 16293-2422 and detected inverse P-Cygni profiles in HCN and CH$_3$OH which indicate infall towards the disc.
 When ALMA is completed, it will be finally possible to spatially resolve these young discs and, for the first time, put stringent constraints on the theoretical models mentioned previously.
@@
 Simulated observations of gravitationally unstable discs have already been performed to study the continuum emission, measure the structure and investigate possible fragmentation \citep{Cossins2010,Ruge2013}.
-Molecular line emission from massive discs has been simulated by \citet{Krumholz2007}, assuming local thermodynamic equilibrium (LTE).
-In this paper, we focus on the self-gravitating discs of \citet{Boley2008}, where episodic heating induced by spiral shocks is present.
-This may be a good representation of the earliest phases of protoplanetary discs and an alternative to the young ``static'' discs studied by, e.g., \citet{Visser2009,Visser2011}.
-As shown by \citet{Ilee2011}, hereafter I2011, the spiral shocks cause desorption of volatiles from dust icy mantles and trigger gas-phase chemical reactions with activation energies, too high to occur at lower temperatures.
+Molecular line emission from massive discs has been simulated by \citet{Krumholz2007}, who assumed local thermodynamic equilibrium (LTE).
+In this paper, we focus on the self-gravitating discs of \citet{Boley2008}, in which episodic heating induced by spiral shocks is present.
+This may be a good representation of the earliest phases of protoplanetary discs and an alternative to the young ``static'' discs studied by, e.
+g.
+\citet{Visser2009,Visser2011}.
+As shown by \citet{Ilee2011}, hereafter I2011, the spiral shocks cause desorption of volatiles from dust icy mantles and trigger gas-phase chemical reactions with activation energies that retard the reaction at lower temperatures.
 These processes produce clear chemical signatures of the disc dynamics.
-With the use of non-LTE 3D radiative transfer modelling, we perform simulated ALMA observations of the disc studied by I2011 and identify the best tracers of the physical structure of self-gravitating discs.
+With the use of non-LTE 3D radiative transfer modelling, we have simulated ALMA observations of the disc studied by I2011 and identify the best tracers of the physical structure of self-gravitating discs.
 The physical, chemical and radiative transfer models are described in Sect.\,\ref{sec:description_model}.
@@
  \includegraphics[width=84mm]{Figures/model/rotational_velocities.eps}
- \caption{Azimuthaly averaged rotational velocity in the disc mid-plane. The best fit curve follows the equation $\frac{31.5}{\sqrt{x+1.68}}+0.518$ .}
+ \caption{Azimuthaly averaged rotational velocity in the disc mid-plane. The best fit curve follows the equation$V_{rot}\frac{31.5}{\sqrt{R+1.68}}+0.518$ .}
  \label{velocity}
@@
  \caption{{\bf Left:} A 3D plot of log number density (cm$^{-3}$) showing the spiral structure in the xy plane and scale height of the disc.
-{\bf Right:} The 3D temperature (K) structure of the disc; regions cooler than 40$\,$K are not shown in 3D, highlighting the narrow central region containing hot material.}
+{\bf Right:} The 3D temperature (K) structure of the disc; regions cooler than 40$\,$K are not shown in 3D, in order to highlight the narrow central region containing hot material.}
  \label{rhoT} 
@@
 \ref{rhoT}).
-For the non-LTE 3D radiative transfer modelling presented here, we interpolate the I2011 simulation output on to a 256$\times$256$\times$64 Cartesian grid with spatial resolution of 0.5$\,$au in x, y, and z and sample from this to create the unstructured radiative transfer grid (see section \ref{subsec:gridding}).
+For the non-LTE 3D radiative transfer modelling presented here, we interpolate the I2011 simulation output on to a 256$\times$256$\times$64 Cartesian grid with spatial resolution of 0.5$\,$au in x, y and z and sample from this to create the unstructured radiative transfer grid (see section \ref{subsec:gridding}).
 As in the hydrodynamics simulation, the dust and gas temperatures are assumed to be in equilibrium within the disc and a gas to dust mass ratio of 100 is used throughout the entirety of the model.
@@
 Chemical abundances in the disc were taken from I2011, who followed gas-grain chemical processes during the dynamical evolution of the disc.
-As described in I2011, the hydrodynamical simulation included Lagrangian tracer fluid elements in addition to solving the equations of hydrodynamics on an Eulerian grid.
+As described in I2011, the hydrodynamical simulation included Lagrangian tracer fluid elements in addition to the solution of the equations of hydrodynamics on an Eulerian grid.
 These fluid elements were used to record the thermal history of the gas as material passed through and between the spiral structure.
 I2011 used this time evolution information from fluid elements to calculate the abundances of 125 species, related by 1334 reactions.
-These abundances were then interpolated by I2011 on to a Cartesian grid with cell sizes 2.2$\times$2.2$\times$0.22$\,$au$^3$ in x, y, and z to reveal the morphology of the disc as seen by different molecular species.
+These abundances were then interpolated by I2011 on to a Cartesian grid with cell sizes 2.2$\times$2.2$\times$0.22$\,$au$^3$ in x, y and z to reveal the morphology of the disc as seen by different molecular species.
 From these we selected the four species which appear to trace different regions of the disc: the inner 30\,au (OCS), the inner 40\,au (H$_2$CO),  the region between $\simeq$40 and 60\,au (HCO$^+$) and the entirety of the disc (C$^{17}$O) (see fig.
@@
 As discussed in the results section \ref{sec:model_results}, abundances have been adopted based on values measured toward similar objects.
-The molecular data used here for the radiative transfer is taken from the Leiden Atomic and Molecular DAtabase (LAMDA) (\citealt{Schoier2005} http://home.strw.leidenuniv.nl/$\sim$moldata/).
+The molecular data used here for the radiative transfer are taken from the Leiden Atomic and Molecular DAtabase (LAMDA) (\citealt{Schoier2005} http://home.strw.leidenuniv.nl/$\sim$moldata/).
 
@@
 These points are then smoothed by Lloyd's algorithm \citep{Lloyd1982} in order to minimise the variation in distance between points whilst keeping the same underlying distribution.
-These points are then connected by Delaunay triangulation\footnote{For three dimensions, Delaunay triangulation means that if four points are connected into a tetrahedron, the sphere circumscribing these four points contains no other points.
-It can be shown that this connection is unique for a given set of points.} and it is down these paths that photon propagation is restricted (fig.
+These points are then connected by Delaunay triangulation and it is between the points connected by this method that photon are allowed to propagate (fig.
 \ref{grid}).
@@
 This is repeated 20 times with the populations of each level converging towards a single value.
-This number of iterations is sufficient for the signal to noise ratio of the level populations (as defined in \citealt{Brinch2010}) to exceed 1000 in 99\% of the points, ensuring that the simulation has converged on a stable level population.
+This number of iterations is sufficient for the signal to noise ratio of the level populations (as defined in \citealt{Brinch2010}) to exceed 1000 for 99\% of the points, ensuring that the simulation has converged on a stable level population.
 After 20 iterations the model is ray-traced in order to produce synthetic brightness maps.
-The average of ten separate runs was taken to minimise the artifacts in the output images, resulting from the grid construction (Fig.
+The average of ten separate runs was taken to minimise the artefacts in the output images, resulting from the grid construction (Fig.
 \ref{averages}).
@@
 In order to construct the grid, candidate points are randomly selected from the volume to be simulated.
-These candidates then have their density and molecular density compared against a reference point in order to decide if the point is to be used in the grid or not.
-Candidate grid points are selected at random in cylindrical coordinates, linearly spaced in z and $\theta$ and logarithmically spaced in r.
+These candidates then have their H$_2$ number density, and the number density of the molecular spieces being simulated, compared against those of a reference point in order to decide if the candidate point is to be used in the grid or not.
+Candidate grid points are selected at random in a cylindrical coordinates that is linearly spaced in z and $\theta$ and logarithmically spaced in r.
 For each point to be selected, a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) as a threshold.
 After selection of random coordinates, the hydrogen density and molecular density at the candidate point (n and m, respectively) are compared against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$).
-If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use, otherwise another r, $\theta$, z co-ordinate is selected and this becomes the candidate point.
-The function comparing the candidate point to the reference point and the candidate point distribution were selected empirically to sample all scales while ensuring that the majority of points are located in the inner disc where the density is higher.
-20\% of these points are forced to be at radii greater than $\sqrt{R_{min}R_{max}}$ (where $R_{min}$ and $R_{max}$ are the inner and outer radius of the model) in order to stop too many of the selected points clustering in the high density disc and leaving the envelope under sampled.
+If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use.
+Otherwise another r, $\theta$, z co-ordinate is selected and it becomes the candidate point.
+20\% of these selected points are forced to be at radii greater than $\sqrt{R_{min}R_{max}}$ (where $R_{min}$ and $R_{max}$ are the inner and outer radii of the model) in order to stop too many of the selected points clustering in the high density disc and leaving the envelope under sampled.
 In addition to this method of selection, 5\% of the points are linearly distributed in x, y and z with no bias with regards to density or abundance.
@@
 \ref{points} for an example of the points distribution in r, z.
+The function comparing the candidate point to the reference point and the candidate point distribution were selected empirically to sample all scales while ensuring that the majority of points are located in the inner disc where the density is higher.
 \smallskip
@@
  \caption{{\bf Left:} A 300$\,$GHz continuum image of the model, created from the average of ten LIME runs.
-{\bf Right:} the output of a single radiative transfer simulation, with artifacts due to finite gridding.}
+{\bf Right:} the output of a single radiative transfer simulation, with artefacts due to finite gridding.}
  \label{averages}
@@
 
-Simulations are limited to molecules for which we have abundances in both the disc and envelope, and also have calculated Einstein and collisional coefficients.
-In the envelope, the HCO$^+$ abundance profile follows the H$_2$O profile of L1544 \citep{Caselli2012}, scaled so the maximum is 1$\times$10$^{-8}$ (assuming, for simplicity, that photodissociation and freeze-out affect these two species in a similar way).
-For H$_2$CO, a step profile was considered, with a fractional abundance of 1.5$\times$10$^{-8}$ at radii greater than 0.04$\,$pc and 1.5$\times$10$^{-9}$ inside it \citep{Young2004}.
+Simulations are limited to molecules for which we have abundances in both the disc and envelope, and also have reliable Einstein and collisional coefficients.
+In the envelope, the HCO$^+$ abundance profile follows the H$_2$O profile of L1544 \citep{Caselli2012}, scaled so the maximum is 1$\times$10$^{-8}$.
+For H$_2$CO, a step profile was considered, with a fractional abundance of 1.5$\times$10$^{-8}$ at radii greater than 0.04$\,$pc and 1.5$\times$10$^{-9}$ at smaller radii \citep{Young2004}.
 For OCS we adopted a constant abundance of 1.9$\times$10$^{-9}$ \citep{Ren2011}.
-The C$^{17}$O abundance profile in the envelope follows the CO profile calculated for L1544 by KC2010, scaled by the $^{17}$O/$^{16}$O elemental abundance.
-These estimates for the abundances in the envelope are simplistic, however, as seen in section \ref{sec:alma_predictions}, the envelope contribution to the line is very limited in velocity and can be spectrally disentangled from the disc contribution.\smallskip
+The C$^{17}$O abundance profile in the envelope follows the CO profile calculated for L1544 by KC2010, scaled by the $^{17}$O/$^{16}$O isotope abundance.
+These estimates for the abundances in the envelope are simplistic.
+However, as seen in section \ref{sec:alma_predictions}, the envelope contribution to the line is very limited in velocity and can be spectrally disentangled from the disc contribution.\smallskip
 
@@
 The inclination angle was varied from 15$^\circ$ to 75$^\circ$ relative to the edge on case.
-In the following, we will show the 30$^\circ$ case, while the 15$^\circ$ is discussed in section \ref{sec:alma_predictions}.
-Other inclinations are shown in appendix \ref{sec:other_inc}.
 From these simulated observations, integrated intensity maps, intensity weighted velocity maps and position velocity diagrams were created.
-The integrated intensity and  intensity weighted velocity maps (fig.s \ref{sim_all}, and \ref{mom0_maps}) were created by integrating between -12.5 to -0.5$\,$km$\,$s$^{-1}$ and +0.5 to +12.5$\,$km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, which can be seen in some PV diagrams as the strong absorption feature at all positions around zero velocity (see section \ref{sec:alma_predictions}).
+The integrated intensity and  intensity weighted velocity maps (figs.
+\ref{sim_all}, and \ref{mom0_maps}) were from -12.5 to -0.5$\,$km$\,$s$^{-1}$ and +0.5 to +12.5$\,$km$\,$s$^{-1}$ to avoid domination by the contribution from the envelope, which can be seen in some PV diagrams as the strong absorption feature at all positions around zero velocity (see section \ref{sec:alma_predictions}).
 Intensity weighted velocity maps are shown with a cut-off of 3$\sigma$ as described in section \ref{sec:alma_predictions}.\smallskip
@@
 {\bf Right:} Intensity weighted velocity maps.
-The spiral structure in different regions of the disc is highlighted by looking at different molecular lines.
+The spiral structures in different regions of the disc are highlighted by different molecular lines.
 From top to bottom the lines displayed are: OCS 26$\rightarrow$25, H$_2$CO 4$_{04}$$\rightarrow$3$_{03}$, C$^{17}$O 3$\rightarrow$2 and HCO$^+$ 3$\rightarrow$2.
-All maps are integrated over -12.5 to -0.5 and 0.5 to 12.5 km$\,$s$^{-1}$ in order to avoid the envelope contribution.}
+All maps are obtained from integration over -12.5 to -0.5 and 0.5 to 12.5 km$\,$s$^{-1}$ in order to avoid the envelope contribution.}
  \label{sim_all}
@@
 \ref{sim_all}).
-As OCS is not seen in outflows (e.g.
+As OCS is not seen in outflows (e.
+g.
 \citealt{Stanke2007}, \citealt{VDTak2003}), it can be used to measure the rotation of the central part of the disc without contamination from shocked material along the outflow.
-The OCS lines are unique amongst the lines simulated in that they trace radii $<$16$\,$au, even smaller than the extent of the OCS column density distribution shown in fig.\ref{Chemistry}.
+The OCS lines are unique amongst the lines simulated in that they trace radii $<$16$\,$au, even smaller than the extent of the OCS column density distribution shown in fig.
+\ref{Chemistry}.
 This is because the OCS line, which has the highest upper energy level among the selected transitions, traces only the hottest and densest regions of the disc where the high energy states are populated.
@@
 The exception to this is towards the centre of the disc where the hole in the hot, dense mid-plane means that there is little continuum to be absorbed.
-However, this may be an artefact of our simplistic treatment of the inner hole, given that we neglect the presence of the protostar and other hot material within the central 2$\,$au.
-Thus, we expect absorption to be also observed toward the central region of the disc.\smallskip
+However, this may be an artefact of our treatment of the inner hole, given that we neglect the presence of the protostar and other hot material within the central 2$\,$au.
+Thus, we expect absorption also to be observed toward the central region of the disc.\smallskip
 
@@
 
+\begin{figure*}
+ \includegraphics[width=110mm]{Figures/sim/appendix_inclinations2.eps}
+ \caption{C$^{17}$O 3$\rightarrow$2 {\bf left:} Continuum subtracted integrated intensity map (in K$\,$km$\,$s$^{-1}$).
+{\bf Centre:} Intensity weighted velocity map (in km$\,$s$^{-1}$).
+{\bf Right:} Position-velocity diagram with intensities in K.
+The inclinations for which results are shown from top to bottom are: 75$^\circ$, 45$^\circ$, 30$^\circ$ and 15$^\circ$ to edge on.}
+ \label{other_inc}
+\end{figure*}
+
+Simulations at inclinations other than 30$^\circ$ were also performed with C$^{17}$O.
+Fig.
+\ref{other_inc} shows the C$^{17}$O 3$\rightarrow$2 line in the same physical model but at 15$^\circ$, 30$^\circ$, 45$^\circ$ and 75$^\circ$ to edge on.
+At 15$^\circ$ to edge on we can still see some structure in the integrated intensity map and the structure is also visible in the position velocity diagram.
+At larger inclinations it gets more difficult to obtain any kinematic information but the physical structure of the disc becomes clearer.
+
 \section{Predictions for ALMA} \label{sec:alma_predictions}
 
-In order to make predictions on the observability of the synthetic brightness maps, the Common Astronomy Software Applications package (CASA) was used to simulate observations with the completed ALMA in the 26th most extended configuration (out of a total of 28).
+In order to make predictions of the observability of the features for which we have constructed synthetic brightness maps, the Common Astronomy Software Applications package (CASA) was used to simulate observations with the completed ALMA in the 26th most extended configuration (out of a total of 28).
 The longest baseline of this configuration is 14.4\,km and the beam sizes range between 0.02 and 0.03 arcseconds at the selected frequencies.
@@
   \begin{minipage}{90mm}
-    \caption{Line sensitivities obtained with ALMA after 6 hours integration time with velocity resolution of 400$\,$m\,s$^{-1}$, using the ALMA on-line sensitivity calculator.}
+    \caption{Line sensitivities obtained with ALMA after 6 hours integration time with velocity resolution of 400$\,$m\,s$^{-1}$, obtained with the ALMA on-line sensitivity calculator.}
     \label{sigmas}
@@
  \includegraphics[width=168mm]{Figures/sim/channel_map-2.eps} 
- \caption{H$_2$CO 4$_{04}\rightarrow$3$_{03}$ channel maps as simulated by CASA.
+ \caption{H$_2$CO 4$_{04}\rightarrow$3$_{03}$ channel maps as simulated with CASA.
 The contours start at 0.35 mJy$\,$beam$^{-1}\,$km$\,$s$^{-1}$  and are in steps of 0.35 mJy$\,$beam$^{-1}\,$km$\,$s$^{-1}$ (absorption in blue, emission in red).
 Overlaid on the 1mm continuum emission.
-Each map integrates over 2.4 km$\,$s$^{-1}$ with the top left from -10.8 to -8.4 km$\,$s$^{-1}$ to the bottom left ranging from 8.4 to 10.8 km$\,$s$^{-1}$}
+the integration range for each map is 2.4 km$\,$s$^{-1}$, for the top left the range is from -10.8 to -8.4 km$\,$s$^{-1}$ and for the bottom right the range is from 8.4 to 10.8 km$\,$s$^{-1}$}
  \label{h2co_chanmap}
@@
 The spiral structure of the disc is clearly visible at this inclination and and it becomes clearer at angles closer to face-on.
-Integrating the flux from y=0.2 to -0.2 and x=0.4 to -0.4 and using the equation $M=\frac{g S_\nu d^2}{\kappa_\nu B_\nu(T_d)}$ where g is the gas/dust mass ratio S$_\nu$ is the integrated flux, d is the distance to the source, $\kappa_\nu$ is the dust opacity and B$_\nu(T_d)$ is the black body function for a given dust temperature \citep{Beltran2006}.
-From this, a disc mass measurement of between 0.1$\,$M$_\odot$ and 0.005$\,$M$_\odot$ was obtained, assuming temperatures of between 40-400K, showing that the disc is not optically thin to millimetre wavelengths.
+A mass estimate for the disc was calculated using the equation $M=g S_\nu d^2/\kappa_\nu B_\nu(T_d)$ where g is the gas/dust mass ratio S$_\nu$ is the integrated flux, d is the distance to the source, $\kappa_\nu$ is the dust opacity and B$_\nu(T_d)$ is the black body function for a given dust temperature \citep{Beltran2006}.
+From this, a disc mass measurement of 0.1$\,$M$_\odot$ was obtained by assuming a dust temperature of 40K, and a measurement of 0.005$\,$M$_\odot$ was obtained by using 400K.
+The flux was integrated from y=0.2 to -0.2 and x=0.4 to -0.4.
+This shows that the disc is not optically thin to millimetre wavelengths.
 This underestimate of the disc mass by at least a factor of 4 shows that in young, massive discs such as those we are investigating, longer wavelength continuum observations are neccesary for determining the disc mass.\smallskip
@@
 Fig.
-\ref{15deg} shows the C$^{17}$O 3$\rightarrow$2 integrated intensity and PV diagram for an inclination angle of 15$^\circ$ to edge on, showing that spiral structure can be clearly seen in the position velocity diagram even at low inclinations.
-The ``finger-like'' structures in the PV diagram are similar to those seen in observations of the Milky Way and in simulations of spirals in the Milky Way (e.g.
+\ref{15deg} shows the C$^{17}$O 3$\rightarrow$2 integrated intensity and PV diagram for an inclination angle of 15$^\circ$ to edge on.
+Spiral structure can be clearly seen in the position velocity diagram even at low inclinations.
+The ``finger-like'' structures in the PV diagram are similar to those seen in observations of the Milky Way and in simulations of spirals in the Milky Way (e.
+g.
 \citealt{Bissantz2003}).
-Although the detail of the spiral structure (number of arms, pitch angle etc.) is difficult to gauge from such a PV diagram, high spectral and angular resolution observations can definitely unveil their presence and thus find gravitationally unstable discs.
+Although the detail of the spiral structure (number of arms, pitch angle etc.) is difficult to gauge from such a PV diagram, high spectral and angular resolution observations can definitely unveil their presence and thus be used to find gravitationally unstable discs.
 \smallskip
@@
 Emission is in red contours, absorption in blue.
-The dots refer to the spectra shown in fig.
-\ref{spectra}.}
+The coloured dots refer to the positions from which the spectra shown in fig.
+\ref{spectra} are taken.}
 \label{mom0_maps}
@@
 As expected from the radiative transfer results, observations of these transitions can probe different regions of the disc, from the OCS line tracing the innermost regions, to the HCO$^+$ line showing the outer regions.
-Thus, the high sensitivity and angular resolution of ALMA will allow detection of spiral structure both in the continuum emission as well as  in appropriately selected molecular transitions.
-Different molecules can trace different regions of the disc.\smallskip
+Thus, the high sensitivity and angular resolution of ALMA will allow detection of spiral structure both in the continuum emission as well as  in appropriately selected molecular transitions.\smallskip
 
@@
 The green curves in each panel of fig.
-\ref{pvs} display the best fit rotation curve of the physical model (see fig.
-\ref{velocity}), showing that the rotation profile of the disc can be well constrained using kinematic information gathered from species tracing different regions of the disc.\smallskip
+\ref{pvs} display the best fit rotation curve for the physical model (see fig.
+\ref{velocity}), showing that the rotation profile of the disc can be constrained by kinematic information gathered from species tracing different regions of the disc.\smallskip
 
@@
 \ref{mom0_maps} (the pink, green and cyan curves are taken from the locations marked by the dots of the same colour).
-In each diagram, the three spectra are taken from three positions on the Y=0 axis, one is at X=0 (green) and the other 2 are from x=$\pm$ N (plus yellow, minus pink) where N is the distance from the centre: 10 au for OCS, 20 au for H$_2$CO, 28 au for C$^{17}$O, 38 au for HCO$^+$.}
+In each diagram, the three spectra are taken from three positions on the Y=0 axis, one is at X=0 (green) and the other 2 are from x=$\pm\,$N (plus yellow, minus pink) where N is the distance from the centre: 10 au for OCS, 20 au for H$_2$CO, 28 au for C$^{17}$O, 38 au for HCO$^+$.}
  \label{spectra}
@@
 
-Spectra are presented in Fig.
-\ref{spectra}, extracted from the maps in fig.
-\ref{mom0_maps} at the positions indicated by the corresponding coloured dots along the Y=0 axis.
-As with all the CASA simulated images, these spectra were simulated with an ALMA window of total bandwidth 938$\,$MHz, giving velocity resolutions of between 418 and 527\,m\,s$^{-1}$.
-The most notable thing about these spectral features is that they are not symmetric about the disc centre.
+The spectra presented in Fig.
+\ref{spectra} were extracted from the maps in fig.
+\ref{mom0_maps} for the positions indicated by the corresponding coloured dots along the Y=0 axis.
+As with all the CASA simulated images, these spectra were simulated with an ALMA window with total bandwidth 938$\,$MHz, giving velocity resolutions of between 418 and 527\,m\,s$^{-1}$.
+Very notably, these spectral features are not symmetric about the disc centre.
 For example, C$^{17}$O(3--2) has a significantly stronger blueshifted absorption, due to the presence of a spiral arm along the same line of sight.
@@
 
-In this paper we have presented radiative transfer simulations of a hybrid model comprising a 0.39$\, M_\odot$ self gravitating disc with radius 64$\,$au showing spiral density waves, surrounded by an envelope simulated as a contracting 10$\,M_\odot$ BE-sphere.
+In this paper we have presented radiative transfer simulations of a hybrid model comprising a 0.39$\, M_\odot$ self gravitating disc with a radius of 64$\,$au and spiral density waves, surrounded by an envelope that is a contracting 10$\,M_\odot$ BE-sphere.
 The main results of these simulations are as follows:\newline
-$\bullet$ CASA simulations of this model show that at a distance of 100$\,$pc, extraction of kinematics and structural information from the continuum and molecular lines is possible with ALMA band 7.\\
+$\bullet$ CASA simulations of this model show that at a distance of 100$\,$pc, extraction of kinematic and structural information from the continuum and molecular lines is possible with ALMA band 7.\\
 $\bullet$ Our simulations show that molecular features are predominantly seen in absorption against the hot mid-plane of self-gravitating protoplanetary discs, with emission only being seen where voids in the structure of the disc do not provide a bright continuum source to be absorbed.\\
@@
 $\bullet$ The lines studied (OCS 26$\rightarrow$25, H$_2$CO 4$_{04}$$\rightarrow$3$_{03}$, C$^{17}$O 3$\rightarrow$2 and HCO$^+$ 3$\rightarrow$2) taken together allow all regions of the disc to be sampled and the rotation of the disc to be constrained from the inner edge to the outer edge.\\
-$\bullet$ Spiral structure in young embedded discs are detectable at a wide range of inclination angles, they can be resolved spatially at angles close to face on and can be inferred from position velocity diagrams at low inclination angles.\smallskip
+$\bullet$ Spiral structures in young embedded discs are detectable at a wide range of inclination angles, they can be resolved spatially at angles close to face on and can be inferred from position velocity diagrams at low inclination angles.\smallskip
 
-One assumption made in this model is that the gas and dust are in thermal equilibrium in the disc.
+One assumption underpoinning this model is that the gas and dust are in thermal equilibrium in the disc.
 If they are not and the dust is significantly cooler than the gas then transitions may not show up in absorption.
-However, the large volume densities are expected to provide an efficient dust-gas coupling.
+However, the large volume densities are expected to provide efficient dust-gas coupling.
 Outflows could contaminate line profiles of  those species  which commonly trace outflows, such as CO and HCO$^+$.
@@
 These results demonstrate that ALMA will be able to probe the very earliest stages of circumstellar discs which feed the growing protostar and eventually will evolve in a planetary system.
-Our results show that ALMA observations in band 7 will be able to assess whether or not these young discs are gravitationally unstable and test theories of pre-stellar $\rightarrow$ protostellar core evolution.
-If such gravitationally instabilities exist they would have significant implications on the evolution of the disc, such as fragmentation, planetesimal formation \citep{Boley2009,Johnson2013,Gibbons2012} and the chemical evolution in the disc (I2011).
+Our results show that ALMA observations in band 7 will allow the assessment of whether or not these young discs are gravitationally unstable and test theories of pre-stellar $\rightarrow$ protostellar core evolution.
+If such gravitationally instabilities exist they will have significant implications for the evolution of the disc.
+For example the will affect fragmentation, planetesimal formation \citep{Boley2009,Johnson2013,Gibbons2012} and the chemical evolution in the disc (I2011).
 
@@
 \bibliography{new_bib}
-
-\appendix
-
-\section{Other Inclinations} \label{sec:other_inc}
-
-\begin{figure*}
- \includegraphics[width=110mm]{Figures/sim/appendix_inclinations2.eps}
-
- \caption{C$^{17}$O 3$\rightarrow$2 {\bf left:} Continuum subtracted integrated intensity map (in K$\,$km$\,$s$^{-1}$).
-{\bf Centre:} Intensity weighted velocity map (in km$\,$s$^{-1}$).
-{\bf Right:} Position-velocity diagram with intensities in K.
-The inclinations shown from top to bottom are 75$^\circ$, 45$^\circ$, 30$^\circ$ and 15$^\circ$ to edge on.}
-\end{figure*}
-
-Simulations at inclinations other than 30$^\circ$ were also performed with C$^{17}$O.
-Figs.
-B1-3 show the C$^{17}$O 3$\rightarrow$2 line in the same physical model but at 15$^\circ$, 30$^\circ$, 45$^\circ$ and 75$^\circ$ to edge on.
-At 15$^\circ$ to edge on we can still see some structure in the integrated intensity map and the structure is also visible in the position velocity diagram.
-At larger inclinations it gets more difficult to obtain any kinematic information but the physical structure of the disc becomes clearer.
-
 \bsp

### 2013-05-03 young_pp_discs.tex
neatened up figures, made first set of reviwer comments changes

@@
 P. Caselli$^{1}$,
-J. D. Ilee$^{1}$,
+J. D. Ilee$^{5,1}$,
 A. C. Boley$^{2}$,
@@
 {\small{\it$^{3}$Department of Astronomy, Indiana University, 727 East 3rd Street, Swain West 319, Bloomington, IN 47405, USA,}}\\
-{\small{\it$^{4}$Department of Physics \& Astronomy, University College London, London WC1E 6BT, UK}}\\}}
+{\small{\it$^{4}$Department of Physics \& Astronomy, University College London, London WC1E 6BT, UK}}\\
+{\small{\it$^{5}$School of Physics and Astronomy, University of St Andrews, North Haugh, St Andrews, KY16 9SS, UK,}}\\
+}}
 
@@
 \begin{abstract}
-The formation and earliest stages of protoplanetary discs poorly constrained by observations.
+The formation and earliest stages of protoplanetary discs remain poorly constrained by observations.
 ALMA will soon revolutionise this field.
@@
 
-Currently few observations constrain the formation and early evolution of protoplanetary discs around solar-type and low-mass protostars, despite of the fast growing list of theoretical models on the dynamical evolution of star forming dense cores (e.
+Currently few observations constrain the formation and early evolution of protoplanetary discs around solar-type and low-mass protostars, despite the fast growing list of theoretical models on the dynamical evolution of star forming dense cores (e.
 g.
@@
 Thus, observations of the young discs, predicted to have sizes of about 100\,au and masses as large as 10 percent the original core mass (e.
-g.\citealt*{Joos2012,Hayfield2011,Machida2011}), are challenging.
+g.
+\citealt{Joos2012,Hayfield2011,Machida2011}), are challenging.
 Sensitive interferometers are needed to achieve high angular resolution and spatially/spectrally disentangle the various disc, envelope and outflow components as well as to filter out the extended emission tracing the envelope material.
@@
 Fig.
-\ref{fig:l1544_model} shows the physical parameters of the core model.
-\smallskip
+\ref{fig:l1544_model} shows the physical parameters of the core model{\bf as used in an improved version of the KC2010 model (Keto et al.
+2013, in preparation).}\smallskip
 
 \begin{figure}
- \includegraphics[width=84mm]{Figures/model/L1544model_used_legend_small2.eps}
+ \includegraphics[width=84mm]{Figures/model/fig01.eps}
  \caption{The spherically symmetric model of the pre-stellar core L1544 used as the envelope of the young protoplanetary disc in the hybrid model.
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/model/rotational_velocities.eps}
- \caption{Azimuthaly averaged rotational velocity in the disc mid-plane. The best fit curve follows the equation$V_{rot}\frac{31.5}{\sqrt{R+1.68}}+0.518$ .}
+ \includegraphics[width=84mm]{Figures/model/fig02.eps}
+ \caption{Azimuthaly averaged rotational velocity in the disc mid-plane. The best fit curve follows the equation$V_{\rm rot}=\frac{31.5}{\sqrt{R+1.68}}+0.518$ .}
  \label{velocity}
@@
 \begin{figure*}
- \includegraphics[width=168mm]{Figures/model/rhoT5.eps}
+ \includegraphics[width=168mm]{Figures/model/fig03.eps}
  \caption{{\bf Left:} A 3D plot of log number density (cm$^{-3}$) showing the spiral structure in the xy plane and scale height of the disc.
@@
 \begin{figure*}
- \includegraphics[width=168mm]{Figures/model/columnDensities3.eps}
+ \includegraphics[width=168mm]{Figures/model/fig04.eps}
  \caption{Column density distributions of OCS, H$_2$CO, HCO$^+$ and CO across the disc, as calculated by I2011.
@@
 The disc structure used is from the same hydrodynamics simulation described in I2011, which is a 1$\,$M$_\odot$ protostar surrounded by a 0.39$\,$M$_\odot$ disc.
-Fig.~\ref{velocity} shows the azimuthally averaged rotational velocity in the disc plane, together with the best fit curve, which will be used in Sec.~\ref{sec:alma_predictions} to compare with position velocity diagrams.
+Fig.\ref{velocity} shows the azimuthally averaged rotational velocity in the disc plane, together with the best fit curve, which will be used in Sec.~\ref{sec:alma_predictions} to compare with position velocity diagrams.
 The system is envisaged to be at a very early stage of evolution and embedded in an envelope.
@@
 The molecular data used here for the radiative transfer are taken from the Leiden Atomic and Molecular DAtabase (LAMDA) (\citealt{Schoier2005} http://home.strw.leidenuniv.nl/$\sim$moldata/).
+\smallskip
+
+{\bf Whilest photochemistry was not included in I2011, it is unclear to what extent the radiation from the protostar will impact upon the disc, given that material infalling from the envelope and newly forming outflows will be obscuring the star.
+Column densities between upper layers of the disc and the protostar in the model used here are on the order of 10$^{23}$ cm$^{-2}$.
+This is in contrast to later stages of disc evolution where the envelope has been almost entirely cleared (e.g.
+Walsh et.
+al), in this case it is clear that the chemistry in the upper layers of the disc will be dominated by photo-chemical processes.}
 
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/model/lime3.eps}
+ \includegraphics[width=84mm]{Figures/model/fig05.eps}
  \caption{A plot of the points selected by the gridding process and the paths down which photons can propagate for points in the central r, $\theta$ plane.
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/continuum2.eps}
+ \includegraphics[width=84mm]{Figures/sim/fig06.eps}
  \caption{{\bf Left:} A 300$\,$GHz continuum image of the model, created from the average of ten LIME runs.
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/model/lime_points_rz_histo3.eps}
+ \includegraphics[width=84mm]{Figures/model/fig07.eps}
  \caption{A 2D histogram of the point distribution throughout the model. The disc and envelope can be seen as two separate entities which have to be sampled using different point distributions.}
@@
 \begin{figure*}
- \includegraphics[width=150mm]{Figures/sim/imageALL_30deg_all2.eps}
+ \includegraphics[width=150mm]{Figures/sim/fig08.eps}
  \caption{{\bf Left:} Continuum subtracted integrated intensity maps.
@@
 \begin{figure*}
- \includegraphics[width=110mm]{Figures/sim/appendix_inclinations2.eps}
+ \includegraphics[width=110mm]{Figures/sim/fig09.eps}
  \caption{C$^{17}$O 3$\rightarrow$2 {\bf left:} Continuum subtracted integrated intensity map (in K$\,$km$\,$s$^{-1}$).
@@
       OCS & 26$\rightarrow$25 & 316.15 & 205 & 0.0275 \\
+      H$_2$CO & 4$_{04}\rightarrow$3$_{03}$ &  290.62 & 34.9 & 0.0228 \\
       HCO$^+$ & 3$\rightarrow$2 & 267.56 & 25.7 & 0.0176 \\
-      H$_2$CO & 4$_{04}\rightarrow$3$_{03}$ &  290.62 & 34.9 & 0.0228 \\
       \hline
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/casa_cont_300GHz_invert2.eps}
+ \includegraphics[width=84mm]{Figures/sim/fig10.eps}
 
@@
 \begin{figure*}
- \includegraphics[width=168mm]{Figures/sim/channel_map-2.eps} 
+ \includegraphics[width=168mm]{Figures/sim/fig11.eps} 
  \caption{H$_2$CO 4$_{04}\rightarrow$3$_{03}$ channel maps as simulated with CASA.
@@
 \begin{figure}
- \includegraphics[width=84mm]{Figures/sim/casa_C17O_15deg_all3.eps}
+ \includegraphics[width=84mm]{Figures/sim/fig12.eps}
 
@@
 \begin{figure*}
- \includegraphics[width=140mm]{Figures/sim/casa_all_30deg_contSub_dots.eps}
+ \includegraphics[width=140mm]{Figures/sim/fig13.eps}
  \caption{Integrated intensity maps for the simulated observations of: {\bf Top Left:} H$_2$CO 4$_{04}\rightarrow$3$_{03}$, {\bf Top Right:} C$^{17}$O 3$\rightarrow$2, {\bf Bottom Left:} OCS 26$\rightarrow$25 and {\bf Bottom Right:} HCO$^+$ 3$\rightarrow$2.
@@
 \begin{figure*}
- \includegraphics[width=180mm]{Figures/sim/casa_all_30deg_PV_rotCurve_small2.eps}
+ \includegraphics[width=180mm]{Figures/sim/fig14.eps}
  \caption{Position velocity diagrams for each of the lines simulated with CASA. The green curve on each diagram is the best fit curve to the azimuthally averaged rotation profile from fig. 4.}
@@
 \begin{figure*}
- \includegraphics[width=168mm]{Figures/sim/casa_all_spectra2.eps}
+ \includegraphics[width=168mm]{Figures/sim/fig15.eps}
  \caption{Simulated spectra for each of the selected transitions at the positions indicated by the coloured dots in fig.
@@
 
+{\bf The disc model used does not include magnetic fields, including magnetic fields may suppress GI and spiral wave formation by slowing down or even preventing early disc growth in the case of sufficicent magnetization and alinegment between the parent cores rotation axis and maxnetic field direction (Joos et al.
+2012, Li et al.
+2013).
+This would mean that if observations similar to the ones we have descirbed are made constraints could be placed on B-field strength within cores/discs.
+\smallskip Future work including looking at the effects of material from the envelope falling onto the disc and how this affects the chemistry and line propagation, and including realistic outflows into the model.}
+
 These results demonstrate that ALMA will be able to probe the very earliest stages of circumstellar discs which feed the growing protostar and eventually will evolve in a planetary system.
-Our results show that ALMA observations in band 7 will allow the assessment of whether or not these young discs are gravitationally unstable and test theories of pre-stellar $\rightarrow$ protostellar core evolution.
-If such gravitationally instabilities exist they will have significant implications for the evolution of the disc.
+Our results show that ALMA observations in band 7 will allow the assessment of whether or not these young discs are gravitationally unstable and test theories of pre-stellar to protostellar core evolution.
+If such gravitational instabilities exist they will have significant implications for the evolution of the disc.
 For example the will affect fragmentation, planetesimal formation \citep{Boley2009,Johnson2013,Gibbons2012} and the chemical evolution in the disc (I2011).
@@
 PC and TWH acknowledge support of successive rolling grants awarded by the UK Science and Technology Funding Council.  
-TAD and JDI acknowledge studentships from the Science and Technology Facilities Council of the United Kingdom (STFC).
-The research leading to these results has received funding from the European Union FP7-2011 under grant agreement no 284405.
-TAD would like to thank Nicol Cunningham for her assistance with CASA and Christian Brinch for his radiative transfer code LIME and for guidance on using it.
+TAD and JDI acknowledge studentships from the Science and Technology Facilities Council of the United Kingdom (STFC), JDI also acknowledges funding from the European Union FP7-2011 under grant agreement no 284405.
+TAD would like to thank Nichol Cunningham for her assistance with CASA and Christian Brinch for his radiative transfer code LIME and for guidance on using it.
 

### 2013-05-03 young_pp_discs.tex
spellcheck etc

@@
 
-{\bf Whilest photochemistry was not included in I2011, it is unclear to what extent the radiation from the protostar will impact upon the disc, given that material infalling from the envelope and newly forming outflows will be obscuring the star.
-Column densities between upper layers of the disc and the protostar in the model used here are on the order of 10$^{23}$ cm$^{-2}$.
+{\bf Whilst photochemistry was not included in I2011, it is unclear to what extent the radiation from the protostar will impact upon the disc, given that material infalling from the envelope and newly forming outflows will be obscuring the star.
+Column densities between upper layers of the disc and the protostar in the model used here are on the order of 10$^{23}$ cm$^{-2}$ (is this enough to block the protostars visible and UV?).
 This is in contrast to later stages of disc evolution where the envelope has been almost entirely cleared (e.g.
@@
 In order to construct the grid, candidate points are randomly selected from the volume to be simulated.
-These candidates then have their H$_2$ number density, and the number density of the molecular spieces being simulated, compared against those of a reference point in order to decide if the candidate point is to be used in the grid or not.
+These candidates then have their H$_2$ number density, and the number density of the molecular species being simulated, compared against those of a reference point in order to decide if the candidate point is to be used in the grid or not.
 Candidate grid points are selected at random in a cylindrical coordinates that is linearly spaced in z and $\theta$ and logarithmically spaced in r.
@@
 This shows that the disc is not optically thin to millimetre wavelengths.
-This underestimate of the disc mass by at least a factor of 4 shows that in young, massive discs such as those we are investigating, longer wavelength continuum observations are neccesary for determining the disc mass.\smallskip
+This underestimate of the disc mass by at least a factor of 4 shows that in young, massive discs such as those we are investigating, longer wavelength continuum observations are necessary for determining the disc mass.\smallskip
 
@@
 
-One assumption underpoinning this model is that the gas and dust are in thermal equilibrium in the disc.
+One assumption underpinning this model is that the gas and dust are in thermal equilibrium in the disc.
 If they are not and the dust is significantly cooler than the gas then transitions may not show up in absorption.
@@
 
-{\bf The disc model used does not include magnetic fields, including magnetic fields may suppress GI and spiral wave formation by slowing down or even preventing early disc growth in the case of sufficicent magnetization and alinegment between the parent cores rotation axis and maxnetic field direction (Joos et al.
+{\bf The disc model used does not include magnetic fields, including magnetic fields may suppress GI and spiral wave formation by slowing down or even preventing early disc growth in the case of sufficient magnetisation and alignment between the parent cores rotation axis and magnetic field direction (Joos et al.
 2012, Li et al.
 2013).
-This would mean that if observations similar to the ones we have descirbed are made constraints could be placed on B-field strength within cores/discs.
-\smallskip Future work including looking at the effects of material from the envelope falling onto the disc and how this affects the chemistry and line propagation, and including realistic outflows into the model.}
+This would mean that if observations similar to the ones we have described are made constraints could be placed on B-field strength within cores/discs.
+\smallskip Futher work to improve these simulated observations would include looking at the effects of material from the envelope falling onto the disc and how this affects the chemistry and line propagation, and including realistic outflows into the model.}
 

### 2013-05-03 young_pp_discs.tex
small changes

@@
 Walsh et.
-al), in this case it is clear that the chemistry in the upper layers of the disc will be dominated by photo-chemical processes.}
+al 2012), in this case it is clear that the chemistry in the upper layers of the disc will be dominated by photo-chemical processes.}
 
@@
 This would mean that if observations similar to the ones we have described are made constraints could be placed on B-field strength within cores/discs.
-\smallskip Futher work to improve these simulated observations would include looking at the effects of material from the envelope falling onto the disc and how this affects the chemistry and line propagation, and including realistic outflows into the model.}
+\smallskip }
+{\bf Futher work to improve these simulated observations would include looking at the effects of material from the envelope falling onto the disc and how this affects the chemistry and line propagation, and including realistic outflows into the model.}
 

### 2013-05-07 young_pp_discs.tex
ref comments addressed

--- 2013-05-03 young_pp_discs.tex
@@
 The KC2010 model follows the dynamical, chemical and thermal evolution of a contracting Bonnor-Ebert sphere \citep{Bonnor1956,Ebert1957} with total mass of 10\,M$_{\odot}$, until it reaches the density, temperature and velocity profiles which best match observations.
-The pre-stellar core model adopted here contains slight modifications due to the inclusion of oxygen cooling in the outer regions of the cloud, where CO is mostly photodissociated \citep{Caselli2012}.
+The pre-stellar core model adopted here contains slight modifications compared to KC2010 due to the inclusion of oxygen cooling in the outer regions of the cloud (Keto et al.
+2013, in preparation), where CO is mostly photodissociated \citep{Caselli2012}.
 Fig.
-\ref{fig:l1544_model} shows the physical parameters of the core model{\bf as used in an improved version of the KC2010 model (Keto et al.
-2013, in preparation).}\smallskip
+\ref{fig:l1544_model} shows the physical parameters of the core model adopted here.
+\smallskip
 
@@
 The pre-stellar core structure is maintained down to a radius of 80\,au, within which the model of the young protoplanetary disc is used.
-The disc structure used is from the same hydrodynamics simulation described in I2011, which is a 1$\,$M$_\odot$ protostar surrounded by a 0.39$\,$M$_\odot$ disc.
+The disc structure is taken from the same hydrodynamics simulation of a 1$\,$M$_\odot$ protostar surrounded by a 0.39$\,$M$_\odot$ disc, described in I2011.
 Fig.\ref{velocity} shows the azimuthally averaged rotational velocity in the disc plane, together with the best fit curve, which will be used in Sec.~\ref{sec:alma_predictions} to compare with position velocity diagrams.
@@
 The hydrodynamics simulation is run with a proper equation of state for molecular hydrogen \citep{Boley2007}.
-The star is allowed to move freely in response to disc torques, and radiative cooling is included \citep{Boley2009}.
+The protostar is allowed to move freely in response to disc torques, and radiative cooling is included \citep{Boley2009}.
 The self-gravitating disc exhibits prominent spiral structure, with H$_2$ number densities in the disc ranging from 10$^4$-10$^{13}$ cm$^{-3}$ and temperatures from 30-400 K (fig.
 \ref{rhoT}).
+{\bf The disc model does not include magnetic fields, which may suppress gravitational instability and spiral wave formation by slowing down or even preventing early disc growth in the case of sufficient magnetisation and alignment between the parent cores rotation axis and magnetic field direction \citep{Joos2012,Li2013}.
+Thus, the observation of spiral structure would provide strong constraints on the dynamical state of discs.
+\smallskip }
+
 For the non-LTE 3D radiative transfer modelling presented here, we interpolate the I2011 simulation output on to a 256$\times$256$\times$64 Cartesian grid with spatial resolution of 0.5$\,$au in x, y and z and sample from this to create the unstructured radiative transfer grid (see section \ref{subsec:gridding}).
 As in the hydrodynamics simulation, the dust and gas temperatures are assumed to be in equilibrium within the disc and a gas to dust mass ratio of 100 is used throughout the entirety of the model.
-The dust opacities were adopted from \citet{Ossenkopf1994} and refer to dust grains with thick icy mantles and 10$^6$ yr coagulation history.
+The dust opacities were adopted from \citet{Ossenkopf1994} and refer to dust grains with thick icy mantles and a 10$^6$ yr coagulation history.
 Although dust grains within the protoplanetary disc are expected to coagulate further,  significantly affecting the opacity, we did not take grain growth into account in our model.
@@
 Chemical abundances in the disc were taken from I2011, who followed gas-grain chemical processes during the dynamical evolution of the disc.
+{\bf Photochemistry is not taken into account, based on the assumption that in the early  (Class 0, early ClassI) stages of protostellar accretion and evolution considered here, the protostar/disc system is heavily embedded in a thick envelope of gas and dust.
+The combination of envelope infall onto the disc and powerful outflows (see e.g.
+\citealt{Machida2013}) may drastically limit the illumination of the upper layers of young discs by the central protostar.
+Observations are needed to shed light on the importance of photochemistry at these early stages.}
+
 As described in I2011, the hydrodynamical simulation included Lagrangian tracer fluid elements in addition to the solution of the equations of hydrodynamics on an Eulerian grid.
@@
 The simple chemistry in the KC2010 model, adopted here as the envelope of the protoplanetary disc, does not provide detailed abundances of molecular species (besides CO and H$_2$O, see also \citealt{Caselli2012}).
-As discussed in the results section \ref{sec:model_results}, abundances have been adopted based on values measured toward similar objects.
+As discussed in the results section \ref{sec:model_results}, abundances in the envelope have been adopted based on values measured toward similar objects.
 The molecular data used here for the radiative transfer are taken from the Leiden Atomic and Molecular DAtabase (LAMDA) (\citealt{Schoier2005} http://home.strw.leidenuniv.nl/$\sim$moldata/).
 \smallskip
-
-{\bf Whilst photochemistry was not included in I2011, it is unclear to what extent the radiation from the protostar will impact upon the disc, given that material infalling from the envelope and newly forming outflows will be obscuring the star.
-Column densities between upper layers of the disc and the protostar in the model used here are on the order of 10$^{23}$ cm$^{-2}$ (is this enough to block the protostars visible and UV?).
-This is in contrast to later stages of disc evolution where the envelope has been almost entirely cleared (e.g.
-Walsh et.
-al), in this case it is clear that the chemistry in the upper layers of the disc will be dominated by photo-chemical processes.}
 
@@
 These points are then smoothed by Lloyd's algorithm \citep{Lloyd1982} in order to minimise the variation in distance between points whilst keeping the same underlying distribution.
-These points are then connected by Delaunay triangulation and it is between the points connected by this method that photon are allowed to propagate (fig.
+These points are then connected by Delaunay triangulation and it is between the points connected by this method that photons are allowed to propagate (fig.
 \ref{grid}).
@@
 \subsection{Grid construction} \label{subsec:gridding}
-In order to construct the grid, candidate points are randomly selected from the volume to be simulated.
-These candidates then have their H$_2$ number density, and the number density of the molecular species being simulated, compared against those of a reference point in order to decide if the candidate point is to be used in the grid or not.
-Candidate grid points are selected at random in a cylindrical coordinates that is linearly spaced in z and $\theta$ and logarithmically spaced in r.
-For each point to be selected, a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) as a threshold.
-After selection of random coordinates, the hydrogen density and molecular density at the candidate point (n and m, respectively) are compared against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$).
+{\bf In order to construct the grid, candidate points are randomly selected from the volume to be simulated.
+These candidate points are associated with values of the H$_2$ number density and the number density of the molecular species being simulated at the position of the point in the underlying model.
+These are then compared against the H$_2$ and molecular density of a reference point in order to decide if they will be included in the grid.
+
+\bf Candidate grid points are selected at random in a cylindrical coordinate system that is linearly spaced in z and $\theta$ and logarithmically spaced in r.
+For each point to be selected, a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) to be used as a threshold.} After selection of random coordinates, the hydrogen density and molecular density at the candidate point (n and m, respectively) are compared against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$).
 If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use.
@@
 We focus on the frequency range available with ALMA, with particular attention to band 7, which offers the best trade off between resolution and sensitivity.
+The results presented in this section are limited to those lines with detectable emission/absorption which can be used to trace either spiral structure or rotation.
 Thus, we consider C$^{17}$O(3$\rightarrow$2), HCO$^+$(3$\rightarrow$2), OCS (26$\rightarrow$25) and H$_2$CO(4$_{04}\rightarrow$3$_{03}$).
 The frequencies and upper level energies of these transitions are given in table \ref{sigmas}.
-The results presented in this section are limited to those lines which show detectable emission/absorption which can be used to trace either spiral structure or rotation.\smallskip
+\smallskip
 
@@
 The integrated intensity and  intensity weighted velocity maps (figs.
-\ref{sim_all}, and \ref{mom0_maps}) were from -12.5 to -0.5$\,$km$\,$s$^{-1}$ and +0.5 to +12.5$\,$km$\,$s$^{-1}$ to avoid domination by the contribution from the envelope, which can be seen in some PV diagrams as the strong absorption feature at all positions around zero velocity (see section \ref{sec:alma_predictions}).
+\ref{sim_all}, and \ref{mom0_maps}) are integrated from -12.5 to -0.5$\,$km$\,$s$^{-1}$ and +0.5 to +12.5$\,$km$\,$s$^{-1}$ to avoid domination by the contribution from the envelope, which can be seen in some PV diagrams as the strong absorption feature at all positions around zero velocity (see section \ref{sec:alma_predictions}).
 Intensity weighted velocity maps are shown with a cut-off of 3$\sigma$ as described in section \ref{sec:alma_predictions}.\smallskip
@@
 \ref{Chemistry}.
-This is because the OCS line, which has the highest upper energy level among the selected transitions, traces only the hottest and densest regions of the disc where the high energy states are populated.
+This is because the OCS line, which has the highest upper energy level among the selected transitions, traces only the hottest and densest regions of the disc, where the high energy states are populated.
 As a result, the innermost spiral structure is best seen in OCS (26$\rightarrow$25), as shown in fig.
 \ref{sim_all}.
-The majority of the OCS line is visible in absorption against the bright continuum emission from the disc mid-plane.
-The exception to this is towards the centre of the disc where the hole in the hot, dense mid-plane means that there is little continuum to be absorbed.
+The OCS line is mostly seen in absorption against the bright continuum emission from the disc mid-plane.
+The exception to this is towards the centre of the disc, where the hole in the hot, dense mid-plane produces little continuum to be absorbed.
 However, this may be an artefact of our treatment of the inner hole, given that we neglect the presence of the protostar and other hot material within the central 2$\,$au.
@@
 \ref{sim_all}).
-As with the OCS line, the majority of the H$_2$CO 4$_{04}$$\rightarrow$3$_{03}$, is seen in absorption against the disc mid-plane continuum, with the central region seen in emission.
+As with the OCS line, the H$_2$CO 4$_{04}$$\rightarrow$3$_{03}$ line is mostly seen in absorption against the disc mid-plane continuum, with the central region seen in emission.
 However, unlike the OCS, the H$_2$CO extends out to large enough radii to trace the voids between the outer spiral arms.
-In these regions, the H$_2$CO line can be seen in emission.\smallskip
+In these regions, H$_2$CO line emission can be seen.\smallskip
 
@@
 \ref{other_inc} shows the C$^{17}$O 3$\rightarrow$2 line in the same physical model but at 15$^\circ$, 30$^\circ$, 45$^\circ$ and 75$^\circ$ to edge on.
-At 15$^\circ$ to edge on we can still see some structure in the integrated intensity map and the structure is also visible in the position velocity diagram.
+At 15$^\circ$ to edge on, some structure in the integrated intensity map is still observable and the spiral pattern is clearly seen in the position velocity diagram.
 At larger inclinations it gets more difficult to obtain any kinematic information but the physical structure of the disc becomes clearer.
@@
 Overlaid on the 1mm continuum emission.
-the integration range for each map is 2.4 km$\,$s$^{-1}$, for the top left the range is from -10.8 to -8.4 km$\,$s$^{-1}$ and for the bottom right the range is from 8.4 to 10.8 km$\,$s$^{-1}$}
+The integration range for each map is 2.4 km$\,$s$^{-1}$, for the top left the range is from -10.8 to -8.4 km$\,$s$^{-1}$ and for the bottom right the range is from 8.4 to 10.8 km$\,$s$^{-1}$.}
  \label{h2co_chanmap}
@@
 Fig.
-\ref{continuum} shows the 1\,mm continuum emission and beam size in the chosen ALMA configuration.
+\ref{continuum} shows the 1\,mm continuum emission as observed with the chosen ALMA configuration.
 The spiral structure of the disc is clearly visible at this inclination and and it becomes clearer at angles closer to face-on.
-A mass estimate for the disc was calculated using the equation $M=g S_\nu d^2/\kappa_\nu B_\nu(T_d)$ where g is the gas/dust mass ratio S$_\nu$ is the integrated flux, d is the distance to the source, $\kappa_\nu$ is the dust opacity and B$_\nu(T_d)$ is the black body function for a given dust temperature \citep{Beltran2006}.
-From this, a disc mass measurement of 0.1$\,$M$_\odot$ was obtained by assuming a dust temperature of 40K, and a measurement of 0.005$\,$M$_\odot$ was obtained by using 400K.
-The flux was integrated from y=0.2 to -0.2 and x=0.4 to -0.4.
-This shows that the disc is not optically thin to millimetre wavelengths.
-This underestimate of the disc mass by at least a factor of 4 shows that in young, massive discs such as those we are investigating, longer wavelength continuum observations are necessary for determining the disc mass.\smallskip
+A mass estimate for the disc was calculated using the equation $M=g S_\nu d^2/\kappa_\nu B_\nu(T_d)$ where $g$ is the gas/dust mass ratio, $S_\nu$ is the integrated flux, $d$ is the distance to the source, $\kappa_\nu$ is the dust opacity and $B_\nu(T_d)$ is the black body function for a given dust temperature \citep{Beltran2006}.
+Using the above equation and integrating the flux from y=0.2 to -0.2 and from x=0.4 to -0.4, we obtain a disc mass of 0.1 and 0.005$\,$M$_\odot$, if the dust temperature is fixed at 40 and 400\,K, respectively.
+This shows that the disc is optically thick to millimetre wavelengths and millimetre observations underestimate the disc mass by at least a factor of 4 (see also \citealt{Forgan2013}).
+In young, massive discs such as those we are investigating, longer wavelength continuum observations are necessary for determining the disc mass.\smallskip
 
@@
 From this it can be seen that the absorption features trace the disc spiral structure whilst the line emission emanates from gaps in the outer disc, where there is less continuum to be absorbed.
-The central panel is dominated by the envelope contribution, causing strong absorption through out the disc.
-The other panels show the line following a rotation profile distorted by the presence of the spiral arms.
+The central panel is dominated by the envelope contribution, causing strong absorption throughout the disc.
+The other panels show the line following a rotation pattern distorted by the presence of the spiral arms.
 \smallskip
@@
 Fig.
-\ref{15deg} shows the C$^{17}$O 3$\rightarrow$2 integrated intensity and PV diagram for an inclination angle of 15$^\circ$ to edge on.
+\ref{15deg} shows the CASA simulation of the C$^{17}$O 3$\rightarrow$2 integrated intensity and PV diagram for an inclination angle of 15$^\circ$ to edge on.
 Spiral structure can be clearly seen in the position velocity diagram even at low inclinations.
@@
 \ref{mom0_maps} for the positions indicated by the corresponding coloured dots along the Y=0 axis.
-As with all the CASA simulated images, these spectra were simulated with an ALMA window with total bandwidth 938$\,$MHz, giving velocity resolutions of between 418 and 527\,m\,s$^{-1}$.
+As with all the CASA simulated images, these spectra were obtained with an ALMA window with total bandwidth 938$\,$MHz, giving velocity resolutions between 418 and 527\,m\,s$^{-1}$.
 Very notably, these spectral features are not symmetric about the disc centre.
@@
 $\bullet$ Our simulations show that molecular features are predominantly seen in absorption against the hot mid-plane of self-gravitating protoplanetary discs, with emission only being seen where voids in the structure of the disc do not provide a bright continuum source to be absorbed.\\
-$\bullet$ The quiescent nature of the envelope around such discs only affect lines within $\pm\,$0.5 km$\,$s$^{-1}$ of the LSR velocity.\\
+$\bullet$ The quiescent nature of the envelope around such discs only affects lines within $\pm\,$0.5 km$\,$s$^{-1}$ of the LSR velocity.\\
 $\bullet$ The lines studied (OCS 26$\rightarrow$25, H$_2$CO 4$_{04}$$\rightarrow$3$_{03}$, C$^{17}$O 3$\rightarrow$2 and HCO$^+$ 3$\rightarrow$2) taken together allow all regions of the disc to be sampled and the rotation of the disc to be constrained from the inner edge to the outer edge.\\
-$\bullet$ Spiral structures in young embedded discs are detectable at a wide range of inclination angles, they can be resolved spatially at angles close to face on and can be inferred from position velocity diagrams at low inclination angles.\smallskip
+$\bullet$ Spiral structures in young embedded discs are detectable at a wide range of inclination angles.
+They can be resolved spatially at angles close to face on and can be inferred from position velocity diagrams at low inclination angles.\\
+{\bf $\bullet$ The dust continuum emission at millimetre wavelengths is optically thick and millimetre observations underestimate the disc mass by significant factors ($>$ 4).\smallskip}
 
@@
 
-{\bf The disc model used does not include magnetic fields, including magnetic fields may suppress GI and spiral wave formation by slowing down or even preventing early disc growth in the case of sufficient magnetisation and alignment between the parent cores rotation axis and magnetic field direction (Joos et al.
-2012, Li et al.
-2013).
-This would mean that if observations similar to the ones we have described are made constraints could be placed on B-field strength within cores/discs.
-\smallskip Futher work to improve these simulated observations would include looking at the effects of material from the envelope falling onto the disc and how this affects the chemistry and line propagation, and including realistic outflows into the model.}
-
 These results demonstrate that ALMA will be able to probe the very earliest stages of circumstellar discs which feed the growing protostar and eventually will evolve in a planetary system.
 Our results show that ALMA observations in band 7 will allow the assessment of whether or not these young discs are gravitationally unstable and test theories of pre-stellar to protostellar core evolution.
-If such gravitational instabilities exist they will have significant implications for the evolution of the disc.
-For example the will affect fragmentation, planetesimal formation \citep{Boley2009,Johnson2013,Gibbons2012} and the chemical evolution in the disc (I2011).
+If such gravitational instabilities exist, they will have significant implications for the evolution of the disc.
+For example, they will affect fragmentation, planetesimal formation \citep{Boley2009,Johnson2013,Gibbons2012} and the chemical evolution in the disc (I2011).
 

### 2013-05-30 young_pp_discs.tex
added PdB files

@@
 \title[Young protoplanetary discs]{Simulated Observations of Young Gravitationally Unstable Protoplanetary Discs}
-%%authors arent splitting over 2 lines so rawlings is pushed off the edge
-%\author[Tom Douglas, Paola Caselli, Et al.]{Tom Douglas$^{1}$\thanks{E-mail:
-%pytd@leeds.ac.uk}, Paola Caselli$^{1}$, Aaron Boley$^{2}$, Richard Durisen$^{3}$, Tom Hartquist$^{1}$, %John Ilee$^{1}$, Jonathon Rawlings$^{4}$ \\
-%$^{1}$School of Physics and Astronomy, University of Leeds, Leeds LS2 9JT, UK \\
-%$^{2}$Department of Astronomy, University of Florida, 211 Bryant Space Center, PO Box 112055, USA\\
-%$^{3}$Department of Astronomy, Indiana University, 727 East 3rd Street, Swain West 319, Bloomington, IN %47405, USA\\
-%%$^{4}$Department of Physics & Astronomy, University College London, London WC1E 6BT, UK\\
-%}
 
@@
 P. Caselli$^{1}$,
-J. D. Ilee$^{5,1}$,
-A. C. Boley$^{2}$,
+J. D. Ilee$^{2,1}$,
+A. C. Boley$^{3}$,
 T. W. Hartquist$^{1}$,
-R. H. Durisen$^{3}$, and
-J. M. C. Rawlings$^{4}$\\
+R. H. Durisen$^{4}$, and
+J. M. C. Rawlings$^{5}$\\
 \vspace{0.1cm}\\
 {\small{\it$^{1}$School of Physics and Astronomy, University of Leeds, Leeds LS2 9JT, UK,}} \\
-{\small{\it$^{2}$Department of Astronomy, University of Florida, 211 Bryant Space Center, PO Box 112055, USA,}}\\
-{\small{\it$^{3}$Department of Astronomy, Indiana University, 727 East 3rd Street, Swain West 319, Bloomington, IN 47405, USA,}}\\
-{\small{\it$^{4}$Department of Physics \& Astronomy, University College London, London WC1E 6BT, UK}}\\
-{\small{\it$^{5}$School of Physics and Astronomy, University of St Andrews, North Haugh, St Andrews, KY16 9SS, UK,}}\\
+{\small{\it$^{2}$School of Physics and Astronomy, University of St Andrews, North Haugh, St Andrews, KY16 9SS, UK,}}\\
+{\small{\it$^{3}$Department of Astronomy, University of Florida, 211 Bryant Space Center, PO Box 112055, USA,}}\\
+{\small{\it$^{4}$Department of Astronomy, Indiana University, 727 East 3rd Street, Swain West 319, Bloomington, IN 47405, USA,}}\\
+{\small{\it$^{5}$Department of Physics \& Astronomy, University College London, London WC1E 6BT, UK}}\\
 }}
-
-%{\parbox{\textwidth}{
-%$^{1}$School of Physics and Astronomy, University of Leeds, Leeds LS2 9JT, UK \\
-%$^{2}$Department of Astronomy, University of Florida, 211 Bryant Space Center, PO Box 112055, USA\\
-%$^{3}$Department of Astronomy, Indiana University, 727 East 3rd Street, Swain West 319, Bloomington, IN %47405, USA\\
-%$^{4}$Department of Physics & Astronomy, University College London, London WC1E 6BT, UK\\
-%}}
 
@@
 
-\date{Mar 2013}
+\date{Accepted May 2013}
 
@@
  \includegraphics[width=84mm]{Figures/model/fig02.eps}
- \caption{Azimuthaly averaged rotational velocity in the disc mid-plane. The best fit curve follows the equation$V_{\rm rot}=\frac{31.5}{\sqrt{R+1.68}}+0.518$ .}
+ \caption{Azimuthally averaged rotational velocity in the disc mid-plane. The best fit curve follows the equation$V_{\rm rot}=\frac{31.5}{\sqrt{R+1.68}}+0.518$ .}
  \label{velocity}
@@
 \ref{rhoT}).
-{\bf The disc model does not include magnetic fields, which may suppress gravitational instability and spiral wave formation by slowing down or even preventing early disc growth in the case of sufficient magnetisation and alignment between the parent cores rotation axis and magnetic field direction \citep{Joos2012,Li2013}.
+The disc model does not include magnetic fields, which may suppress gravitational instability and spiral wave formation by slowing down or even preventing early disc growth in the case of sufficient magnetisation and alignment between the parent cores rotation axis and magnetic field direction \citep{Joos2012,Li2013}.
 Thus, the observation of spiral structure would provide strong constraints on the dynamical state of discs.
-\smallskip }
+\smallskip
 
@@
 Chemical abundances in the disc were taken from I2011, who followed gas-grain chemical processes during the dynamical evolution of the disc.
-{\bf Photochemistry is not taken into account, based on the assumption that in the early  (Class 0, early ClassI) stages of protostellar accretion and evolution considered here, the protostar/disc system is heavily embedded in a thick envelope of gas and dust.
+Photochemistry is not taken into account, based on the assumption that in the early (Class 0, early ClassI) stages of protostellar accretion and evolution considered here, the protostar/disc system is heavily embedded in a thick envelope of gas and dust.
 The combination of envelope infall onto the disc and powerful outflows (see e.g.
 \citealt{Machida2013}) may drastically limit the illumination of the upper layers of young discs by the central protostar.
-Observations are needed to shed light on the importance of photochemistry at these early stages.}
+Observations are needed to shed light on the importance of photochemistry at these early stages.
 
@@
 \subsection{Grid construction} \label{subsec:gridding}
-{\bf In order to construct the grid, candidate points are randomly selected from the volume to be simulated.
+ In order to construct the grid, candidate points are randomly selected from the volume to be simulated.
 These candidate points are associated with values of the H$_2$ number density and the number density of the molecular species being simulated at the position of the point in the underlying model.
@@
 
-\bf Candidate grid points are selected at random in a cylindrical coordinate system that is linearly spaced in z and $\theta$ and logarithmically spaced in r.
-For each point to be selected, a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) to be used as a threshold.} After selection of random coordinates, the hydrogen density and molecular density at the candidate point (n and m, respectively) are compared against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$).
+Candidate grid points are selected at random in a cylindrical coordinate system that is linearly spaced in z and $\theta$ and logarithmically spaced in r.
+For each point to be selected, a random number $\alpha$ is drawn from the semi-open set [0,$\,$1) to be used as a threshold.
+After selection of random coordinates, the hydrogen density and molecular density at the candidate point (n and m, respectively) are compared against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$).
 If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use.
@@
 Using the above equation and integrating the flux from y=0.2 to -0.2 and from x=0.4 to -0.4, we obtain a disc mass of 0.1 and 0.005$\,$M$_\odot$, if the dust temperature is fixed at 40 and 400\,K, respectively.
-This shows that the disc is optically thick to millimetre wavelengths and millimetre observations underestimate the disc mass by at least a factor of 4 (see also \citealt{Forgan2013}).
+This shows that the disc is optically thick to millimetre wavelengths and millimetre observations underestimate the disc mass significantly, by factors of 4 or more (see also \citealt{Forgan2013}).
 In young, massive discs such as those we are investigating, longer wavelength continuum observations are necessary for determining the disc mass.\smallskip
@@
  \caption{Simulated spectra for each of the selected transitions at the positions indicated by the coloured dots in fig.
-\ref{mom0_maps} (the pink, green and cyan curves are taken from the locations marked by the dots of the same colour).
+\ref{mom0_maps} (the pink, green and yellow curves are taken from the locations marked by the dots of the same colour).
 In each diagram, the three spectra are taken from three positions on the Y=0 axis, one is at X=0 (green) and the other 2 are from x=$\pm\,$N (plus yellow, minus pink) where N is the distance from the centre: 10 au for OCS, 20 au for H$_2$CO, 28 au for C$^{17}$O, 38 au for HCO$^+$.}
@@
 They can be resolved spatially at angles close to face on and can be inferred from position velocity diagrams at low inclination angles.\\
-{\bf $\bullet$ The dust continuum emission at millimetre wavelengths is optically thick and millimetre observations underestimate the disc mass by significant factors ($>$ 4).\smallskip}
+ $\bullet$ The dust continuum emission at millimetre wavelengths is optically thick and millimetre observations significantly underestimate the disc mass, by a factor of 4 or more.\smallskip
 
@@
 TAD would like to thank Nichol Cunningham for her assistance with CASA and Christian Brinch for his radiative transfer code LIME and for guidance on using it.
+We also thank the anonymous referee whose comments improved the initial draft of this manuscript.
 
